### 2010-02-20 proposal.tex
Added end-note library, notes in diary, brainstorming for proposal

\title To Identify the characteristics of SSL applications

\brief Encrypted traffic is indistinguishable from noise. At least, the raw data is. When sent over a radio connection at a constant rate the only information one can get is the raw data. However on a network like the internet, the protocols used to transmit encrypted data give away a great deal of information. This paper seeks to answer the question: can we identify information about an encrypted connection by looking at this additional information. Can we identify the software the user is using? How fast can we make a positive identification?

The Internet provides two protocols for commonly used communications:
\list
  \item UDP
  \item TCP

UDP communications involve individual packets with a destination. They are not stateless.

TCP is stateful, it maintains a connection. Most SSL applications operate over TCP, this is for a number of reasons:

\list
  \item Exchanging an encryption key to begin a communication is costly, therefore it is best to keep a connection open for a long period
  \item SSL encryption is sensitive to order, TCP maintains order

For this reason, TCP leaks a lot of information about an SSL stream. This information is:

\list
  \item Individual packet size
  \item Individual packet flags
  \item Period between last packet

Additionally, the way a program is can influence many of these values above. If packets are written to buffers properly, if there is serious computation between certain operations etc. This can
be present in the shape of the traffic, allowing us to fingerprint certain applications.

Ways of identifying applications:
  Bytes in recognizeable chunks (multiples of 512?)
  Large burst of traffic at traffic initiation
  Length of sessions (all a certain time like say 10 mins?)
  Source port
  Keepalives?
  Nagle algorithm
  Window size

  \section

  Because projects such as ToR and Freenet lack the critical mass / exposure to normal use, it is easy to justify blocking them alltogether in the name of national security, that they are only used by paedophiles and criminals etc. For this reason it is beneficial to make them indistinguishable from normal ssl applications so they cannot be blocked automatically.

### 2010-02-27 downloaded/econp2p03.tex
Renamed papers dir to downloaded - since that's what these files are

\documentclass[times,10pt,twocolumn]{article}
\usepackage{latex8}
\usepackage{url}
\usepackage{graphics}
\usepackage{amsmath}

\newcommand{\workingnote}[1]{}        % The version that hides the note.
%\newcommand{\workingnote}[1]{(**#1)}   % The version that makes the note visible.

\renewcommand\url{\begingroup \def\UrlLeft{<}\def\UrlRight{>}\urlstyle{tt}\Url}
\newcommand\emailaddr{\begingroup \def\UrlLeft{<}\def\UrlRight{>}\urlstyle{tt}\Url}

% If an URL ends up with '%'s in it, that's because the line *in the .bib/.tex
% file* is too long, so break it there (it doesn't matter if the next line is
% indented with spaces). -DH

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%   \pdffalse
%\else
%   \pdfoutput=1
%   \pdftrue
%\fi

\begin{document}

\title{Reputation in P2P Anonymity Systems}

\author{Roger Dingledine \\ The Free Haven Project \\ arma@freehaven.net \and
Nick Mathewson \\ The Free Haven Project \\ nickm@freehaven.net \and
Paul Syverson \\ Naval Research Lab \\ syverson@itd.nrl.navy.mil}

\maketitle
%\thispagestyle{empty}

\begin{abstract}

Decentralized anonymity systems tend to be unreliable, because users
must choose nodes in the network without knowing the entire state
of the network. Reputation systems promise to improve reliability by
predicting network state. In this paper we focus on anonymous remailers
and anonymous publishing, explain why the systems can benefit from
reputation, and describe our experiences designing reputation systems
for them while still ensuring anonymity. We find that in each example we
first must redesign the underlying anonymity system to support verifiable
transactions.

\end{abstract}

\section{Introduction}

In decentralized networks, many traditional means of ensuring
accountability between participants become unworkable.  As the
combined resources of individual participants outgrow those of a
(possibly nonexistent) central authority, top-down enforcement of good
behavior becomes unwieldy.  As the number of participants grows,
repeated interactions between participants can become
infrequent, and so individuals cannot rely on their own past
experience to recognize those who behave badly.  Under these
circumstances, reputation is one of few workable mechanisms to keep hostile
and freeloading nodes from damaging the system.

But when the network's very purpose is to provide anonymity, reputation
itself becomes problematic. Firstly, location protection enables an
attacker or freeloader to cheaply throw away a pseudonym that has acquired
a bad reputation. Secondly, it is hard to detect or verify a participant's
behavior while at the same time maintaining
his anonymity. And thirdly, reputation information can be exploited by
an adversary to reduce a participant's anonymity.

So we are left with a conundrum: if the network's stability relies
on the good behavior of individual nodes, reputation may be the
only way to achieve it.  But reputation data is hard to gather in
the presence of anonymity, and even when gathered, poses a potential
vulnerability for an attacker to exploit.

As with security, it is tempting but incorrect to think that
reputation is a simple matter of bolting an extra service to the side
of an existing system.  In the rest of this paper, we illustrate this
point with examples from reputation systems that have been designed
for use in networks that provide pseudonymity and anonymity.  First,
however, we outline the incentive structures involved in deploying
such networks.

\section{An Economics of Anonymity}

Unlike confidentiality (encryption), anonymity cannot be created by the
sender or receiver. Alice cannot decide by herself to send anonymous
messages --- she must trust the infrastructure to provide protection, and
others must use the same infrastructure. Anonymity systems use messages
to hide messages: senders are consumers of anonymity and also providers
of the cover traffic that creates anonymity for others. Thus users are
always better off on crowded systems because of the noise other users provide.

Because high traffic is necessary for strong anonymity, agents must
balance their incentives and find a common equilibrium, rather than
each using a system of their own.
The high traffic they create together
also enables better performance: a system that processes only light
traffic must delay messages to achieve adequately large anonymity sets.
But systems that process the most traffic do not necessarily provide the
best hiding: if trust is not well distributed, a high volume system is
vulnerable to insiders and attackers who target the trust bottlenecks.

Anonymity systems face a surprisingly wide variety of direct
anonymity-breaking attacks \cite{back01,raymond00}. Additionally,
adversaries can also attack the efficiency or reliability of nodes, or
try to increase the cost of running nodes. All of these factors combine
to threaten the \emph{anonymity} of the system.  As Back et al.\ point
out, ``in anonymity systems usability, efficiency, reliability and cost
become \emph{security} objectives because they affect the size of the
user base which in turn affects the degree of anonymity it is possible
to achieve.'' \cite{back01}

Early work on the economics of anonymity \cite{econymics} has focused on
the incentives for participants to act as senders and nodes, providing
three results: Firstly, systems must attract cover traffic (many
low-sensitivity users) before they can attract the high-sensitivity
users. Weak security parameters (e.g. smaller batches or lower latency) may produce
\emph{stronger} anonymity by bringing more users. But to attract this
cover traffic, they may well have to address the fact that most users do
not want (or do not realize they want) anonymity protection. Secondly,
high-sensitivity agents have incentive to run nodes, so they can be
certain their first hop is honest. There can be an optimal level of
free-riding: in some conditions these agents will opt to accept the cost
of offering service to others in order to gain cover traffic. Thirdly,
while there are economic reasons for distributed trust, the deployment of
a completely decentralized system might involve coordination costs which
make it unfeasible. A central coordination authority to redistribute
payments may be more practical, but could provide a trust bottleneck
for an adversary to exploit.

The reputation systems we discuss below would enable users 
to direct their traffic to reliable nodes --- thus giving
high-sensitivity agents incentive to provide {\it reliable} service, and making
the network as a whole more reliable.  Below, we examine several
designs for reputation systems for anonymity networks.

\section{An Example: Remailer Networks}

Remailer networks allow people to send and receive mail while protecting
their identities. Today's remailer networks use a handful of long-lived,
static servers with fairly uniform reliability. Currently deployed
reputation systems \cite{echolot} send periodic test messages through
each remailer to determine which are currently working. This ``pinging''
approach works well enough for a small static list of servers. However,
a network that is made of a small static set of remailers is potentially
vulnerable to a well-funded adversary in a variety of ways, e.g.,
denial of service or remailer compromise. %Any solution based only on
%hardening the nodes runs contrary to the basic premise of remailers
%that trust is distributed rather than mutually assured.
Thus, to better
resist a well-funded adversary, the remailer network must grow so it has
enough nodes to properly distribute trust. Pinging for reputation breaks
down in an environment where the network is made up of many transient
volunteer nodes. On the other hand, an adversary might render a growing,
dynamic network useless by volunteering a flood of unreliable remailers,
or it might manipulate the reputation system to improve the standing of
remailers it owns.

The reputation system presented in \cite{mix-acc} aims to improve
remailer reliability. Remailer reputation is based on both positive and
negative performance. If it were based only on successes, an adversary
could pump up his reputation by sending his own messages through the
node while ignoring other messages. On the other hand, recording only
failures is also insufficient, because new unreliable remailers would be
rated the same or better than remailers that consistently perform well
\cite{cheap-pseudonyms}. In this design, each remailer in the message's
path passes back a receipt to the one behind it. Senders can successively
query for receipts to determine which remailer to blame for delivery
failure. However, a remailer might refuse to provide a receipt for a
particular message either because it didn't try to send the message, or
because it tried but was unable to obtain a receipt from the next hop. We
solve the problem of pinpointing failures by introducing a set of weakly
trusted global witnesses. These witnesses are contacted when the next
hop in the path refuses the message, allowing a remailer to prove that it
made a best-effort delivery attempt. Senders can also tell witnesses about
remailers that silently dropped messages (meaning they got a copy but did
not attempt to pass it on). These witnesses verify and tally failures, and
also send their own test messages to distinguish reliable remailers from
new ones that have not yet been tested. Reputations are %tabulated and
made available to client software, which can use them to choose reliable
remailers for sending anonymous mail.

This reputation system attempts to improve reliability in a long-term
sense, rather than giving provable delivery guarantees for each
message \cite{shuffle}.
On the other hand, it still relies both on proofs of correct behavior
to establish reputations, and trusted witnesses to determine and
keep track of them. These witnesses are both a trust bottleneck and a
communications bottleneck. Further, an anonymity-breaking adversary with
an adequate budget would do best to provide very good service, possibly
also attempting DoS against other high-quality providers. The
usual performance and efficiency metrics cannot distinguish the bad guys.

The reputation system in \cite{casc-rep} does
away with trusted witnesses and proofs in favor of self-rating groups
of remailers. Remailers are arranged in cascades (fixed paths through the
network, so batches of messages go through in synchrony).
New cascades are formed at a regular interval (e.g. daily),
and the formation of cascades is based on a communally generated
random value so that no set of collaborating remailers can predict which
remailer will be in which cascade, as long as at least one remailer is
honest. Remailers send test messages through their own cascades and
can also receive evidence of failure from client senders. Rather than
depending on proofs of remailer performance, a cascade fails when and
only when some member of that cascade has declared it to have failed. All
members of cascades that do not fail during an interval increase in
reputation; all members of cascades that fail decrease. To make it
harder for the head remailer of a cascade to undetectably fail or fail
selectively, each of the cascade members is responsible for a portion of
the messages that go through a cascade in each batch. In effect, each
member is the head for some of the messages. Similarly, the tail of
the cascade sends each outgoing message to each of the other cascade
members rather than just directly to the recipient. All then attempt to
deliver the message to the recipient. (Efficiency of communication for
final delivery can be improved by using delivery receipts when that is feasible.)

In both of these remailer reputation systems, it was necessary to redesign the
remailer protocol so we could track remailer behavior. In the first
case, we added receipts for each delivery to each remailer and to
the ultimate destination, and we added trusted witnesses to verify
delivery and record success or failure. In the second case, we used
the usual remailer cascade protocol for messages inside the cascade,
but we introduced a new protocol for sending messages into the cascade
and delivering messages from the cascade.

\section{An Example: Anonymous Publishing}

Free Haven \cite{freehaven-berk} describes a design for a publishing
system that can resist the attempts of powerful adversaries to find or
destroy any stored data. It provides anonymity for readers and publishers,
and also hides the locations of the servers that store and serve the
documents. Unlike related designs such as Freenet \cite{freenet},
the publisher of a document --- not the servers holding the document
--- determines its lifetime. To counter malicious or flaky servers,
publishers break documents up into shares, any adequately sized subset of
which is sufficient to reconstruct the document. Servers then trade these
shares around, allowing for servers to join and leave smoothly and also
providing a moving target for an adversary hunting a particular share.

To prevent selfish or malicious users from filling up the available disk
space, all who would publish must also provide servers, and servers form
contracts to store each other's material for a certain period of time.
Because servers can cheat and drop data early, Free Haven employs a
reputation system to limit the damage done by servers that misbehave.
Successfully fulfilling a contract increases a server's reputation and
thus its ability to store some of its own data on other servers. This
gives an incentive for each server to behave well --- that is, as long
as cheating servers can be identified.

In such a dynamic and anonymous environment, it is very difficult to
reliably notice if a server drops data early. We might give the original
publisher the task of monitoring the availability of his documents; he can
then broadcast a claim that a particular document has been dropped early.
If we don't want to rely on the original publisher, we can assign a
random server as a ``shepherd'' for a document. Or for a more dynamic
solution, we can use a ``buddy system'', where publishers put in two
copies of each share, and the copies watch each other and broadcast a
complaint if either disappears.

Anyone wishing to claim misbehavior can present a signed contract as
an indication the file should have been kept, but there are a number
of special cases where a signed contract is not sufficient proof to
pinpoint a particular server as the culprit, such as if the server traded
the share away before the contract expired. Because a claim cannot be
taken as absolute proof, servers are left with the grim task of trying
to determine the credibility of the claimer: if two or more servers
disagree, onlookers need a way to determine which to believe. Keeping
track of all claims ever made and tracking their results might give a
server enough information to make reasonable guesses about the validity
of each claim. This approach gets complex very quickly, and leaves lots
of holes for a smart adversary.

Providing a way to verify claims in Free Haven remains an open problem.
Given our experience designing the remailer reputation systems above,
it seems most promising to redesign the entire system from the ground up,
this time with verifiable claims in mind. Designing the original system
without a clear idea of the reputation and verifiability requirements made Free Haven's
design complex and brittle.

It's tempting to scale down the reputation system instead. That is,
servers use only local information from their own transactions and
trades. In this scenario, a new server must separately convince each
server it encounters that it is reputable before that server will
allow it to publish any data. Because news about good and bad behavior
does not propagate, servers must be more conservative about offering
resources to unfamiliar nodes. To prevent stabilization into a static
network with a small number of nodes trading data among each other and
ignoring newcomers, many servers must explicitly risk resources on new
nodes. Rather than the global gossip system where the whole world learns
from a server's first interaction, now each new server has a chance to
waste the time and resources of every other server (the ``screw everyone
once'' attack).

Perhaps the most interesting point of Free Haven reputations is that
servers use their reputation capital to obtain proportional resources
from other servers. In order to build up to a reputation that allows
a server to store a certain amount in the system (think of it like a
credit limit), the server must previously have successfully stored that
same size of other documents. Each server is able to commit at most his
current credit limit in new contracts, and successfully completing a
contract raises his credit limit. Because a server can cheat on at most
the amount of useful work he has already done, each server is forced to
perform at least 50\% useful work. We will say more about this notion of
``spending'' reputation and quantifying risk below.

\section{Reputation and Anonymity}

Although the examples described above associate non-transferable
reputation with long-lived pseudonyms (nyms for short), there are many
ways to vary this formula. Entities may be anonymous or have only
short-lived names; reputations may be short-lived or transferable;
and bindings between nyms, entities, and reputations may be varied.
We have already noted that in Free Haven, a server can both acquire and
spend reputation. A central register or registers can keep track of each
server's current reputation credit level, or each server can maintain its
own view of the system. It is a small step from here to consider systems
in which reputation can be paid in the form of coins or tokens. With such
a system, the same entity can maintain reputation even while changing
nyms. An entity that holds different nyms in different
contexts can benefit from this feature -- either to preserve reputation
independent of private key compromise, or to maintain perfect forward
anonymity (future compromises linking a nym to an entity will not reveal
previous transactions by the entity bearing that nym, even if all past
behavior under all nyms is logged \cite{unlinkable-serial-transactions}).

Along with the advantages of fungible reputation come some potential
problems. For example, an entity can obtain reputation in one context
where it has functioned well and spend it in another context where
it has not. Or the entity can transfer reputation to another entity
entirely. This capability might be controlled by using cryptographic
techniques that, e.g., bind all the reputation to the same nym or the
same entity without revealing which nym (or entity) that is. But there
are other concerns for this approach. For example, how do you diminish
reputations for bad performance in such a model? (If it is possible
to bind reputation tokens to an entity in an anonymity preserving way,
it may also be possible to bind them to a duration so that the amount of
reputation can be evaluated with respect to the time that the reputation
bearer has existed. Thus we can distinguish longstanding, low-performing
entities from untested ones.)

On the other hand, in some contexts transferable reputation may not be a
problem. For example, in a system like Free Haven that ``pays'' you for
good performance with system services from others, as long as the amount
of service credit taken from the system is no more than the amount of
service provided to it, does it matter if that credit is transferred
to others?

\section{Conclusion: New Directions, Misdirections, and Other Questions}

Reputation systems are already gathering momentum at the grassroots of the
Internet. Special-purpose systems --- some more {\it ad hoc} than others --- have
already been rolled into online auction services, messaging protocols, and
online discussion sites. But despite this growing body of experience at
building simple reputation systems and designing more complex ones for
anonymity systems, the questions remain as intriguing as the solutions.

How can we fine-tune a reputation system in response to a specific threat
model? In a relatively low-threat environment (e.g., tracking ISP uptime),
ordinary statistical models will suffice. But most statistical models
assume that data is biased at worst, not maliciously chosen by an adversary
who wants us to make a particular decision. At this point, the emphasis in
current research shifts from predicting behavior to minimizing risk. Is it
really necessary to abandon statistical rigor? The field of machine
learning has a rich history and a lot of experience at solving related
problems. Is there some way to adapt these solutions to an adversarial
context?

Similarly, what can we do when statements aren't verifiable, and where an
adversary can either lie about real interactions, or fabricate spurious
interactions and lie about those?  We could try to make credibility charts
and weight statements by credibility --- but a smart adversary could try to
trick our credibility calculations as well. If somebody finds a way to
establish bounds on malicious influence on such a system, the range of
problems we can solve with reputation would explode overnight.

We have already seen how reputation can enhance privacy. Can we go one step
further, and assign reputation based on an expectation of protecting
privacy? In distributed privacy systems, the privacy provided is typically
based on an assumption that some subset of system components will both
perform duties correctly {\it and} will not reveal some parts of their data
and/or operations. A privacy destroying adversary might offer very reliable
service while using information from various compromised system elements to
compromise privacy. Can we say anything meaningful about reputations based
on reliability at keeping secrets, or are we limited to making statements
about the probability of privacy compromise given the likelihood and
structure of component compromise?

What if we treat reputation as currency? Currency implies economics. How do
you get reputation currency? Do currency-based approaches always imply
transitive trust? Is the supply of reputation currency constant,
increasing, or decreasing? Does it expire, or slowly lose value over time?
Where, ultimately, does a currency come from --- a decentralized Federal
Reserve? Does it materialize as a side-effect of performing work from the
system? Is there credit? Or does currency only appear when the system is
bootstrapped, and if so, how? Is currency global, or do individual servers
mint their own currencies? Can we evolve a viable market that is scalable
based on these local currencies issued by individual servers? Can a global
currency be bootstrapped from local currencies?

The number and diversity of real-world reputation systems is staggering.
Through a byzantine mass of credit reports, product reviews, earnings
statements, flat-out gossip, and a thousand other information channels, we
try to convince one another of our honesty and competence. In the process
we expose far more detail about ourselves than we might wish. Online
reputation systems promise to be still more complex and difficult to build
than their real-world analogues, but they hold out the promise of enabling
decentralized interaction and protecting privacy in ways that today's
systems of trust cannot.

\bibliographystyle{latex8}
\bibliography{econp2p03}

\end{document}

### 2010-02-27 thesis/thesis.tex
Work for weekend, new papers, diary entry, beginning of literature review in proposal, cleanups

\abstract The Internet is a powerful tool for publishing speech and opinion, for this reason it has significant implications for policial speech. Unfortunately this ability to speak out is being destroyed by an increasingly hungry powerful elite who attempt to stomp out political assent by any means necessary. Dissenters who publish their opinions using the internet are increasingly being identified and subject to imprisonment. Tools are available to hide provide levels of anonymity to such users, but these tools really provide anonymity? Can they provide anonymity in such regimes if they are easily distinguishable from normal traffic? This paper seeks to investigate the qualities of encrypted communications on the Internet and compare normal encrypted communications to those performed by anonymizing tools such as TOR and I2P. A number of simulations will be run with these applications and the traffic monitored to gather important information and characteristics. These will be compared to identify what characteristics make a particular application identifiable and what qualities are used for this identity. The aim of this research is to provide insight into what qualities other than data make an application uniquely identifiable, despite using strong encryption.

### 2010-04-24 extract.rb
Won't need this anymore as using latex

@@ -1,53 +1,0 @@
-#!/usr/bin/ruby
-
-class ReferenceExtractor
-  def self.extract(filename)
-    references = {}
-    File.open(filename) do |file|
-      grab = Proc.new do |no, line, matcher|
-        while match = line.match(matcher)
-          line.slice!(matcher)
-          ref = {:year => match[2], :author => match[1]}
-          references[ref] = match[0]
-          STDERR.puts "#{no}: #{ref[:year]}, #{ref[:author]}"
-        end
-      end
-
-      file.each do |line|
-        # In the form of Erzats et al., (2004)
-        grab.call 1, line, /([A-Z][^\s]+?\s+et\s+al.),?\s*\(([12][0-9]{3}[A-Za-z]*)\)/
-
-        # In the form of Dougan and Howard (2004)
-        grab.call 2, line, /([A-Z][^\s()]+?\s+and\s+[A-Z][^\s()]+?)\s*\(([12][0-9]{3}[A-Za-z]*)\)/
-
-        # In the form of (Zekis, 2009)
-        grab.call 3, line, /\(([^(,]+?),\s*([12][0-9]{3}[A-Za-z]*)\)/
-
-        # In the form of Danezis (1999)
-        grab.call 4, line, /([A-Z][^\s()]+?),?\s*\(([12][0-9]{3}[a-z]*)\)/i
-      end
-    end
-    puts "# Found #{references.size} references"
-    puts "# listing alphabetically..."
-    references.to_a.sort do |a,b|
-      a[0][:year] <=> b[0][:year] &&
-      a[0][:author] <=> b[0][:author]
-    end.each do |reference|
-      puts "#{reference[0][:year]}, #{reference[0][:author]}"
-    end
-  end
-end
-
-if ARGV.size != 1 || ARGV[0].match(/(-h|--help|\/?)/i) || !File.exists?(ARGV[0])
-  puts <<-eol
-Usage: #{$0} <filename>
-Options:
-  -h --help   Print this usage message
-
-Extracts all percieved in text references from a text file and prints them to
-stdout, sorted alphabetically
-  eol
-  exit
-end
-
-ReferenceExtractor.extract(ARGV[0])

### 2010-04-24 conference-paper/proposal.tex
Start of conference paper

\documentclass{ecuthesis}

% Packages
\usepackage{graphicx}

% Setup the variables for the title page
\title{Using traffic analysis to identify anonymous networks}
\author{John Barker}
\department{School of Computer and Security Science}
\school{Edith Cowan University}
\degree{Computer Science (Honours)}
\email{jebarker@our.ecu.edu.au}
\studentid{0991300}
\supervisor{Dr Christopher Bolan}
\supervisor{Mr Peter Hannay}
\supervisor{Mr Patryk Szewczyk}

% Begin document
\begin{document}
\maketitle

\begin{abstract}

Traditional attacks against anonymous systems aim to uncover the identities of those involved. However, a more likely goal of attackers is to block or degrade the network itself, discouraging participation and forcing vulnerable users to communicate using less secure means. Since anonymous networks operate on known protocols and employ strong encryption it is difficult to distinguish them from regular traffic. This proposal describes a method for identifying traffic belonging to anonymous networks by examining their communication patterns.

\end{abstract}

\chapter{Introduction}

\section{Background}

The Internet has revolutionised the political sphere in providing a platform for the publication of speech to a far greater audience than was ever available before digital communications systems \citep{Bonchek:1997p3455}. The publication of less desirable political speech, criticism or challenging ideas still carries with it great risk, with numerous publications leading to arrest. This has spawned headlines such as \emph{Egypt arrests another blog critic} \citeyear{website:egypt-arrests}, \emph{Chinese couple sue Yahoo! in US over torture case} \citep{website:china-yahoo-torture}, \emph{Vietnam bloggers arrested over China shirt protest} \citep{website:vietnam-bloggers-arrested}, \emph{23 Journalists/Bloggers Arrested in Iran, Including Head of Top Group} \citeyear{website:iran-bloggers-arrested} and \emph{Blogger Arrests} \citep{website:blogger-arrests}. The Internet, like conventional media is still vulnerable to censorship by oppressive governments and malicious attackers \citep{Crandall:2007p6165,Karlin:2009p6166}.

In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity. Recent examples of such software include Freenet \citep{Clarke:2001p2435} and The Second Generation Onion Router (Tor). Tor is an anonymous network which uses various techniques to provide low latency anonymity to network participants \citep{Dingledine:2004p314}. It also aims to provide resistance against censorship based blocking attempts \citep{Dingledine:2008p1542}.

Although such networks provide avenues for users to avoid censorship and a certain amount of privacy, it may be possible to use traffic analysis techniques to automatically these communications and distinguish them from regular traffic. This paper proposes a quasi-experimental methodology for identifying Tor traffic which may be used by censors in the future.

\section{Significance}

Traffic analysis is a well established field, and there are a significant number of known papers that propose traffic analysis attacks against modern communications networks \citep{Zhang:2009p1188}. When considering anonymous and censorship resistant networks, typical traffic analysis attacks focus on techniques and attacks designed to uncover the identities of participants. As stated in \citet{Murdoch:2005p325} “The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa”.

Tor’s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \citep{website:tor-anonymity-online}.

The traffic analysis techniques proposed in this paper will attempt to classify network streams belonging to Tor users and distinguish them from regular encrypted communications.

\section{Research Questions}

Given a motivated and universal attacker, it is inexpensive and straightforward to disconnect a user from these networks by blocking access to well known and published resources. Once these avenues of attack have been exhausted it is still possible to connect to the network by connecting to lesser known access points. Since these networks are capable of communicating using many of the same methods as most conventional Internet applications, a blanket ban on this kind of communication would be too broad and extensive.

Tor employs strong encryption the goal of which is to ensure that the data transmitted is indistinguishable from random noise. To an observer, data transmitted using encryption looks the same. Thus the traditional means of identifying these protocols are ineffective.

This raises the question: is it possible to distinguish the traffic created by these networks, from encrypted traffic produced by conventional software? This question can be broken down further:

\begin{enumerate*}
\item Can the traffic be classified using automated matching techniques?
\item Do these networks have characteristics that make them readily distinguishable using heuristics based matching?
\item Do they have characteristics that make them distinguishable using a machine learning technique?
\item How long does a user have to be connected to the network before a confident match can be made?
\end{enumerate*}

\chapter{Literature Review}

The main areas of research included papers and proposals on the design of anonymity networks and those covering the subject of traffic analysis. Particular attention has been paid to encryption as it is the primary function by which these systems operate and a good understanding is necessary for the development of an appropriate traffic analysis method.

\section{Encryption}

Since the inception of language, hostile forces and their attempts to intercept messages have necessitated the development of secretive communications. This deliberate transformation of a messages so that only the intended recipient can understand it is known as encryption. The process of examining these obfuscated messages and attempting to reverse the transformation is known as cryptanalysis \citep{Schneier:1995p3908}. These fields have been locked in an arms race ever since, each side continually advancing their capabilities in an attempt to gain ground.

Apart from One Time Pads, no encryption methodology has ever proven to be unbreakable \citep{Shannon:2001p6583}. This means that all remaining cryptographic methods are a way of transforming information, so that for an attacker the difficulty in reversing this transformation is too costly to make it worthwhile. The invention of robots and computers was precipitated by the need to break encryption methods of increasing complexity and at the same time has lead to the increasing complexity of encryption algorithms \citep{Kahn:1967p1005}.

In \citeyear{Jevons:1874p1167}, \citeauthor{Jevons:1874p1167} perhaps unknowingly, uncovered the basis of public key cryptography in his publication \emph{The Principles of Science: A Treatise on Logic and Scientific Method}. He recognised that certain mathematical operations yielded products that were impossible or difficult to reverse in order to uncover the factors used.

The possibility of public key cryptography, described as ‘non-secret encryption’ was conceived by James H. Ellis in \citeyearpar{Ellis:1970p3249} and later developed into both a method for sharing secret encryption keys by Malcolm J. Williamson in 1974 \citep{Singh:1999p3277} and a method for asymmetric encryption \citep{Cocks:1973p3265}.

These papers were not published at the time due to being classified information, allowing these methods to be reinvented independently \citep{Singh:1999p3277}. The method for key sharing developed by Ellis later became known as the Diffie-Hellman key exchange \cite{Diffie:1976p585}, while the method for asymmetric encryption is now known as RSA encryption, taking its name from the initials of its creators Rivest, Shamir and Adleman \citet*{Rivest:1978p708}. Figure \ref{key-exchange} shows how discrete logarithms are used in the Diffie-Hellman algorithm to generate a shared encryption key.

\begin{figure}[H]
\center \includegraphics[width=\linewidth]{key-exchange}
\caption{Diffie-Hellman Key Exchange}
\label{key-exchange}
\end{figure}

Public key cryptography has seen a number of advancements based on these early discoveries, with the development of an asymmetric key encryption method based on Diffie-Hellman named after its creator \citet*{ElGamal:1985p529}. Various mathematical problems have been used in the development of newer crypto systems, with increasing complexity such as the use of  elliptic curve cryptography in \cite{Miller:1986p2966} and \cite{Koblitz:1987p3109}, probabilistic functions in \cite{Paillier:1999p3152} and to address weaknesses in \cite{Cramer:1998p3186}.

Public key cryptography is the foundation of Internet based cryptography and anonymous networks. Conventional methods of sharing secret keys by courier or post are costly and negate the benefits provided by a digital network. Although \cite{Baran:1964p384} proposed encryption for usage in digital communications, citing benefits such as tamper resistance, message secrecy and resistance to traffic analysis. This system was never implemented.

Early work in encrypted Internet communications includes the Secure Network Programming (SNP) applications programming interface (API) \citep{Woo:1994p2532}. This was simply a framework providing numerous encryption, signing and authentication methods. The Secure Sockets Layer (SSL) is an encryption layer which provided end to end communications secrecy on the Internet \citep{website:SSL}. It makes use of public key cryptography to ensure secrecy.

This proposed standard went through a number of revisions, with early versions suffering security flaws \citep{Wagner:1996p385}. SSL is now known as Transport Layer Security, with the latest version 1.2 being released August 2008 \citep{website:TLS}. TLS addresses some issues in SSL and provides a number of enhancements, but is not compatible.

The Hypertext Transfer Protocol Secure (HTTPS) makes use of both SSL and TLS and the Hypertext Transfer Protocol (HTTP) to provide encryption and secure identification when visiting websites \citep{website:HTTPS}. This is also the protocol used by Tor.

\section{Anonymous and Censorship Resistant Networks}

The first anonymous network system was proposed in \cite{Chaum:1981p296}. This proposal included the use of public key cryptography and a centrally located server known as a ‘mix’. By wrapping the information and address of a destination in a message and encrypting it with the mix’s public key, only the mix system is able to read the message.

\begin{figure}[H]
\center \includegraphics[width=\linewidth]{chaums-mix-network}
\caption{Chaum's Mix Network}
\label{chaums-mix-network}
\end{figure}

The mix system then delivers the message to its destination without passing any information on about the sender. Because the destination system only communicates with the mix server, it has no information available about the sender in which to make a positive identification.

Since this proposal, many networks have been developed that provide features such as anonymity and censorship resistance. The proposed systems differ with regard to the motivation behind providing anonymity. Like cryptography, an arms race between anonymous network designers and those discovering attacks has motivated development of iterative refinements in response to weaknesses.

Many early systems were designed to provide anonymous email delivery, these include Babel \citep{Gulcu:1996p1662}, Mixminion \citep{Danezis:2003p1616} as well as Nym servers \citep{Mazieres:1998p4560} and two commercial offerings Underhill and NymBaron. One of the earliest anonymous remailers anon.penet.fi was created by Johan Helsingius in 1993, but was shutdown in 1996 due to a combination of legal pressure and an inability to provide true anonymity \cite{Danezis:2008p346}.

The need for anonymous networks to resist attack and node failure led to the development of various robust mix networks such as \citep{Waidner:1989p5870}, \citep{Park:1994p5051}, (Kilian  Sako, 1995), \citep{Ogata:1997p5083}, \citep{Abe:1998p1898}, \citep{Jakobsson:1998p5137} and (Desmedt and Kurosawa, 2000).  An avenue of research in robust mix networks is universal re-encryption described in \citep{Fairbrother:2005p5357}, \citep{Lu:2005p5387}, (Lu et al., 2006) and \citep{Gomukiewicz:2004p294}.

The problem of mathematically provable anonymity is a difficult one, and many proposals have been developed \citep{Chaum:1988p5869}, \citep{Rackoff:1993p5817}, \citep{Kesdogan:1998p2027}, \citep{Jakobsson:1999p2008} \cite{Neff:2001p2068}, \cite{Furukawa:2001p5158}, \citep{Golle:2004p5204}, \citep{Gomukiewicz:2003p5816}, \citep{Berman:2004p303}, \citep{Golle:2004p5204}, \citep{Adida:2007p5205}, \citep{Klonowski:2005p5379}, \citep{Nguyen:2008p3837}. In practice however, strong provable anonymity incurs a great deal of performance overhead and has not seen wide usage \citep{Danezis:2008p346}.

Attempts to make provable anonymity more attractive by increasing performance includes Flash mixing, a scheme for more efficient anonymity using mixes \citep{Jakobsson:1999p2008}.

Stop and Go Mixes which provide probabilistic anonymity and don’t require a confirmed identity to participate \citep{Kesdogan:1998p2027}.

Discouraging network operators from divulging known identities is a feature of intentionally fragile mix networks such as \citep{Reiter:2004p5868} and (Golle et al., 2006). These networks are designed to make the process of tracing a single message damaging to the system or its property of anonymity, making compulsion potentially expensive.

\cite{Jakobsson:2002p5815} \cite{Goel:2003p5871}

The practice of steganography allows for the hiding of messages within existing mechanisms, which provides some measure of anonymity and censorship resistance by making messages undetectable to observers. Steganography has been proposed as a way of providing censorship resistance in (Feamster et al., 2002), (Feamster et al., 2003). The use of covering traffic and rerouting of messages to complicate traffic analysis is discovered in \citep{Venkatraman:1995p6008}, (Timmerman, 1997), (Timmerman, 1999), (Guan et al., 2001) and (Newman et al., 2003).

Most anonymous and censorship resistant networks provide means for using well established Internet protocols in an anonymous manner, some however have provided standalone means of publishing information anonymously. These include Freedom (Boucher et al., 2000) and Freenet (Clarke et al., 2001) which provides a network for publishing with anonymity for both authors and readers by collectively sharing storage.

The success of peer to peer (p2p) systems such as Bittorrent and Kazaa has inspired the development of p2p anonymous networks such as MorphMix \citep{Rennhard:2002p4559}, Tarzan (Freedman, 2002) and P5 (Sherwood et al., 2005).

Private Information Retrieval:

(Kissner et al., 2004) (Sassaman et al., 2005) (Danezis and Diaz, 2006) (Ostrovsky and Keith, 2007) (Bethencourt et al., 2009)

Some anonymous networks have been developed with the explicit goal of censorship resistance, these include aChord (Hazel and Wiley, 2002), gnuNet (Hazel and Wiley, 2002), (Anderson, 1996), (Serjantov, 2002) and (Clayton et al., 2006)

\subsection{The Second Generation Onion Router(Tor)}

Tor was first described in Tor: The Second-Generation Onion Router (Dingledine et al., 2004). This new generation of onion router was designed with a number of defences for common traffic analysis attacks and weaknesses in previous proposals. A number of these design decisions make Tor a more attractive system for the general user and have encouraged wider deployment.

The Tor network, like the Mix-Net proposed in Chaum (1981) uses public key encryption and cascades of servers to ensure message anonymity. In Tor these mixes are known as ‘relays’. Relays that allow connections directly from Tor clients are known as ‘bridges’ and relays that deliver messages from the frontier of the Tor network are known as ‘exit nodes’. Figure \ref{tor-network} shows how a client connects to the Tor network.

\begin{figure}[H]
\center \includegraphics[width=\linewidth]{tor-network-diagram}
\caption{The Tor Network}
\label{tor-network}
\end{figure}

When a relay joins the Tor network, it trades symmetric cipher keys with its neighbours using public key cryptography. These keys are used to encrypt communications and are destroyed when the session is closed to prevent replay attacks.

After it was noticed that Tor was being used to circumvent censorship as well as for anonymity, a proposal was developed to improve its blocking resistance \citep{Dingledine:2008p1542}. Many of the suggestions in this proposal have been implemented, but many still remain.

Apart from traffic analysis attacks, Tor nodes have been run by hostile parties to capture private information (Goodin, 2007)

\section{Traffic Analysis}

The development of radio led to a great change in the theatre of war, giving generals almost instant control over their armies. This proved to be a double edged sword, the broadcast nature of radio communications made it easier for enemies to intercept communications. While encryption methods were developed to provide resistance against eavesdropping, the patterns exhibited by radio signals allowed for the identification of the communicators, the language they used or the location they resided \cite{Kahn:1967p1005}.

When considering the use of traffic analysis for Internet communications, three  techniques are used. These are: exact matching, heuristic matching and machine learning \citep{Zhang:2009p1188}.

Exact matching techniques recognise properties of communications that mirror known protocols and communication patterns. This might include the port an application uses or the format of its payload. Since anonymous networks typically use encryption and avoid using known or published communication patterns, these kind of attacks are not applicable.

Heuristic matching looks for patterns in conversations to determine communications patterns and infer relationships. Finally, machine learning involves the use of statistics to train computer algorithms to classify traffic. Both heuristic and machine matching techniques are suitable for traffic analysis of anonymous networks because they do not rely on analysing the content of messages.

\subsection{Heuristic Techniques}

The increasing burden of peer to peer (P2P) applications on campus networks, and their shift to encryption motivated the development of heuristics based techniques for identifying P2P traffic. Early techniques include identifying known properties of P2P networks such as often communicating using both the UDP and TCP protocols simultaneously and using a solitary connection to transfer high volumes \citep{Karagiannis:2004p6400}. This paper also reduced the number of false positives by eliminating packets that matched known communications protocols.

Similar techniques have been developed in \citep{Perenyi:2006p6325} and \citep{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating more false positives. In \cite{Oneil:2004p6451} the same heuristics are used to identify P2P nodes before applying a secondary heuristic to identify ‘supernodes’ which are a subset of all P2P nodes.

Classifying traffic based on system roles is a key feature of the technique that appears in BLINC: Multilevel Traffic Classification in the Dark \citep{Karagiannis:2005p6359}. By analyzing communications at the host level then at increasing levels of granularity, a greater level of accuracy is achieved.

The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in \cite{Iliofotou:2008p6373} and \cite{Iliofotou:2009p6461}. Once traffic flows are represented in a TDG, mathematical properties of the flow can be analyzed to make positive identifications.

Viruses have also posed a problem for network administrators, often over-utilizing network resources and using the network to infect new machines. A technique for identifying various worms was proposed in \cite{Lazarevic:2003p6450}.

\subsection{Machine Learning Techniques}

\subsubsection{Expectation-Maximisation}

The first use of machine learning to categorise traffic flows appears in \cite{McGregor:2004p3826}. A detailed analysis of the attributes that can be used for machine learning and an attempt at coarse grained classification using an Expectation-Maximisation (EM) algorithm are demonstrated. The same technique is also demonstrated in \cite{Soule:2004p3817} using histograms for finer grained classification. The EM algorithm is again used in \cite{Zander:2005p6212} and \cite{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.

\subsubsection{Naïve Bayes}

\cite{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content. This paper focuses on many of the most commonly used Internet protocols while \cite{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.

\cite{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor. This technique performed poorly when applied to the Tor network, but it suggests that Tor traffic has particular characteristics that distinguish it from many existing PETs. It makes a particularly useful observation: “The most frequent packet sizes in the Tor traffic dumps are, in descending order, 1500, −52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.”

\subsubsection{Hidden Markov Model}

Hidden Markov Models are first used as a traffic analysis technique in HMM profiles for network traffic classification \citep{Wright:2004p3860}. The primary identification characteristics for use with this algorithm are packet size and inter-packet arrival times. With refinement this algorithm is used with increasing accuracy in \cite{Wright:2006p322} and \cite{Dainotti:2008p1435}. HMMs are also used in \cite{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.

\subsubsection{Clustering}

Clustering algorithms group observations into subsets based on similar characteristics. They have been used in a number of traffic classification techniques with the K-Means clustering technique being the most prominent. K-Means cluster analysis appears in Bernaille et al. (2006), \cite{Erman:2007p3764}, \cite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \cite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.

\subsubsection{Other Techniques}

Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \citep{Roughan:2004p3823}, Normalized Threshold \citep{Crotti:2007p3824}. The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \cite{Dusi:2008p6254}.

\subsubsection{Comparing Techniques}

It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \citep{Kim:2007p3867}. However some attempt has been made at comparison in \cite{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms. \cite{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.

An excellent meta study on traffic analysis techniques is presented in \cite{Nguyen:2008p3837}. This paper compares many of the published papers, the techniques used, criteria analysed and how effectively they meet stated goals.

\chapter{Theoretical Framework}

The proposed research will use a methodology typical of machine learning traffic analysis papers, substituting data captured from a controlled simulation in place of live network captures.

The experiment will be conducted in two phases, the first being a data collection phase. The second phase will include a quasi experimental methodology which may include data manipulation techniques to prepare the collected data and a comparison of various heuristics and machine learning based traffic analysis to classify the collected data.

\section{Assumptions}

It is assumed that the usage patterns exhibited by individual users will be smaller than the communications characteristics that will lead to the identification of anonymous and censorship resistant networks. Thus there is no need to obtain a large sample of regular network traffic from varying user profiles.

As of the current implementation, Tor network traffic is readily distinguishable by looking at the handshake packets. It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \cite{Dingledine:2008p1542}. For this reason, this proposal focuses on traffic analysis techniques that are content agnostic.

\section{Variables}

The data capturing stage will be affected by a number of variables that will influence the accuracy of the chosen matching algorithms.

\subsection{System Performance}

Packet latency is highly dependent on the performance of a computer system  and how busy it is. Performance related variables include:

\begin{itemize*}
\item CPU speed and number of cores
\item RAM speed and amount
\item Performance of integrated components, system bus etc.
\item Hard disk size, access time and throughput
\item Installed and running applications
\item System configuration
\end{itemize*}

To remedy this, the systems used to simulate the Tor network should be made uniform. This means an identical hardware and software configuration for all systems in the simulation network.

In addition it is noted that system performance can degrade over time due to both memory and hard disk fragmentation. This can be avoided by running the simulations in a virtualisation environment that support snapshots, rolling back to a known configuration point after each test.

\subsection{Network Performance}

Like system performance, latency is also dependent on the quality of the network. Network switching equipment has limited resources for routing packets and competing network traffic can introduce unpredictable delays into the sampled data.

Isolating the test network from the wide area network or Internet can help reduce these variables significantly as well as ensuring that all unnecessary network related software is uninstalled or disabled.

\subsection{Application Protocol}

Tor provides communications facilities to a number of Internet enabled applications by providing an interface using the SOCKS protocol. This means that the Tor network can proxy regular web browsing, email or any other TCP based communication protocol. Each of these application protocols have their own distinguishing communications characteristics which will influence the matching algorithm. It is not yet clear how transparent the Tor network will be regarding these characteristics and thus, for the purposes of classification a single protocol should be chosen.

\subsection{Quality of the Anonymous Network}

An individual connection to the Tor network traverses a number of nodes to create a circuit, these individual nodes can vary wildly in the following ways:

\begin{itemize*}
\item The geographic location of each node
\item Network bandwidth and latency
\item System load
\item Network load
\item Configuration
\end{itemize*}

Each communication session established creates a new circuit, of which the nodes that comprise this circuit are chosen randomly.

For testing purposes, the Tor network can be simulated on a small network. This will eliminate a lot of the variability that comes from monitoring the real Tor network. Factors that affect the quality of the network can be controlled by limiting the number of competing network applications, controlling the number of running Tor instances and ensuring a consistent configuration across all nodes.

\subsection{Caching}

Both web browsers and web servers are designed for high performance and often cache requests so that they can be delivered faster in the future. While this is a normal part of communications traffic and should be considered, it is important that uncached and cached requests appear in equal volume in all experiments. Manually flushing the cache or rolling back to a known virtual machine snapshot between each simulation can ensure this outcome.

\chapter{Materials and Methods}

\section{Equipment Requirements}

The following list describes computer systems and hardware required to run the data capture simulations:

\begin{itemize*}
\item 1 Computer system running web browser and Tor
\item 1 Computer running packet sniffing software
\item N Computer systems running Tor, configured as bridges
\item 1 Computer running web server and Tor directory server
\item Cat 5 cable to connect all computer systems
\item Network Hub or Switch capable of disabling ‘learning’ \citep{website:hub-reference}
\end{itemize*}

The computer systems running Tor bridges represent the simulation network. Although it is feasible to have a single system representing the simulation network the combined system load may be too great and introduce  excessive latency.

Packet capture is a performance intensive application, 1 machine should be reserved for this application. It must include adequate disk space, preferably of a high speed.

The required software includes:

\begin{itemize*}
\item Virtualisation software
\item Web browser
\item Tor
\item Packet capture software
\end{itemize*}

\subsection{Procedure}

\subsubsection{Phase 1}

\paragraph{Hardware Configuration}

All systems will be configured and connected to the same isolated network through the hub as shown in Figure \ref{physical-setup}.

\begin{figure}[h]
\center \includegraphics[scale=0.8]{physical-setup}
\caption{Physical Setup}
\label{physical-setup}
\end{figure}

\paragraph{Software Configuration}

Software is installed and configured on all machines. The simulation network is configured to use the private Tor directory server rather than the public ones specified by default.

The packet sniffer is configured to capture only the packets relevant for each data set.

Figure \ref{network-diagram} shows the placement of applications and relevant data flows.

\begin{figure}
\includegraphics[width=\linewidth]{network-diagram}
\caption{Network Diagram}
\label{network-diagram}
\end{figure}

\paragraph{Simulations}

A number of simulations will be performed. The web server

\paragraph{Data Capture}

Three sets of data must be collected, and kept separate. The first set is a sample that is known to belong to the anonymous networks in question. To capture this the software will be configured to communicate using known parameters. It will also be ensured that no other applications are communicating using these parameters that may pollute the data set.

This first set of data can be partitioned to make the second set, which will be used to confirm the false negative rate of the matching technique.

The third set of data must constitute traffic that is known to not contain any traffic from the networks being catalogues. This data set will be used to confirm the rate of false positives.

\subsection{Phase 2}

\subsubsection{Data Preparation}

The captured data will be in the data file format used by the capture software. For analysis the most relevant information needs to be retrieved from the data files and prepared in a suitable format for the matching algorithm.

\paragraph{Analysis}

The training data set will be supplied to the algorithm for training purposes. Once training is complete, this algorithm can be tested against the confirmation data set to obtain the rate of false negatives. The regular traffic will be used to determine the false positive rate. This allows the construction of the Receiver Operating Characteristic (ROC) curve, a measurement of the performance of the matching algorithm.

\section{Limitations}

The process has been designed with a goal to minimising variables that may affect matching performance - this is unusual for traffic analysis papers which typically sample real world traffic in large volumes. In the case of a machine learning technique, this may bias the chosen algorithm against real world data, making it impractical for any real world use.

\section{Schedule}

\begin{tabular}{llr}
\toprule
Activity & Duration & Date \\
\midrule
Phase 1 \\
1 - Setup hardware & 1 week \\
2 - Configure simulations & 1 week \\
3 - Run simulations/data capture & 4 weeks \\
Phase 2 \\
1 - Data preparation & 4 week \\
2 - Algorithm training and selection & 8 weeks \\
Document final results and writeup & * \\
\midrule
Thesis submission & & December 4th, 2011 \\
\bottomrule
\end{tabular}

\bibliography{papers,websites}

\end{document}

% vim: fdm=syntax

### 2010-04-24 conference-paper/proposal.tex
Work on stripping proposal down into conference

@@
-\documentclass{ecuthesis}
+\documentclass{conference}
 
@@
 
-% Setup the variables for the title page
-\title{Using traffic analysis to identify anonymous networks}
-\author{John Barker}
-\department{School of Computer and Security Science}
-\school{Edith Cowan University}
-\degree{Computer Science (Honours)}
-\email{jebarker@our.ecu.edu.au}
-\studentid{0991300}
-\supervisor{Dr Christopher Bolan}
-\supervisor{Mr Peter Hannay}
-\supervisor{Mr Patryk Szewczyk}
-
 % Begin document
 \begin{document}
-\maketitle
+{\center \Large \bfseries \MakeUppercase{Using traffic analysis to identify Tor} \par}
+
+{ \center
+  \begin{tabular*}{\textwidth}{cccc}
+  John Barker & Peter Hannay & Christopher Bolan & Patryk Szewczyk \\
+  jebarker@our.ecu.edu.au & p.hannay@ecu.edu.a & c.bolan@ecu.edu.au & p.szewczyk@ecu.edu.au \\
+  \end{tabular*}
+}
 
@@
 
-\chapter{Introduction}
-
-\section{Background}
+\section{Introduction}
 
@@
 
-In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity.
-Recent examples of such software include Freenet \citep{Clarke:2001p2435} and The Second Generation Onion Router (Tor).
+In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity, including The Second Generation Onion Router (Tor).
 Tor is an anonymous network which uses various techniques to provide low latency anonymity to network participants \citep{Dingledine:2004p314}.
@@
 
-Although such networks provide avenues for users to avoid censorship and a certain amount of privacy, it may be possible to use traffic analysis techniques to automatically these communications and distinguish them from regular traffic.
-This paper proposes a quasi-experimental methodology for identifying Tor traffic which may be used by censors in the future.
+Although Tor provides censorship resistance and a certain amount of privacy, it may be possible to use traffic analysis techniques to automatically identify Tor connections and target them for attacks.
+Since Tor relies on large numbers of users for the protections it provides, attacks that affect the reliability of the network can discourage participation, rendering it`s protections useless.
+This paper proposes a statistical methodology for identifying Tor traffic which may be used for such attacks in the future.
 
@@
 
-Traffic analysis is a well established field, and there are a significant number of known papers that propose traffic analysis attacks against modern communications networks \citep{Zhang:2009p1188}.
-When considering anonymous and censorship resistant networks, typical traffic analysis attacks focus on techniques and attacks designed to uncover the identities of participants.
-As stated in \citet{Murdoch:2005p325} “The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa”.
-
-Tor’s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \citep{website:tor-anonymity-online}.
+Tor`s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \citep{website:tor-anonymity-online}.
+It has been the subject of many technical papers proposing traffic analysis attacks, however the primary objective has historically been attacks that reveal the identity of participants.
+As stated in \citet{Murdoch:2005p325} ``The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa''.
 
@@
 
-Given a motivated and universal attacker, it is inexpensive and straightforward to disconnect a user from these networks by blocking access to well known and published resources.
-Once these avenues of attack have been exhausted it is still possible to connect to the network by connecting to lesser known access points.
-Since these networks are capable of communicating using many of the same methods as most conventional Internet applications, a blanket ban on this kind of communication would be too broad and extensive.
-
-Tor employs strong encryption the goal of which is to ensure that the data transmitted is indistinguishable from random noise.
-To an observer, data transmitted using encryption looks the same.
-Thus the traditional means of identifying these protocols are ineffective.
+The ability of Tor to connect on any port and it`s usage of strong encryption mean that recognizing traffic belonging to Tor is not straightforward.
+However it is possible that the communications patterns exhibited by Tor nodes are recognizeable using statistical methods.
 
@@
 
-\chapter{Literature Review}
-
-The main areas of research included papers and proposals on the design of anonymity networks and those covering the subject of traffic analysis.
-Particular attention has been paid to encryption as it is the primary function by which these systems operate and a good understanding is necessary for the development of an appropriate traffic analysis method.
-
-\section{Encryption}
-
-Since the inception of language, hostile forces and their attempts to intercept messages have necessitated the development of secretive communications.
-This deliberate transformation of a messages so that only the intended recipient can understand it is known as encryption.
-The process of examining these obfuscated messages and attempting to reverse the transformation is known as cryptanalysis \citep{Schneier:1995p3908}.
-These fields have been locked in an arms race ever since, each side continually advancing their capabilities in an attempt to gain ground.
-
-Apart from One Time Pads, no encryption methodology has ever proven to be unbreakable \citep{Shannon:2001p6583}.
-This means that all remaining cryptographic methods are a way of transforming information, so that for an attacker the difficulty in reversing this transformation is too costly to make it worthwhile.
-The invention of robots and computers was precipitated by the need to break encryption methods of increasing complexity and at the same time has lead to the increasing complexity of encryption algorithms \citep{Kahn:1967p1005}.
-
-In \citeyear{Jevons:1874p1167}, \citeauthor{Jevons:1874p1167} perhaps unknowingly, uncovered the basis of public key cryptography in his publication \emph{The Principles of Science: A Treatise on Logic and Scientific Method}.
-He recognised that certain mathematical operations yielded products that were impossible or difficult to reverse in order to uncover the factors used.
-
-The possibility of public key cryptography, described as ‘non-secret encryption’ was conceived by James H.
-Ellis in \citeyearpar{Ellis:1970p3249} and later developed into both a method for sharing secret encryption keys by Malcolm J.
-Williamson in 1974 \citep{Singh:1999p3277} and a method for asymmetric encryption \citep{Cocks:1973p3265}.
-
-These papers were not published at the time due to being classified information, allowing these methods to be reinvented independently \citep{Singh:1999p3277}.
-The method for key sharing developed by Ellis later became known as the Diffie-Hellman key exchange \cite{Diffie:1976p585}, while the method for asymmetric encryption is now known as RSA encryption, taking its name from the initials of its creators Rivest, Shamir and Adleman \citet*{Rivest:1978p708}.
-Figure \ref{key-exchange} shows how discrete logarithms are used in the Diffie-Hellman algorithm to generate a shared encryption key.
-
-\begin{figure}[H]
-\center \includegraphics[width=\linewidth]{key-exchange}
-\caption{Diffie-Hellman Key Exchange}
-\label{key-exchange}
-\end{figure}
-
-Public key cryptography has seen a number of advancements based on these early discoveries, with the development of an asymmetric key encryption method based on Diffie-Hellman named after its creator \citet*{ElGamal:1985p529}.
-Various mathematical problems have been used in the development of newer crypto systems, with increasing complexity such as the use of  elliptic curve cryptography in \cite{Miller:1986p2966} and \cite{Koblitz:1987p3109}, probabilistic functions in \cite{Paillier:1999p3152} and to address weaknesses in \cite{Cramer:1998p3186}.
-
-Public key cryptography is the foundation of Internet based cryptography and anonymous networks.
-Conventional methods of sharing secret keys by courier or post are costly and negate the benefits provided by a digital network.
-Although \cite{Baran:1964p384} proposed encryption for usage in digital communications, citing benefits such as tamper resistance, message secrecy and resistance to traffic analysis.
-This system was never implemented.
-
-Early work in encrypted Internet communications includes the Secure Network Programming (SNP) applications programming interface (API) \citep{Woo:1994p2532}.
-This was simply a framework providing numerous encryption, signing and authentication methods.
-The Secure Sockets Layer (SSL) is an encryption layer which provided end to end communications secrecy on the Internet \citep{website:SSL}.
-It makes use of public key cryptography to ensure secrecy.
-
-This proposed standard went through a number of revisions, with early versions suffering security flaws \citep{Wagner:1996p385}.
-SSL is now known as Transport Layer Security, with the latest version 1.2 being released August 2008 \citep{website:TLS}.
-TLS addresses some issues in SSL and provides a number of enhancements, but is not compatible.
-
-The Hypertext Transfer Protocol Secure (HTTPS) makes use of both SSL and TLS and the Hypertext Transfer Protocol (HTTP) to provide encryption and secure identification when visiting websites \citep{website:HTTPS}.
-This is also the protocol used by Tor.
-
 \section{Anonymous and Censorship Resistant Networks}
 
-The first anonymous network system was proposed in \cite{Chaum:1981p296}.
-This proposal included the use of public key cryptography and a centrally located server known as a ‘mix’.
-By wrapping the information and address of a destination in a message and encrypting it with the mix’s public key, only the mix system is able to read the message.
+The first anonymous network system was proposed in \citet{Chaum:1981p296}.
+This proposal included the use of public key cryptography and a centrally located server known as a `mix'.
+By wrapping the information and address of a destination in a message and encrypting it with the mix`s public key, only the mix system is able to read the message.
 
-\begin{figure}[H]
-\center \includegraphics[width=\linewidth]{chaums-mix-network}
-\caption{Chaum's Mix Network}
-\label{chaums-mix-network}
-\end{figure}
+\subsection{The Second Generation Onion Router (Tor)}
 
-The mix system then delivers the message to its destination without passing any information on about the sender.
-Because the destination system only communicates with the mix server, it has no information available about the sender in which to make a positive identification.
-
-Since this proposal, many networks have been developed that provide features such as anonymity and censorship resistance.
-The proposed systems differ with regard to the motivation behind providing anonymity.
-Like cryptography, an arms race between anonymous network designers and those discovering attacks has motivated development of iterative refinements in response to weaknesses.
-
-Many early systems were designed to provide anonymous email delivery, these include Babel \citep{Gulcu:1996p1662}, Mixminion \citep{Danezis:2003p1616} as well as Nym servers \citep{Mazieres:1998p4560} and two commercial offerings Underhill and NymBaron.
-One of the earliest anonymous remailers anon.penet.fi was created by Johan Helsingius in 1993, but was shutdown in 1996 due to a combination of legal pressure and an inability to provide true anonymity \cite{Danezis:2008p346}.
-
-The need for anonymous networks to resist attack and node failure led to the development of various robust mix networks such as \citep{Waidner:1989p5870}, \citep{Park:1994p5051}, (Kilian  Sako, 1995), \citep{Ogata:1997p5083}, \citep{Abe:1998p1898}, \citep{Jakobsson:1998p5137} and (Desmedt and Kurosawa, 2000).
-An avenue of research in robust mix networks is universal re-encryption described in \citep{Fairbrother:2005p5357}, \citep{Lu:2005p5387}, (Lu et al., 2006) and \citep{Gomukiewicz:2004p294}.
-
-The problem of mathematically provable anonymity is a difficult one, and many proposals have been developed \citep{Chaum:1988p5869}, \citep{Rackoff:1993p5817}, \citep{Kesdogan:1998p2027}, \citep{Jakobsson:1999p2008} \cite{Neff:2001p2068}, \cite{Furukawa:2001p5158}, \citep{Golle:2004p5204}, \citep{Gomukiewicz:2003p5816}, \citep{Berman:2004p303}, \citep{Golle:2004p5204}, \citep{Adida:2007p5205}, \citep{Klonowski:2005p5379}, \citep{Nguyen:2008p3837}.
-In practice however, strong provable anonymity incurs a great deal of performance overhead and has not seen wide usage \citep{Danezis:2008p346}.
-
-Attempts to make provable anonymity more attractive by increasing performance includes Flash mixing, a scheme for more efficient anonymity using mixes \citep{Jakobsson:1999p2008}.
-
-Stop and Go Mixes which provide probabilistic anonymity and don’t require a confirmed identity to participate \citep{Kesdogan:1998p2027}.
-
-Discouraging network operators from divulging known identities is a feature of intentionally fragile mix networks such as \citep{Reiter:2004p5868} and (Golle et al., 2006).
-These networks are designed to make the process of tracing a single message damaging to the system or its property of anonymity, making compulsion potentially expensive.
-
-\cite{Jakobsson:2002p5815} \cite{Goel:2003p5871}
-
-The practice of steganography allows for the hiding of messages within existing mechanisms, which provides some measure of anonymity and censorship resistance by making messages undetectable to observers.
-Steganography has been proposed as a way of providing censorship resistance in (Feamster et al., 2002), (Feamster et al., 2003).
-The use of covering traffic and rerouting of messages to complicate traffic analysis is discovered in \citep{Venkatraman:1995p6008}, (Timmerman, 1997), (Timmerman, 1999), (Guan et al., 2001) and (Newman et al., 2003).
-
-Most anonymous and censorship resistant networks provide means for using well established Internet protocols in an anonymous manner, some however have provided standalone means of publishing information anonymously.
-These include Freedom (Boucher et al., 2000) and Freenet (Clarke et al., 2001) which provides a network for publishing with anonymity for both authors and readers by collectively sharing storage.
-
-The success of peer to peer (p2p) systems such as Bittorrent and Kazaa has inspired the development of p2p anonymous networks such as MorphMix \citep{Rennhard:2002p4559}, Tarzan (Freedman, 2002) and P5 (Sherwood et al., 2005).
-
-Private Information Retrieval:
-
-(Kissner et al., 2004) (Sassaman et al., 2005) (Danezis and Diaz, 2006) (Ostrovsky and Keith, 2007) (Bethencourt et al., 2009)
-
-Some anonymous networks have been developed with the explicit goal of censorship resistance, these include aChord (Hazel and Wiley, 2002), gnuNet (Hazel and Wiley, 2002), (Anderson, 1996), (Serjantov, 2002) and (Clayton et al., 2006)
-
-\subsection{The Second Generation Onion Router(Tor)}
-
-Tor was first described in Tor: The Second-Generation Onion Router (Dingledine et al., 2004).
-This new generation of onion router was designed with a number of defences for common traffic analysis attacks and weaknesses in previous proposals.
-A number of these design decisions make Tor a more attractive system for the general user and have encouraged wider deployment.
-
-The Tor network, like the Mix-Net proposed in Chaum (1981) uses public key encryption and cascades of servers to ensure message anonymity.
+The Tor network, like the Mix-Net proposed by \citet{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \citep{Dingledine:2004p314}.
 In Tor these mixes are known as ‘relays’.
@@
 \begin{figure}[H]
-\center \includegraphics[width=\linewidth]{tor-network-diagram}
+\center \includegraphics{tor-network-diagram}
 \caption{The Tor Network}
@@
 
-Apart from traffic analysis attacks, Tor nodes have been run by hostile parties to capture private information (Goodin, 2007)
-
 \section{Traffic Analysis}
 
-The development of radio led to a great change in the theatre of war, giving generals almost instant control over their armies.
-This proved to be a double edged sword, the broadcast nature of radio communications made it easier for enemies to intercept communications.
-While encryption methods were developed to provide resistance against eavesdropping, the patterns exhibited by radio signals allowed for the identification of the communicators, the language they used or the location they resided \cite{Kahn:1967p1005}.
-
-When considering the use of traffic analysis for Internet communications, three  techniques are used. These are: exact matching, heuristic matching and machine learning \citep{Zhang:2009p1188}.
-
-Exact matching techniques recognise properties of communications that mirror known protocols and communication patterns.
-This might include the port an application uses or the format of its payload.
-Since anonymous networks typically use encryption and avoid using known or published communication patterns, these kind of attacks are not applicable.
-
-Heuristic matching looks for patterns in conversations to determine communications patterns and infer relationships.
-Finally, machine learning involves the use of statistics to train computer algorithms to classify traffic.
-Both heuristic and machine matching techniques are suitable for traffic analysis of anonymous networks because they do not rely on analysing the content of messages.
+When considering the use of traffic analysis for Internet communications, three primary techniques are used.
+These are: exact matching, heuristic matching and machine learning \citep{Zhang:2009p1188}.
+Exact matching techniques are ineffective in recognizing Tor communications as Tor can operate on any available port and uses encryption to hide communications.
+This leaves heuristic and machine learning matching techniques.
 
@@
 Early techniques include identifying known properties of P2P networks such as often communicating using both the UDP and TCP protocols simultaneously and using a solitary connection to transfer high volumes \citep{Karagiannis:2004p6400}.
-This paper also reduced the number of false positives by eliminating packets that matched known communications protocols.
+Similar techniques have been developed in \citep{Perenyi:2006p6325} and \citep{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating false positives using exact matching techniques.
 
-Similar techniques have been developed in \citep{Perenyi:2006p6325} and \citep{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating more false positives.
-In \cite{Oneil:2004p6451} the same heuristics are used to identify P2P nodes before applying a secondary heuristic to identify ‘supernodes’ which are a subset of all P2P nodes.
-
-Classifying traffic based on system roles is a key feature of the technique that appears in BLINC: Multilevel Traffic Classification in the Dark \citep{Karagiannis:2005p6359}.
-By analyzing communications at the host level then at increasing levels of granularity, a greater level of accuracy is achieved.
-
-The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in \cite{Iliofotou:2008p6373} and \cite{Iliofotou:2009p6461}.
-Once traffic flows are represented in a TDG, mathematical properties of the flow can be analyzed to make positive identifications.
-
-Viruses have also posed a problem for network administrators, often over-utilizing network resources and using the network to infect new machines.
-A technique for identifying various worms was proposed in \cite{Lazarevic:2003p6450}.
+Heuristics based matching techniques have also been used to identify traffic belonging to network worms \citep{Lazarevic:2003p6450} and the Skype protocol \citep{Ehlert:2006p2396}.
 
@@
 
-The data capturing stage will be affected by a number of variables that will influence the accuracy of the chosen matching algorithms.
+The data capturing stage will be affected by a number of variables that will influence the accuracy of the chosen matching algorithms. These include:
 
-\subsection{System Performance}
+\begin{enumerate*}
+\item System Performance
+\item Network Performance
+\item Application Protocol
+\item Quality of the Anonymous Network
+\item Caching
+\end{enumerate*}
 
-Packet latency is highly dependent on the performance of a computer system  and how busy it is. Performance related variables include:
-
-\begin{itemize*}
-\item CPU speed and number of cores
-\item RAM speed and amount
-\item Performance of integrated components, system bus etc.
-\item Hard disk size, access time and throughput
-\item Installed and running applications
-\item System configuration
-\end{itemize*}
-
-To remedy this, the systems used to simulate the Tor network should be made uniform. This means an identical hardware and software configuration for all systems in the simulation network.
-
-In addition it is noted that system performance can degrade over time due to both memory and hard disk fragmentation.
-This can be avoided by running the simulations in a virtualisation environment that support snapshots, rolling back to a known configuration point after each test.
-
-\subsection{Network Performance}
-
-Like system performance, latency is also dependent on the quality of the network.
-Network switching equipment has limited resources for routing packets and competing network traffic can introduce unpredictable delays into the sampled data.
-
-Isolating the test network from the wide area network or Internet can help reduce these variables significantly as well as ensuring that all unnecessary network related software is uninstalled or disabled.
-
-\subsection{Application Protocol}
-
-Tor provides communications facilities to a number of Internet enabled applications by providing an interface using the SOCKS protocol.
-This means that the Tor network can proxy regular web browsing, email or any other TCP based communication protocol.
-Each of these application protocols have their own distinguishing communications characteristics which will influence the matching algorithm.
-It is not yet clear how transparent the Tor network will be regarding these characteristics and thus, for the purposes of classification a single protocol should be chosen.
-
-\subsection{Quality of the Anonymous Network}
-
-An individual connection to the Tor network traverses a number of nodes to create a circuit, these individual nodes can vary wildly in the following ways:
-
-\begin{itemize*}
-\item The geographic location of each node
-\item Network bandwidth and latency
-\item System load
-\item Network load
-\item Configuration
-\end{itemize*}
-
-Each communication session established creates a new circuit, of which the nodes that comprise this circuit are chosen randomly.
-
-For testing purposes, the Tor network can be simulated on a small network.
-This will eliminate a lot of the variability that comes from monitoring the real Tor network.
-Factors that affect the quality of the network can be controlled by limiting the number of competing network applications, controlling the number of running Tor instances and ensuring a consistent configuration across all nodes.
-
-\subsection{Caching}
-
-Both web browsers and web servers are designed for high performance and often cache requests so that they can be delivered faster in the future.
-While this is a normal part of communications traffic and should be considered, it is important that uncached and cached requests appear in equal volume in all experiments.
-Manually flushing the cache or rolling back to a known virtual machine snapshot between each simulation can ensure this outcome.
+An attempt will be made to reduce the impact of these variables by capturing packets generated by an isolated simulation of the Tor network, ensuring only vital network applications are running and executing software inside a virtual machine which can be rolled back to a known snapshot \citep{website:snapshot-definition}.
 
@@
 
-\section{Equipment Requirements}
-
-The following list describes computer systems and hardware required to run the data capture simulations:
-
-\begin{itemize*}
-\item 1 Computer system running web browser and Tor
-\item 1 Computer running packet sniffing software
-\item N Computer systems running Tor, configured as bridges
-\item 1 Computer running web server and Tor directory server
-\item Cat 5 cable to connect all computer systems
-\item Network Hub or Switch capable of disabling ‘learning’ \citep{website:hub-reference}
-\end{itemize*}
-
-The computer systems running Tor bridges represent the simulation network.
-Although it is feasible to have a single system representing the simulation network the combined system load may be too great and introduce  excessive latency.
-
-Packet capture is a performance intensive application, 1 machine should be reserved for this application. It must include adequate disk space, preferably of a high speed.
-
-The required software includes:
-
-\begin{itemize*}
-\item Virtualisation software
-\item Web browser
-\item Tor
-\item Packet capture software
-\end{itemize*}
-
-\subsection{Procedure}
-
-\subsubsection{Phase 1}
-
-\paragraph{Hardware Configuration}
-
-All systems will be configured and connected to the same isolated network through the hub as shown in Figure \ref{physical-setup}.
-
-\begin{figure}[h]
-\center \includegraphics[scale=0.8]{physical-setup}
-\caption{Physical Setup}
-\label{physical-setup}
-\end{figure}
-
-\paragraph{Software Configuration}
-
-Software is installed and configured on all machines. The simulation network is configured to use the private Tor directory server rather than the public ones specified by default.
-
-The packet sniffer is configured to capture only the packets relevant for each data set.
+The experiment will consist of two phases, first a simulation phase which involves the capture of packets belonging to a Tor network
 
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{network-diagram}
+\center \includegraphics[scale=0.8]{network-diagram}
 \caption{Network Diagram}
@@
 \end{figure}
-
-\paragraph{Simulations}
-
-A number of simulations will be performed. The web server
-
-\paragraph{Data Capture}
-
-Three sets of data must be collected, and kept separate.
-The first set is a sample that is known to belong to the anonymous networks in question.
-To capture this the software will be configured to communicate using known parameters.
-It will also be ensured that no other applications are communicating using these parameters that may pollute the data set.
-
-This first set of data can be partitioned to make the second set, which will be used to confirm the false negative rate of the matching technique.
-
-The third set of data must constitute traffic that is known to not contain any traffic from the networks being catalogues. This data set will be used to confirm the rate of false positives.
-
-\subsection{Phase 2}
-
-\subsubsection{Data Preparation}
-
-The captured data will be in the data file format used by the capture software.
-For analysis the most relevant information needs to be retrieved from the data files and prepared in a suitable format for the matching algorithm.
-
-\paragraph{Analysis}
-
-The training data set will be supplied to the algorithm for training purposes.
-Once training is complete, this algorithm can be tested against the confirmation data set to obtain the rate of false negatives.
-The regular traffic will be used to determine the false positive rate.
-This allows the construction of the Receiver Operating Characteristic (ROC) curve, a measurement of the performance of the matching algorithm.
-
-\section{Limitations}
-
-The process has been designed with a goal to minimising variables that may affect matching performance - this is unusual for traffic analysis papers which typically sample real world traffic in large volumes.
-In the case of a machine learning technique, this may bias the chosen algorithm against real world data, making it impractical for any real world use.
-
-\section{Schedule}
-
-\begin{tabular}{llr}
-\toprule
-Activity & Duration & Date \\
-\midrule
-Phase 1 \\
-1 - Setup hardware & 1 week \\
-2 - Configure simulations & 1 week \\
-3 - Run simulations/data capture & 4 weeks \\
-Phase 2 \\
-1 - Data preparation & 4 week \\
-2 - Algorithm training and selection & 8 weeks \\
-Document final results and writeup & * \\
-\midrule
-Thesis submission & & December 4th, 2011 \\
-\bottomrule
-\end{tabular}
 

### 2010-04-25 conference-paper/proposal.tex
More work cutting
Moved to biblatex, which seems to be the ultimate solution for my referencing needs

@@
 
-% Packages
+% For graphics
 \usepackage{graphicx}
+
+% Bibliography
+\bibliography{papers,websites,patents}
 
@@
 In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity, including The Second Generation Onion Router (Tor).
-Tor is an anonymous network which uses various techniques to provide low latency anonymity to network participants \citep{Dingledine:2004p314}.
+Tor is an anonymous network which uses Onion Routing to provide low latency anonymity to network participants \citep{Dingledine:2004p314}.
 It also aims to provide resistance against censorship based blocking attempts \citep{Dingledine:2008p1542}.
@@
 
-The traffic analysis techniques proposed in this paper will attempt to classify network streams belonging to Tor users and distinguish them from regular encrypted communications.
+The traffic analysis techniques proposed will attempt to classify network streams belonging to Tor users to distinguish them from regular encrypted communications.
 
@@
 However it is possible that the communications patterns exhibited by Tor nodes are recognizeable using statistical methods.
-
-This raises the question: is it possible to distinguish the traffic created by these networks, from encrypted traffic produced by conventional software? This question can be broken down further:
+This raises the question: is it possible to distinguish the traffic created by these networks, from encrypted traffic produced by conventional software?
+This question can be broken down further:
 
@@
 
-\section{Anonymous and Censorship Resistant Networks}
+\section{Background Information}
 
@@
 
+Onion routing was first described in a patent by \cite{Michael:2001}.
+Like the mix network is uses public key cryptography to provide anonymity, it differs in that messages are repeatedly encrypted then passed through several nodes in a network known as onion routers.
+Each of these routers is capable of removing a single layer of encryption to reveal delivery instructions.
+This layering prevents individual nodes obtaining the identity of the sender, receiver and the contents of the message.
+
 \subsection{The Second Generation Onion Router (Tor)}
 
+The Second Generation Onion Router (Tor) uses a form of Onion Routing 
 The Tor network, like the Mix-Net proposed by \citet{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \citep{Dingledine:2004p314}.
@@
 
-\section{Traffic Analysis}
+\section{Related Work}
 
@@
 
-The first use of machine learning to categorise traffic flows appears in \cite{McGregor:2004p3826}.
+The first use of machine learning to categorise traffic flows appears in \citet{McGregor:2004p3826}.
 A detailed analysis of the attributes that can be used for machine learning and an attempt at coarse grained classification using an Expectation-Maximisation (EM) algorithm are demonstrated.
-The same technique is also demonstrated in \cite{Soule:2004p3817} using histograms for finer grained classification.
-The EM algorithm is again used in \cite{Zander:2005p6212} and \cite{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
+The same technique is also demonstrated in \citet{Soule:2004p3817} using histograms for finer grained classification.
+The EM algorithm is again used in \citet{Zander:2005p6212} and \citet{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
 
@@
 
-\cite{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
-This paper focuses on many of the most commonly used Internet protocols while \cite{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
+\citet{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
+This paper focuses on many of the most commonly used Internet protocols while \citet{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
 
-\cite{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+\citet{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
 This technique performed poorly when applied to the Tor network, but it suggests that Tor traffic has particular characteristics that distinguish it from many existing PETs.
@@
 The primary identification characteristics for use with this algorithm are packet size and inter-packet arrival times.
-With refinement this algorithm is used with increasing accuracy in \cite{Wright:2006p322} and \cite{Dainotti:2008p1435}.
-HMMs are also used in \cite{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
+With refinement this algorithm is used with increasing accuracy in \citet{Wright:2006p322} and \citet{Dainotti:2008p1435}.
+HMMs are also used in \citet{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
 
@@
 K-Means cluster analysis appears in Bernaille et al.
-(2006), \cite{Erman:2007p3764}, \cite{Erman:2007p6206}.
-The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \cite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
+(2006), \citet{Erman:2007p3764}, \citet{Erman:2007p6206}.
+The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \citet{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
 
@@
 Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \citep{Roughan:2004p3823}, Normalized Threshold \citep{Crotti:2007p3824}.
-The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \cite{Dusi:2008p6254}.
+The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \citet{Dusi:2008p6254}.
 
@@
 It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \citep{Kim:2007p3867}.
-However some attempt has been made at comparison in \cite{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
-\cite{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
+However some attempt has been made at comparison in \citet{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
+\citet{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
 
-An excellent meta study on traffic analysis techniques is presented in \cite{Nguyen:2008p3837}.
+An excellent meta study on traffic analysis techniques is presented in \citet{Nguyen:2008p3837}.
 This paper compares many of the published papers, the techniques used, criteria analysed and how effectively they meet stated goals.
 
-\chapter{Theoretical Framework}
+\section{Theoretical Framework}
 
-The proposed research will use a methodology typical of machine learning traffic analysis papers, substituting data captured from a controlled simulation in place of live network captures.
+The proposed experiment will employ a quasi-experimental research method, employing techniques common to traffic analysis papers.
+This includes the capturing of packet traces, development of a matching technique/algorithm and documentation of efficacy and results.
+The first phase of the experiment covers the data capturing phase, while the second phase concludes the traffic analysis technique.
 
-The experiment will be conducted in two phases, the first being a data collection phase.
-The second phase will include a quasi experimental methodology which may include data manipulation techniques to prepare the collected data and a comparison of various heuristics and machine learning based traffic analysis to classify the collected data.
-
-\section{Assumptions}
+\subsection{Assumptions}
 
@@
 As of the current implementation, Tor network traffic is readily distinguishable by looking at the handshake packets.
-It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \cite{Dingledine:2008p1542}.
+It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \citet{Dingledine:2008p1542}.
 For this reason, this proposal focuses on traffic analysis techniques that are content agnostic.
 
-\section{Variables}
+\subsection{Variables}
 
@@
 
-\chapter{Materials and Methods}
+\section{Materials and Methods}
 
-The experiment will consist of two phases, first a simulation phase which involves the capture of packets belonging to a Tor network
+The experiment will consist of two phases, first a simulation phase which involves the capture of packets belonging to a Tor network, the second will be a comparison and documentation of the results of using several techniques to identify Tor traffic.
 
-Figure \ref{network-diagram} shows the placement of applications and relevant data flows.
+Figure \ref{network-diagram} shows the placement of applications and relevant data flows for the simulation phase.
 
 \begin{figure}
-\center \includegraphics[scale=0.8]{network-diagram}
+\center \includegraphics[scale=0.7]{network-diagram}
 \caption{Network Diagram}
@@
 
-\bibliography{papers,websites}
+\printbibliography[title=REFERENCES]
 

### 2010-04-25 conference-paper/proposal.tex
Tweaks to get citations working even better: issues with month in bib files, links, abbreviation of names in citations

@@
 
-The Internet has revolutionised the political sphere in providing a platform for the publication of speech to a far greater audience than was ever available before digital communications systems \citep{Bonchek:1997p3455}.
+The Internet has revolutionised the political sphere in providing a platform for the publication of speech to a far greater audience than was ever available before digital communications systems \parencite{Bonchek:1997p3455}.
 The publication of less desirable political speech, criticism or challenging ideas still carries with it great risk, with numerous publications leading to arrest.
 This has spawned headlines such as \emph{Egypt arrests another blog critic} \citeyear{website:egypt-arrests}, \emph{Chinese couple sue Yahoo!
-in US over torture case} \citep{website:china-yahoo-torture}, \emph{Vietnam bloggers arrested over China shirt protest} \citep{website:vietnam-bloggers-arrested}, \emph{23 Journalists/Bloggers Arrested in Iran, Including Head of Top Group} \citeyear{website:iran-bloggers-arrested} and \emph{Blogger Arrests} \citep{website:blogger-arrests}.
-The Internet, like conventional media is still vulnerable to censorship by oppressive governments and malicious attackers \citep{Crandall:2007p6165,Karlin:2009p6166}.
+in US over torture case} \parencite{website:china-yahoo-torture}, \emph{Vietnam bloggers arrested over China shirt protest} \parencite{website:vietnam-bloggers-arrested}, \emph{23 Journalists/Bloggers Arrested in Iran, Including Head of Top Group} \citeyear{website:iran-bloggers-arrested} and \emph{Blogger Arrests} \parencite{website:blogger-arrests}.
+The Internet, like conventional media is still vulnerable to censorship by oppressive governments and malicious attackers \parencite{Crandall:2007p6165,Karlin:2009p6166}.
 
 In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity, including The Second Generation Onion Router (Tor).
-Tor is an anonymous network which uses Onion Routing to provide low latency anonymity to network participants \citep{Dingledine:2004p314}.
-It also aims to provide resistance against censorship based blocking attempts \citep{Dingledine:2008p1542}.
+Tor is an anonymous network which uses Onion Routing to provide low latency anonymity to network participants \parencite{Dingledine:2004p314}.
+It also aims to provide resistance against censorship based blocking attempts \parencite{Dingledine:2008p1542}.
 
@@
 
-Tor`s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \citep{website:tor-anonymity-online}.
+Tor`s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \parencite{website:tor-anonymity-online}.
 It has been the subject of many technical papers proposing traffic analysis attacks, however the primary objective has historically been attacks that reveal the identity of participants.
-As stated in \citet{Murdoch:2005p325} ``The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa''.
+As stated in \textcite{Murdoch:2005p325} ``The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa''.
 
@@
 
-The first anonymous network system was proposed in \citet{Chaum:1981p296}.
+The first anonymous network system was proposed in \textcite{Chaum:1981p296}.
 This proposal included the use of public key cryptography and a centrally located server known as a `mix'.
@@
 The Second Generation Onion Router (Tor) uses a form of Onion Routing 
-The Tor network, like the Mix-Net proposed by \citet{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \citep{Dingledine:2004p314}.
+The Tor network, like the Mix-Net proposed by \textcite{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \parencite{Dingledine:2004p314}.
 In Tor these mixes are known as ‘relays’.
@@
 
-After it was noticed that Tor was being used to circumvent censorship as well as for anonymity, a proposal was developed to improve its blocking resistance \citep{Dingledine:2008p1542}.
+After it was noticed that Tor was being used to circumvent censorship as well as for anonymity, a proposal was developed to improve its blocking resistance \parencite{Dingledine:2008p1542}.
 Many of the suggestions in this proposal have been implemented, but many still remain.
@@
 When considering the use of traffic analysis for Internet communications, three primary techniques are used.
-These are: exact matching, heuristic matching and machine learning \citep{Zhang:2009p1188}.
+These are: exact matching, heuristic matching and machine learning \parencite{Zhang:2009p1188}.
 Exact matching techniques are ineffective in recognizing Tor communications as Tor can operate on any available port and uses encryption to hide communications.
@@
 The increasing burden of peer to peer (P2P) applications on campus networks, and their shift to encryption motivated the development of heuristics based techniques for identifying P2P traffic.
-Early techniques include identifying known properties of P2P networks such as often communicating using both the UDP and TCP protocols simultaneously and using a solitary connection to transfer high volumes \citep{Karagiannis:2004p6400}.
-Similar techniques have been developed in \citep{Perenyi:2006p6325} and \citep{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating false positives using exact matching techniques.
+Early techniques include identifying known properties of P2P networks such as often communicating using both the UDP and TCP protocols simultaneously and using a solitary connection to transfer high volumes \parencite{Karagiannis:2004p6400}.
+Similar techniques have been developed in \parencite{Perenyi:2006p6325} and \parencite{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating false positives using exact matching techniques.
 
-Heuristics based matching techniques have also been used to identify traffic belonging to network worms \citep{Lazarevic:2003p6450} and the Skype protocol \citep{Ehlert:2006p2396}.
+Heuristics based matching techniques have also been used to identify traffic belonging to network worms \parencite{Lazarevic:2003p6450} and the Skype protocol \parencite{Ehlert:2006p2396}.
 
@@
 
-The first use of machine learning to categorise traffic flows appears in \citet{McGregor:2004p3826}.
+The first use of machine learning to categorise traffic flows appears in \textcite{McGregor:2004p3826}.
 A detailed analysis of the attributes that can be used for machine learning and an attempt at coarse grained classification using an Expectation-Maximisation (EM) algorithm are demonstrated.
-The same technique is also demonstrated in \citet{Soule:2004p3817} using histograms for finer grained classification.
-The EM algorithm is again used in \citet{Zander:2005p6212} and \citet{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
+The same technique is also demonstrated in \textcite{Soule:2004p3817} using histograms for finer grained classification.
+The EM algorithm is again used in \textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
 
@@
 
-\citet{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
-This paper focuses on many of the most commonly used Internet protocols while \citet{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
+\textcite{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
+This paper focuses on many of the most commonly used Internet protocols while \textcite{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
 
-\citet{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+\textcite{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
 This technique performed poorly when applied to the Tor network, but it suggests that Tor traffic has particular characteristics that distinguish it from many existing PETs.
@@
 
-Hidden Markov Models are first used as a traffic analysis technique in HMM profiles for network traffic classification \citep{Wright:2004p3860}.
+Hidden Markov Models are first used as a traffic analysis technique in HMM profiles for network traffic classification \parencite{Wright:2004p3860}.
 The primary identification characteristics for use with this algorithm are packet size and inter-packet arrival times.
-With refinement this algorithm is used with increasing accuracy in \citet{Wright:2006p322} and \citet{Dainotti:2008p1435}.
-HMMs are also used in \citet{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
+With refinement this algorithm is used with increasing accuracy in \textcite{Wright:2006p322} and \textcite{Dainotti:2008p1435}.
+HMMs are also used in \textcite{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
 
@@
 K-Means cluster analysis appears in Bernaille et al.
-(2006), \citet{Erman:2007p3764}, \citet{Erman:2007p6206}.
-The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \citet{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
+(2006), \textcite{Erman:2007p3764}, \textcite{Erman:2007p6206}.
+The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
 
@@
 
-Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \citep{Roughan:2004p3823}, Normalized Threshold \citep{Crotti:2007p3824}.
-The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \citet{Dusi:2008p6254}.
+Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized Threshold \parencite{Crotti:2007p3824}.
+The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \textcite{Dusi:2008p6254}.
 
@@
 
-It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \citep{Kim:2007p3867}.
-However some attempt has been made at comparison in \citet{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
-\citet{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
+It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \parencite{Kim:2007p3867}.
+However some attempt has been made at comparison in \textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
+\textcite{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
 
-An excellent meta study on traffic analysis techniques is presented in \citet{Nguyen:2008p3837}.
+An excellent meta study on traffic analysis techniques is presented in \textcite{Nguyen:2008p3837}.
 This paper compares many of the published papers, the techniques used, criteria analysed and how effectively they meet stated goals.
@@
 As of the current implementation, Tor network traffic is readily distinguishable by looking at the handshake packets.
-It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \citet{Dingledine:2008p1542}.
+It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \textcite{Dingledine:2008p1542}.
 For this reason, this proposal focuses on traffic analysis techniques that are content agnostic.
@@
 
-An attempt will be made to reduce the impact of these variables by capturing packets generated by an isolated simulation of the Tor network, ensuring only vital network applications are running and executing software inside a virtual machine which can be rolled back to a known snapshot \citep{website:snapshot-definition}.
+An attempt will be made to reduce the impact of these variables by capturing packets generated by an isolated simulation of the Tor network, ensuring only vital network applications are running and executing software inside a virtual machine which can be rolled back to a known snapshot \parencite{website:snapshot-definition}.
 

### 2010-04-26 conference-paper/proposal.tex
First draft of conference submitted

@@
 Onion routing was first described in a patent by \cite{Michael:2001}.
-Like the mix network is uses public key cryptography to provide anonymity, it differs in that messages are repeatedly encrypted then passed through several nodes in a network known as onion routers.
+Like the mix network it uses public key cryptography to provide anonymity, it differs in that messages are repeatedly encrypted then passed through several nodes in a network known as onion routers.
 Each of these routers is capable of removing a single layer of encryption to reveal delivery instructions.
@@
 
-The Second Generation Onion Router (Tor) uses a form of Onion Routing 
-The Tor network, like the Mix-Net proposed by \textcite{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \parencite{Dingledine:2004p314}.
-In Tor these mixes are known as ‘relays’.
-Relays that allow connections directly from Tor clients are known as ‘bridges’ and relays that deliver messages from the frontier of the Tor network are known as ‘exit nodes’.
+The Second Generation Onion Router (Tor) uses a form of Onion Routing which employs telescoping circuits to provide low latency anonymity \parencite{Dingledine:2004p314}.
+A connection through the Tor network constitutes a \emph{circuit}, which hops over several Tor nodes known as \emph{relays}.
+Relays that allow connections directly from Tor clients are known as \emph{bridges} and relays that deliver messages from the frontier of the Tor network are known as \emph{exit nodes}.
 Figure \ref{tor-network} shows how a client connects to the Tor network.
@@
 \begin{figure}[H]
-\center \includegraphics{tor-network-diagram}
+\center \includegraphics[scale=0.8]{tor-network-diagram}
 \caption{The Tor Network}
@@
 
-\subsubsection{Expectation-Maximisation}
-
+There are a vast number of traffic analysis papers that utilize machine learning techniques for the purpose of traffic classification, demonstrating a wide variety of algorithms for this purpose.
 The first use of machine learning to categorise traffic flows appears in \textcite{McGregor:2004p3826}.
 A detailed analysis of the attributes that can be used for machine learning and an attempt at coarse grained classification using an Expectation-Maximisation (EM) algorithm are demonstrated.
-The same technique is also demonstrated in \textcite{Soule:2004p3817} using histograms for finer grained classification.
-The EM algorithm is again used in \textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
+The same technique is also employed in \textcite{Soule:2004p3817} using histograms for finer grained classification.
+The EM algorithm is again used in \textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Na\"ive Bayes classifier.
 
-\subsubsection{Naïve Bayes}
-
-\textcite{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
+\textcite{Moore:2005p3827} demonstrates the usage of a supervised Na\"ive Bayes algorithm to classify traffic flows.
 This paper focuses on many of the most commonly used Internet protocols while \textcite{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
 
-\textcite{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
 This technique performed poorly when applied to the Tor network, but it suggests that Tor traffic has particular characteristics that distinguish it from many existing PETs.
-It makes a particularly useful observation: “The most frequent packet sizes in the Tor traffic dumps are, in descending order, 1500, −52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.”
+It makes a particularly useful observation: ``The most frequent packet sizes in the Tor traffic dumps are, in descending order, 1500, −52, −638, 52, 638 and 1150 bytes, accounting for 87.6\% of all Tor packets.''
 
-\subsubsection{Hidden Markov Model}
-
-Hidden Markov Models are first used as a traffic analysis technique in HMM profiles for network traffic classification \parencite{Wright:2004p3860}.
+Hidden Markov Models (HMMs) are first used as a traffic analysis technique in \emph{HMM profiles for network traffic classification} \parencite{Wright:2004p3860}.
 The primary identification characteristics for use with this algorithm are packet size and inter-packet arrival times.
@@
 HMMs are also used in \textcite{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
-
-\subsubsection{Clustering}
 
@@
 
-\subsubsection{Other Techniques}
-
 Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized Threshold \parencite{Crotti:2007p3824}.
@@
 
-\subsubsection{Comparing Techniques}
+\subsection{Comparing Techniques}
 
-It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \parencite{Kim:2007p3867}.
-However some attempt has been made at comparison in \textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
-\textcite{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
-
-An excellent meta study on traffic analysis techniques is presented in \textcite{Nguyen:2008p3837}.
-This paper compares many of the published papers, the techniques used, criteria analysed and how effectively they meet stated goals.
+It is difficult to say which technique would be most suitable for identifying Tor traffic.
+In the literature, no particular consensus has been reached and no two papers use the same baseline data set for their technique and so no comparison can be made \parencite{Kim:2007p3867}.
+Although there have been some comparisons of machine learning algorithms \parencite{Williams:2006p3849,Mohd:2009p6484}, no paper has published their data set due to privacy concerns.
+It is clear that choosing the right technique will require some experimentation and comparison of the effectiveness of each algorithm.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \center \includegraphics[scale=0.7]{network-diagram}
@@
 \end{figure}
+
+\subsection{Methodology}
+
+\subsubsection{Data Collection}
+
+The data collection phase will be conducted by running a series of simulations designed to mimic real world traffic.
+These simulations will be controlled so that the data captured will only contain Tor traffic in the training and testing data sets, and non Tor encrypted traffic in the data set for determining the false positive rate.
+
+\subsubsection{Algorithm Selection}
+
+Once the data collection phase is complete, a number of different algorithms will be chosen to classify Tor traffic.
+These will be compared using a number of criteria to rate effectiveness.
+These will include the accuracy of the matching technique and the number of packets needed to make a confident identification.
 

### 2010-08-22 bibliography/fix-papers.rb
Bibliography in subdir

@@ -1,0 +1,22 @@
+#!/usr/bin/ruby
+#
+# Papers outputs standard bibtex catalogs, which biblatex has some slight
+# trouble with
+#
+# 1.
+#
+# Biblatex prefers months in format {1} -> {12}
+# Bibtex uses months in abbrev {Jan} -> {Dec}
+#
+MONTHS = %w[Jan Feb Mar Apr May June July Aug Sept Oct Nov Dec]
+File.open(ARGV[0]) do |file|
+  file.each do |line|
+    matches = line.match(/month\s*=\s*\{([A-Za-z]+)\}/)
+    if matches #and MONTHS.include?(matches[1])
+      index = MONTHS.index(matches[1]) + 1
+      puts "#{line[0..(matches.offset(1)[0] - 1)]}#{index}#{line[(matches.offset(1)[1])..-1]}"
+    else
+      puts line
+    end
+  end
+end

### 2010-08-22 thesis/thesis.tex
Add in thesis files (renamed proposal for now)

@@
-\abstract The Internet is a powerful tool for publishing speech and opinion, for this reason it has significant implications for policial speech.
-Unfortunately this ability to speak out is being destroyed by an increasingly hungry powerful elite who attempt to stomp out political assent by any means necessary.
-Dissenters who publish their opinions using the internet are increasingly being identified and subject to imprisonment.
-Tools are available to hide provide levels of anonymity to such users, but these tools really provide anonymity?
-Can they provide anonymity in such regimes if they are easily distinguishable from normal traffic?
-This paper seeks to investigate the qualities of encrypted communications on the Internet and compare normal encrypted communications to those performed by anonymizing tools such as TOR and I2P.
-A number of simulations will be run with these applications and the traffic monitored to gather important information and characteristics.
-These will be compared to identify what characteristics make a particular application identifiable and what qualities are used for this identity.
-The aim of this research is to provide insight into what qualities other than data make an application uniquely identifiable, despite using strong encryption.
+\documentclass{ecuthesis}
+
+% For graphics
+\usepackage{graphicx}
+
+% Bibliography
+\bibliography{fullrefs,websites,patents,papers}
+
+% Setup the variables for the title page
+\title{Using traffic analysis to identify The Second Generation Onion Router}
+\author{John Barker}
+\department{School of Computer and Security Science}
+\school{Edith Cowan University}
+\degree{Computer Science (Honours)}
+\email{jebarker@our.ecu.edu.au}
+\studentid{0991300}
+\supervisor{Dr Christopher Bolan}
+\supervisor{Mr Peter Hannay}
+\supervisor{Mr Patryk Szewczyk}
+
+% Begin document
+\begin{document}
+\maketitle
+
+\begin{abstract}
+\thispagestyle{empty}
+
+Traditional attacks against anonymity providing systems aim to uncover the
+identities of those involved. However, a more likely goal of attackers is to
+block or degrade the network itself, discouraging participation and forcing
+vulnerable users to communicate using less secure means. Since anonymous
+networks operate on known protocols and employ strong encryption it is
+difficult to distinguish them from regular traffic. This proposal describes a
+method for identifying traffic belonging to anonymous networks by examining
+their communication patterns.
+
+\end{abstract}
+
+\chapter{Introduction}
+
+\section{Background}
+
+The Internet has revolutionised the political sphere in providing a platform
+for the publication of speech to a far greater audience than was ever available
+before digital communications systems \parencite{Bonchek:1997p3455}. The
+publication of less desirable political speech, criticism or challenging ideas
+still carries with it great risk, with numerous publications leading to arrest.
+This has spawned headlines such as \textcite{website:egypt-arrests},
+\citetitle{website:china-yahoo-torture}
+\parencite{website:china-yahoo-torture},
+\citetitle{website:vietnam-bloggers-arrested}
+\parencite{website:vietnam-bloggers-arrested},
+\textcite{website:iran-bloggers-arrested} and
+\citetitle{website:blogger-arrests} \parencite{website:blogger-arrests}. The
+Internet, like conventional media, is still vulnerable to censorship by
+oppressive governments and malicious attackers
+\parencite{Crandall:2007p6165,Karlin:2009p6166}.
+
+In response to these threats, a number of systems have been proposed which use
+various techniques, primarily cryptography and covering traffic, to provide
+censorship resistance and anonymity. The Second Generation Onion Router (Tor),
+is an anonymous network which uses a variant of Onion Routing, to provide low
+latency anonymous communications to a wide variety of Internet communications
+protocols \parencite{Dingledine:2004p314}. It also aims to provide resistance
+against censorship based blocking attempts \parencite{Dingledine:2008p1542}.
+
+Although Tor succeeds to a certain extent in these goals, it may be possible to
+use traffic analysis techniques to automatically identify Tor connections and
+target them for attacks. Since Tor relies on large numbers of users for the
+protections it provides, attacks that affect the reliability of the network can
+discourage participation, making it ineffective. This paper proposes a traffic
+analysis methodology for identifying Tor traffic which may be used for such
+attacks in the future.
+
+\section{Significance}
+
+Tor is one of the most successful and widely deployed anonymous networks, with
+around one thousand, eight hundred users at the time of writing
+\parencite{website:tor-anonymity-online}. While it has been the subject of many
+traffic analysis attacks, the primary objective has historically been the
+attempt to reveal participant identities: ``The principal objective of an
+adversary attacking an anonymous communication system is to link the initiators
+of connections with their respective communication partners and vice versa''
+\parencite[page 3]{Murdoch:2005p325}.
+
+The traffic analysis techniques proposed will attempt to classify network
+streams belonging to Tor users to distinguish them from regular encrypted
+communications. This research may provide a greater understanding of just
+how much anonymity a user of the Tor network is provided and inspire
+the development of countermeasures against analysis.
+
+\section{Research Questions}
+
+Given a motivated and universal attacker, it is inexpensive and straightforward
+to disconnect a user from these networks by blocking access to well known and
+published resources. Once these avenues of attack have been exhausted it is
+still possible to connect to the network by connecting to lesser known access
+points. Since these networks are capable of communicating using many of the
+same methods as most conventional Internet applications, a blanket ban on this
+kind of communication would be too broad and extensive.
+
+Tor employs strong encryption, the goal of which is to ensure that the data
+transmitted is indistinguishable from random noise. To an observer, data
+transmitted using encryption looks the same. Thus the traditional means of
+identifying these protocols are ineffective.
+
+This raises the question: is it possible to distinguish the traffic created by
+these networks, from encrypted traffic produced by conventional software? This
+question can be broken down further:
+
+\begin{enumerate*}
+  \item Can the traffic be classified using automated matching techniques?
+  \item Do these networks have characteristics that make them readily
+    distinguishable using heuristics based matching?
+  \item Do they have characteristics that make them distinguishable using a
+    machine learning technique?
+  \item How long does a user have to be
+    connected to the network before a confident match can be made?
+\end{enumerate*}
+
+\chapter{Literature Review}
+
+The main areas of research included papers and proposals on the design of
+anonymity networks and those covering the subject of traffic analysis.
+Particular attention has been paid to encryption as it is the primary function
+by which these systems operate and a good understanding is necessary for the
+development of an appropriate traffic analysis method.
+
+\section{Encryption}
+
+Since the creation of language, the interception of messages by hostile forces
+has compelled the development of secretive communications. This deliberate
+transformation of a message, so that only the intended recipient can understand
+it, is known as encryption. The process of examining these obfuscated messages
+and attempting to reverse the transformation is known as cryptanalysis
+\parencite{Schneier:1996uq}. These fields have been locked in an arms race
+ever since, each side continually advancing their capabilities in an attempt to
+gain ground.
+
+Apart from One Time Pads, no encryption methodology has ever proven to be
+unbreakable \parencite{Shannon:1948p6583}. This means that all remaining
+cryptographic methods are a way of transforming information, so that for an
+attacker the difficulty in reversing this transformation is too costly to make
+it worthwhile. The invention of robots and computers was precipitated by the
+need to break encryption methods of increasing complexity and at the same time
+has lead to the increasing complexity of encryption algorithms
+\parencite{Kahn:1974:C}.
+
+Historically, all encryption methods have required an interaction between those
+communicating. A meeting to exchange the secret communications key, or a
+courier to deliver the encryption device. This made anonymous communications
+difficult, especially when using digital communications technologies.  In
+\citeyear{Jevons:1874vn}, \citeauthor{Jevons:1874vn}, perhaps
+unknowingly, uncovered the mathematical techniques that would allow for public
+key cryptography in his publication \citetitle{Jevons:1874vn}. He recognised
+that certain mathematical operations yielded products that were impossible or
+difficult to reverse in order to uncover the factors used.
+
+The possibility of public key cryptography, or \emph{non-secret
+encryption} was conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and
+later developed into both a method for sharing secret encryption keys by
+Malcolm J. Williamson in 1974 \parencite{Singh:1999:CBE} and a method for
+asymmetric encryption \parencite{Cocks:1973p3265}.
+
+These papers were not published at the time due to their military
+classification, allowing these methods to be reinvented independently
+\parencite{Singh:1999:CBE}. The method for key sharing developed by Ellis
+later became known as the Diffie-Hellman key exchange
+\parencite{Diffie:1976p585}, while the method for asymmetric encryption is now
+known as RSA encryption, taking its name from the initials of its creators,
+Rivest, Shamir and Adleman \parencite{Rivest:1978p708}. Figure
+\ref{key-exchange} shows how discrete logarithms are used in the Diffie-Hellman
+algorithm to generate a shared encryption key.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{key-exchange}
+  \caption{Diffie-Hellman Key Exchange}
+  \label{key-exchange}
+\end{figure}
+
+% How to relate back to Tor:
+% What algorithm does Tor use
+% How does encryption resist traffic analysis
+% Modern encryption algorithms ensure resistance to frequency analysis by making sure every character in a message appears as likely as every other character.
+To an observer, this means that encrypted messages appear to be indistinguishable to noise.
+
+While these early public key encryption algorithms are still in use, newer
+implementations have appeared which make improvements including
+\textcite*{ElGamal:1985p529} and \textcite{Cramer:1998p3186}. Attempts to make
+these encryption algorithms more difficult to break have involved the use of
+increasingly complex mathematical problems such as elliptic curves
+\parencite{Miller:1986p2966,Koblitz:1987p3109} and probabilistic functions
+\parencite{Paillier:1999p3152}. Many of these encryption algorithms are
+available in modern encryption protocols.
+
+Early proposals for digital networks included extensive usage of encryption
+technology. \textcite{Baran:1964p384} suggested that future digital military
+networks should use encryption for all messages, even those that did not
+require any secrecy. He cited benefits such as tamper resistance, message
+secrecy and resistance to traffic analysis, although this system was never
+implemented. The Internet, was developed without encryption features
+\parencite{website:internet}.
+
+Early work in encrypted Internet communications includes the Secure Network
+Programming (SNP) applications programming interface (API)
+\parencite{Woo:1994p2532}. This was a simple framework providing numerous
+encryption, signing and authentication methods. The Secure Sockets Layer (SSL)
+is an encryption layer which provided end-to-end communications secrecy on the
+Internet \parencite{website:SSL}. A primary feature of SSL is the ability to
+exchange secret keys using public key algorithms.
+
+This proposed standard went through a number of revisions, with early versions
+suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
+Transport Layer Security, with the latest version 1.2 being released August
+2008 \parencite{website:TLS}. TLS addresses some issues in SSL and provides a
+number of enhancements, but is not compatible with SSL.
+
+The Hypertext Transfer Protocol Secure (HTTPS) provides encryption using both
+the TLS and SSL protocols \parencite{website:HTTPS} and is available in almost
+all modern web browsers including Firefox
+\parencite{website:firefox-encryption}, Safari
+\parencite{website:safari-features} and Internet Explorer
+\parencite{website:microsoft-tls}. Tor provides encryption through usage of the
+TLS protocol.
+
+\section{Anonymous and Censorship Resistant Networks}
+
+The first anonymous network system \emph{MixNet}, was described in
+\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
+encryption to prevent eavesdroppers from obtaining message delivery
+information. Senders in the network communicate with a centrally located server
+known as a \emph{mix}, delivering a message with the address of the intended
+recipient. The mix server discards any information about the sender and
+delivers it to the final destination. Figure \ref{chaums-mix-network} depicts
+the process of message delivery in Chaum's MixNet. Chaum's proposal also
+allowed for the chaining of multiple mix servers together to form a
+\emph{cascade}.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{chaums-mix-network}
+  \caption{MixNet Message Delivery}
+  \label{chaums-mix-network}
+\end{figure}
+
+Since the inception of MixNet, numerous anonymous networks have been proposed,
+each design being influenced by diverse motivations for obtaining anonymity.
+These include:
+
+\begin{itemize*}
+  \item Anonymous remailers such as \emph{Babel} \parencite{Gulcu:1996p1662}
+    and \emph{Mixminion} \parencite{Danezis:2003ys}.
+  \item Networks that provide mathematically provable anonymity
+    \parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303}.
+  \item Anonymity that degrades gracefully when subject to attack, so called
+    \emph{robust anonymity} \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
+  \item Anonymous publishing in \emph{Freedom} \parencite{Goldberg:1999p2231}
+    and \emph{Freenet} \parencite{Clarke:2001p2435}.
+  \item Peer to Peer (P2P) anonymity such as \emph{MorphMix}
+    \parencite{Rennhard:2002p4559}, \emph{Tarzan} \parencite{Freedman:2002kx} and
+    \emph{P5} \parencite{P5Sherwood:2005p5872}.
+  \item Censorship resistance in \emph{aChord} and \emph{gnuNet}
+    \parencite{Hazel:2002p6929}, \emph{Infranet} \parencite{Feamster:2002p307}
+    and of course Tor.
+\end{itemize*}
+
+This is by no means an exhaustive list, for an excellent survey of anonymous
+networks consult \textcite{Danezis:2008p346}.
+
+Although this research has yielded a variety of designs, all anonymous
+networks essentially operate on all or some of the following principles:
+
+\begin{itemize*}
+  \item Encrypting traffic to prevent eavesdropping.
+  \item Providing covering traffic through a network of active users or by
+    generating it automatically.
+  \item Normalizing message delivery so that individual communication patterns
+    are not identifiable.
+\end{itemize*}
+
+In theory, the normalization techniques used by anonymous networks should make
+them readily distinguishable from non anonymous communications.
+
+\subsection{The Second Generation Onion Router (Tor)}
+
+Tor was first described in \citetitle{Dingledine:2004p314}
+\parencite{Dingledine:2004p314}. This new generation of onion router was
+designed with a number of defences for common traffic analysis attacks and
+weaknesses discovered in other proposals. With a focus on deployability,
+usability, flexibility and simple-design \parencite[p. 3-4]{Dingledine:2004p314}
+as well as a successful implementation, it has seen wider deployment than most
+other anonymous networks.
+
+Like MixNet, public key cryptography is combined with intermediate servers
+responsible for message delivery to provide a degree of anonymity. In Tor,
+these mixes are known as \emph{relays} and are typically chained together to
+construct a \emph{circuit}. Clients connect to the Tor network by communicating
+with a special relay known as a \emph{bridge}, which constitutes the first
+relay in a circuit. Traffic is repeatedly delivered through relays until it
+reaches another special relay known as an \emph{exit node}, where it is
+delivered unencrypted to the final destination. Figure \ref{tor-network} shows
+this typical usage of the Tor network.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
+  \caption{The Tor Network}
+  \label{tor-network}
+\end{figure}
+
+Messages delivered through the Tor network are encrypted multiple times using a
+variation of onion routing \parencite{Michael:2001} known as \emph{telescopic
+onion routing}. Circuits are built incrementally, obtaining a session key from
+each successive relay in the circuit and encrypting messages so that
+intermediate relays are unable to decrypt the message. Since circuits can take
+some time to build, they are pre-emptively created at regular intervals
+\parencite[p. 5]{Dingledine:2004p314}. Although Tor does not support many of
+the traffic normalization techniques that provide strong anonymity, messages
+passed through the Tor network are packaged in \emph{cells} of a fixed size of
+512 bytes \parencite[p. 5]{Dingledine:2004p314}. Tor also provides application
+level filters that remove identifying features from common application
+protocols.
+
+After it was noticed that Tor was being used to circumvent censorship as well
+as for anonymity, a publication was released which attempts to identify the
+issues that need to be addressed in order for Tor to provide some level of
+censorship resistance \parencite{Dingledine:2008p1542}. Although this paper
+foresees future attacks such as the one contained in this proposal, it mostly
+tackles social issues of censorship resistance.
+
+\section{Traffic Analysis}
+
+Research into Tor weaknesses has included the use of hostile exit nodes to
+capture private information \parencite{website:tor-password-leak}, attacks that
+take advantages of web based technologies such as Javascript and Flash to
+reveal user's identities \parencite{Abbott:2007p298} and a number of identity
+revealing traffic analysis techniques
+\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}. Notable is the
+discovery of a method for identifying bridge operators as discussed in
+\textcite{McLachlan:2009p197}. This attack takes advantages in weaknesses of
+the Tor protocol to enumerate bridges and some approaches to mitigation are
+suggested. It is believed that this is the first proposal of a traffic analysis
+technique for classification of Tor network streams.
+
+When considering the use of traffic analysis for classification of Internet
+communications, three techniques are used. These are: exact matching, heuristic
+matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
+techniques recognise properties of communications that mirror known protocols
+and communication patterns. This might include the port an application uses or
+the format of its payload. Since Tor employs strong encryption and communicates
+using known and commonly used protocols, exact matching techniques would prove
+ineffective for classification. Heuristic matching looks for patterns in
+conversations to determine communications patterns and infer relationships,
+while machine learning involves the use of statistics to train computer
+algorithms to classify traffic. Both heuristic and machine matching techniques
+are suitable for traffic analysis of anonymous networks because they do not
+rely on analysing the content of messages.
+
+\subsection{Heuristic Techniques}
+
+The increasing burden of peer to peer (P2P) applications on campus networks,
+and their shift to encryption motivated the development of heuristics based
+techniques for identifying P2P traffic. Early techniques include identifying
+known properties of P2P networks such as often communicating using both the UDP
+and TCP protocols simultaneously and using a solitary connection to transfer
+high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
+number of false positives by eliminating packets that matched known
+communications protocols.
+
+Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
+\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
+through early elimination of false positives and by expanding the scope of
+matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
+to identify P2P nodes before applying a secondary heuristic to identify
+‘supernodes’ which are a subset of all P2P nodes.
+
+Classifying traffic based on system roles is a key feature of the technique
+that appears in \citetitle{Karagiannis:2005p6359}
+\parencite{Karagiannis:2005p6359}. By analysing communications at the host
+level then at increasing levels of granularity, a greater level of accuracy is
+achieved.
+
+The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
+\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
+flows are represented in a TDG, mathematical properties of the flow can be
+analysed to make positive identifications.
+
+Viruses have also posed a problem for network administrators, often
+over-utilizing network resources and using the network to infect new machines.
+A technique for identifying various worms was proposed in
+\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
+from network administrators to avoid detection, presenting the same problems of
+identification as Tor network traffic.
+
+\subsection{Machine Learning Techniques}
+
+\subsubsection{Expectation-Maximisation}
+
+The first use of machine learning to categorise traffic flows appears in
+\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
+be used for machine learning and an attempt at coarse grained classification
+using an expectation-maximisation (EM) algorithm are demonstrated. The
+expectation-maximisation algorithm is a method for finding probabilistic
+estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
+same technique is also demonstrated in \textcite{Soule:2004p3817} using
+histograms for finer grained classification.  The EM algorithm is again used in
+\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
+comparing EM favourably against a Na\"{i}ve Bayes classifier.
+
+\subsubsection{Na\"{i}ve Bayes}
+
+\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
+flows that have previously been sorted into groups by analysing the flow
+content. This paper focuses on many of the most commonly used Internet
+protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
+identifying traffic belonging to the Skype application.
+
+\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
+websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+This technique performed poorly when applied to the Tor network, but it
+suggests that Tor traffic has particular characteristics that distinguish it
+from many existing PETs. It makes a particularly useful observation: ``The most
+frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
+−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
+
+\subsubsection{Markov Models}
+
+Hidden Markov Models (HMM) are a statistical modelling technique useful
+for classification of systems with an unobservable state
+\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
+technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
+primary identification characteristics for use with this algorithm are packet
+size and inter-packet arrival times. With refinement this algorithm is used
+with increasing accuracy in \textcite{Wright:2006p322} and
+\textcite{Dainotti:2008p1435}.
+
+In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
+discover distinguishing characteristics of traffic flows, rather than with a
+specific set of classification goals. This information is used to build HMMs
+for the purpose of traffic classification.
+
+Since HMMs model particular behaviours, they can be used to recognize
+deviations from normal behaviour as shown in
+\textcite{EstevezTapiador:2003p7201}. Motivated by
+\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
+flags and the position of individual packets in a stream to train an Observable
+Markov Model for traffic classification, achieving greater classification
+accuracy than \citeauthor{Bernaille:2005p6205}.
+
+\subsubsection{Clustering}
+
+Clustering algorithms group observations into subsets based on similar
+characteristics, they are a form of unsupervised learning technique designed to
+discover organization in unlabelled data sets. They have been the basis of a
+number of traffic classification techniques with the K-Means clustering
+technique being the most prominent.  K-Means cluster analysis appears in
+\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
+\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
+Applications with Noise (DBSCAN) algorithm appears in
+\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
+
+\subsubsection{Other Techniques}
+
+Other algorithms used for traffic classification include Nearest Neighbour and
+Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
+Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
+to identify applications and identities inside SSH tunnels was demonstrated in
+\textcite{Dusi:2008p6254}. Several algorithms are compared in
+\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
+for identifying Skype and SSH traffic.
+
+\subsubsection{Comparing Techniques}
+
+It is difficult to say what machine learning technique is the most effective as
+no consensus has been reached, the literature covers a wide variety of
+techniques each with vastly different goals and no two techniques can be
+directly compared as the data used for analysis has not been disclosed
+\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
+\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
+greatest performance and accuracy when compared to a number of Bayesian
+algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
+algorithms  to find random tree, IBI, IBK and random forest algorithms
+obtaining the greatest classification accuracy.
+
+An excellent meta study on traffic analysis techniques is presented in
+\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
+the techniques used, criteria analysed and how effectively they meet stated
+goals.
+
+\chapter{Theoretical Framework}
+
+The proposed research will use a methodology typical of machine learning
+traffic analysis papers, substituting data captured from a controlled
+simulation in place of live network captures.
+
+The experiment will be conducted in two phases, the first being a data
+collection phase. The second phase will include a quasi experimental
+methodology which may include data manipulation techniques to prepare the
+collected data and a comparison of various heuristics and machine learning
+based traffic analysis to classify the collected data.
+
+\section{Assumptions}
+
+It is assumed that the usage patterns exhibited by individual users will be
+smaller than the communications characteristics that will lead to the
+identification of anonymous and censorship resistant networks. Thus there is no
+need to obtain a large sample of regular network traffic from varying user
+profiles.
+
+As of the current implementation, Tor network traffic is readily
+distinguishable by looking at the handshake packets. It is likely that this
+weakness will be addressed in a future version of the Tor protocol as it is
+recognised as a design goal in \textcite{Dingledine:2008p1542}. For this
+reason, this proposal focuses on traffic analysis techniques that are content
+agnostic.
+
+\section{Variables}
+
+The data capturing stage will be affected by a number of variables that will
+influence the accuracy of the chosen matching algorithms.
+
+\subsection{Quality of the Anonymous Network}
+
+An individual connection to the Tor network traverses a number of nodes to
+create a circuit. The path a circuit uses is first defined by the exit node,
+then chosen based on a number of constraints with a preference for high
+bandwidth relays \parencite{website:tor-path-selection}. Since each connection
+uses a different circuit and bandwidth demands are constantly changing, it is
+difficult to predict the composition of a Tor circuit.
+
+This means that any individual Tor circuit could be composed of systems with
+differing capabilities, network throughput and configuration.
+
+For testing purposes, the Tor network can be simulated on a small isolated
+network. This will eliminate a lot of the variability that comes from
+monitoring the real Tor network. Factors that affect the quality of the network
+can be controlled by limiting the number of competing network applications,
+controlling the number of running Tor instances and ensuring a consistent
+configuration across all nodes.
+
+\subsection{System Performance}
+
+The ability of Tor to route packets in a timely fashion is highly dependent on
+the performance of the system it is executing on. This is greatly compounded by
+the usage of strong encryption which is computationally expensive. Packet
+latency is one of the key parameters used in traffic classification techniques.
+Performance related variables include:
+
+\begin{itemize*}
+  \item CPU speed and number of cores
+  \item RAM speed and amount
+  \item Performance of integrated components, system bus etc.
+  \item Hard disk size, access time and throughput
+  \item Installed and running applications
+  \item System configuration
+\end{itemize*}
+
+To remedy this, the systems used to simulate the Tor network should be made
+uniform. This means an identical hardware and software configuration for all
+systems in the simulation network.
+
+In addition it is noted that system performance can degrade over time due to
+both memory and hard disk fragmentation. This can be avoided by running the
+simulations in a virtualisation environment that support snapshots, rolling
+back to a known configuration point after each test.
+
+\subsection{Network Performance}
+
+Like system performance, latency is also dependent on the quality of the
+network. Network switching equipment has limited resources for routing packets
+and competing network traffic can introduce congestion which would radically
+alter the observable communications patterns \parencite{Jacobson:1995p6768}.
+Tor also supports congestion mitigation techniques which alter communication
+patterns \parencite[p. 8]{Dingledine:2004p314}.
+
+Latency and network performance over the Internet are highly variable and
+beyond the control of any one individual. Usage patterns vary according to
+geographic region, societal conventions and the period in which they occur
+\parencite{Thompson97wide-areainternet,Ken03longitudinalstudy}. The Internet,
+and by necessity the public Tor network are globally distributed, which means
+that circuits traverse a large variety of unpredictable network conditions. By
+isolating the test network, these variables can be controlled ensuring low
+latency high bandwidth communications or congestion as necessary.
+
+\subsection{Application Protocol}
+
+Tor provides communications facilities to a number of Internet enabled
+applications by providing an interface using the SOCKS protocol \parencite[p.
+17]{Dingledine:2004p314}. This means that the Tor network can proxy regular web
+browsing, email or any other TCP or UDP based communication protocol
+\parencite{website:socks}. Each of these application protocols have their own
+distinguishing communications characteristics which will influence the matching
+algorithm. It is not yet clear how transparent the Tor network will be
+regarding these characteristics and thus, for the purposes of classification a
+single protocol should be chosen.
+
+\subsection{Caching}
+
+Both web browsers and web servers are designed for high performance and often
+cache requests so that they can be delivered faster in the future
+\parencite{Caceres:1998p7419}. While this is a normal part of communications
+traffic and should be considered, it is important that both regular and cached
+requests appear uniformly across all experiments. Manually flushing the cache
+or rolling back to a known virtual machine snapshot between each simulation can
+ensure this outcome.
+
+\chapter{Materials and Methods}
+
+\section{Equipment Requirements}
+
+The following list describes computer systems and hardware required to run the
+data capture simulations:
+
+\begin{itemize*}
+  \item 1 Computer system running web browser and Tor
+  \item 1 Computer running packet sniffing software
+  \item N Computer systems running Tor, configured as bridges
+  \item 1 Computer running web server and Tor directory server
+  \item Cat 5 cable to connect all computer systems
+  \item Network Hub or Switch capable of disabling ‘learning’
+    \parencite{website:hub-reference}
+\end{itemize*}
+
+The computer systems running Tor bridges represent the simulation network.
+Although it is feasible to have a single system representing the simulation
+network the combined system load may be too great and introduce  excessive
+latency.
+
+Packet capture is a performance intensive application, one machine should be
+reserved for this application. It must include adequate disk space, preferably
+of a high speed.
+
+The required software includes:
+
+\begin{itemize*}
+  \item Virtualisation software
+  \item Web browser
+  \item Tor
+  \item Packet capture software
+\end{itemize*}
+
+\section{Procedure}
+
+\subsection{Phase 1}
+
+\subsubsection{Hardware Configuration}
+
+All systems will be configured and connected to the same isolated network
+through the hub as shown in Figure \ref{physical-setup}.
+
+\begin{figure}[H]
+  \centering\includegraphics[scale=0.6]{physical-setup}
+  \caption{Physical Setup}
+  \label{physical-setup}
+\end{figure}
+
+\subsubsection{Software Configuration}
+
+Software is installed and configured on all machines. The simulation network is
+configured to use the private Tor directory server rather than the public ones
+specified by default \parencite{website:private-tor-network}.
+
+The packet sniffer is configured to capture only the packets relevant for each
+data set.
+
+Figure \ref{network-diagram} shows the placement of applications and relevant
+data flows.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{network-diagram}
+  \caption{Network Diagram}
+  \label{network-diagram}
+\end{figure}
+
+\subsubsection{Simulations}
+
+To provide a large training set, capture traffic can be generated by a series
+of automated simulations. This stage of the research will include identifying a
+number of commonly used websites and other hosts that employ TLS encryption,
+and simulating these on the test network through mirroring or other means. This
+will include selection of tools to assist in automating this process.
+
+\subsubsection{Data Capture}
+
+Three sets of data must be collected, and kept separate. The first set is a
+sample that is known to belong to the anonymous networks in question. To
+capture this the software will be configured to communicate using known
+parameters. It will also be ensured that no other applications are
+communicating using these parameters that may pollute the data set.
+
+This first set of data can be partitioned to make the second set, which will be
+used to confirm the false negative rate of the matching technique.
+
+The third set of data must constitute traffic that is known to not contain any
+traffic from the networks being catalogued. This data set will be used to
+confirm the rate of false positives.
+
+\subsection{Phase 2}
+
+\subsubsection{Data Preparation}
+
+The captured data will be in the data file format used by the capture software.
+For analysis the most relevant information needs to be retrieved from the data
+files and prepared in a suitable format for the matching algorithm. This stage
+of the research includes identifying the attributes of the captured data that
+would be most suitable for analytical purposes, and providing them in a format
+suitable for processing by an automatic classifier.
+
+\subsubsection{Analysis}
+
+The training data set will be supplied to the algorithm for training purposes.
+Once training is complete, this algorithm can be tested against the
+confirmation data set to obtain the rate of false negatives. The regular
+traffic will be used to determine the false positive rate. This allows the
+construction of the Receiver Operating Characteristic (ROC) curve, a
+measurement of the performance of the matching algorithm.
+
+\section{Limitations}
+
+The process has been designed with the goal of minimising variables that may
+affect matching performance. This is unusual for traffic analysis papers which
+typically sample real world traffic in large volumes. In the case of a machine
+learning technique, this may bias the chosen algorithm against real world data,
+making it impractical for any real world use.
+
+\section{Schedule}
+
+\begin{tabular}{llr}
+  \toprule
+  Activity & Duration & Date \\
+  \midrule
+  Phase 1 \\
+  1 - Design simulations & 4 weeks \\
+  2 - Setup test network & 1 week \\
+  3 - Configure simulations & 1 week \\
+  4 - Perform simulation and data capture & 8 weeks \\
+  Phase 2 \\
+  1 - Examination of data & 2 weeks \\
+  2 - Data preparation & 4 weeks \\
+  3 - Algorithm training & 1 week \\
+  4 - Algorithm selection and comparison & 8 weeks \\
+  5 - Algorithm tailoring and tuning & 8 weeks \\
+  6 - Document final results & * \\
+  \midrule
+  Thesis submission & & December 4th, 2011 \\
+  \bottomrule
+\end{tabular}
+
+* Till submission date or completion.
+
+\printbibliography[title=REFERENCES]
+
+\end{document}
+
+% vim: fdm=syntax wrapmargin=80

### 2010-08-22 thesis/build.sh
Something weird going on, only works with ?= in .ini and defined in environment as well.

@@ -1,0 +1,3 @@
+#!/bin/bash
+export BIBINPUTS=".:../bibliography//"
+make

### 2010-08-28 thesis/experiment.tex
Description of experiment

\chapter{Experiment}

Several systems are configured and installed using the Ubuntu operating system with VirtualBox installed. The systems are:

Lankiveil 192.168.0.16
Client system
Ginaz 192.168.0.17
Web hosting system

Ginaz
Ginaz hosts a number of web site simultions. These include a series of static web sites with different configuration combinations, representing available web tools and technologies. \cite

These sites are hosted using a self signed SSL certificate \cite, although most commercial sites would not use a self signed certificate, it should not have any bearing on the communications fingerprint \cite.

Controls
Web server:
  Apache
  Nginx
Web site:
  Static(1-20)
  Random
Method:
  SSL
  Tor
  SSL over Tor
Clients:
  Selenium firefox
  Curl

Lankiveil 
Lankiveil executes a basic ruby script which runs a number of simulations:
\begin{itemize*}
  \item RSpec tests that go through selenium scripts, simulating user interaction, by mimicking user interactions with a web site through the Firefox browser.
  \item Automated fetching of websites using the Curl program.
\end{itemize*}

Corrin 192.168.0.18
Is the control system, it monitors packets and ensures the simulation is running. tcpdump is configured on this system to monitor ports that have been configured for encrypted traffic.

### 2010-10-24 special-topic/paper.tex
Beginning of special topic paper

--- 2010-04-25 conference-paper/proposal.tex
@@
-\documentclass{conference}
+\documentclass{ecuthesis}
 
@@
 % Bibliography
-\bibliography{papers,websites,patents}
+\bibliography{fullrefs,websites,patents,papers}
 
-% Begin document
 \begin{document}
@@
 
-\begin{abstract}
-
-Traditional attacks against anonymous systems aim to uncover the identities of those involved.
-However, a more likely goal of attackers is to block or degrade the network itself, discouraging participation and forcing vulnerable users to communicate using less secure means.
-Since anonymous networks operate on known protocols and employ strong encryption it is difficult to distinguish them from regular traffic.
-This proposal describes a method for identifying traffic belonging to anonymous networks by examining their communication patterns.
-
-\end{abstract}
-
-\section{Introduction}
-
-The Internet has revolutionised the political sphere in providing a platform for the publication of speech to a far greater audience than was ever available before digital communications systems \citep{Bonchek:1997p3455}.
-The publication of less desirable political speech, criticism or challenging ideas still carries with it great risk, with numerous publications leading to arrest.
-This has spawned headlines such as \emph{Egypt arrests another blog critic} \citeyear{website:egypt-arrests}, \emph{Chinese couple sue Yahoo!
-in US over torture case} \citep{website:china-yahoo-torture}, \emph{Vietnam bloggers arrested over China shirt protest} \citep{website:vietnam-bloggers-arrested}, \emph{23 Journalists/Bloggers Arrested in Iran, Including Head of Top Group} \citeyear{website:iran-bloggers-arrested} and \emph{Blogger Arrests} \citep{website:blogger-arrests}.
-The Internet, like conventional media is still vulnerable to censorship by oppressive governments and malicious attackers \citep{Crandall:2007p6165,Karlin:2009p6166}.
-
-In response to these threats, a number of systems have been proposed which use cryptography to provide censorship resistance and anonymity, including The Second Generation Onion Router (Tor).
-Tor is an anonymous network which uses Onion Routing to provide low latency anonymity to network participants \citep{Dingledine:2004p314}.
-It also aims to provide resistance against censorship based blocking attempts \citep{Dingledine:2008p1542}.
-
-Although Tor provides censorship resistance and a certain amount of privacy, it may be possible to use traffic analysis techniques to automatically identify Tor connections and target them for attacks.
-Since Tor relies on large numbers of users for the protections it provides, attacks that affect the reliability of the network can discourage participation, rendering it`s protections useless.
-This paper proposes a statistical methodology for identifying Tor traffic which may be used for such attacks in the future.
-
-\section{Significance}
-
-Tor`s availability, unrestrictive license and platform portability has made it a popular anonymous network with around one thousand eight hundred users at the time of writing \citep{website:tor-anonymity-online}.
-It has been the subject of many technical papers proposing traffic analysis attacks, however the primary objective has historically been attacks that reveal the identity of participants.
-As stated in \citet{Murdoch:2005p325} ``The principal objective of an adversary attacking an anonymous communication system is to link the initiators of connections with their respective communication partners and vice versa''.
-
-The traffic analysis techniques proposed will attempt to classify network streams belonging to Tor users to distinguish them from regular encrypted communications.
-
-\section{Research Questions}
-
-The ability of Tor to connect on any port and it`s usage of strong encryption mean that recognizing traffic belonging to Tor is not straightforward.
-However it is possible that the communications patterns exhibited by Tor nodes are recognizeable using statistical methods.
-This raises the question: is it possible to distinguish the traffic created by these networks, from encrypted traffic produced by conventional software?
-This question can be broken down further:
-
-\begin{enumerate*}
-\item Can the traffic be classified using automated matching techniques?
-\item Do these networks have characteristics that make them readily distinguishable using heuristics based matching?
-\item Do they have characteristics that make them distinguishable using a machine learning technique?
-\item How long does a user have to be connected to the network before a confident match can be made?
-\end{enumerate*}
-
-\section{Background Information}
-
-The first anonymous network system was proposed in \citet{Chaum:1981p296}.
-This proposal included the use of public key cryptography and a centrally located server known as a `mix'.
-By wrapping the information and address of a destination in a message and encrypting it with the mix`s public key, only the mix system is able to read the message.
-
-Onion routing was first described in a patent by \cite{Michael:2001}.
-Like the mix network is uses public key cryptography to provide anonymity, it differs in that messages are repeatedly encrypted then passed through several nodes in a network known as onion routers.
-Each of these routers is capable of removing a single layer of encryption to reveal delivery instructions.
-This layering prevents individual nodes obtaining the identity of the sender, receiver and the contents of the message.
-
-\subsection{The Second Generation Onion Router (Tor)}
-
-The Second Generation Onion Router (Tor) uses a form of Onion Routing 
-The Tor network, like the Mix-Net proposed by \citet{Chaum:1981p296} uses public key encryption and cascades of servers to ensure message anonymity \citep{Dingledine:2004p314}.
-In Tor these mixes are known as ‘relays’.
-Relays that allow connections directly from Tor clients are known as ‘bridges’ and relays that deliver messages from the frontier of the Tor network are known as ‘exit nodes’.
-Figure \ref{tor-network} shows how a client connects to the Tor network.
-
-\begin{figure}[H]
-\center \includegraphics{tor-network-diagram}
-\caption{The Tor Network}
-\label{tor-network}
-\end{figure}
-
-When a relay joins the Tor network, it trades symmetric cipher keys with its neighbours using public key cryptography.
-These keys are used to encrypt communications and are destroyed when the session is closed to prevent replay attacks.
-
-After it was noticed that Tor was being used to circumvent censorship as well as for anonymity, a proposal was developed to improve its blocking resistance \citep{Dingledine:2008p1542}.
-Many of the suggestions in this proposal have been implemented, but many still remain.
-
-\section{Related Work}
-
-When considering the use of traffic analysis for Internet communications, three primary techniques are used.
-These are: exact matching, heuristic matching and machine learning \citep{Zhang:2009p1188}.
-Exact matching techniques are ineffective in recognizing Tor communications as Tor can operate on any available port and uses encryption to hide communications.
-This leaves heuristic and machine learning matching techniques.
-
-\subsection{Heuristic Techniques}
-
-The increasing burden of peer to peer (P2P) applications on campus networks, and their shift to encryption motivated the development of heuristics based techniques for identifying P2P traffic.
-Early techniques include identifying known properties of P2P networks such as often communicating using both the UDP and TCP protocols simultaneously and using a solitary connection to transfer high volumes \citep{Karagiannis:2004p6400}.
-Similar techniques have been developed in \citep{Perenyi:2006p6325} and \citep{John:2008p1376}, both of which attempt to improve matching accuracy by expanding the scope of matching parameters and eliminating false positives using exact matching techniques.
-
-Heuristics based matching techniques have also been used to identify traffic belonging to network worms \citep{Lazarevic:2003p6450} and the Skype protocol \citep{Ehlert:2006p2396}.
-
-\subsection{Machine Learning Techniques}
-
-\subsubsection{Expectation-Maximisation}
-
-The first use of machine learning to categorise traffic flows appears in \citet{McGregor:2004p3826}.
-A detailed analysis of the attributes that can be used for machine learning and an attempt at coarse grained classification using an Expectation-Maximisation (EM) algorithm are demonstrated.
-The same technique is also demonstrated in \citet{Soule:2004p3817} using histograms for finer grained classification.
-The EM algorithm is again used in \citet{Zander:2005p6212} and \citet{Erman:2006p3825}, with the latter also comparing this algorithm favourably against a Naïve Bayes classifier.
-
-\subsubsection{Naïve Bayes}
-
-\citet{Moore:2005p3827} use a supervised Naïve Bayes to classify traffic flows that have previously been sorted into groups by analysing the flow content.
-This paper focuses on many of the most commonly used Internet protocols while \citet{Bonfiglio:2007p6453} uses the technique for identifying traffic belonging to the commercial Skype application.
-
-\citet{Herrmann:2009p1189} use Bayesian networks to fingerprint visited websites accessed through Privacy Enhancing Technologies (PET), including Tor.
-This technique performed poorly when applied to the Tor network, but it suggests that Tor traffic has particular characteristics that distinguish it from many existing PETs.
-It makes a particularly useful observation: “The most frequent packet sizes in the Tor traffic dumps are, in descending order, 1500, −52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.”
-
-\subsubsection{Hidden Markov Model}
-
-Hidden Markov Models are first used as a traffic analysis technique in HMM profiles for network traffic classification \citep{Wright:2004p3860}.
-The primary identification characteristics for use with this algorithm are packet size and inter-packet arrival times.
-With refinement this algorithm is used with increasing accuracy in \citet{Wright:2006p322} and \citet{Dainotti:2008p1435}.
-HMMs are also used in \citet{Bernaille:2005p6205} to discover distinguishing characteristics of traffic flows, rather than specifically as a classifier.
-
-\subsubsection{Clustering}
-
-Clustering algorithms group observations into subsets based on similar characteristics.
-They have been used in a number of traffic classification techniques with the K-Means clustering technique being the most prominent.
-K-Means cluster analysis appears in Bernaille et al.
-(2006), \citet{Erman:2007p3764}, \citet{Erman:2007p6206}.
-The use of the Density Based Spatial Clustering of Applications with Noise (DBSCAN) algorithm appears in \citet{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
-
-\subsubsection{Other Techniques}
-
-Other algorithms used for traffic classification include Nearest Neighbour and  Linear Discriminant Analysis \citep{Roughan:2004p3823}, Normalized Threshold \citep{Crotti:2007p3824}.
-The use of the Gaussian Mixture Model to identify applications and identities inside SSH tunnels was demonstrated in \citet{Dusi:2008p6254}.
-
-\subsubsection{Comparing Techniques}
-
-It is difficult to say what machine learning technique is the most effective as no consensus has been reached, the literature covers a wide variety of techniques each with vastly different goals and no two techniques can be directly compared as the data used for analysis has not been disclosed \citep{Kim:2007p3867}.
-However some attempt has been made at comparison in \citet{Williams:2006p3849} which suggests that the C4.5 algorithm has the greatest performance and accuracy when compared to a number of Bayesian algorithms.
-\citet{Mohd:2009p6484} compares thirty machine learning algorithms  to find random tree, IBI, IBK and random forest algorithms obtaining the greatest classification accuracy.
-
-An excellent meta study on traffic analysis techniques is presented in \citet{Nguyen:2008p3837}.
-This paper compares many of the published papers, the techniques used, criteria analysed and how effectively they meet stated goals.
-
-\section{Theoretical Framework}
-
-The proposed experiment will employ a quasi-experimental research method, employing techniques common to traffic analysis papers.
-This includes the capturing of packet traces, development of a matching technique/algorithm and documentation of efficacy and results.
-The first phase of the experiment covers the data capturing phase, while the second phase concludes the traffic analysis technique.
-
-\subsection{Assumptions}
-
-It is assumed that the usage patterns exhibited by individual users will be smaller than the communications characteristics that will lead to the identification of anonymous and censorship resistant networks.
-Thus there is no need to obtain a large sample of regular network traffic from varying user profiles.
-
-As of the current implementation, Tor network traffic is readily distinguishable by looking at the handshake packets.
-It is likely that this weakness will be addressed in a future version of the Tor protocol as it is recognised as a design goal in \citet{Dingledine:2008p1542}.
-For this reason, this proposal focuses on traffic analysis techniques that are content agnostic.
-
-\subsection{Variables}
-
-The data capturing stage will be affected by a number of variables that will influence the accuracy of the chosen matching algorithms. These include:
-
-\begin{enumerate*}
-\item System Performance
-\item Network Performance
-\item Application Protocol
-\item Quality of the Anonymous Network
-\item Caching
-\end{enumerate*}
-
-An attempt will be made to reduce the impact of these variables by capturing packets generated by an isolated simulation of the Tor network, ensuring only vital network applications are running and executing software inside a virtual machine which can be rolled back to a known snapshot \citep{website:snapshot-definition}.
-
-\section{Materials and Methods}
-
-The experiment will consist of two phases, first a simulation phase which involves the capture of packets belonging to a Tor network, the second will be a comparison and documentation of the results of using several techniques to identify Tor traffic.
-
-Figure \ref{network-diagram} shows the placement of applications and relevant data flows for the simulation phase.
-
-\begin{figure}
-\center \includegraphics[scale=0.7]{network-diagram}
-\caption{Network Diagram}
-\label{network-diagram}
-\end{figure}
+\input ../thesis/experiment
 
@@
 
-% vim: fdm=syntax
+% vim: fdm=syntax wrapmargin=80

### 2010-10-24 special-topic/paper.tex
Work on special topic paper, experiment notes, minted syntax highlighting, fix to thesis class

@@
 
+% Setup the variables for the title page
+\title{Using traffic analysis to identify The Second Generation Onion Router}
+\author{John Barker}
+\department{School of Computer and Security Science}
+\school{Edith Cowan University}
+\degree{Computer Science (Honours)}
+\email{jebarker@our.ecu.edu.au}
+\studentid{0991300}
+\supervisor{Dr Andrew Woodward}
+\supervisor{Mr Peter Hannay}
+\supervisor{Mr Patryk Szewczyk}
+
 \begin{document}
-{\center \Large \bfseries \MakeUppercase{Using traffic analysis to identify Tor} \par}
+\maketitle
 
-{ \center
-  \begin{tabular*}{\textwidth}{cccc}
-  John Barker & Peter Hannay & Christopher Bolan & Patryk Szewczyk \\
-  jebarker@our.ecu.edu.au & p.hannay@ecu.edu.a & c.bolan@ecu.edu.au & p.szewczyk@ecu.edu.au \\
-  \end{tabular*}
-}
+\chapter{Introduction}
+
+\section{Background}
+
+This document describes the procedures for configuring a small network of
+computer systems to emulate a small sample of web based traffic using both the
+HTTPS protocol and the Tor protocol. All traffic between the systems is captured
+for the purpose of traffic analysis.
 
 \input ../thesis/experiment
+
+\chapter{Appendix}
+
+\section{Manager Script}
+\inputminted{ruby}{../experiment/simulation/manager/run_simulation.rb}
+
+\section{Client Script}
+\inputminted{ruby}{../experiment/simulation/client/client.rb}
+
+\section{Selenium-RC Script}
+\inputminted{bash}{../experiment/simulation/client/selenium-rc-with_tor.sh}
+
+\section{Selenium-RC Script (with Tor)}
+\inputminted{bash}{../experiment/simulation/client/selenium-rc.sh}
+
+\section{Hosts file}
+\inputminted{bash}{../experiment/hosts}
+
+\section{Apache Site Configuration}
+\inputminted{apacheconf}{../experiment/simulation/site/000-default-ssl}
+
+\section{Tor Setup Script}
+\inputminted{bash}{../experiment/simulation/tor/make_private_network.sh}
+
+\section{Tor Running Script}
+\inputminted{bash}{../experiment/simulation/tor/run_private_network.sh}
 
@@
 
-% vim: fdm=syntax wrapmargin=80
+% vim: fdm=syntax

### 2010-10-24 thesis/experiment.tex
Work on special topic paper, experiment notes, minted syntax highlighting, fix to thesis class

@@
-\chapter{Experiment}
+\section{Hardware Configuration}
 
-Several systems are configured and installed using the Ubuntu operating system with VirtualBox installed. The systems are:
+All systems will be configured and connected to the same isolated network
+through the hub as shown in Figure \ref{physical-setup}.
 
-Lankiveil 192.168.0.16
-Client system
-Ginaz 192.168.0.17
-Web hosting system
+\begin{figure}[H]
+  \centering\includegraphics[scale=0.6]{physical-setup}
+  \caption{Physical Setup}
+  \label{physical-setup}
+\end{figure}
 
-Ginaz
-Ginaz hosts a number of web site simultions. These include a series of static web sites with different configuration combinations, representing available web tools and technologies. \cite
+\section{Software Configuration}
 
-These sites are hosted using a self signed SSL certificate \cite, although most commercial sites would not use a self signed certificate, it should not have any bearing on the communications fingerprint \cite.
+Software is installed and configured on all machines. The simulation network is
+configured to use the private Tor directory server rather than the public ones
+specified by default \parencite{website:private-tor-network}.
 
-Controls
-Web server:
-  Apache
-  Nginx
-Web site:
-  Static(1-20)
-  Random
-Method:
-  SSL
-  Tor
-  SSL over Tor
-Clients:
-  Selenium firefox
-  Curl
+The packet sniffer is configured to capture only the packets relevant for each
+data set.
 
-Lankiveil 
-Lankiveil executes a basic ruby script which runs a number of simulations:
+Figure \ref{network-diagram} shows the placement of applications and relevant
+data flows.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{network-diagram}
+  \caption{Network Diagram}
+  \label{network-diagram}
+\end{figure}
+
+\section{Systems}
+
+A number of systems will be configured both physical and virtual.
+The \emph{Host Systems}, those running natively on a physical PC with a Virtual Box environment to host a Guest Operating System.
+The \emph{Guest Systems}, operating systems running inside a Virtual Box environment on top of a Host System, and the Sniffing system, which is responsible for capturing the experiment results.
+
+The name, IP Address and role of each system in the simulation network is shown in Table \ref{table:hosts}.
+
+\begin{tabular}{lrr}
+  \toprule
+  Host Name & IP Address & Role\\
+  \midrule
+  Grumman & 192.168.0.100 & Management and Host of Client System \\
+  Arrakis & 192.168.0.001 & Host of Server System \\
+  Richese & 192.168.0.102 & Host of Tor Network System \\
+  \midrule
+  Ipyr & 192.168.0.200 & Sniffing System \\
+  \midrule
+  Lankiveil & 192.168.0.16 & Client Guest System \\
+  Ginaz & 192.168.0.17 & Server Guest System \\
+  Sikun & 192.168.0.18 & Tor Network Guest System \\
+  \botomrule
+  \label{table:hosts}
+\end{tabular}
+
+\subsection{Sniffing System}
+
+The sniffing system has a very basic role: to capture packets.
+It is configured with the Ubuntu 10.04 Server Operating system.
+Most basic features are disabled and tcpdump is configured to run at startup saving all captures to 1mb files in a directory indicating when the system was booted.
+
+\subsection{Host Systems}
+
+All the host systems are configured identically. The following procedure is carried out to prepare a host system.
+
 \begin{itemize*}
-  \item RSpec tests that go through selenium scripts, simulating user interaction, by mimicking user interactions with a web site through the Firefox browser.
-  \item Automated fetching of websites using the Curl program.
+  \item Install Ubuntu 10.04 Desktop Operating System
+    \begin{itemize*}
+      \item Use entire disk
+      \item Set time zone to GMT +8 WST (Perth)
+    \end{itemize*}
+  \item Turn off automatic package updates
+  \item Turn off powersaving features
+  \item Install OpenSSH Server
+  \item Add Virtual Box repository to sources.lst
+  \item Update sources and install Virtual Box
+  \item Ensure Virtual Box starts with system and disable all other startup applications
 \end{itemize*}
 
-Corrin 192.168.0.18
-Is the control system, it monitors packets and ensures the simulation is running. tcpdump is configured on this system to monitor ports that have been configured for encrypted traffic.
+One of the host systems is set aside as a management system, which is responsible for ensuring the experiment runs and restarts it if there are any problems.
+On this machine a private ssh key is created, and copied to the authorized keys file on all other hosts.
+This allows the management system to connect to all the other systems and issue commands without user interaction.
+
+The management script runs on the management system to watch the experiment's progress.
+This is a simple Ruby script which uses SSH to control the other Host systems and opens a socket which waits for a connection that indicates that the experiment has finished.
+Every time it starts the experiment, it rolls back each virtual machine to a preconfigured snapshot.
+If the experiment takes too long, say because a virtual machine hangs or something is wrong, it will be started without waiting for the finish condition.
+
+Note that restarting each snapshot ensures that the system clock of each guest operating system is synchronized with that of the host operating system.
+The Tor network is sensitive to differences in time between hosts and this ensures correct operation.
+
+\subsection{Guest Systems}
+
+\subsubsection{Client System}
+
+The client system runs Ubuntu 10.04 Desktop Operating System as well as a number of applications that allow it to perform automated web browsing.
+Tor is configured on this system as well for the Tor part of the experiment but is initially disabled.
+
+The software installed on this system includes:
+
+\begin{itemize*}
+  \item Ruby
+  \item Rubygems:
+    \begin{itemize*}
+      \item Selenium
+      \item DaemonController
+      \item RSpec
+    \end{itemize*}
+  \item Selenium-RC
+  \item Firefox web browser
+  \item Tor
+\end{itemize*}
+
+The client operation is controlled by a Ruby script which ensures that the Selenium-RC server is running, executes a number of Selenium browser simulations using RSpec and reports it's success by connecting to an open socket on the management system.
+
+There are 170 simulations which emulate simple website interactions which have different traffic profiles against 30 different websites on the Server system.
+
+For the non-SSL portion of the experiment, Selenium is configured to use a special proxy which automatically accepts self signed certificates.
+Typical interactions with SSL encrypted websites are signed by a certificate authority, so no user interaction is required to begin browsing.
+
+\subsubsection{Server System}
+
+The host system runs an apache web server which serves two sets of sample websites, static and dynamic.
+The static websites are served each from a different numbered directory and accessible over a different virtual host.
+This means that when a web browser is pointed at the directory \verb+site1.static.torsim+ the files in \verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the browser.
+
+For the SSL part of the experiment, only the HTTPS port 443 is accessed and all information is sent to the browser using encryption.
+
+The dynamic sample websites change subtly with each attempted access. There are 10 sample websites each a slightly different Ruby Sinatra application.
+
+\subsubsection{Tor Simulation}
+
+The Tor Simulation Guest is responsible for emulating a Tor network. It runs three Tor directory authorities as well as fifteen relays.
+
+Each Tor instance on the Tor Simulation system is given it's own separate directory for configuration, logging and temporary files.
+
+\section{Procedure}
+
+\subsection{Preparation}
+
+\subsubsection{Host Systems}
+
+The preparation for the host operating systems is identical except for the hostname and IP address.
+
+Installing the Host operating system:
+
+\begin{enumerate*}
+  \item Power on machine
+  \item Interrupt BIOS boot process
+  \begin{enumerate*}
+    \item Load default BIOS settings
+    \item Set boot order to ensure CD-ROM is first
+    \item Disable unnecessary boot devices
+    \item Ensure system clock is correct
+  \end{enumerate*}
+  \item Boot from Ubuntu 10.04 Desktop cd
+  \item Select the language you wish to use for installation (English) and click 'Forward'
+  \item Select the region (Australia/Perth) and click 'Forward'
+  \item Select an appropriate keymap (USA) and click 'Forward'
+  \item Select 'Erase and use the entire disk' and click 'Forward'
+  \item Enter your details, select 'Log in automatically' and click 'Forward'
+\end{enumerate*}
+
+At this point the installation will begin and should take about 35 minutes.
+'Log in automatically' is selected to ensure that the experiment will continue even if power is lost.
+Once installation is complete remove the CD and reboot the system.
+
+Configuring the Host operating system:
+
+\begin{enumerate*}
+  \item Configure the network adapter
+  \item Install Virtual Box
+  \item Load the guest operating system virtual machine image
+\end{enumerate*}
+
+To install Virtual Box, the following procedure is used:
+
+\begin{enumerate*}
+  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
+  \begin{verbatim}
+deb http://download.virtualbox.org/virtualbox/debian lucid non-free
+  \end{verbatim}
+  \item Install the GPG key for the Virtual Box packages:
+  \begin{verbatim}
+wget -q http://download.virtualbox.org/virtualbox/debian/oracle_vbox.asc -O- | sudo apt-key add -
+  \end{verbatim}
+  \item Then install VirtualBox 3.2 with the command:
+  \begin{verbatim}
+sudo apt-get update && sudo apt-get install virtualbox-3.2
+  \end{verbatim}
+\end{enumerate*}
+
+For the management system, some additional commands need to be run:
+
+\begin{enumerate*}
+  \item Generate a private ssh key for the user with the command: \verb+ssh-keygen+, when prompted for a password enter nothing.
+  \item SSH to the other host systems on the network, and copy the contents of \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the destination system.
+  \item Install ruby so that the management script can be run:
+    \begin{verbatim}
+sudo apt-get install ruby rubygems
+    \end{verbatim}
+  \item Ensure the script \verb+run_simulation.rb+ is started on login.
+\end{enumerate*}
+
+\subsubsection{Tor System}
+
+Install Ubuntu 10.04 Server.
+
+Deploy the experiment files.
+
+Install Tor:
+
+\begin{enumerate*}
+  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
+  \begin{verbatim}
+deb http://deb.torproject.org/torproject.org lucid main
+  \end{verbatim}
+  \item Install the GPG key for the Tor packages:
+  \begin{verbatim}
+gpg --keyserver keys.gnupg.net --recv 886DDD89
+gpg --export A3C4F0F979CAA22CDBA8F512EE8CBC9E886DDD89 | sudo apt-key add -
+  \end{verbatim}
+  \item Install Tor:
+  \begin{verbatim}
+sudo apt-get update && sudo apt-get install tor
+  \end{verbatim}
+\end{enumerate*}
+
+\subsubsection{Client System}
+
+Install Ubuntu 10.04 Desktop as in the Host system directions, leaving out the Virtual Box installation.
+
+\begin{enumerate*}
+  \item Deploy the experiment files onto the client system.
+  \item Install Ruby
+  \item Install the bundler ruby gem with the command:
+    \begin{verbatim}
+gem install bundler
+    \end{verbatim}
+  \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
+    \begin{verbatim}
+bundle install
+    \end{verbatim}
+  \item Ensure that the client script is executed at system startup.
+\end{enumerate*}
+
+\subsubsection{Configuring the Management Script}
+
+Once all systems are deployed, the management script needs to be altered to
+
+\subsection{Execution}
+
+Running the experiment is a matter of ensuring all Host systems are powered on, if everything is configured correctly the experiment will continue to run until stopped manually.

### 2010-12-18 thesis/experiment.tex
Quick description of setting up selenium

@@
 Typical interactions with SSL encrypted websites are signed by a certificate authority, so no user interaction is required to begin browsing.
+
+\subsubsubsection{Selenium}
+
+SSL + Tor over selenium.
+
+Generate a selenium firefox profile. First launch selenium in interactive mode specifying a proxy:
+
+java -jar $selenium.jar -interactive
+
+This will start a prompt to which you can edit commands, you must launch a browser to get selenium to create a firefox profile directory.
+
+cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
+
+Generate a firefox profile, then edit the proxy.pac file to
+
+function FindProxyForURL(url, host) {
+   if(shExpMatch(url, '*/selenium-server/*')) {
+       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
+   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
+       return 'DIRECT';
+   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
+       return 'DIRECT';
+   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
+       return 'DIRECT';
+   } else {
+       return 'PROXY proxy.ourdomain.dom:8080';
+   }
+}
+
+or
+
+function FindProxyForURL(url, host) {
+   if(shExpMatch(host, '*torsim')) {
+       return 'PROXY localhost:8118';
+   }
+   return 'PROXY localhost:4444; DIRECT';
+}
+
+This makes sure that your proxy (Tor) gets used for outgoing connections, and the selenium proxy is used for running tests.
+
+To get SSL certificates accepted, you must manually accept them permanently for each host. This will update the cert_override.txt and cert8.db files.
+
+Tor must have the following setting supplied:
+
+ExitPolicyRejectPrivate 0
+
+Since we are using a 192.* network. - Not true, testing mode flag sets this.
+
+But the tor relays must be able to resolve names using DNS, if you use socks4a protocol.
 

### 2010-12-29 thesis/experiment.tex
Started putting in summaries of software, with quotes

@@
+\chapter{Materials and Methods}
+
+\section{Instruments and Apparatus}
+
+The experiment described requires a number of computer systems and associated hardware to run the simulation and capture appropriate data. This equipment is described in the following chapter.
+
+\section{Personal Computer}
+
+\section{Hub/Unmanaged Router}
+\section{Tor Software}
+\section{'tcpdump' Software}
+\section{Weka Software}
+\section{VirtualBox Software}
+\section{Ruby Software}
+
+\section{Ubuntu Linux Software}
+
+The Ubuntu Linux operating system is freely available Linux operating system
+available for desktop personal computers.
+
+\section{Selenium Software}
+
+Selenium is a web testing framework with a number of components that allow
+developers to write automated tests of web applications using most modern web
+browsers \parencite{:2010ys}. Using the Selenium framework one can mimic the
+actions of an actual user interacting with a web site.
+
+\section{Firefox Software}
+
+Firefox is a web browser developed by the Mozilla organization and freely
+available for most desktop personal computers \parencite{mozilla}. It's strong
+standards compliance \parencite{Hammond:2010fk} and popularity
+\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal candidate for
+this experiment .
+
+\section{OpenSSH Software}
+
+\cite{Tucker:2010ly}
+\cite{:2010zr}
+\cite{:ve}
+
+\section{Apache Software}
+
+\cite{:qf}
+
+\section{Sinatra Software}
+
 \section{Hardware Configuration}

### 2010-12-31 thesis/experiment.tex
Some more software summaries

@@
 
-\section{Personal Computer}
+\subsection{Personal Computer}
 
-\section{Hub/Unmanaged Router}
-\section{Tor Software}
-\section{'tcpdump' Software}
-\section{Weka Software}
-\section{VirtualBox Software}
-\section{Ruby Software}
+Four computer systems were employed each with the same specifications.
 
-\section{Ubuntu Linux Software}
+\subsection{Hub/Managed Router}
+
+The network equipment chosen to run the experiment is a simple hub or
+'repeater' which duplicates all packets transmitted on all ports. This makes it
+easy to monitor all communications across the network for analysis purposes
+\parencite{website:hub-reference}.
+
+\subsection{Tor Software}
+
+\subsection{'tcpdump' Software}
+
+The tcpdump software captures network packets that are transferred using
+network interfaces attached to the current hardware \parencite{:2009cr}.  It is
+available on most operating systems and supports a flexible filtering language
+for capturing only the specific packets desired. The format of output produced
+by tcpdump is well documented \parencite{:nx} which makes it ideal for
+transformation and processing by third party tools.
+
+\subsection{Weka Software}
+
+Weka is data mining software which includes tools for classification of data
+sources using a wide variety of machine learning algorithms
+\parencite{Hall:2009p7662}.
+
+\subsection{VirtualBox Software}
+
+VirtualBox is virtualization software that allows the running of a guest
+operating system in its own environment on another host operating system
+\parencite{:fk}.  It supports snapshots and a remote control facility which
+make it useful for running repetitions in an experimental environment
+\parencite{:uq}.
+
+\subsection{Ruby Software}
+
+Ruby is an object orientated, dynamic programming language which is useful for
+quick prototyping and as such has been used to automate the simulation
+described in this experiment \parencite{:2010uq}.
+
+(I used it because it is a language that is fast to develop in and I am
+familiar with it)
+
+\subsection{Ubuntu Linux Software}
 
@@
 
-\section{Selenium Software}
+\cite{:2010ly}
+
+\subsection{Selenium Software}
 
@@
 
-\section{Firefox Software}
+\subsection{Firefox Software}
 
@@
 standards compliance \parencite{Hammond:2010fk} and popularity
-\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal candidate for
-this experiment .
+\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
+candidate for this experiment.
 
-\section{OpenSSH Software}
+\subsection{OpenSSH Software}
 
-\cite{Tucker:2010ly}
+OpenSSH is a freely available suite of connectivity tools
+\parencite{:2010zr,:ve} that supports remote command execution
+\parencite{Tucker:2010ly}.
+
 \cite{:2010zr}
-\cite{:ve}
 
-\section{Apache Software}
+\subsection{Apache Software}
 
@@
 
-\section{Sinatra Software}
+\subsection{Sinatra Software}
 
-\section{Hardware Configuration}
+Sinatra is a simple framework for creating dynamic web applications using the
+Ruby programming language \parencite{:2010bh}.
+
+\section{Procedure}
+
+\subsection{Hardware Configuration}
 
@@
 
-\section{Software Configuration}
+\subsection{Software Configuration}
 

### 2010-12-31 thesis/thesis.tex
Include experiment in thesis file.

@@
 
-\chapter{Materials and Methods}
-
-\section{Equipment Requirements}
-
-The following list describes computer systems and hardware required to run the
-data capture simulations:
-
-\begin{itemize*}
-  \item 1 Computer system running web browser and Tor
-  \item 1 Computer running packet sniffing software
-  \item N Computer systems running Tor, configured as bridges
-  \item 1 Computer running web server and Tor directory server
-  \item Cat 5 cable to connect all computer systems
-  \item Network Hub or Switch capable of disabling ‘learning’
-    \parencite{website:hub-reference}
-\end{itemize*}
-
-The computer systems running Tor bridges represent the simulation network.
-Although it is feasible to have a single system representing the simulation
-network the combined system load may be too great and introduce  excessive
-latency.
-
-Packet capture is a performance intensive application, one machine should be
-reserved for this application. It must include adequate disk space, preferably
-of a high speed.
-
-The required software includes:
-
-\begin{itemize*}
-  \item Virtualisation software
-  \item Web browser
-  \item Tor
-  \item Packet capture software
-\end{itemize*}
-
-\section{Procedure}
-
-\subsection{Phase 1}
-
-\subsubsection{Hardware Configuration}
-
-All systems will be configured and connected to the same isolated network
-through the hub as shown in Figure \ref{physical-setup}.
-
-\begin{figure}[H]
-  \centering\includegraphics[scale=0.6]{physical-setup}
-  \caption{Physical Setup}
-  \label{physical-setup}
-\end{figure}
-
-\subsubsection{Software Configuration}
-
-Software is installed and configured on all machines. The simulation network is
-configured to use the private Tor directory server rather than the public ones
-specified by default \parencite{website:private-tor-network}.
-
-The packet sniffer is configured to capture only the packets relevant for each
-data set.
-
-Figure \ref{network-diagram} shows the placement of applications and relevant
-data flows.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{network-diagram}
-  \caption{Network Diagram}
-  \label{network-diagram}
-\end{figure}
-
-\subsubsection{Simulations}
-
-To provide a large training set, capture traffic can be generated by a series
-of automated simulations. This stage of the research will include identifying a
-number of commonly used websites and other hosts that employ TLS encryption,
-and simulating these on the test network through mirroring or other means. This
-will include selection of tools to assist in automating this process.
-
-\subsubsection{Data Capture}
-
-Three sets of data must be collected, and kept separate. The first set is a
-sample that is known to belong to the anonymous networks in question. To
-capture this the software will be configured to communicate using known
-parameters. It will also be ensured that no other applications are
-communicating using these parameters that may pollute the data set.
-
-This first set of data can be partitioned to make the second set, which will be
-used to confirm the false negative rate of the matching technique.
-
-The third set of data must constitute traffic that is known to not contain any
-traffic from the networks being catalogued. This data set will be used to
-confirm the rate of false positives.
-
-\subsection{Phase 2}
-
-\subsubsection{Data Preparation}
-
-The captured data will be in the data file format used by the capture software.
-For analysis the most relevant information needs to be retrieved from the data
-files and prepared in a suitable format for the matching algorithm. This stage
-of the research includes identifying the attributes of the captured data that
-would be most suitable for analytical purposes, and providing them in a format
-suitable for processing by an automatic classifier.
-
-\subsubsection{Analysis}
-
-The training data set will be supplied to the algorithm for training purposes.
-Once training is complete, this algorithm can be tested against the
-confirmation data set to obtain the rate of false negatives. The regular
-traffic will be used to determine the false positive rate. This allows the
-construction of the Receiver Operating Characteristic (ROC) curve, a
-measurement of the performance of the matching algorithm.
-
-\section{Limitations}
-
-The process has been designed with the goal of minimising variables that may
-affect matching performance. This is unusual for traffic analysis papers which
-typically sample real world traffic in large volumes. In the case of a machine
-learning technique, this may bias the chosen algorithm against real world data,
-making it impractical for any real world use.
-
-\section{Schedule}
-
-\begin{tabular}{llr}
-  \toprule
-  Activity & Duration & Date \\
-  \midrule
-  Phase 1 \\
-  1 - Design simulations & 4 weeks \\
-  2 - Setup test network & 1 week \\
-  3 - Configure simulations & 1 week \\
-  4 - Perform simulation and data capture & 8 weeks \\
-  Phase 2 \\
-  1 - Examination of data & 2 weeks \\
-  2 - Data preparation & 4 weeks \\
-  3 - Algorithm training & 1 week \\
-  4 - Algorithm selection and comparison & 8 weeks \\
-  5 - Algorithm tailoring and tuning & 8 weeks \\
-  6 - Document final results & * \\
-  \midrule
-  Thesis submission & & December 4th, 2011 \\
-  \bottomrule
-\end{tabular}
-
-* Till submission date or completion.
+\input experiment.tex
 
@@
 
-% vim: fdm=syntax wrapmargin=80
+% vim: fdm=syntax tw=80

### 2011-01-03 thesis/experiment.tex
More write up work, redid the physical setup diagram

@@
 
-The experiment described requires a number of computer systems and associated hardware to run the simulation and capture appropriate data. This equipment is described in the following chapter.
-
-\subsection{Personal Computer}
-
-Four computer systems were employed each with the same specifications.
+The experiment described requires a number of computer systems and associated
+hardware to run the simulation and capture appropriate data. This equipment is
+described in the following chapter.
 
@@
 
-\cite{:qf}
+The Apache web server is the most prevalent web server used on the internet
+\parencite{2010:dq}.  \cite{:qf}
 
@@
 
+The experiment involves two stages, an initial configuration stage to prepare
+equipment, install software, configure and test the design and the final stage
+of executing the simulation to capture packet traces.
+
 \subsection{Hardware Configuration}
 
-All systems will be configured and connected to the same isolated network
-through the hub as shown in Figure \ref{physical-setup}.
+Four identical IBM desktop computer systems were prepared and arranged as shown
+in figure \ref{physical-setup}.
 
 \begin{figure}[H]
-  \centering\includegraphics[scale=0.6]{physical-setup}
+  \centering\includegraphics[scale=0.7]{physical-setup}
   \caption{Physical Setup}
@@
 
-Software is installed and configured on all machines. The simulation network is
-configured to use the private Tor directory server rather than the public ones
-specified by default \parencite{website:private-tor-network}.
+Table \ref{table:hosts} shows the role of each system in the experiment as well
+as the edition of operating system in use and the IP address they were
+configured with on the network.
 
-The packet sniffer is configured to capture only the packets relevant for each
-data set.
+\begin{tabular}{lrr}
+  \toprule
+  Role & Operating System Version & IP Address\\
+  \midrule
+  Client Host & Desktop & 192.168.0.100\\
+  Server Host & Desktop & 192.168.0.001\\
+  Tor Host & Desktop & 192.168.0.102\\
+  \midrule
+  Sniffing System & Server & 192.168.0.200\\
+  \midrule
+  Client Guest & Desktop & 192.168.0.16\\
+  Server Guest & Server & 192.168.0.17\\
+  Tor Network Guest & Server & 192.168.0.18\\
+  \botomrule
+  \label{table:hosts}
+\end{tabular}
 
@@
 
-\section{Systems}
-
-A number of systems will be configured both physical and virtual.
-The \emph{Host Systems}, those running natively on a physical PC with a Virtual Box environment to host a Guest Operating System.
-The \emph{Guest Systems}, operating systems running inside a Virtual Box environment on top of a Host System, and the Sniffing system, which is responsible for capturing the experiment results.
-
-The name, IP Address and role of each system in the simulation network is shown in Table \ref{table:hosts}.
-
-\begin{tabular}{lrr}
-  \toprule
-  Host Name & IP Address & Role\\
-  \midrule
-  Grumman & 192.168.0.100 & Management and Host of Client System \\
-  Arrakis & 192.168.0.001 & Host of Server System \\
-  Richese & 192.168.0.102 & Host of Tor Network System \\
-  \midrule
-  Ipyr & 192.168.0.200 & Sniffing System \\
-  \midrule
-  Lankiveil & 192.168.0.16 & Client Guest System \\
-  Ginaz & 192.168.0.17 & Server Guest System \\
-  Sikun & 192.168.0.18 & Tor Network Guest System \\
-  \botomrule
-  \label{table:hosts}
-\end{tabular}
-
 \subsection{Sniffing System}
 
-The sniffing system has a very basic role: to capture packets.
-It is configured with the Ubuntu 10.04 Server Operating system.
-Most basic features are disabled and tcpdump is configured to run at startup saving all captures to 1mb files in a directory indicating when the system was booted.
+The sniffing system was based on a basic installation of the Ubuntu 10.04 server
+operating system with no additional packages installed.
+
+An init.d script was installed to execute the tcpdump program with a specific
+filter string after the system had powered on. All capture files were limited to
+1mb in size and put into a time stamped directory. To ensure that only relevant
+packets were collected the filter string was tuned for each phase of the
+experiment. The filter string for each phase is shown below.
+
+Phase 1:
+\begin{lstlisting}[language=sh]
+dst port 443
+\end{lstlisting}
+
+Phase 2 and 3:
+\begin{lstlisting}[language=sh]
+dst port 5000-5015
+\end{lstlisting}
 
@@
 
-All the host systems are configured identically. The following procedure is carried out to prepare a host system.
+All the host systems are configured identically. The following procedure is
+carried out to prepare a host system.
 
@@
   \item Turn off automatic package updates
-  \item Turn off powersaving features
+  \item Turn off power saving features
   \item Install OpenSSH Server
@@
   \item Update sources and install Virtual Box
-  \item Ensure Virtual Box starts with system and disable all other startup applications
+  \item Ensure Virtual Box starts with system and disable all other start
+    up applications
 \end{itemize*}
 
-One of the host systems is set aside as a management system, which is responsible for ensuring the experiment runs and restarts it if there are any problems.
-On this machine a private ssh key is created, and copied to the authorized keys file on all other hosts.
-This allows the management system to connect to all the other systems and issue commands without user interaction.
+One of the host systems is set aside as a management system, which is
+responsible for ensuring the experiment runs and restarts it if there are any
+problems. On this machine a private ssh key is created, and copied to the
+authorized keys file on all other hosts. This allows the management system to
+connect to all the other systems and issue commands without user interaction.
 
-The management script runs on the management system to watch the experiment's progress.
-This is a simple Ruby script which uses SSH to control the other Host systems and opens a socket which waits for a connection that indicates that the experiment has finished.
-Every time it starts the experiment, it rolls back each virtual machine to a preconfigured snapshot.
-If the experiment takes too long, say because a virtual machine hangs or something is wrong, it will be started without waiting for the finish condition.
+The management script runs on the management system to watch the experiment's
+progress. This is a simple Ruby script which uses SSH to control the other Host
+systems and opens a socket which waits for a connection that indicates that the
+experiment has finished. Every time it starts the experiment, it rolls back
+each virtual machine to a preconfigured snapshot. If the experiment takes too
+long, say because a virtual machine hangs or something is wrong, it will be
+started without waiting for the finish condition.
 
-Note that restarting each snapshot ensures that the system clock of each guest operating system is synchronized with that of the host operating system.
-The Tor network is sensitive to differences in time between hosts and this ensures correct operation.
+Note that restarting each snapshot ensures that the system clock of each guest
+operating system is synchronized with that of the host operating system. The
+Tor network is sensitive to differences in time between hosts and this ensures
+correct operation.
 
@@
 
-The client system runs Ubuntu 10.04 Desktop Operating System as well as a number of applications that allow it to perform automated web browsing.
-Tor is configured on this system as well for the Tor part of the experiment but is initially disabled.
+The client system runs Ubuntu 10.04 Desktop Operating System as well as a
+number of applications that allow it to perform automated web browsing. Tor is
+configured on this system as well for the Tor part of the experiment but is
+initially disabled.
 
@@
 
-The client operation is controlled by a Ruby script which ensures that the Selenium-RC server is running, executes a number of Selenium browser simulations using RSpec and reports it's success by connecting to an open socket on the management system.
+The client operation is controlled by a Ruby script which ensures that the
+Selenium-RC server is running, executes a number of Selenium browser
+simulations using RSpec and reports it's success by connecting to an open
+socket on the management system.
 
-There are 170 simulations which emulate simple website interactions which have different traffic profiles against 30 different websites on the Server system.
+There are 170 simulations which emulate simple website interactions which have
+different traffic profiles against 30 different websites on the Server system.
 
-For the non-SSL portion of the experiment, Selenium is configured to use a special proxy which automatically accepts self signed certificates.
-Typical interactions with SSL encrypted websites are signed by a certificate authority, so no user interaction is required to begin browsing.
+For the non-SSL portion of the experiment, Selenium is configured to use a
+special proxy which automatically accepts self signed certificates. Typical
+interactions with SSL encrypted websites are signed by a certificate authority,
+so no user interaction is required to begin browsing.
 
@@
 
+\begin{lstlisting}[language=sh]
 java -jar $selenium.jar -interactive
+\end{lstlisting}
 
@@
 
+\begin{lstlisting}[language=sh]
 function FindProxyForURL(url, host) {
@@
 }
+\end{lstlisting}
 
@@
 
+\begin{lstlisting}[language=sh]
 ExitPolicyRejectPrivate 0
+\end{lstlisting}
 
@@
 
-The host system runs an apache web server which serves two sets of sample websites, static and dynamic.
-The static websites are served each from a different numbered directory and accessible over a different virtual host.
-This means that when a web browser is pointed at the directory \verb+site1.static.torsim+ the files in \verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the browser.
+The host system runs an apache web server which serves two sets of sample
+websites, static and dynamic. The static websites are served each from a
+different numbered directory and accessible over a different virtual host. This
+means that when a web browser is pointed at the directory
+\verb+site1.static.torsim+ the files in
+\verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the
+browser.
 
-For the SSL part of the experiment, only the HTTPS port 443 is accessed and all information is sent to the browser using encryption.
+For the SSL part of the experiment, only the HTTPS port 443 is accessed and all
+information is sent to the browser using encryption.
 
-The dynamic sample websites change subtly with each attempted access. There are 10 sample websites each a slightly different Ruby Sinatra application.
+The dynamic sample websites change subtly with each attempted access. There are
+10 sample websites each a slightly different Ruby Sinatra application.
 
@@
 
-The Tor Simulation Guest is responsible for emulating a Tor network. It runs three Tor directory authorities as well as fifteen relays.
+The Tor Simulation Guest is responsible for emulating a Tor network. It runs
+three Tor directory authorities as well as fifteen relays.
 
-Each Tor instance on the Tor Simulation system is given it's own separate directory for configuration, logging and temporary files.
+Each Tor instance on the Tor Simulation system is given it's own separate
+directory for configuration, logging and temporary files.
 
@@
 
-The preparation for the host operating systems is identical except for the hostname and IP address.
+The preparation for the host operating systems is identical except for the
+hostname and IP address.
 
@@
 At this point the installation will begin and should take about 35 minutes.
-'Log in automatically' is selected to ensure that the experiment will continue even if power is lost.
-Once installation is complete remove the CD and reboot the system.
+'Log in automatically' is selected to ensure that the experiment will continue
+even if power is lost. Once installation is complete remove the CD and reboot
+the system.
 
@@
 \begin{enumerate*}
-  \item Generate a private ssh key for the user with the command: \verb+ssh-keygen+, when prompted for a password enter nothing.
-  \item SSH to the other host systems on the network, and copy the contents of \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the destination system.
+  \item Generate a private ssh key for the user with the command:
+    \verb+ssh-keygen+, when prompted for a password enter nothing.
+  \item SSH to the other host systems on the network, and copy the contents of
+    \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the
+    destination system.
   \item Install ruby so that the management script can be run:
-    \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 sudo apt-get install ruby rubygems
-    \end{verbatim}
+    \end{lstlisting}
   \item Ensure the script \verb+run_simulation.rb+ is started on login.
@@
   \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
-  \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 deb http://deb.torproject.org/torproject.org lucid main
-  \end{verbatim}
+    \end{lstlisting}
   \item Install the GPG key for the Tor packages:
-  \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 gpg --keyserver keys.gnupg.net --recv 886DDD89
 gpg --export A3C4F0F979CAA22CDBA8F512EE8CBC9E886DDD89 | sudo apt-key add -
-  \end{verbatim}
+    \end{lstlisting}
   \item Install Tor:
-  \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 sudo apt-get update && sudo apt-get install tor
-  \end{verbatim}
+    \end{lstlisting}
 \end{enumerate*}
@@
 
-Install Ubuntu 10.04 Desktop as in the Host system directions, leaving out the Virtual Box installation.
+Install Ubuntu 10.04 Desktop as in the Host system directions, leaving out the
+Virtual Box installation.
 
@@
   \item Install the bundler ruby gem with the command:
-    \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 gem install bundler
-    \end{verbatim}
+    \end{lstlisting}
   \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
-    \begin{verbatim}
+    \begin{lstlisting}[language=sh]
 bundle install
-    \end{verbatim}
+    \end{lstlisting}
   \item Ensure that the client script is executed at system startup.
@@
 
-Running the experiment is a matter of ensuring all Host systems are powered on, if everything is configured correctly the experiment will continue to run until stopped manually.
+Running the experiment is a matter of ensuring all Host systems are powered on,
+if everything is configured correctly the experiment will continue to run until
+stopped manually.
+
+\subsection{Processing of Results}
+
+The experiment was run over the course of 8 weeks yielding three sets of sample
+data.
+
+\begin{tabular}{lrr}
+  \toprule
+  Phase & Size (bytes) & Number of sessions\\
+  \midrule
+  HTTPS & 2326328 & 236659\\
+  HTTP over Tor & 2869624 & 168876\\
+  HTTPS over Tor & 1591112 & 95203\\
+  \bottomrule
+  \label{table:datasets}
+\end{tabular}
+
+The data captured was in the form of 1mb capture files which were recombined
+with mergecap and processed by NetAI to produce ARFF format files for use by
+Weka. Each data set were given the nominal classification 'http',
+'http_over_tor' and 'https_over_tor', all other nominal attributes were removed.
+
+% vim: fdm=syntax tw=80

### 2011-01-03 thesis/thesis.tex
More write up work, redid the physical setup diagram

@@
 
+\chapter{Results}
+
+\section{Results}
+
+The classification results are tabulated below. The best performing algorithm
+j4.8 was able to classify HTTP over Tor with 97.8\% accuracy and a false
+positive rate of 4.3\%. HTTPS was more easily identified with a 97\% accuracy
+and low false positive rate of 0.7\%.
+
+\begin{tabular}{lrrr}
+  \toprule
+  & True Positive Rate & False Positive Rate & ROC \\
+  \midrule
+  Random Forest\\
+  \midrule
+  HTTPS & 0.957 & 0.036\\
+  HTTP over Tor & 0.937 & 0.037\\
+  HTTPS over Tor & 0.977 & 0.003\\
+  \midrule
+  j4.8 With 10 fold cross validation\\
+  \midrule
+  HTTPS & 0.951 & 0.04\\
+  HTTP over Tor & 0.978 & 0.043\\
+  HTTPS over Tor & 0.97 & 0.007\\
+  \midrule
+  Random Tree\\
+  \midrule
+  HTTPS & 0.961 & 0.046\\
+  HTTP over Tor & 0.906 & 0.04\\
+  HTTPS over Tor & 0.955 & 0.01\\
+  \midrule
+  Adaboost\\
+  \midrule
+  HTTPS & 0.95 & 0.001\\
+  HTTP over Tor & 0.999 & 0.324\\
+  HTTPS over Tor & 0 & 0\\
+  \botomrule
+  \label{table:results}
+\end{tabular}
+
+\chapter{Discussion of Results}
+
+\section{Limitations}
+
+The classifiers developed within this experiment have been trained against
+a relatively small sample set of simulated data, which may only represent
+a small fraction of the width and breadth of conditions available on a wider
+area network. The characteristics that allow for classification of Tor network
+may be masked by the natural variability introduced by a heterogeneous network.
+
+\section{Addressing Research Questions}
+
+\subsection{Can the traffic be classified using automated matching techniques?}
+
+Yes.
+
+\subsection{Do these networks have characteristics that make them readily
+distinguishable using heuristics based matching?}
+
+\subsection{Do they have characteristics that make them distinguishable using a
+machine learning technique?}
+
+Yes.
+
+\subsection{How long does a user have to be connected to the network before a
+confident match can be made?}
+
+Don't know... yet.
+
+\section{Possible Implications of Results}
+
+\chapter{Conclusion}
+
+While it is difficult to draw a broad conclusion with the limited nature of the
+experiment conducted, the findings suggest that the strategies used by anonymous
+networks to thwart identity revealing traffic analysis may make them easier to
+identify.
+
+Research has shown that the low latency design of Tor means it is vulnerable to
+traffic analysis attacks that correlate traffic patterns with users. This
+transparency should in fact make Tor more difficult to classify than more
+'anonymous' network designs which employ batching and traffic normalizing.
+Steganography is a difficult problem and it may be that the extra traffic
+required to maintain the Tor network means it will always be easily
+differentiated from regular encrypted traffic.
+
 \printbibliography[title=REFERENCES]

### 2011-01-23 thesis/experiment.tex
Some bug fixes and syntax errors, add in appendices, add units to lstlistings values, escape '_'s, better use of \verb, \botomrule typo fixed, more section rearrangement

@@
 sources using a wide variety of machine learning algorithms
-\parencite{Hall:2009p7662}.
+\parencite{Hall:2009p7662}. It supports processing of an input
+Attribute-Relation File Format (ARFF), a file which contains ASCII text
+describing a list of items with common attributes. Items can be given an
+attribute which provides a nominal classification for verification purposes.
 
@@
 
-VirtualBox is virtualization software that allows the running of a guest
-operating system in its own environment on another host operating system
-\parencite{:fk}.  It supports snapshots and a remote control facility which
-make it useful for running repetitions in an experimental environment
-\parencite{:uq}.
+VirtualBox provides a virtualization environment that allows guest operating
+systems to run in a virtual environment on a host operating system
+\parencite{:fk}. It supports snapshots and a remote control facility which make
+it useful for running a controlled experiment \parencite{:uq}.
 
@@
 Ruby is an object orientated, dynamic programming language which is useful for
-quick prototyping and as such has been used to automate the simulation
+rapid prototyping and as such has been used to automate the simulation
 described in this experiment \parencite{:2010uq}.
@@
 
-Selenium is a web testing framework with a number of components that allow
-developers to write automated tests of web applications using most modern web
-browsers \parencite{:2010ys}. Using the Selenium framework one can mimic the
-actions of an actual user interacting with a web site.
+Selenium is a web testing framework which allows automated testing of web pages
+through any Javascript enabled web browser \parencite{:2010ys}. A web browser
+can be controlled remotely using the Selenium Remote Control Server component,
+which in turn can be controlled with a number of programming languages including
+Ruby. This experiment makes use of a number of selenium scripts which
+approximate user interactions with a website which trigger network traffic.
 
@@
   Tor Network Guest & Server & 192.168.0.18\\
-  \botomrule
+  \bottomrule
   \label{table:hosts}
@@
 
+\subsubsection{Standard OS Installation Procedure}
+\label{section:os_install}
+
+All systems in the experiment use a variation of the Ubuntu Linux operating
+system. The installation process followed is detailed below:
+
+\begin{enumerate*}
+  \item Configure system BIOS to boot from CD-ROM
+  \item Insert Ubuntu operating system installation CD
+  \item Select the language you wish to use for installation (English) and click
+    'Forward'
+  \item Select the region (Australia/Perth) and click 'Forward'
+  \item Select an appropriate keymap (USA) and click 'Forward'
+  \item Select 'Erase and use the entire disk' and click 'Forward'
+  \item Enter the user name (John Barker), select 'Log in automatically' and click 'Forward'
+\end{enumerate*}
+
+At this point the installation will begin and should take about 35 minutes.
+'Log in automatically' is selected to ensure that the experiment will continue
+even if power is lost. Once installation is complete remove the CD and reboot
+the system. Once booted the system is ready for further configuration.
+
+Each system is given a statically assigned IP address, this is done by editing
+the file \verb+/etc/network/interfaces+ and changing the line \verb+iface eth0 inet dhcp+
+to:
+
+\begin{lstlisting}[language=sh]
+iface eth0 inet static
+  address 192.168.0.16
+  netmask 255.255.255.0
+  network 192.168.0.0
+  broadcast 192.168.0.255
+\end{lstlisting}
+
+Substituting \verb+eth0+ with the physical network interface identifier as
+appropriate, and the address \verb+192.168.0.16+ with the desired value.
+
 \subsection{Sniffing System}
 
-The sniffing system was based on a basic installation of the Ubuntu 10.04 server
-operating system with no additional packages installed.
+The sniffing system is prepared as described in \ref{section:os_install} with an
+Ubuntu 10.04 server CD. The base install of Ubuntu server has all the required
+packages included so no additional software installation is required.
 
-An init.d script was installed to execute the tcpdump program with a specific
+An init.d script was created to execute the tcpdump program with a specific
 filter string after the system had powered on. All capture files were limited to
@@
 \begin{lstlisting}[language=sh]
-dst port 443
+tcp port 443
 \end{lstlisting}
@@
 \begin{lstlisting}[language=sh]
-dst port 5000-5015
+tcp portrange 5000-5015
+\end{lstlisting}
+
+The capture script appears below with the filter string as required for phase 2
+and 3:
+
+\begin{lstlisting}[language=sh]
+#!/bin/bash
+export capture_date=`date`
+cd /home/john/ssl-captures
+mkdir "./${capture_date}"
+tcpdump -vv -C 1 -i eth0 -w "./${capture_date}/capture.dat" tcp portrange 5001-5015
 \end{lstlisting}
@@
 
-All the host systems are configured identically. The following procedure is
-carried out to prepare a host system.
+The host systems all run an identically configured Ubuntu 10.04 desktop
+operating system, except for the IP address which is configured as detailed in
+\ref{table:hosts}. To support the guest operating systems, VirtualBox is
+required. The procedure for installing VirtualBox is detailed below:
 
-\begin{itemize*}
-  \item Install Ubuntu 10.04 Desktop Operating System
-    \begin{itemize*}
-      \item Use entire disk
-      \item Set time zone to GMT +8 WST (Perth)
-    \end{itemize*}
-  \item Turn off automatic package updates
-  \item Turn off power saving features
-  \item Install OpenSSH Server
-  \item Add Virtual Box repository to sources.lst
-  \item Update sources and install Virtual Box
-  \item Ensure Virtual Box starts with system and disable all other start
-    up applications
-\end{itemize*}
+\begin{enumerate*}
+  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
+\begin{lstlisting}[language=sh]
+deb http://download.virtualbox.org/virtualbox/debian lucid non-free
+\end{lstlisting}
+  \item Install the GPG key for the Virtual Box packages:
+\begin{lstlisting}[language=sh]
+wget -q http://download.virtualbox.org/virtualbox/debian/oracle_vbox.asc -O- | sudo apt-key add -
+\end{lstlisting}
+  \item Then install VirtualBox 3.2 with the command:
+\begin{lstlisting}[language=sh]
+sudo apt-get update && sudo apt-get install virtualbox-3.2
+\end{lstlisting}
+\end{enumerate*}
+
+The guest operating system images can then be created or imported from an
+external disk.
+
+\subsubsection{Server Host}
 
@@
 responsible for ensuring the experiment runs and restarts it if there are any
-problems. On this machine a private ssh key is created, and copied to the
+problems. On this machine a private SSH key is created, and copied to the
 authorized keys file on all other hosts. This allows the management system to
@@
 long, say because a virtual machine hangs or something is wrong, it will be
-started without waiting for the finish condition.
+started without waiting for the finish condition. Figure
+\ref{manager-flow-diagram} contains a diagram which outlines the basic flow of
+the manager script.
+
+\begin{figure}[H]
+  \centering\includegraphics[scale=0.7]{manager-flow}
+  \caption{Manager Script Flow Chart}
+  \label{manager-flow-diagram}
+\end{figure}
 
@@
 
-\subsubsubsection{Selenium}
+\paragraph{Selenium}
 
@@
 
-Generate a selenium firefox profile. First launch selenium in interactive mode specifying a proxy:
+Generate a selenium firefox profile. First launch selenium in interactive mode
+specifying a proxy:
 
@@
 
-This will start a prompt to which you can edit commands, you must launch a browser to get selenium to create a firefox profile directory.
+This will start a prompt to which you can edit commands, you must launch a
+browser to get selenium to create a firefox profile directory.
 
+\begin{lstlisting}[language=sh]
 cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
+\end{lstlisting}
 
@@
 
-This makes sure that your proxy (Tor) gets used for outgoing connections, and the selenium proxy is used for running tests.
+This makes sure that your proxy (Tor) gets used for outgoing connections, and
+the selenium proxy is used for running tests.
 
-To get SSL certificates accepted, you must manually accept them permanently for each host. This will update the cert_override.txt and cert8.db files.
+To get SSL certificates accepted, you must manually accept them permanently for
+each host. This will update the \verb+cert_override.txt+ and \verb+cert8.db+
+files.
 
@@
 directory for configuration, logging and temporary files.
-
-\section{Procedure}
-
-\subsection{Preparation}
-
-\subsubsection{Host Systems}
-
-The preparation for the host operating systems is identical except for the
-hostname and IP address.
-
-Installing the Host operating system:
-
-\begin{enumerate*}
-  \item Power on machine
-  \item Interrupt BIOS boot process
-  \begin{enumerate*}
-    \item Load default BIOS settings
-    \item Set boot order to ensure CD-ROM is first
-    \item Disable unnecessary boot devices
-    \item Ensure system clock is correct
-  \end{enumerate*}
-  \item Boot from Ubuntu 10.04 Desktop cd
-  \item Select the language you wish to use for installation (English) and click 'Forward'
-  \item Select the region (Australia/Perth) and click 'Forward'
-  \item Select an appropriate keymap (USA) and click 'Forward'
-  \item Select 'Erase and use the entire disk' and click 'Forward'
-  \item Enter your details, select 'Log in automatically' and click 'Forward'
-\end{enumerate*}
-
-At this point the installation will begin and should take about 35 minutes.
-'Log in automatically' is selected to ensure that the experiment will continue
-even if power is lost. Once installation is complete remove the CD and reboot
-the system.
-
-Configuring the Host operating system:
-
-\begin{enumerate*}
-  \item Configure the network adapter
-  \item Install Virtual Box
-  \item Load the guest operating system virtual machine image
-\end{enumerate*}
-
-To install Virtual Box, the following procedure is used:
-
-\begin{enumerate*}
-  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
-  \begin{verbatim}
-deb http://download.virtualbox.org/virtualbox/debian lucid non-free
-  \end{verbatim}
-  \item Install the GPG key for the Virtual Box packages:
-  \begin{verbatim}
-wget -q http://download.virtualbox.org/virtualbox/debian/oracle_vbox.asc -O- | sudo apt-key add -
-  \end{verbatim}
-  \item Then install VirtualBox 3.2 with the command:
-  \begin{verbatim}
-sudo apt-get update && sudo apt-get install virtualbox-3.2
-  \end{verbatim}
-\end{enumerate*}
-
-For the management system, some additional commands need to be run:
-
-\begin{enumerate*}
-  \item Generate a private ssh key for the user with the command:
-    \verb+ssh-keygen+, when prompted for a password enter nothing.
-  \item SSH to the other host systems on the network, and copy the contents of
-    \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the
-    destination system.
-  \item Install ruby so that the management script can be run:
-    \begin{lstlisting}[language=sh]
-sudo apt-get install ruby rubygems
-    \end{lstlisting}
-  \item Ensure the script \verb+run_simulation.rb+ is started on login.
-\end{enumerate*}
-
-\subsubsection{Tor System}
-
-Install Ubuntu 10.04 Server.
 
@@
 Weka. Each data set were given the nominal classification 'http',
-'http_over_tor' and 'https_over_tor', all other nominal attributes were removed.
+'http\_over\_tor' and 'https\_over\_tor', all other nominal attributes were
+removed.
 

### 2011-01-27 thesis/thesis.tex
Some bug fixes and syntax errors, add in appendices, add units to lstlistings values, escape '_'s, better use of \verb, \botomrule typo fixed, more section rearrangement
New supervisor (damn splitter!)
Table of contents, figures and tables
Abbreviations and titleization

@@
 \studentid{0991300}
-\supervisor{Dr Christopher Bolan}
+\supervisor{Dr Andrew Woodward}
 \supervisor{Mr Peter Hannay}
@@
 \maketitle
+
+\tableofcontents
+\listoftables
+\listoffigures
 
@@
 Early work in encrypted Internet communications includes the Secure Network
-Programming (SNP) applications programming interface (API)
+Programming (SNP) Applications Programming Interface (API)
 \parencite{Woo:1994p2532}. This was a simple framework providing numerous
@@
 suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
-Transport Layer Security, with the latest version 1.2 being released August
-2008 \parencite{website:TLS}. TLS addresses some issues in SSL and provides a
-number of enhancements, but is not compatible with SSL.
+Transport Layer Security (TLS), with the latest version 1.2 being released
+August 2008 \parencite{website:TLS}. TLS addresses some issues in SSL and
+provides a number of enhancements, but is not compatible with SSL.
 
@@
 
-The first anonymous network system \emph{MixNet}, was described in
+The first anonymous network system MixNet, was described in
 \textcite{Chaum:1981p296}. This proposal makes essential usage of public key
-encryption to prevent eavesdroppers from obtaining message delivery
-information. Senders in the network communicate with a centrally located server
-known as a \emph{mix}, delivering a message with the address of the intended
-recipient. The mix server discards any information about the sender and
-delivers it to the final destination. Figure \ref{chaums-mix-network} depicts
-the process of message delivery in Chaum's MixNet. Chaum's proposal also
-allowed for the chaining of multiple mix servers together to form a
-\emph{cascade}.
+encryption to prevent eavesdroppers from obtaining message delivery information.
+Senders in the network communicate with a centrally located server known as a
+\emph{mix}, delivering a message with the address of the intended recipient. The
+mix server discards any information about the sender and delivers it to the
+final destination. Figure \ref{chaums-mix-network} depicts the process of
+message delivery in Chaum's MixNet. Chaum's proposal also allowed for the
+chaining of multiple mix servers together to form a \emph{cascade}.
 
@@
   HTTPS over Tor & 0 & 0\\
-  \botomrule
+  \bottomrule
   \label{table:results}
@@
 
+\chapter{Appendix}
+
+\section{Manager Script}
+
+\lstinputlisting{../experiment/simulation/manager/run_simulation.rb}
+
+\section{Client Script}
+
+\lstinputlisting[]{../experiment/simulation/client/client.rb}
+
+\section{Run Tor Network Script}
+
+\lstinputlisting[]{../experiment/simulation/tor/run_private_network.sh}
+
 \printbibliography[title=REFERENCES]

### 2011-01-30 thesis/thesis.tex
Put results in table section, confident methodology, put 3 in parencite postnote, rather than 'page 3'

@@
 of connections with their respective communication partners and vice versa''
-\parencite[page 3]{Murdoch:2005p325}.
+\parencite[3]{Murdoch:2005p325}.
 
@@
 collection phase. The second phase will include a quasi experimental
-methodology which may include data manipulation techniques to prepare the
+methodology which will include data manipulation techniques to prepare the
 collected data and a comparison of various heuristics and machine learning
@@
 
+\begin{table}
   \begin{tabular}{lrrr}
@@
   \end{tabular}
+  \caption{Results}
+\end{table}
 

### 2011-01-30 thesis/build.sh
Fix up bibliography usage, just symlink into subdir, now can just use regular make

@@ -1,3 +1,0 @@
-#!/bin/bash
-export BIBINPUTS=".:../bibliography//"
-make

### 2011-01-30 thesis/thesis.tex
Listings in their correct languages

@@
 
-\lstinputlisting{../experiment/simulation/manager/run_simulation.rb}
+\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}
 
@@
 
-\lstinputlisting[]{../experiment/simulation/client/client.rb}
+\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}
 
@@
 
-\lstinputlisting[]{../experiment/simulation/tor/run_private_network.sh}
+\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}
 

### 2011-01-30 thesis/thesis.tex
3-4 instead of 'p. 3-4' uses appropriate pages label

@@
 weaknesses discovered in other proposals. With a focus on deployability,
-usability, flexibility and simple-design \parencite[p. 3-4]{Dingledine:2004p314}
+usability, flexibility and simple-design \parencite[3-4]{Dingledine:2004p314}
 as well as a successful implementation, it has seen wider deployment than most

### 2011-01-30 thesis/thesis.tex
Remove more erroneous page prefixes in citations, remove emphasis everywhere - using it wrongly

@@
 
-The possibility of public key cryptography, or \emph{non-secret
-encryption} was conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and
-later developed into both a method for sharing secret encryption keys by
-Malcolm J. Williamson in 1974 \parencite{Singh:1999:CBE} and a method for
-asymmetric encryption \parencite{Cocks:1973p3265}.
+The possibility of public key cryptography, or non-secret encryption was
+conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and later developed
+into both a method for sharing secret encryption keys by Malcolm J. Williamson
+in 1974 \parencite{Singh:1999:CBE} and a method for asymmetric encryption
+\parencite{Cocks:1973p3265}.
 
@@
 Senders in the network communicate with a centrally located server known as a
-\emph{mix}, delivering a message with the address of the intended recipient. The
-mix server discards any information about the sender and delivers it to the
-final destination. Figure \ref{chaums-mix-network} depicts the process of
-message delivery in Chaum's MixNet. Chaum's proposal also allowed for the
-chaining of multiple mix servers together to form a \emph{cascade}.
+mix, delivering a message with the address of the intended recipient. The mix
+server discards any information about the sender and delivers it to the final
+destination. Figure \ref{chaums-mix-network} depicts the process of message
+delivery in Chaum's MixNet. Chaum's proposal also allowed for the chaining of
+multiple mix servers together to form a cascade.
 
@@
 \begin{itemize*}
-  \item Anonymous remailers such as \emph{Babel} \parencite{Gulcu:1996p1662}
-    and \emph{Mixminion} \parencite{Danezis:2003ys}.
+  \item Anonymous remailers such as Babel \parencite{Gulcu:1996p1662} and
+    Mixminion \parencite{Danezis:2003ys}.
   \item Networks that provide mathematically provable anonymity
@@
   \item Anonymity that degrades gracefully when subject to attack, so called
-    \emph{robust anonymity} \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
-  \item Anonymous publishing in \emph{Freedom} \parencite{Goldberg:1999p2231}
-    and \emph{Freenet} \parencite{Clarke:2001p2435}.
-  \item Peer to Peer (P2P) anonymity such as \emph{MorphMix}
-    \parencite{Rennhard:2002p4559}, \emph{Tarzan} \parencite{Freedman:2002kx} and
-    \emph{P5} \parencite{P5Sherwood:2005p5872}.
-  \item Censorship resistance in \emph{aChord} and \emph{gnuNet}
-    \parencite{Hazel:2002p6929}, \emph{Infranet} \parencite{Feamster:2002p307}
-    and of course Tor.
+    robust anonymity \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
+  \item Anonymous publishing in Freedom \parencite{Goldberg:1999p2231} and
+    Freenet \parencite{Clarke:2001p2435}.
+  \item Peer to Peer (P2P) anonymity such as MorphMix
+    \parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
+    \parencite{P5Sherwood:2005p5872}.
+  \item Censorship resistance in aChord and gnuNet \parencite{Hazel:2002p6929},
+    Infranet \parencite{Feamster:2002p307} and of course Tor.
 \end{itemize*}
@@
 responsible for message delivery to provide a degree of anonymity. In Tor,
-these mixes are known as \emph{relays} and are typically chained together to
-construct a \emph{circuit}. Clients connect to the Tor network by communicating
-with a special relay known as a \emph{bridge}, which constitutes the first
+these mixes are known as relays and are typically chained together to
+construct a circuit. Clients connect to the Tor network by communicating
+with a special relay known as a bridge, which constitutes the first
 relay in a circuit. Traffic is repeatedly delivered through relays until it
-reaches another special relay known as an \emph{exit node}, where it is
+reaches another special relay known as an exit node, where it is
 delivered unencrypted to the final destination. Figure \ref{tor-network} shows
@@
 Messages delivered through the Tor network are encrypted multiple times using a
-variation of onion routing \parencite{Michael:2001} known as \emph{telescopic
-onion routing}. Circuits are built incrementally, obtaining a session key from
-each successive relay in the circuit and encrypting messages so that
-intermediate relays are unable to decrypt the message. Since circuits can take
-some time to build, they are pre-emptively created at regular intervals
-\parencite[p. 5]{Dingledine:2004p314}. Although Tor does not support many of
-the traffic normalization techniques that provide strong anonymity, messages
-passed through the Tor network are packaged in \emph{cells} of a fixed size of
-512 bytes \parencite[p. 5]{Dingledine:2004p314}. Tor also provides application
-level filters that remove identifying features from common application
-protocols.
+variation of onion routing \parencite{Michael:2001} known as telescopic onion
+routing. Circuits are built incrementally, obtaining a session key from each
+successive relay in the circuit and encrypting messages so that intermediate
+relays are unable to decrypt the message. Since circuits can take some time to
+build, they are pre-emptively created at regular intervals
+\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
+traffic normalization techniques that provide strong anonymity, messages passed
+through the Tor network are packaged in cells of a fixed size of 512 bytes
+\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
+that remove identifying features from common application protocols.
 
@@
 Tor also supports congestion mitigation techniques which alter communication
-patterns \parencite[p. 8]{Dingledine:2004p314}.
+patterns \parencite[8]{Dingledine:2004p314}.
 
@@
 Tor provides communications facilities to a number of Internet enabled
-applications by providing an interface using the SOCKS protocol \parencite[p.
-17]{Dingledine:2004p314}. This means that the Tor network can proxy regular web
-browsing, email or any other TCP or UDP based communication protocol
+applications by providing an interface using the SOCKS protocol
+\parencite[17]{Dingledine:2004p314}. This means that the Tor network can proxy
+regular web browsing, email or any other TCP or UDP based communication protocol
 \parencite{website:socks}. Each of these application protocols have their own
 distinguishing communications characteristics which will influence the matching
-algorithm. It is not yet clear how transparent the Tor network will be
-regarding these characteristics and thus, for the purposes of classification a
-single protocol should be chosen.
+algorithm. It is not yet clear how transparent the Tor network will be regarding
+these characteristics and thus, for the purposes of classification a single
+protocol should be chosen.
 

### 2011-01-30 thesis/experiment.tex
Subsection, not subsubsection
Put into enumerable list vs subsections
Bit more content in the tools section

@@
 
-\subsection{Hub/Managed Router}
+\begin{enumerate}
+  \item Hub/Managed Router
 
@@
 
-\subsection{Tor Software}
-
-\subsection{'tcpdump' Software}
+  \item 'tcpdump' Software
 
@@
 
-\subsection{Weka Software}
+  \item Tor Software
+
+  The Tor software is available on a number of operating systems and the Tor
+  project makes packages available for the Ubuntu operating system.
+
+  \item Weka Software
 
@@
 
-\subsection{VirtualBox Software}
+  \item VirtualBox Software
 
@@
 
-\subsection{Ruby Software}
+  \item Ruby Software
 
@@
   rapid prototyping and as such has been used to automate the simulation
-described in this experiment \parencite{:2010uq}.
+  described in this experiment \parencite{:2010uq}. It is supported by the
+  Selenium framework and so can be used to automate a web browser and includes
+  community developed plug-in modules called gems that provide functionality for
+  monitoring automated software and performing test sequences.
 
-(I used it because it is a language that is fast to develop in and I am
-familiar with it)
-
-\subsection{Ubuntu Linux Software}
+  \item Ubuntu Linux Software
 
   The Ubuntu Linux operating system is freely available Linux operating system
-available for desktop personal computers.
+  available for desktop personal computers \parencite{:2010ly}. It comes
+  packaged with the 'tcpdump' software and can be configured in a reliable and
+  consistent way with typical set of POSIX tools and the 'apt-get' package
+  manager. \parencite{Pereira:2011uq}.
 
-\cite{:2010ly}
-
-\subsection{Selenium Software}
+  \item Selenium Software
 
@@
 
-\subsection{Firefox Software}
+  \item Firefox Software
 
   Firefox is a web browser developed by the Mozilla organization and freely
-available for most desktop personal computers \parencite{mozilla}. It's strong
-standards compliance \parencite{Hammond:2010fk} and popularity
+  available for most desktop personal computers \parencite{Foundation:2011fk}.
+  It's strong standards compliance \parencite{Hammond:2010fk} and popularity
   \parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
@@
 
-\subsection{OpenSSH Software}
+  \item OpenSSH Software
 
@@
   \parencite{:2010zr,:ve} that supports remote command execution
-\parencite{Tucker:2010ly}.
+  \parencite{Tucker:2010ly, :2010zr}.
 
-\cite{:2010zr}
-
-\subsection{Apache Software}
+  \item Apache Software
 
   The Apache web server is the most prevalent web server used on the internet
-\parencite{2010:dq}.  \cite{:qf}
+  \parencite{2010:dq}. Details about apache go here \parencite{:qf}.
 
-\subsection{Sinatra Software}
+  \item Sinatra Software
 
@@
   Ruby programming language \parencite{:2010bh}.
+
+\end{enumerate}
 
@@
 
-\subsubsection{Standard OS Installation Procedure}
+\subsection{Standard OS Installation Procedure}
 \label{section:os_install}
@@
 Each system is given a statically assigned IP address, this is done by editing
-the file \verb+/etc/network/interfaces+ and changing the line \verb+iface eth0 inet dhcp+
-to:
+the file \verb+/etc/network/interfaces+ and changing the line
+\verb+iface eth0 inet dhcp+ to:
 

### 2011-02-26 thesis/experiment.tex
Rewriting of some bits of the equipment section

@@
 
-  The network equipment chosen to run the experiment is a simple hub or
-  'repeater' which duplicates all packets transmitted on all ports. This makes it
-  easy to monitor all communications across the network for analysis purposes
-  \parencite{website:hub-reference}.
+  Most modern network appliances used for routing, even those labelled as hubs,
+  include switching capabilities, which means that packets routed are only
+  delivered to the addressed host. This makes eavesdropping difficult. For
+  the purpose of this experiment a simple hub or repeater is required. A hub
+  does not examine packet delivery information, it simple broadcasts all packets
+  received to every connected port, allowing for passive eavesdropping without
+  complicated network configuration \parencite{website:hub-reference}.
 
@@
 
-  VirtualBox provides a virtualization environment that allows guest operating
-  systems to run in a virtual environment on a host operating system
-  \parencite{:fk}. It supports snapshots and a remote control facility which make
-  it useful for running a controlled experiment \parencite{:uq}.
+  VirtualBox software allows multiple guest operating systems to run in an
+  isolated virtual environment on a host operating system \parencite{:fk}.
+  It is free software and supports both snapshots and a remote control facility
+  which make it useful for running a controlled experiment \parencite{:uq}.
 
@@
   Ruby is an object orientated, dynamic programming language which is useful for
-  rapid prototyping and as such has been used to automate the simulation
-  described in this experiment \parencite{:2010uq}. It is supported by the
-  Selenium framework and so can be used to automate a web browser and includes
-  community developed plug-in modules called gems that provide functionality for
-  monitoring automated software and performing test sequences.
+  rapid prototyping and is supported by a large community that has developed
+  powerful add on software in the form of Ruby Gems \parencite{:2010uq}. These
+  Gems include support for the Selenium browser testing framework, process
+  monitoring, dynamic web content generation and automated testing.
 
@@
   consistent way with typical set of POSIX tools and the 'apt-get' package
-  manager. \parencite{Pereira:2011uq}.
+  manager \parencite{Pereira:2011uq}.
 
@@
   which in turn can be controlled with a number of programming languages including
-  Ruby. This experiment makes use of a number of selenium scripts which
-  approximate user interactions with a website which trigger network traffic.
+  Ruby. Using Selenium the typical interactions a user makes when viewing a
+  website can be simulated.
 
@@
   \parencite{:2010zr,:ve} that supports remote command execution
-  \parencite{Tucker:2010ly, :2010zr}.
+  \parencite{Tucker:2010ly, :2010zr}. The client component of OpenSSH is
+  installed by default on the Ubuntu operating system and the server component
+  is easily installed using the apt-get package management system.
 
@@
 
-  The Apache web server is the most prevalent web server used on the internet
-  \parencite{2010:dq}. Details about apache go here \parencite{:qf}.
+  The Apache web server is the most prevalent web server used on the Internet
+  \parencite{2010:dq}. The Apache web server can serve static web content over
+  both the HTTP and HTTPS protocols \parencite{Foundation:2011uq}. Combined with
+  software such as Sinatra it can serve dynamic web content.
 
@@
   Sinatra is a simple framework for creating dynamic web applications using the
-  Ruby programming language \parencite{:2010bh}.
+  Ruby programming language \parencite{:2010bh}. Sinatra requires very little
+  configuration and development time to develop dynamic web applications.
 
@@
 
-Four identical IBM desktop computer systems were prepared and arranged as shown
+Four identical desktop computer systems were prepared and arranged as shown
 in figure \ref{physical-setup}.

### 2011-02-26 thesis/experiment.tex
Lots more rewriting of methods

@@
   It is free software and supports both snapshots and a remote control facility
-  which make it useful for running a controlled experiment \parencite{:uq}.
+  which make it useful for running a controlled experiment \parencite{Oracle:2011kx}.
 
@@
 
+  \item RSpec
+
+  RSpec is a testing framework for Ruby which allows the creation of examples in
+  an easy to read Domain Specific Language (DSL). It is well integrated with
+  Selenium which makes it ideal for running large suites of Selenium tests.
+
 \end{enumerate}
@@
 of executing the simulation to capture packet traces.
+
+The final stage simulation will be run in three phases:
+
+\begin{enumerate*}
+  \item Web requests over HTTPS
+  \item Web requests over HTTP proxied by Tor
+  \item Web requests over HTTPS proxied by Tor
+\end{enumerate*}
 
@@
 
-Table \ref{table:hosts} shows the role of each system in the experiment as well
-as the edition of operating system in use and the IP address they were
-configured with on the network.
+Table \ref{table:hosts} shows the role, edition of the Ubuntu operating system
+installed and the IP address assigned to each host in the experiment network.
 
@@
   Client Host & Desktop & 192.168.0.100\\
-  Server Host & Desktop & 192.168.0.001\\
+  Server Host & Desktop & 192.168.0.101\\
   Tor Host & Desktop & 192.168.0.102\\
@@
 Figure \ref{network-diagram} shows the placement of applications and relevant
-data flows.
+data flows when running the simulation in HTTPS mode.
 
@@
   \centering\includegraphics[width=\linewidth]{network-diagram}
-  \caption{Network Diagram}
+  \caption{Network Diagram: Phase 1}
   \label{network-diagram}
+\end{figure}
+
+Figure \ref{network-diagram-with-tor} shows the network configuration when
+running the experiment in HTTP over Tor mode.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{network-diagram-with-tor}
+  \caption{Network Diagram: Phase 2}
+  \label{network-diagram-with-tor}
+\end{figure}
+
+Figure \ref{network-diagram-with-tor-encrypted} shows the network configuration when
+running the experiment in HTTPS over Tor mode.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{network-diagram-with-tor-encrypted}
+  \caption{Network Diagram: Phase 3}
+  \label{network-diagram-with-tor-encrypted}
 \end{figure}
@@
 Substituting \verb+eth0+ with the physical network interface identifier as
-appropriate, and the address \verb+192.168.0.16+ with the desired value.
+appropriate, and the address \verb+192.168.0.16+ with the desired value. All
+systems were assigned IP Addresses as listed in \ref{table:hosts}.
 
@@
 The host systems all run an identically configured Ubuntu 10.04 desktop
-operating system, except for the IP address which is configured as detailed in
+operating system, except for the IP address which is configured as described in
 \ref{table:hosts}. To support the guest operating systems, VirtualBox is
-required. The procedure for installing VirtualBox is detailed below:
+required. The procedure used to install VirtualBox is described below:
 
@@
 
-The guest operating system images can then be created or imported from an
-external disk.
+The guest operating systems were copied across using a USB thumb drive and
+installed using the VirtualBox import feature.
 
-\subsubsection{Server Host}
+\subsubsection{Client Host}
 
-One of the host systems is set aside as a management system, which is
+One of the host systems was set aside as a management system, which is
 responsible for ensuring the experiment runs and restarts it if there are any
-problems. On this machine a private SSH key is created, and copied to the
-authorized keys file on all other hosts. This allows the management system to
-connect to all the other systems and issue commands without user interaction.
+problems.
 
-The management script runs on the management system to watch the experiment's
-progress. This is a simple Ruby script which uses SSH to control the other Host
-systems and opens a socket which waits for a connection that indicates that the
-experiment has finished. Every time it starts the experiment, it rolls back
-each virtual machine to a preconfigured snapshot. If the experiment takes too
-long, say because a virtual machine hangs or something is wrong, it will be
-started without waiting for the finish condition. Figure
-\ref{manager-flow-diagram} contains a diagram which outlines the basic flow of
-the manager script.
+For delivering remote commands from the management system to other hosts without
+interactive prompts, SSH is used with automatic private key authentication. To
+enable automatic private key authentication, first a private key was generated
+by executing the following commands in a terminal prompt:
+
+\begin{enumerate*}
+  \item \verb+ssh-keygen+
+  \item Press enter to use default keyfile (\verb+/Users/john/.ssh/id_rsa+)
+  \item Press enter twice to supply a blank passphrase
+\end{enumerate*}
+
+The public key is then copied to the other hosts using secure copy (SCP), for example:
+\begin{lstlisting}[language=sh]
+  scp ~/.ssh/id_rsa.pub john@192.168.0.101:
+\end{lstlisting}
+
+This file was then appended to the authorized hosts file on each system, by
+executing the following command from each host system:
+\begin{lstlisting}[language=sh]
+  cat id_rsa.pub >> ~/.ssh/authorized_keys
+\end{lstlisting}
+
+The management script runs on the management system to monitor experiment
+progress. This simple script manages the VirtualBox instances on the other hosts
+by remotely executing VirtualBox control commands using SSH. It ensures that
+each time the experiment is finished, the VirtualBox instances are rolled back
+and restarted. If the experiment takes too long, it is manually restarted. The
+script listens on a port for a connection from the experiment client which
+indicates the experiment has finished. Figure \ref{manager-flow-diagram}
+contains a diagram which outlines the basic flow of the manager script.
 
@@
 
-\subsubsection{Client System}
+\subsubsection{Client Guest}
 
@@
 number of applications that allow it to perform automated web browsing. Tor is
-configured on this system as well for the Tor part of the experiment but is
-initially disabled.
+configured on this system but disabled for the first phase of the simulation.
 
@@
 The client operation is controlled by a Ruby script which ensures that the
-Selenium-RC server is running, executes a number of Selenium browser
-simulations using RSpec and reports it's success by connecting to an open
-socket on the management system.
+Selenium-RC server is running, executes a number of Selenium browser simulations
+using RSpec and reports completion by connecting to an open socket on the
+management system. This script is configured to run at boot time so that as soon
+as the system is powered on the simulation commences. The complete client script
+is included in the Appendix, section \ref{client-script}.
 
-There are 170 simulations which emulate simple website interactions which have
-different traffic profiles against 30 different websites on the Server system.
+The simulation component consists of 170 different RSpec examples which emulate
+various profiles of website traffic against 30 different example websites
+provided by the Server system.
 
-For the non-SSL portion of the experiment, Selenium is configured to use a
-special proxy which automatically accepts self signed certificates. Typical
-interactions with SSL encrypted websites are signed by a certificate authority,
-so no user interaction is required to begin browsing.
+\paragraph{Tor}
+\label{install-tor}
 
-\paragraph{Selenium}
-
-SSL + Tor over selenium.
-
-Generate a selenium firefox profile. First launch selenium in interactive mode
-specifying a proxy:
-
-\begin{lstlisting}[language=sh]
-java -jar $selenium.jar -interactive
-\end{lstlisting}
-
-This will start a prompt to which you can edit commands, you must launch a
-browser to get selenium to create a firefox profile directory.
-
-\begin{lstlisting}[language=sh]
-cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
-\end{lstlisting}
-
-Generate a firefox profile, then edit the proxy.pac file to
-
-\begin{lstlisting}[language=sh]
-function FindProxyForURL(url, host) {
-   if(shExpMatch(url, '*/selenium-server/*')) {
-       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
-   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
-       return 'DIRECT';
-   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
-       return 'DIRECT';
-   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
-       return 'DIRECT';
-   } else {
-       return 'PROXY proxy.ourdomain.dom:8080';
-   }
-}
-\end{lstlisting}
-
-or
-
-\begin{lstlisting}[language=sh]
-function FindProxyForURL(url, host) {
-   if(shExpMatch(host, '*torsim')) {
-       return 'PROXY localhost:8118';
-   }
-   return 'PROXY localhost:4444; DIRECT';
-}
-\end{lstlisting}
-
-This makes sure that your proxy (Tor) gets used for outgoing connections, and
-the selenium proxy is used for running tests.
-
-To get SSL certificates accepted, you must manually accept them permanently for
-each host. This will update the \verb+cert_override.txt+ and \verb+cert8.db+
-files.
-
-Tor must have the following setting supplied:
-
-\begin{lstlisting}[language=sh]
-ExitPolicyRejectPrivate 0
-\end{lstlisting}
-
-Since we are using a 192.* network. - Not true, testing mode flag sets this.
-
-But the tor relays must be able to resolve names using DNS, if you use socks4a protocol.
-
-\subsubsection{Server System}
-
-The host system runs an apache web server which serves two sets of sample
-websites, static and dynamic. The static websites are served each from a
-different numbered directory and accessible over a different virtual host. This
-means that when a web browser is pointed at the directory
-\verb+site1.static.torsim+ the files in
-\verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the
-browser.
-
-For the SSL part of the experiment, only the HTTPS port 443 is accessed and all
-information is sent to the browser using encryption.
-
-The dynamic sample websites change subtly with each attempted access. There are
-10 sample websites each a slightly different Ruby Sinatra application.
-
-\subsubsection{Tor Simulation}
-
-The Tor Simulation Guest is responsible for emulating a Tor network. It runs
-three Tor directory authorities as well as fifteen relays.
-
-Each Tor instance on the Tor Simulation system is given it's own separate
-directory for configuration, logging and temporary files.
-
-Deploy the experiment files.
-
-Install Tor:
+Tor is installed on the client guest using the following procedure:
 
@@
 
-\subsubsection{Client System}
+\paragraph{RSpec}
 
-Install Ubuntu 10.04 Desktop as in the Host system directions, leaving out the
-Virtual Box installation.
+Each RSpec example specifies the site to test and the directions to send to the
+Firefox browser, the first RSpec example is listed below and shows a simple test
+which accesses \verb+https://site1.static.torsim/+ and opens the root web page.
+
+\begin{lstlisting}[language=ruby]
+require "rubygems"
+gem "rspec"
+gem "selenium-client"
+require "selenium/client"
+require "selenium/rspec/spec_helper"
+
+describe "site1.static.torsim.1" do
+  attr_reader :selenium_driver
+  alias :page :selenium_driver
+
+  before(:all) do
+    @verification_errors = []
+    @selenium_driver = Selenium::Client::Driver.new \
+      :host => "localhost",
+      :port => 4444,
+      :browser => "*firefoxproxy",
+      :url => "https://site1.static.torsim/",
+      :timeout_in_second => 60
+  end
+
+  before(:each) do
+    @selenium_driver.start_new_browser_session
+  end
+
+  append_after(:each) do
+    @selenium_driver.close_current_browser_session
+    @verification_errors.should == []
+  end
+
+  it "test_site1.static.torsim.1" do
+    page.open "/"
+  end
+end
+\end{lstlisting}
+
+\paragraph{Selenium}
+
+There are a number of concerns with using Selenium and HTTPS as well as self
+signed certificates.
+
+Typical websites that provide HTTPS on the world wide web have a server
+certificate signed by a trusted authority, so the user is not required to agree
+to communicating with a possibly forged website. For the experiment a self
+signed certificate was used, which triggers a number of security warnings when
+accessed through most modern browsers. To automate acceptance of this security
+risk Selenium was configured with a special proxy which implicitly accepts any
+self signed certificates. The following steps were used to configure this proxy:
 
 \begin{enumerate*}
-  \item Deploy the experiment files onto the client system.
-  \item Install Ruby
-  \item Install the bundler ruby gem with the command:
+  \item A Firefox custom profile was generated. First Selenium was launched in
+    interactive mode:
 \begin{lstlisting}[language=sh]
-gem install bundler
+java -jar $selenium.jar -interactive
 \end{lstlisting}
-  \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
+  \item This starts an interactive prompt, a Firefox browser is then launched
+    using the following command:
 \begin{lstlisting}[language=sh]
-bundle install
+cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com
 \end{lstlisting}
-  \item Ensure that the client script is executed at system startup.
+  \item This created a profile directory in /tmp. This directory is copied to a
+    safe place, then all files were deleted except for \verb+cert_override.txt+
+    and \verb+cert8.db+.
+  \item All of the simulation sites were manually visited, with the server
+    certificate being permanently accepted. This saves the certificates to
+    \verb+cert_override.txt+ for future sessions.
 \end{enumerate*}
 
-\subsubsection{Configuring the Management Script}
+To configure selenium for use in Phase 2 and 3, the file \verb+proxy.pac+ is
+added to the Firefox profile with the following text:
 
-Once all systems are deployed, the management script needs to be altered to
+\begin{lstlisting}[language=java]
+function FindProxyForURL(url, host) {
+   if(shExpMatch(host, '*torsim')) {
+       return 'PROXY localhost:8118';
+   }
+   return 'PROXY localhost:4444; DIRECT';
+}
+\end{lstlisting}
+
+This makes sure that Tor gets used for outgoing connections, and the selenium
+proxy is used for running tests.
+
+But the tor relays must be able to resolve names using DNS, if you use socks4a protocol.
+
+\subsubsection{Server Guest}
+
+The host system runs an Apache web server which serves two sets of sample
+websites, static and dynamic. The static websites are served each from a
+different numbered directory and accessible over a different virtual host. This
+means that when a web browser is pointed at the host
+\verb+https://site1.static.torsim/+ the files in
+\verb+/var/www/thesis/experiment/simulation/static/site1+ are served to the
+browser.
+
+The dynamic web sites use Sinatra to serve content that varies over time, an
+example Sinatra script for \verb+https://site59.dynamic.torsim/+ is included
+below:
+
+\paragraph{index.rb}
+\lstinputlisting[language=ruby]{../experiment/simulation/site/dynamic/site59/index.rb}
+
+\paragraph{index.haml}
+\lstinputlisting[language=ruby]{../experiment/simulation/site/dynamic/site59/views/index.haml}
+
+Each time this site is accessed it renders a random number of iframes between 1
+and 20, with each iframe accessing the URI \verb+/content+ which renders between
+1 and 1000 random characters. This website periodically refreshes itself every
+five seconds.
+
+\subsubsection{Tor Network Guest}
+
+The Tor Network Guest is responsible for emulating a Tor network. It runs three
+Tor directory authorities as well as fifteen relays. Tor was installed on the
+Tor Network Guest using the same procedure listed in \ref{install-tor}. By
+default the Tor installation runs at start time, but this is disabled by
+removing execute permissions from the file \verb+/etc/init.d/tor+.
+
+The Tor nodes are configured using the script included in the Appendix section
+\ref{generate-tor-network-script}. At boot time the Tor Network Guest executes
+the Run Tor Network Script included in the Appendix section
+\ref{run-tor-network-script}.
 
@@
 
-Running the experiment is a matter of ensuring all Host systems are powered on,
-if everything is configured correctly the experiment will continue to run until
-stopped manually.
+Running the experiment is a matter of ensuring all hardware is configured
+correctly, all network connections active and all systems are powered on. Each
+simulation phase was executed for two weeks without any power outages or
+failures.
 

### 2011-02-26 thesis/thesis.tex
Ram speed and 'capacity' instead of amount
Add in another appendix, clarify one of the answers
Rewrite abstract

@@
 
-Traditional attacks against anonymity providing systems aim to uncover the
-identities of those involved. However, a more likely goal of attackers is to
-block or degrade the network itself, discouraging participation and forcing
-vulnerable users to communicate using less secure means. Since anonymous
-networks operate on known protocols and employ strong encryption it is
-difficult to distinguish them from regular traffic. This proposal describes a
-method for identifying traffic belonging to anonymous networks by examining
-their communication patterns.
+Anonymous networks provide security for users by obfuscating messages with
+encryption and hiding communications amongst cover traffic provided by other
+network participants. In the academic literature, traditionally these networks
+have been attacked with techniques that aim to uncover the identify of
+participants. But the success of an anonymous network relies not only on it's
+technical capabilities, but on adoption by a large enough user base to provide
+adequate cover traffic. If anonymous network participants can be identified, the
+users can be harassed, discouraging participation. Tor is an example of widely
+used anonymous network which uses a form of Onion Routing to provide low latency
+anonymous communications. This paper demonstrates that traffic from a simulated
+Tor network can be distinguished from regular encrypted traffic, suggesting that
+real world Tor users may be vulnerable to the same analysis.
 
@@
   \item CPU speed and number of cores
-  \item RAM speed and amount
+  \item RAM speed and capacity
   \item Performance of integrated components, system bus etc.
@@
 
-Yes.
+Yes, the classification algorithms trialled were all able to identify Tor traffic
+with reasonable accuracy.
 
@@
 confident match can be made?}
-
-Don't know... yet.
 
@@
 
+\label{manager-script}
 \lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}
@@
 
+\label{client-script}
 \lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}
+
+\section{Generate Tor Network Script}
+
+\label{generate-tor-network-script}
+\lstinputlisting[language=sh]{../experiment/simulation/tor/make_private_network.sh}
 
@@
 
+\label{run-tor-network-script}
 \lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}

### 2011-02-26 thesis/thesis.tex
Research methodology

@@
 encryption and hiding communications amongst cover traffic provided by other
-network participants. In the academic literature, traditionally these networks
-have been attacked with techniques that aim to uncover the identify of
-participants. But the success of an anonymous network relies not only on it's
-technical capabilities, but on adoption by a large enough user base to provide
-adequate cover traffic. If anonymous network participants can be identified, the
-users can be harassed, discouraging participation. Tor is an example of widely
-used anonymous network which uses a form of Onion Routing to provide low latency
+network participants. The traditional goal of academic research into these
+networks has been attacks that aim to uncover the identity of network users.
+But the success of an anonymous network relies not only on it's technical
+capabilities, but on adoption by a large enough user base to provide adequate
+cover traffic. If anonymous network nodes can be identified, the users
+can be harassed, discouraging participation. Tor is an example of widely used
+anonymous network which uses a form of Onion Routing to provide low latency
 anonymous communications. This paper demonstrates that traffic from a simulated
@@
 
-The proposed research will use a methodology typical of machine learning
-traffic analysis papers, substituting data captured from a controlled
-simulation in place of live network captures.
+\section{Research Methodology}
 
-The experiment will be conducted in two phases, the first being a data
-collection phase. The second phase will include a quasi experimental
-methodology which will include data manipulation techniques to prepare the
-collected data and a comparison of various heuristics and machine learning
-based traffic analysis to classify the collected data.
+The experiment conducted in this paper utilize a non-equivalent group design.
+The experimental groups are generated using simulations which allow for a great
+deal of control over independent variables, ensuring minimal difference between
+the control and treatment groups. Both experiment groups perform the exact same
+simulations. The control group performs all simulations using regular HTTPS,
+while the treatment group proxies all communications over Tor. The treatment
+group can be broken into HTTP over Tor and HTTPS over Tor based simulations.
 

### 2011-02-26 thesis/experiment.tex
Remove script copied verbatim, refer to file instead

@@
 
-\begin{lstlisting}[language=ruby]
-require "rubygems"
-gem "rspec"
-gem "selenium-client"
-require "selenium/client"
-require "selenium/rspec/spec_helper"
-
-describe "site1.static.torsim.1" do
-  attr_reader :selenium_driver
-  alias :page :selenium_driver
-
-  before(:all) do
-    @verification_errors = []
-    @selenium_driver = Selenium::Client::Driver.new \
-      :host => "localhost",
-      :port => 4444,
-      :browser => "*firefoxproxy",
-      :url => "https://site1.static.torsim/",
-      :timeout_in_second => 60
-  end
-
-  before(:each) do
-    @selenium_driver.start_new_browser_session
-  end
-
-  append_after(:each) do
-    @selenium_driver.close_current_browser_session
-    @verification_errors.should == []
-  end
-
-  it "test_site1.static.torsim.1" do
-    page.open "/"
-  end
-end
-\end{lstlisting}
+\lstinputlisting[language=ruby]{../experiment/simulation/client/scripts/site1.static.torsim.1_spec.rb}
 
@@
 
-But the tor relays must be able to resolve names using DNS, if you use socks4a protocol.
+But the tor relays must be able to resolve names using DNS, if you use socks4a
+protocol.
 
@@
 default the Tor installation runs at start time, but this is disabled by
-removing execute permissions from the file \verb+/etc/init.d/tor+.
+removing executable permissions from the file \verb+/etc/init.d/tor+.
 

### 2011-02-26 thesis/thesis.tex
Confounding variables, not independent. Conclusion and implications of results.

@@
 The experimental groups are generated using simulations which allow for a great
-deal of control over independent variables, ensuring minimal difference between
+deal of control over confounding variables, ensuring minimal difference between
 the control and treatment groups. Both experiment groups perform the exact same
@@
 
-\chapter{Conclusion}
-
-While it is difficult to draw a broad conclusion with the limited nature of the
-experiment conducted, the findings suggest that the strategies used by anonymous
-networks to thwart identity revealing traffic analysis may make them easier to
-identify.
+The research results suggest that the strategies used by anonymous networks to
+hide the identity of network participants, may make those anonymous networks
+more easy to distinguish from networks and software that do not provide any
+anonymity.
 
@@
 traffic analysis attacks that correlate traffic patterns with users. This
-transparency should in fact make Tor more difficult to classify than more
-'anonymous' network designs which employ batching and traffic normalizing.
-Steganography is a difficult problem and it may be that the extra traffic
-required to maintain the Tor network means it will always be easily
-differentiated from regular encrypted traffic.
+vulnerability is indicative of the subtle amount of overhead incurred when
+sending traffic through Tor. This should make it difficult to identify whether a
+connection is using Tor VS not using Tor, though it is clearly still possible.
+Reducing this overhead further may reduce the success of Tor traffic
+identification.
+
+Stronger anonymity providing networks utilize more sophisticated techniques to
+hide individual identities such as batching, queuing and normalization. While
+they may be more resistant to identity uncovering attacks, this may also make
+them more easily identifiable by classification techniques.
+
+\chapter{Conclusion}
+
+Using Tor as a communications proxy incurs some overhead, sufficient enough that
+when using a Tor proxy in controlled conditions, Tor traffic can be
+distinguished from regularly encrypted traffic. This overhead may be sufficient
+enough that Tor nodes in a real world network can be identified by using readily
+available eavesdropping techniques.
+
+However, the experiment was based on a small set of simulated data, with which
+it would be impossible to cover all the possible real world conditions. The
+variability present in the real Tor network may make this classification
+technique impossible. Further research needs to be conducted with live packet
+traces from real participants in the Tor network.
 

### 2011-02-27 thesis/experiment.tex
Split out into different sections, more rewriting as per suggestions.

@@
   \parencite{:2010zr,:ve} that supports remote command execution
-  \parencite{Tucker:2010ly, :2010zr}. The client component of OpenSSH is
-  installed by default on the Ubuntu operating system and the server component
-  is easily installed using the apt-get package management system.
+  \parencite{Tucker:2010ly}. The client component of OpenSSH is installed by
+  default on the Ubuntu operating system and the server component is easily
+  installed using the apt-get package management system.
 
@@
 
-  RSpec is a testing framework for Ruby which allows the creation of examples in
-  an easy to read Domain Specific Language (DSL). It is well integrated with
-  Selenium which makes it ideal for running large suites of Selenium tests.
+  RSpec is a behaviour driven testing framework for Ruby which allows the
+  creation of examples in an easy to read Domain Specific Language (DSL)
+  \parencite{Chelimsky:2010vn}. It is well integrated with Selenium which makes
+  it ideal for running large suites of Selenium tests.
 
@@
 Four identical desktop computer systems were prepared and arranged as shown
-in figure \ref{physical-setup}.
+in figure \ref{fig:physical-setup}.
 
@@
   \caption{Physical Setup}
-  \label{physical-setup}
+  \label{fig:physical-setup}
 \end{figure}
@@
 
+\begin{table}[H]
   \begin{tabular}{lrr}
@@
     \bottomrule
+  \end{tabular}
+  \caption{System Roles}
   \label{table:hosts}
-\end{tabular}
+\end{table}
 
-Figure \ref{network-diagram} shows the placement of applications and relevant
+Figure \ref{fig:network-diagram} shows the placement of applications and relevant
 data flows when running the simulation in HTTPS mode.
@@
   \caption{Network Diagram: Phase 1}
-  \label{network-diagram}
+  \label{fig:network-diagram}
 \end{figure}
 
-Figure \ref{network-diagram-with-tor} shows the network configuration when
+Figure \ref{fig:network-diagram-with-tor} shows the network configuration when
 running the experiment in HTTP over Tor mode.
@@
   \caption{Network Diagram: Phase 2}
-  \label{network-diagram-with-tor}
+  \label{fig:network-diagram-with-tor}
 \end{figure}
 
-Figure \ref{network-diagram-with-tor-encrypted} shows the network configuration when
+Figure \ref{fig:network-diagram-with-tor-encrypted} shows the network configuration when
 running the experiment in HTTPS over Tor mode.
@@
   \caption{Network Diagram: Phase 3}
-  \label{network-diagram-with-tor-encrypted}
+  \label{fig:network-diagram-with-tor-encrypted}
 \end{figure}
@@
 All systems in the experiment use a variation of the Ubuntu Linux operating
-system. The installation process followed is detailed below:
+system. Table \ref{table:config-options} specifies the options supplied when
+installing each operating system for the experiment.
 
-\begin{enumerate*}
-  \item Configure system BIOS to boot from CD-ROM
-  \item Insert Ubuntu operating system installation CD
-  \item Select the language you wish to use for installation (English) and click
-    'Forward'
-  \item Select the region (Australia/Perth) and click 'Forward'
-  \item Select an appropriate keymap (USA) and click 'Forward'
-  \item Select 'Erase and use the entire disk' and click 'Forward'
-  \item Enter the user name (John Barker), select 'Log in automatically' and click 'Forward'
-\end{enumerate*}
-
-At this point the installation will begin and should take about 35 minutes.
-'Log in automatically' is selected to ensure that the experiment will continue
-even if power is lost. Once installation is complete remove the CD and reboot
-the system. Once booted the system is ready for further configuration.
+\begin{table}[H]
+  \begin{tabular}{lr}
+    \toprule
+    Prompt & Value\\
+    \midrule
+    Where are you? & Australia/Perth\\
+    Which layout is most similar to your keyboard? & USA\\
+    How do you want to partition the disk? & Erase and use the entire disk\\
+    What is your name? & John Barker\\
+    What name do you want to use to log in? & john\\
+    \bottomrule
+  \end{tabular}
+  \caption{Ubuntu Installation Parameters}
+  \label{table:config-options}
+\end{table}
 
@@
 filter string after the system had powered on. All capture files were limited to
-1mb in size and put into a time stamped directory. To ensure that only relevant
+1MB in size and put into a time stamped directory. To ensure that only relevant
 packets were collected the filter string was tuned for each phase of the
@@
 
+\begin{table}[H]
   \begin{tabular}{lrr}
     \toprule
-  Phase & Size (bytes) & Number of sessions\\
+    Phase & Size in bytes & Number of sessions\\
     \midrule
@@
   \end{tabular}
+  \caption{Captured Data}
+\end{table}
 
-The data captured was in the form of 1mb capture files which were recombined
+The data captured was in the form of 1MB capture files which were recombined
 with mergecap and processed by NetAI to produce ARFF format files for use by

### 2011-02-27 thesis/litreview.tex
Split out into different sections, more rewriting as per suggestions.

--- 2011-02-26 thesis/thesis.tex
@@
-\documentclass{ecuthesis}
-
-% For graphics
-\usepackage{graphicx}
-
-% Bibliography
-\bibliography{fullrefs,websites,patents,papers}
-
-% Setup the variables for the title page
-\title{Using traffic analysis to identify The Second Generation Onion Router}
-\author{John Barker}
-\department{School of Computer and Security Science}
-\school{Edith Cowan University}
-\degree{Computer Science (Honours)}
-\email{jebarker@our.ecu.edu.au}
-\studentid{0991300}
-\supervisor{Dr Andrew Woodward}
-\supervisor{Mr Peter Hannay}
-\supervisor{Mr Patryk Szewczyk}
-
-% Begin document
-\begin{document}
-\maketitle
-
-\tableofcontents
-\listoftables
-\listoffigures
-
-\begin{abstract}
-\thispagestyle{empty}
-
-Anonymous networks provide security for users by obfuscating messages with
-encryption and hiding communications amongst cover traffic provided by other
-network participants. In the academic literature, traditionally these networks
-have been attacked with techniques that aim to uncover the identify of
-participants. But the success of an anonymous network relies not only on it's
-technical capabilities, but on adoption by a large enough user base to provide
-adequate cover traffic. If anonymous network participants can be identified, the
-users can be harassed, discouraging participation. Tor is an example of widely
-used anonymous network which uses a form of Onion Routing to provide low latency
-anonymous communications. This paper demonstrates that traffic from a simulated
-Tor network can be distinguished from regular encrypted traffic, suggesting that
-real world Tor users may be vulnerable to the same analysis.
-
-\end{abstract}
-
-\chapter{Introduction}
-
-\section{Background}
-
-The Internet has revolutionised the political sphere in providing a platform
-for the publication of speech to a far greater audience than was ever available
-before digital communications systems \parencite{Bonchek:1997p3455}. The
-publication of less desirable political speech, criticism or challenging ideas
-still carries with it great risk, with numerous publications leading to arrest.
-This has spawned headlines such as \textcite{website:egypt-arrests},
-\citetitle{website:china-yahoo-torture}
-\parencite{website:china-yahoo-torture},
-\citetitle{website:vietnam-bloggers-arrested}
-\parencite{website:vietnam-bloggers-arrested},
-\textcite{website:iran-bloggers-arrested} and
-\citetitle{website:blogger-arrests} \parencite{website:blogger-arrests}. The
-Internet, like conventional media, is still vulnerable to censorship by
-oppressive governments and malicious attackers
-\parencite{Crandall:2007p6165,Karlin:2009p6166}.
-
-In response to these threats, a number of systems have been proposed which use
-various techniques, primarily cryptography and covering traffic, to provide
-censorship resistance and anonymity. The Second Generation Onion Router (Tor),
-is an anonymous network which uses a variant of Onion Routing, to provide low
-latency anonymous communications to a wide variety of Internet communications
-protocols \parencite{Dingledine:2004p314}. It also aims to provide resistance
-against censorship based blocking attempts \parencite{Dingledine:2008p1542}.
-
-Although Tor succeeds to a certain extent in these goals, it may be possible to
-use traffic analysis techniques to automatically identify Tor connections and
-target them for attacks. Since Tor relies on large numbers of users for the
-protections it provides, attacks that affect the reliability of the network can
-discourage participation, making it ineffective. This paper proposes a traffic
-analysis methodology for identifying Tor traffic which may be used for such
-attacks in the future.
-
-\section{Significance}
-
-Tor is one of the most successful and widely deployed anonymous networks, with
-around one thousand, eight hundred users at the time of writing
-\parencite{website:tor-anonymity-online}. While it has been the subject of many
-traffic analysis attacks, the primary objective has historically been the
-attempt to reveal participant identities: ``The principal objective of an
-adversary attacking an anonymous communication system is to link the initiators
-of connections with their respective communication partners and vice versa''
-\parencite[3]{Murdoch:2005p325}.
-
-The traffic analysis techniques proposed will attempt to classify network
-streams belonging to Tor users to distinguish them from regular encrypted
-communications. This research may provide a greater understanding of just
-how much anonymity a user of the Tor network is provided and inspire
-the development of countermeasures against analysis.
-
-\section{Research Questions}
-
-Given a motivated and universal attacker, it is inexpensive and straightforward
-to disconnect a user from these networks by blocking access to well known and
-published resources. Once these avenues of attack have been exhausted it is
-still possible to connect to the network by connecting to lesser known access
-points. Since these networks are capable of communicating using many of the
-same methods as most conventional Internet applications, a blanket ban on this
-kind of communication would be too broad and extensive.
-
-Tor employs strong encryption, the goal of which is to ensure that the data
-transmitted is indistinguishable from random noise. To an observer, data
-transmitted using encryption looks the same. Thus the traditional means of
-identifying these protocols are ineffective.
-
-This raises the question: is it possible to distinguish the traffic created by
-these networks, from encrypted traffic produced by conventional software? This
-question can be broken down further:
-
-\begin{enumerate*}
-  \item Can the traffic be classified using automated matching techniques?
-  \item Do these networks have characteristics that make them readily
-    distinguishable using heuristics based matching?
-  \item Do they have characteristics that make them distinguishable using a
-    machine learning technique?
-  \item How long does a user have to be
-    connected to the network before a confident match can be made?
-\end{enumerate*}
-
 \chapter{Literature Review}
@@
 capture private information \parencite{website:tor-password-leak}, attacks that
-take advantages of web based technologies such as Javascript and Flash to
-reveal user's identities \parencite{Abbott:2007p298} and a number of identity
-revealing traffic analysis techniques
-\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}. Notable is the
-discovery of a method for identifying bridge operators as discussed in
-\textcite{McLachlan:2009p197}. This attack takes advantages in weaknesses of
-the Tor protocol to enumerate bridges and some approaches to mitigation are
-suggested. It is believed that this is the first proposal of a traffic analysis
-technique for classification of Tor network streams.
+take advantages of web based technologies such as Javascript and Flash to reveal
+user's identities \parencite{Abbott:2007p298} and a number of identity revealing
+traffic analysis techniques
+\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}.
+\citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
+operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.  It
+is believed that this is the first proposal of a traffic analysis technique for
+classification of Tor network streams.
 
@@
 goals.
-
-\chapter{Theoretical Framework}
-
-The proposed research will use a methodology typical of machine learning
-traffic analysis papers, substituting data captured from a controlled
-simulation in place of live network captures.
-
-The experiment will be conducted in two phases, the first being a data
-collection phase. The second phase will include a quasi experimental
-methodology which will include data manipulation techniques to prepare the
-collected data and a comparison of various heuristics and machine learning
-based traffic analysis to classify the collected data.
-
-\section{Assumptions}
-
-It is assumed that the usage patterns exhibited by individual users will be
-smaller than the communications characteristics that will lead to the
-identification of anonymous and censorship resistant networks. Thus there is no
-need to obtain a large sample of regular network traffic from varying user
-profiles.
-
-As of the current implementation, Tor network traffic is readily
-distinguishable by looking at the handshake packets. It is likely that this
-weakness will be addressed in a future version of the Tor protocol as it is
-recognised as a design goal in \textcite{Dingledine:2008p1542}. For this
-reason, this proposal focuses on traffic analysis techniques that are content
-agnostic.
-
-\section{Variables}
-
-The data capturing stage will be affected by a number of variables that will
-influence the accuracy of the chosen matching algorithms.
-
-\subsection{Quality of the Anonymous Network}
-
-An individual connection to the Tor network traverses a number of nodes to
-create a circuit. The path a circuit uses is first defined by the exit node,
-then chosen based on a number of constraints with a preference for high
-bandwidth relays \parencite{website:tor-path-selection}. Since each connection
-uses a different circuit and bandwidth demands are constantly changing, it is
-difficult to predict the composition of a Tor circuit.
-
-This means that any individual Tor circuit could be composed of systems with
-differing capabilities, network throughput and configuration.
-
-For testing purposes, the Tor network can be simulated on a small isolated
-network. This will eliminate a lot of the variability that comes from
-monitoring the real Tor network. Factors that affect the quality of the network
-can be controlled by limiting the number of competing network applications,
-controlling the number of running Tor instances and ensuring a consistent
-configuration across all nodes.
-
-\subsection{System Performance}
-
-The ability of Tor to route packets in a timely fashion is highly dependent on
-the performance of the system it is executing on. This is greatly compounded by
-the usage of strong encryption which is computationally expensive. Packet
-latency is one of the key parameters used in traffic classification techniques.
-Performance related variables include:
-
-\begin{itemize*}
-  \item CPU speed and number of cores
-  \item RAM speed and capacity
-  \item Performance of integrated components, system bus etc.
-  \item Hard disk size, access time and throughput
-  \item Installed and running applications
-  \item System configuration
-\end{itemize*}
-
-To remedy this, the systems used to simulate the Tor network should be made
-uniform. This means an identical hardware and software configuration for all
-systems in the simulation network.
-
-In addition it is noted that system performance can degrade over time due to
-both memory and hard disk fragmentation. This can be avoided by running the
-simulations in a virtualisation environment that support snapshots, rolling
-back to a known configuration point after each test.
-
-\subsection{Network Performance}
-
-Like system performance, latency is also dependent on the quality of the
-network. Network switching equipment has limited resources for routing packets
-and competing network traffic can introduce congestion which would radically
-alter the observable communications patterns \parencite{Jacobson:1995p6768}.
-Tor also supports congestion mitigation techniques which alter communication
-patterns \parencite[8]{Dingledine:2004p314}.
-
-Latency and network performance over the Internet are highly variable and
-beyond the control of any one individual. Usage patterns vary according to
-geographic region, societal conventions and the period in which they occur
-\parencite{Thompson97wide-areainternet,Ken03longitudinalstudy}. The Internet,
-and by necessity the public Tor network are globally distributed, which means
-that circuits traverse a large variety of unpredictable network conditions. By
-isolating the test network, these variables can be controlled ensuring low
-latency high bandwidth communications or congestion as necessary.
-
-\subsection{Application Protocol}
-
-Tor provides communications facilities to a number of Internet enabled
-applications by providing an interface using the SOCKS protocol
-\parencite[17]{Dingledine:2004p314}. This means that the Tor network can proxy
-regular web browsing, email or any other TCP or UDP based communication protocol
-\parencite{website:socks}. Each of these application protocols have their own
-distinguishing communications characteristics which will influence the matching
-algorithm. It is not yet clear how transparent the Tor network will be regarding
-these characteristics and thus, for the purposes of classification a single
-protocol should be chosen.
-
-\subsection{Caching}
-
-Both web browsers and web servers are designed for high performance and often
-cache requests so that they can be delivered faster in the future
-\parencite{Caceres:1998p7419}. While this is a normal part of communications
-traffic and should be considered, it is important that both regular and cached
-requests appear uniformly across all experiments. Manually flushing the cache
-or rolling back to a known virtual machine snapshot between each simulation can
-ensure this outcome.
-
-\input experiment.tex
-
-\chapter{Results}
-
-\section{Results}
-
-The classification results are tabulated below. The best performing algorithm
-j4.8 was able to classify HTTP over Tor with 97.8\% accuracy and a false
-positive rate of 4.3\%. HTTPS was more easily identified with a 97\% accuracy
-and low false positive rate of 0.7\%.
-
-\begin{table}
-  \begin{tabular}{lrrr}
-    \toprule
-    & True Positive Rate & False Positive Rate & ROC \\
-    \midrule
-    Random Forest\\
-    \midrule
-    HTTPS & 0.957 & 0.036\\
-    HTTP over Tor & 0.937 & 0.037\\
-    HTTPS over Tor & 0.977 & 0.003\\
-    \midrule
-    j4.8 With 10 fold cross validation\\
-    \midrule
-    HTTPS & 0.951 & 0.04\\
-    HTTP over Tor & 0.978 & 0.043\\
-    HTTPS over Tor & 0.97 & 0.007\\
-    \midrule
-    Random Tree\\
-    \midrule
-    HTTPS & 0.961 & 0.046\\
-    HTTP over Tor & 0.906 & 0.04\\
-    HTTPS over Tor & 0.955 & 0.01\\
-    \midrule
-    Adaboost\\
-    \midrule
-    HTTPS & 0.95 & 0.001\\
-    HTTP over Tor & 0.999 & 0.324\\
-    HTTPS over Tor & 0 & 0\\
-    \bottomrule
-    \label{table:results}
-  \end{tabular}
-  \caption{Results}
-\end{table}
-
-\chapter{Discussion of Results}
-
-\section{Limitations}
-
-The classifiers developed within this experiment have been trained against
-a relatively small sample set of simulated data, which may only represent
-a small fraction of the width and breadth of conditions available on a wider
-area network. The characteristics that allow for classification of Tor network
-may be masked by the natural variability introduced by a heterogeneous network.
-
-\section{Addressing Research Questions}
-
-\subsection{Can the traffic be classified using automated matching techniques?}
-
-Yes, the classification algorithms trialled were all able to identify Tor traffic
-with reasonable accuracy.
-
-\subsection{Do these networks have characteristics that make them readily
-distinguishable using heuristics based matching?}
-
-\subsection{Do they have characteristics that make them distinguishable using a
-machine learning technique?}
-
-Yes.
-
-\subsection{How long does a user have to be connected to the network before a
-confident match can be made?}
-
-\section{Possible Implications of Results}
-
-\chapter{Conclusion}
-
-While it is difficult to draw a broad conclusion with the limited nature of the
-experiment conducted, the findings suggest that the strategies used by anonymous
-networks to thwart identity revealing traffic analysis may make them easier to
-identify.
-
-Research has shown that the low latency design of Tor means it is vulnerable to
-traffic analysis attacks that correlate traffic patterns with users. This
-transparency should in fact make Tor more difficult to classify than more
-'anonymous' network designs which employ batching and traffic normalizing.
-Steganography is a difficult problem and it may be that the extra traffic
-required to maintain the Tor network means it will always be easily
-differentiated from regular encrypted traffic.
-
-\chapter{Appendix}
-
-\section{Manager Script}
-
-\label{manager-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}
-
-\section{Client Script}
-
-\label{client-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}
-
-\section{Generate Tor Network Script}
-
-\label{generate-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/make_private_network.sh}
-
-\section{Run Tor Network Script}
-
-\label{run-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}
-
-\printbibliography[title=REFERENCES]
-
-\end{document}
-
-% vim: fdm=syntax tw=80

### 2011-02-27 thesis/results.tex
Split out into different sections, more rewriting as per suggestions.

--- 2011-02-26 thesis/thesis.tex
@@
-\documentclass{ecuthesis}
-
-% For graphics
-\usepackage{graphicx}
-
-% Bibliography
-\bibliography{fullrefs,websites,patents,papers}
-
-% Setup the variables for the title page
-\title{Using traffic analysis to identify The Second Generation Onion Router}
-\author{John Barker}
-\department{School of Computer and Security Science}
-\school{Edith Cowan University}
-\degree{Computer Science (Honours)}
-\email{jebarker@our.ecu.edu.au}
-\studentid{0991300}
-\supervisor{Dr Andrew Woodward}
-\supervisor{Mr Peter Hannay}
-\supervisor{Mr Patryk Szewczyk}
-
-% Begin document
-\begin{document}
-\maketitle
-
-\tableofcontents
-\listoftables
-\listoffigures
-
-\begin{abstract}
-\thispagestyle{empty}
-
-Anonymous networks provide security for users by obfuscating messages with
-encryption and hiding communications amongst cover traffic provided by other
-network participants. The traditional goal of academic research into these
-networks has been attacks that aim to uncover the identity of network users.
-But the success of an anonymous network relies not only on it's technical
-capabilities, but on adoption by a large enough user base to provide adequate
-cover traffic. If anonymous network nodes can be identified, the users
-can be harassed, discouraging participation. Tor is an example of widely used
-anonymous network which uses a form of Onion Routing to provide low latency
-anonymous communications. This paper demonstrates that traffic from a simulated
-Tor network can be distinguished from regular encrypted traffic, suggesting that
-real world Tor users may be vulnerable to the same analysis.
-
-\end{abstract}
-
-\chapter{Introduction}
-
-\section{Background}
-
-The Internet has revolutionised the political sphere in providing a platform
-for the publication of speech to a far greater audience than was ever available
-before digital communications systems \parencite{Bonchek:1997p3455}. The
-publication of less desirable political speech, criticism or challenging ideas
-still carries with it great risk, with numerous publications leading to arrest.
-This has spawned headlines such as \textcite{website:egypt-arrests},
-\citetitle{website:china-yahoo-torture}
-\parencite{website:china-yahoo-torture},
-\citetitle{website:vietnam-bloggers-arrested}
-\parencite{website:vietnam-bloggers-arrested},
-\textcite{website:iran-bloggers-arrested} and
-\citetitle{website:blogger-arrests} \parencite{website:blogger-arrests}. The
-Internet, like conventional media, is still vulnerable to censorship by
-oppressive governments and malicious attackers
-\parencite{Crandall:2007p6165,Karlin:2009p6166}.
-
-In response to these threats, a number of systems have been proposed which use
-various techniques, primarily cryptography and covering traffic, to provide
-censorship resistance and anonymity. The Second Generation Onion Router (Tor),
-is an anonymous network which uses a variant of Onion Routing, to provide low
-latency anonymous communications to a wide variety of Internet communications
-protocols \parencite{Dingledine:2004p314}. It also aims to provide resistance
-against censorship based blocking attempts \parencite{Dingledine:2008p1542}.
-
-Although Tor succeeds to a certain extent in these goals, it may be possible to
-use traffic analysis techniques to automatically identify Tor connections and
-target them for attacks. Since Tor relies on large numbers of users for the
-protections it provides, attacks that affect the reliability of the network can
-discourage participation, making it ineffective. This paper proposes a traffic
-analysis methodology for identifying Tor traffic which may be used for such
-attacks in the future.
-
-\section{Significance}
-
-Tor is one of the most successful and widely deployed anonymous networks, with
-around one thousand, eight hundred users at the time of writing
-\parencite{website:tor-anonymity-online}. While it has been the subject of many
-traffic analysis attacks, the primary objective has historically been the
-attempt to reveal participant identities: ``The principal objective of an
-adversary attacking an anonymous communication system is to link the initiators
-of connections with their respective communication partners and vice versa''
-\parencite[3]{Murdoch:2005p325}.
-
-The traffic analysis techniques proposed will attempt to classify network
-streams belonging to Tor users to distinguish them from regular encrypted
-communications. This research may provide a greater understanding of just
-how much anonymity a user of the Tor network is provided and inspire
-the development of countermeasures against analysis.
-
-\section{Research Questions}
-
-Given a motivated and universal attacker, it is inexpensive and straightforward
-to disconnect a user from these networks by blocking access to well known and
-published resources. Once these avenues of attack have been exhausted it is
-still possible to connect to the network by connecting to lesser known access
-points. Since these networks are capable of communicating using many of the
-same methods as most conventional Internet applications, a blanket ban on this
-kind of communication would be too broad and extensive.
-
-Tor employs strong encryption, the goal of which is to ensure that the data
-transmitted is indistinguishable from random noise. To an observer, data
-transmitted using encryption looks the same. Thus the traditional means of
-identifying these protocols are ineffective.
-
-This raises the question: is it possible to distinguish the traffic created by
-these networks, from encrypted traffic produced by conventional software? This
-question can be broken down further:
-
-\begin{enumerate*}
-  \item Can the traffic be classified using automated matching techniques?
-  \item Do these networks have characteristics that make them readily
-    distinguishable using heuristics based matching?
-  \item Do they have characteristics that make them distinguishable using a
-    machine learning technique?
-  \item How long does a user have to be
-    connected to the network before a confident match can be made?
-\end{enumerate*}
-
-\chapter{Literature Review}
-
-The main areas of research included papers and proposals on the design of
-anonymity networks and those covering the subject of traffic analysis.
-Particular attention has been paid to encryption as it is the primary function
-by which these systems operate and a good understanding is necessary for the
-development of an appropriate traffic analysis method.
-
-\section{Encryption}
-
-Since the creation of language, the interception of messages by hostile forces
-has compelled the development of secretive communications. This deliberate
-transformation of a message, so that only the intended recipient can understand
-it, is known as encryption. The process of examining these obfuscated messages
-and attempting to reverse the transformation is known as cryptanalysis
-\parencite{Schneier:1996uq}. These fields have been locked in an arms race
-ever since, each side continually advancing their capabilities in an attempt to
-gain ground.
-
-Apart from One Time Pads, no encryption methodology has ever proven to be
-unbreakable \parencite{Shannon:1948p6583}. This means that all remaining
-cryptographic methods are a way of transforming information, so that for an
-attacker the difficulty in reversing this transformation is too costly to make
-it worthwhile. The invention of robots and computers was precipitated by the
-need to break encryption methods of increasing complexity and at the same time
-has lead to the increasing complexity of encryption algorithms
-\parencite{Kahn:1974:C}.
-
-Historically, all encryption methods have required an interaction between those
-communicating. A meeting to exchange the secret communications key, or a
-courier to deliver the encryption device. This made anonymous communications
-difficult, especially when using digital communications technologies.  In
-\citeyear{Jevons:1874vn}, \citeauthor{Jevons:1874vn}, perhaps
-unknowingly, uncovered the mathematical techniques that would allow for public
-key cryptography in his publication \citetitle{Jevons:1874vn}. He recognised
-that certain mathematical operations yielded products that were impossible or
-difficult to reverse in order to uncover the factors used.
-
-The possibility of public key cryptography, or non-secret encryption was
-conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and later developed
-into both a method for sharing secret encryption keys by Malcolm J. Williamson
-in 1974 \parencite{Singh:1999:CBE} and a method for asymmetric encryption
-\parencite{Cocks:1973p3265}.
-
-These papers were not published at the time due to their military
-classification, allowing these methods to be reinvented independently
-\parencite{Singh:1999:CBE}. The method for key sharing developed by Ellis
-later became known as the Diffie-Hellman key exchange
-\parencite{Diffie:1976p585}, while the method for asymmetric encryption is now
-known as RSA encryption, taking its name from the initials of its creators,
-Rivest, Shamir and Adleman \parencite{Rivest:1978p708}. Figure
-\ref{key-exchange} shows how discrete logarithms are used in the Diffie-Hellman
-algorithm to generate a shared encryption key.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{key-exchange}
-  \caption{Diffie-Hellman Key Exchange}
-  \label{key-exchange}
-\end{figure}
-
-% How to relate back to Tor:
-% What algorithm does Tor use
-% How does encryption resist traffic analysis
-% Modern encryption algorithms ensure resistance to frequency analysis by making sure every character in a message appears as likely as every other character.
-To an observer, this means that encrypted messages appear to be indistinguishable to noise.
-
-While these early public key encryption algorithms are still in use, newer
-implementations have appeared which make improvements including
-\textcite*{ElGamal:1985p529} and \textcite{Cramer:1998p3186}. Attempts to make
-these encryption algorithms more difficult to break have involved the use of
-increasingly complex mathematical problems such as elliptic curves
-\parencite{Miller:1986p2966,Koblitz:1987p3109} and probabilistic functions
-\parencite{Paillier:1999p3152}. Many of these encryption algorithms are
-available in modern encryption protocols.
-
-Early proposals for digital networks included extensive usage of encryption
-technology. \textcite{Baran:1964p384} suggested that future digital military
-networks should use encryption for all messages, even those that did not
-require any secrecy. He cited benefits such as tamper resistance, message
-secrecy and resistance to traffic analysis, although this system was never
-implemented. The Internet, was developed without encryption features
-\parencite{website:internet}.
-
-Early work in encrypted Internet communications includes the Secure Network
-Programming (SNP) Applications Programming Interface (API)
-\parencite{Woo:1994p2532}. This was a simple framework providing numerous
-encryption, signing and authentication methods. The Secure Sockets Layer (SSL)
-is an encryption layer which provided end-to-end communications secrecy on the
-Internet \parencite{website:SSL}. A primary feature of SSL is the ability to
-exchange secret keys using public key algorithms.
-
-This proposed standard went through a number of revisions, with early versions
-suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
-Transport Layer Security (TLS), with the latest version 1.2 being released
-August 2008 \parencite{website:TLS}. TLS addresses some issues in SSL and
-provides a number of enhancements, but is not compatible with SSL.
-
-The Hypertext Transfer Protocol Secure (HTTPS) provides encryption using both
-the TLS and SSL protocols \parencite{website:HTTPS} and is available in almost
-all modern web browsers including Firefox
-\parencite{website:firefox-encryption}, Safari
-\parencite{website:safari-features} and Internet Explorer
-\parencite{website:microsoft-tls}. Tor provides encryption through usage of the
-TLS protocol.
-
-\section{Anonymous and Censorship Resistant Networks}
-
-The first anonymous network system MixNet, was described in
-\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
-encryption to prevent eavesdroppers from obtaining message delivery information.
-Senders in the network communicate with a centrally located server known as a
-mix, delivering a message with the address of the intended recipient. The mix
-server discards any information about the sender and delivers it to the final
-destination. Figure \ref{chaums-mix-network} depicts the process of message
-delivery in Chaum's MixNet. Chaum's proposal also allowed for the chaining of
-multiple mix servers together to form a cascade.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{chaums-mix-network}
-  \caption{MixNet Message Delivery}
-  \label{chaums-mix-network}
-\end{figure}
-
-Since the inception of MixNet, numerous anonymous networks have been proposed,
-each design being influenced by diverse motivations for obtaining anonymity.
-These include:
-
-\begin{itemize*}
-  \item Anonymous remailers such as Babel \parencite{Gulcu:1996p1662} and
-    Mixminion \parencite{Danezis:2003ys}.
-  \item Networks that provide mathematically provable anonymity
-    \parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303}.
-  \item Anonymity that degrades gracefully when subject to attack, so called
-    robust anonymity \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
-  \item Anonymous publishing in Freedom \parencite{Goldberg:1999p2231} and
-    Freenet \parencite{Clarke:2001p2435}.
-  \item Peer to Peer (P2P) anonymity such as MorphMix
-    \parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
-    \parencite{P5Sherwood:2005p5872}.
-  \item Censorship resistance in aChord and gnuNet \parencite{Hazel:2002p6929},
-    Infranet \parencite{Feamster:2002p307} and of course Tor.
-\end{itemize*}
-
-This is by no means an exhaustive list, for an excellent survey of anonymous
-networks consult \textcite{Danezis:2008p346}.
-
-Although this research has yielded a variety of designs, all anonymous
-networks essentially operate on all or some of the following principles:
-
-\begin{itemize*}
-  \item Encrypting traffic to prevent eavesdropping.
-  \item Providing covering traffic through a network of active users or by
-    generating it automatically.
-  \item Normalizing message delivery so that individual communication patterns
-    are not identifiable.
-\end{itemize*}
-
-In theory, the normalization techniques used by anonymous networks should make
-them readily distinguishable from non anonymous communications.
-
-\subsection{The Second Generation Onion Router (Tor)}
-
-Tor was first described in \citetitle{Dingledine:2004p314}
-\parencite{Dingledine:2004p314}. This new generation of onion router was
-designed with a number of defences for common traffic analysis attacks and
-weaknesses discovered in other proposals. With a focus on deployability,
-usability, flexibility and simple-design \parencite[3-4]{Dingledine:2004p314}
-as well as a successful implementation, it has seen wider deployment than most
-other anonymous networks.
-
-Like MixNet, public key cryptography is combined with intermediate servers
-responsible for message delivery to provide a degree of anonymity. In Tor,
-these mixes are known as relays and are typically chained together to
-construct a circuit. Clients connect to the Tor network by communicating
-with a special relay known as a bridge, which constitutes the first
-relay in a circuit. Traffic is repeatedly delivered through relays until it
-reaches another special relay known as an exit node, where it is
-delivered unencrypted to the final destination. Figure \ref{tor-network} shows
-this typical usage of the Tor network.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
-  \caption{The Tor Network}
-  \label{tor-network}
-\end{figure}
-
-Messages delivered through the Tor network are encrypted multiple times using a
-variation of onion routing \parencite{Michael:2001} known as telescopic onion
-routing. Circuits are built incrementally, obtaining a session key from each
-successive relay in the circuit and encrypting messages so that intermediate
-relays are unable to decrypt the message. Since circuits can take some time to
-build, they are pre-emptively created at regular intervals
-\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
-traffic normalization techniques that provide strong anonymity, messages passed
-through the Tor network are packaged in cells of a fixed size of 512 bytes
-\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
-that remove identifying features from common application protocols.
-
-After it was noticed that Tor was being used to circumvent censorship as well
-as for anonymity, a publication was released which attempts to identify the
-issues that need to be addressed in order for Tor to provide some level of
-censorship resistance \parencite{Dingledine:2008p1542}. Although this paper
-foresees future attacks such as the one contained in this proposal, it mostly
-tackles social issues of censorship resistance.
-
-\section{Traffic Analysis}
-
-Research into Tor weaknesses has included the use of hostile exit nodes to
-capture private information \parencite{website:tor-password-leak}, attacks that
-take advantages of web based technologies such as Javascript and Flash to
-reveal user's identities \parencite{Abbott:2007p298} and a number of identity
-revealing traffic analysis techniques
-\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}. Notable is the
-discovery of a method for identifying bridge operators as discussed in
-\textcite{McLachlan:2009p197}. This attack takes advantages in weaknesses of
-the Tor protocol to enumerate bridges and some approaches to mitigation are
-suggested. It is believed that this is the first proposal of a traffic analysis
-technique for classification of Tor network streams.
-
-When considering the use of traffic analysis for classification of Internet
-communications, three techniques are used. These are: exact matching, heuristic
-matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
-techniques recognise properties of communications that mirror known protocols
-and communication patterns. This might include the port an application uses or
-the format of its payload. Since Tor employs strong encryption and communicates
-using known and commonly used protocols, exact matching techniques would prove
-ineffective for classification. Heuristic matching looks for patterns in
-conversations to determine communications patterns and infer relationships,
-while machine learning involves the use of statistics to train computer
-algorithms to classify traffic. Both heuristic and machine matching techniques
-are suitable for traffic analysis of anonymous networks because they do not
-rely on analysing the content of messages.
-
-\subsection{Heuristic Techniques}
-
-The increasing burden of peer to peer (P2P) applications on campus networks,
-and their shift to encryption motivated the development of heuristics based
-techniques for identifying P2P traffic. Early techniques include identifying
-known properties of P2P networks such as often communicating using both the UDP
-and TCP protocols simultaneously and using a solitary connection to transfer
-high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
-number of false positives by eliminating packets that matched known
-communications protocols.
-
-Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
-\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
-through early elimination of false positives and by expanding the scope of
-matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
-to identify P2P nodes before applying a secondary heuristic to identify
-‘supernodes’ which are a subset of all P2P nodes.
-
-Classifying traffic based on system roles is a key feature of the technique
-that appears in \citetitle{Karagiannis:2005p6359}
-\parencite{Karagiannis:2005p6359}. By analysing communications at the host
-level then at increasing levels of granularity, a greater level of accuracy is
-achieved.
-
-The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
-\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
-flows are represented in a TDG, mathematical properties of the flow can be
-analysed to make positive identifications.
-
-Viruses have also posed a problem for network administrators, often
-over-utilizing network resources and using the network to infect new machines.
-A technique for identifying various worms was proposed in
-\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
-from network administrators to avoid detection, presenting the same problems of
-identification as Tor network traffic.
-
-\subsection{Machine Learning Techniques}
-
-\subsubsection{Expectation-Maximisation}
-
-The first use of machine learning to categorise traffic flows appears in
-\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
-be used for machine learning and an attempt at coarse grained classification
-using an expectation-maximisation (EM) algorithm are demonstrated. The
-expectation-maximisation algorithm is a method for finding probabilistic
-estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
-same technique is also demonstrated in \textcite{Soule:2004p3817} using
-histograms for finer grained classification.  The EM algorithm is again used in
-\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
-comparing EM favourably against a Na\"{i}ve Bayes classifier.
-
-\subsubsection{Na\"{i}ve Bayes}
-
-\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
-flows that have previously been sorted into groups by analysing the flow
-content. This paper focuses on many of the most commonly used Internet
-protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
-identifying traffic belonging to the Skype application.
-
-\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
-websites accessed through Privacy Enhancing Technologies (PET), including Tor.
-This technique performed poorly when applied to the Tor network, but it
-suggests that Tor traffic has particular characteristics that distinguish it
-from many existing PETs. It makes a particularly useful observation: ``The most
-frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
-−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
-
-\subsubsection{Markov Models}
-
-Hidden Markov Models (HMM) are a statistical modelling technique useful
-for classification of systems with an unobservable state
-\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
-technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
-primary identification characteristics for use with this algorithm are packet
-size and inter-packet arrival times. With refinement this algorithm is used
-with increasing accuracy in \textcite{Wright:2006p322} and
-\textcite{Dainotti:2008p1435}.
-
-In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
-discover distinguishing characteristics of traffic flows, rather than with a
-specific set of classification goals. This information is used to build HMMs
-for the purpose of traffic classification.
-
-Since HMMs model particular behaviours, they can be used to recognize
-deviations from normal behaviour as shown in
-\textcite{EstevezTapiador:2003p7201}. Motivated by
-\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
-flags and the position of individual packets in a stream to train an Observable
-Markov Model for traffic classification, achieving greater classification
-accuracy than \citeauthor{Bernaille:2005p6205}.
-
-\subsubsection{Clustering}
-
-Clustering algorithms group observations into subsets based on similar
-characteristics, they are a form of unsupervised learning technique designed to
-discover organization in unlabelled data sets. They have been the basis of a
-number of traffic classification techniques with the K-Means clustering
-technique being the most prominent.  K-Means cluster analysis appears in
-\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
-\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
-Applications with Noise (DBSCAN) algorithm appears in
-\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
-
-\subsubsection{Other Techniques}
-
-Other algorithms used for traffic classification include Nearest Neighbour and
-Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
-Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
-to identify applications and identities inside SSH tunnels was demonstrated in
-\textcite{Dusi:2008p6254}. Several algorithms are compared in
-\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
-for identifying Skype and SSH traffic.
-
-\subsubsection{Comparing Techniques}
-
-It is difficult to say what machine learning technique is the most effective as
-no consensus has been reached, the literature covers a wide variety of
-techniques each with vastly different goals and no two techniques can be
-directly compared as the data used for analysis has not been disclosed
-\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
-\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
-greatest performance and accuracy when compared to a number of Bayesian
-algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
-algorithms  to find random tree, IBI, IBK and random forest algorithms
-obtaining the greatest classification accuracy.
-
-An excellent meta study on traffic analysis techniques is presented in
-\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
-the techniques used, criteria analysed and how effectively they meet stated
-goals.
-
-\chapter{Theoretical Framework}
-
-\section{Research Methodology}
-
-The experiment conducted in this paper utilize a non-equivalent group design.
-The experimental groups are generated using simulations which allow for a great
-deal of control over confounding variables, ensuring minimal difference between
-the control and treatment groups. Both experiment groups perform the exact same
-simulations. The control group performs all simulations using regular HTTPS,
-while the treatment group proxies all communications over Tor. The treatment
-group can be broken into HTTP over Tor and HTTPS over Tor based simulations.
-
-\section{Assumptions}
-
-It is assumed that the usage patterns exhibited by individual users will be
-smaller than the communications characteristics that will lead to the
-identification of anonymous and censorship resistant networks. Thus there is no
-need to obtain a large sample of regular network traffic from varying user
-profiles.
-
-As of the current implementation, Tor network traffic is readily
-distinguishable by looking at the handshake packets. It is likely that this
-weakness will be addressed in a future version of the Tor protocol as it is
-recognised as a design goal in \textcite{Dingledine:2008p1542}. For this
-reason, this proposal focuses on traffic analysis techniques that are content
-agnostic.
-
-\section{Variables}
-
-The data capturing stage will be affected by a number of variables that will
-influence the accuracy of the chosen matching algorithms.
-
-\subsection{Quality of the Anonymous Network}
-
-An individual connection to the Tor network traverses a number of nodes to
-create a circuit. The path a circuit uses is first defined by the exit node,
-then chosen based on a number of constraints with a preference for high
-bandwidth relays \parencite{website:tor-path-selection}. Since each connection
-uses a different circuit and bandwidth demands are constantly changing, it is
-difficult to predict the composition of a Tor circuit.
-
-This means that any individual Tor circuit could be composed of systems with
-differing capabilities, network throughput and configuration.
-
-For testing purposes, the Tor network can be simulated on a small isolated
-network. This will eliminate a lot of the variability that comes from
-monitoring the real Tor network. Factors that affect the quality of the network
-can be controlled by limiting the number of competing network applications,
-controlling the number of running Tor instances and ensuring a consistent
-configuration across all nodes.
-
-\subsection{System Performance}
-
-The ability of Tor to route packets in a timely fashion is highly dependent on
-the performance of the system it is executing on. This is greatly compounded by
-the usage of strong encryption which is computationally expensive. Packet
-latency is one of the key parameters used in traffic classification techniques.
-Performance related variables include:
-
-\begin{itemize*}
-  \item CPU speed and number of cores
-  \item RAM speed and capacity
-  \item Performance of integrated components, system bus etc.
-  \item Hard disk size, access time and throughput
-  \item Installed and running applications
-  \item System configuration
-\end{itemize*}
-
-To remedy this, the systems used to simulate the Tor network should be made
-uniform. This means an identical hardware and software configuration for all
-systems in the simulation network.
-
-In addition it is noted that system performance can degrade over time due to
-both memory and hard disk fragmentation. This can be avoided by running the
-simulations in a virtualisation environment that support snapshots, rolling
-back to a known configuration point after each test.
-
-\subsection{Network Performance}
-
-Like system performance, latency is also dependent on the quality of the
-network. Network switching equipment has limited resources for routing packets
-and competing network traffic can introduce congestion which would radically
-alter the observable communications patterns \parencite{Jacobson:1995p6768}.
-Tor also supports congestion mitigation techniques which alter communication
-patterns \parencite[8]{Dingledine:2004p314}.
-
-Latency and network performance over the Internet are highly variable and
-beyond the control of any one individual. Usage patterns vary according to
-geographic region, societal conventions and the period in which they occur
-\parencite{Thompson97wide-areainternet,Ken03longitudinalstudy}. The Internet,
-and by necessity the public Tor network are globally distributed, which means
-that circuits traverse a large variety of unpredictable network conditions. By
-isolating the test network, these variables can be controlled ensuring low
-latency high bandwidth communications or congestion as necessary.
-
-\subsection{Application Protocol}
-
-Tor provides communications facilities to a number of Internet enabled
-applications by providing an interface using the SOCKS protocol
-\parencite[17]{Dingledine:2004p314}. This means that the Tor network can proxy
-regular web browsing, email or any other TCP or UDP based communication protocol
-\parencite{website:socks}. Each of these application protocols have their own
-distinguishing communications characteristics which will influence the matching
-algorithm. It is not yet clear how transparent the Tor network will be regarding
-these characteristics and thus, for the purposes of classification a single
-protocol should be chosen.
-
-\subsection{Caching}
-
-Both web browsers and web servers are designed for high performance and often
-cache requests so that they can be delivered faster in the future
-\parencite{Caceres:1998p7419}. While this is a normal part of communications
-traffic and should be considered, it is important that both regular and cached
-requests appear uniformly across all experiments. Manually flushing the cache
-or rolling back to a known virtual machine snapshot between each simulation can
-ensure this outcome.
-
-\input experiment.tex
-
-\chapter{Results}
+\chapter{Discussion of Results}
 
@@
 The classification results are tabulated below. The best performing algorithm
-j4.8 was able to classify HTTP over Tor with 97.8\% accuracy and a false
-positive rate of 4.3\%. HTTPS was more easily identified with a 97\% accuracy
-and low false positive rate of 0.7\%.
+random forest was able to classify HTTP over Tor with 93.7\% accuracy and a
+false positive rate of 3.7\%. HTTPS over Tor was more easily identified with a
+97.7\% accuracy and low false positive rate of 0.3\%.
 
-\begin{table}
+\begin{table}[H]
   \begin{tabular}{lrrr}
@@
     \midrule
-    HTTPS & 0.957 & 0.036\\
-    HTTP over Tor & 0.937 & 0.037\\
-    HTTPS over Tor & 0.977 & 0.003\\
+    HTTPS & 0.957 & 0.036 & 0.99\\
+    HTTP over Tor & 0.937 & 0.037 & 0.986\\
+    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
+    Weighted Avg. & 0.954 & 0.03 & 0.99\\
     \midrule
@@
     \midrule
-    HTTPS & 0.951 & 0.04\\
-    HTTP over Tor & 0.978 & 0.043\\
-    HTTPS over Tor & 0.97 & 0.007\\
+    HTTPS & 0.951 & 0.04 & 0.989\\
+    HTTP over Tor & 0.978 & 0.043 & 0.98\\
+    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
+    Weighted Avg. & 0.964 & 0.018 & 0.986\\
     \midrule
@@
     \midrule
-    HTTPS & 0.961 & 0.046\\
-    HTTP over Tor & 0.906 & 0.04\\
-    HTTPS over Tor & 0.955 & 0.01\\
+    HTTPS & 0.961 & 0.046 & 0.963\\
+    HTTP over Tor & 0.906 & 0.04 & 0.94\\
+    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
+    Weighted Avg. & 0.941 & 0.037 & 0.957\\
     \midrule
@@
     \midrule
-    HTTPS & 0.95 & 0.001\\
-    HTTP over Tor & 0.999 & 0.324\\
-    HTTPS over Tor & 0 & 0\\
+    HTTPS & 0.95 & 0.001 & 0.975\\
+    HTTP over Tor & 0.999 & 0.324 & 0.838\\
+    HTTPS over Tor & 0 & 0 & 0.777\\
+    Weighted Avg. & 0.785 & 0.109 & 0.891\\
     \bottomrule
-    \label{table:results}
   \end{tabular}
   \caption{Results}
+  \label{table:results}
 \end{table}
-
-\chapter{Discussion of Results}
 
@@
 
-\subsection{Can the traffic be classified using automated matching techniques?}
+\begin{enumerate*}
+  \item{Can the traffic be classified using automated matching techniques?}
 
@@
 
-\subsection{Do these networks have characteristics that make them readily
+  \item{Do these networks have characteristics that make them readily
   distinguishable using heuristics based matching?}
 
-\subsection{Do they have characteristics that make them distinguishable using a
+  Insert answer here.
+
+  \item{Do they have characteristics that make them distinguishable using a
   machine learning technique?}
 
-Yes.
+  Insert answer here.
 
-\subsection{How long does a user have to be connected to the network before a
+  \item{How long does a user have to be connected to the network before a
   confident match can be made?}
+
+  Insert answer here.
+
+\end{enumerate*}
 
@@
 
-\chapter{Conclusion}
+\section{Conclusion}
 
@@
 
-However, the experiment was based on a small set of simulated data, with which
+However, this experiment was based on a small set of simulated data, with which
 it would be impossible to cover all the possible real world conditions. The
@@
 traces from real participants in the Tor network.
-
-\chapter{Appendix}
-
-\section{Manager Script}
-
-\label{manager-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}
-
-\section{Client Script}
-
-\label{client-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}
-
-\section{Generate Tor Network Script}
-
-\label{generate-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/make_private_network.sh}
-
-\section{Run Tor Network Script}
-
-\label{run-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}
-
-\printbibliography[title=REFERENCES]
-
-\end{document}
-
-% vim: fdm=syntax tw=80

### 2011-02-27 thesis/thesis.tex
Split out into different sections, more rewriting as per suggestions.

--- 2011-02-26 thesis/thesis.tex
@@
 
-\chapter{Literature Review}
-
-The main areas of research included papers and proposals on the design of
-anonymity networks and those covering the subject of traffic analysis.
-Particular attention has been paid to encryption as it is the primary function
-by which these systems operate and a good understanding is necessary for the
-development of an appropriate traffic analysis method.
-
-\section{Encryption}
-
-Since the creation of language, the interception of messages by hostile forces
-has compelled the development of secretive communications. This deliberate
-transformation of a message, so that only the intended recipient can understand
-it, is known as encryption. The process of examining these obfuscated messages
-and attempting to reverse the transformation is known as cryptanalysis
-\parencite{Schneier:1996uq}. These fields have been locked in an arms race
-ever since, each side continually advancing their capabilities in an attempt to
-gain ground.
-
-Apart from One Time Pads, no encryption methodology has ever proven to be
-unbreakable \parencite{Shannon:1948p6583}. This means that all remaining
-cryptographic methods are a way of transforming information, so that for an
-attacker the difficulty in reversing this transformation is too costly to make
-it worthwhile. The invention of robots and computers was precipitated by the
-need to break encryption methods of increasing complexity and at the same time
-has lead to the increasing complexity of encryption algorithms
-\parencite{Kahn:1974:C}.
-
-Historically, all encryption methods have required an interaction between those
-communicating. A meeting to exchange the secret communications key, or a
-courier to deliver the encryption device. This made anonymous communications
-difficult, especially when using digital communications technologies.  In
-\citeyear{Jevons:1874vn}, \citeauthor{Jevons:1874vn}, perhaps
-unknowingly, uncovered the mathematical techniques that would allow for public
-key cryptography in his publication \citetitle{Jevons:1874vn}. He recognised
-that certain mathematical operations yielded products that were impossible or
-difficult to reverse in order to uncover the factors used.
-
-The possibility of public key cryptography, or non-secret encryption was
-conceived by James H. Ellis in \citeyear{Ellis:1970p3249} and later developed
-into both a method for sharing secret encryption keys by Malcolm J. Williamson
-in 1974 \parencite{Singh:1999:CBE} and a method for asymmetric encryption
-\parencite{Cocks:1973p3265}.
-
-These papers were not published at the time due to their military
-classification, allowing these methods to be reinvented independently
-\parencite{Singh:1999:CBE}. The method for key sharing developed by Ellis
-later became known as the Diffie-Hellman key exchange
-\parencite{Diffie:1976p585}, while the method for asymmetric encryption is now
-known as RSA encryption, taking its name from the initials of its creators,
-Rivest, Shamir and Adleman \parencite{Rivest:1978p708}. Figure
-\ref{key-exchange} shows how discrete logarithms are used in the Diffie-Hellman
-algorithm to generate a shared encryption key.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{key-exchange}
-  \caption{Diffie-Hellman Key Exchange}
-  \label{key-exchange}
-\end{figure}
-
-% How to relate back to Tor:
-% What algorithm does Tor use
-% How does encryption resist traffic analysis
-% Modern encryption algorithms ensure resistance to frequency analysis by making sure every character in a message appears as likely as every other character.
-To an observer, this means that encrypted messages appear to be indistinguishable to noise.
-
-While these early public key encryption algorithms are still in use, newer
-implementations have appeared which make improvements including
-\textcite*{ElGamal:1985p529} and \textcite{Cramer:1998p3186}. Attempts to make
-these encryption algorithms more difficult to break have involved the use of
-increasingly complex mathematical problems such as elliptic curves
-\parencite{Miller:1986p2966,Koblitz:1987p3109} and probabilistic functions
-\parencite{Paillier:1999p3152}. Many of these encryption algorithms are
-available in modern encryption protocols.
-
-Early proposals for digital networks included extensive usage of encryption
-technology. \textcite{Baran:1964p384} suggested that future digital military
-networks should use encryption for all messages, even those that did not
-require any secrecy. He cited benefits such as tamper resistance, message
-secrecy and resistance to traffic analysis, although this system was never
-implemented. The Internet, was developed without encryption features
-\parencite{website:internet}.
-
-Early work in encrypted Internet communications includes the Secure Network
-Programming (SNP) Applications Programming Interface (API)
-\parencite{Woo:1994p2532}. This was a simple framework providing numerous
-encryption, signing and authentication methods. The Secure Sockets Layer (SSL)
-is an encryption layer which provided end-to-end communications secrecy on the
-Internet \parencite{website:SSL}. A primary feature of SSL is the ability to
-exchange secret keys using public key algorithms.
-
-This proposed standard went through a number of revisions, with early versions
-suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
-Transport Layer Security (TLS), with the latest version 1.2 being released
-August 2008 \parencite{website:TLS}. TLS addresses some issues in SSL and
-provides a number of enhancements, but is not compatible with SSL.
-
-The Hypertext Transfer Protocol Secure (HTTPS) provides encryption using both
-the TLS and SSL protocols \parencite{website:HTTPS} and is available in almost
-all modern web browsers including Firefox
-\parencite{website:firefox-encryption}, Safari
-\parencite{website:safari-features} and Internet Explorer
-\parencite{website:microsoft-tls}. Tor provides encryption through usage of the
-TLS protocol.
-
-\section{Anonymous and Censorship Resistant Networks}
-
-The first anonymous network system MixNet, was described in
-\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
-encryption to prevent eavesdroppers from obtaining message delivery information.
-Senders in the network communicate with a centrally located server known as a
-mix, delivering a message with the address of the intended recipient. The mix
-server discards any information about the sender and delivers it to the final
-destination. Figure \ref{chaums-mix-network} depicts the process of message
-delivery in Chaum's MixNet. Chaum's proposal also allowed for the chaining of
-multiple mix servers together to form a cascade.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{chaums-mix-network}
-  \caption{MixNet Message Delivery}
-  \label{chaums-mix-network}
-\end{figure}
-
-Since the inception of MixNet, numerous anonymous networks have been proposed,
-each design being influenced by diverse motivations for obtaining anonymity.
-These include:
-
-\begin{itemize*}
-  \item Anonymous remailers such as Babel \parencite{Gulcu:1996p1662} and
-    Mixminion \parencite{Danezis:2003ys}.
-  \item Networks that provide mathematically provable anonymity
-    \parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303}.
-  \item Anonymity that degrades gracefully when subject to attack, so called
-    robust anonymity \parencite{Waidner:1989p5870,Jakobsson:1998p5137}.
-  \item Anonymous publishing in Freedom \parencite{Goldberg:1999p2231} and
-    Freenet \parencite{Clarke:2001p2435}.
-  \item Peer to Peer (P2P) anonymity such as MorphMix
-    \parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
-    \parencite{P5Sherwood:2005p5872}.
-  \item Censorship resistance in aChord and gnuNet \parencite{Hazel:2002p6929},
-    Infranet \parencite{Feamster:2002p307} and of course Tor.
-\end{itemize*}
-
-This is by no means an exhaustive list, for an excellent survey of anonymous
-networks consult \textcite{Danezis:2008p346}.
-
-Although this research has yielded a variety of designs, all anonymous
-networks essentially operate on all or some of the following principles:
-
-\begin{itemize*}
-  \item Encrypting traffic to prevent eavesdropping.
-  \item Providing covering traffic through a network of active users or by
-    generating it automatically.
-  \item Normalizing message delivery so that individual communication patterns
-    are not identifiable.
-\end{itemize*}
-
-In theory, the normalization techniques used by anonymous networks should make
-them readily distinguishable from non anonymous communications.
-
-\subsection{The Second Generation Onion Router (Tor)}
-
-Tor was first described in \citetitle{Dingledine:2004p314}
-\parencite{Dingledine:2004p314}. This new generation of onion router was
-designed with a number of defences for common traffic analysis attacks and
-weaknesses discovered in other proposals. With a focus on deployability,
-usability, flexibility and simple-design \parencite[3-4]{Dingledine:2004p314}
-as well as a successful implementation, it has seen wider deployment than most
-other anonymous networks.
-
-Like MixNet, public key cryptography is combined with intermediate servers
-responsible for message delivery to provide a degree of anonymity. In Tor,
-these mixes are known as relays and are typically chained together to
-construct a circuit. Clients connect to the Tor network by communicating
-with a special relay known as a bridge, which constitutes the first
-relay in a circuit. Traffic is repeatedly delivered through relays until it
-reaches another special relay known as an exit node, where it is
-delivered unencrypted to the final destination. Figure \ref{tor-network} shows
-this typical usage of the Tor network.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
-  \caption{The Tor Network}
-  \label{tor-network}
-\end{figure}
-
-Messages delivered through the Tor network are encrypted multiple times using a
-variation of onion routing \parencite{Michael:2001} known as telescopic onion
-routing. Circuits are built incrementally, obtaining a session key from each
-successive relay in the circuit and encrypting messages so that intermediate
-relays are unable to decrypt the message. Since circuits can take some time to
-build, they are pre-emptively created at regular intervals
-\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
-traffic normalization techniques that provide strong anonymity, messages passed
-through the Tor network are packaged in cells of a fixed size of 512 bytes
-\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
-that remove identifying features from common application protocols.
-
-After it was noticed that Tor was being used to circumvent censorship as well
-as for anonymity, a publication was released which attempts to identify the
-issues that need to be addressed in order for Tor to provide some level of
-censorship resistance \parencite{Dingledine:2008p1542}. Although this paper
-foresees future attacks such as the one contained in this proposal, it mostly
-tackles social issues of censorship resistance.
-
-\section{Traffic Analysis}
-
-Research into Tor weaknesses has included the use of hostile exit nodes to
-capture private information \parencite{website:tor-password-leak}, attacks that
-take advantages of web based technologies such as Javascript and Flash to
-reveal user's identities \parencite{Abbott:2007p298} and a number of identity
-revealing traffic analysis techniques
-\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}. Notable is the
-discovery of a method for identifying bridge operators as discussed in
-\textcite{McLachlan:2009p197}. This attack takes advantages in weaknesses of
-the Tor protocol to enumerate bridges and some approaches to mitigation are
-suggested. It is believed that this is the first proposal of a traffic analysis
-technique for classification of Tor network streams.
-
-When considering the use of traffic analysis for classification of Internet
-communications, three techniques are used. These are: exact matching, heuristic
-matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
-techniques recognise properties of communications that mirror known protocols
-and communication patterns. This might include the port an application uses or
-the format of its payload. Since Tor employs strong encryption and communicates
-using known and commonly used protocols, exact matching techniques would prove
-ineffective for classification. Heuristic matching looks for patterns in
-conversations to determine communications patterns and infer relationships,
-while machine learning involves the use of statistics to train computer
-algorithms to classify traffic. Both heuristic and machine matching techniques
-are suitable for traffic analysis of anonymous networks because they do not
-rely on analysing the content of messages.
-
-\subsection{Heuristic Techniques}
-
-The increasing burden of peer to peer (P2P) applications on campus networks,
-and their shift to encryption motivated the development of heuristics based
-techniques for identifying P2P traffic. Early techniques include identifying
-known properties of P2P networks such as often communicating using both the UDP
-and TCP protocols simultaneously and using a solitary connection to transfer
-high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
-number of false positives by eliminating packets that matched known
-communications protocols.
-
-Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
-\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
-through early elimination of false positives and by expanding the scope of
-matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
-to identify P2P nodes before applying a secondary heuristic to identify
-‘supernodes’ which are a subset of all P2P nodes.
-
-Classifying traffic based on system roles is a key feature of the technique
-that appears in \citetitle{Karagiannis:2005p6359}
-\parencite{Karagiannis:2005p6359}. By analysing communications at the host
-level then at increasing levels of granularity, a greater level of accuracy is
-achieved.
-
-The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
-\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
-flows are represented in a TDG, mathematical properties of the flow can be
-analysed to make positive identifications.
-
-Viruses have also posed a problem for network administrators, often
-over-utilizing network resources and using the network to infect new machines.
-A technique for identifying various worms was proposed in
-\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
-from network administrators to avoid detection, presenting the same problems of
-identification as Tor network traffic.
-
-\subsection{Machine Learning Techniques}
-
-\subsubsection{Expectation-Maximisation}
-
-The first use of machine learning to categorise traffic flows appears in
-\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
-be used for machine learning and an attempt at coarse grained classification
-using an expectation-maximisation (EM) algorithm are demonstrated. The
-expectation-maximisation algorithm is a method for finding probabilistic
-estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
-same technique is also demonstrated in \textcite{Soule:2004p3817} using
-histograms for finer grained classification.  The EM algorithm is again used in
-\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
-comparing EM favourably against a Na\"{i}ve Bayes classifier.
-
-\subsubsection{Na\"{i}ve Bayes}
-
-\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
-flows that have previously been sorted into groups by analysing the flow
-content. This paper focuses on many of the most commonly used Internet
-protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
-identifying traffic belonging to the Skype application.
-
-\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
-websites accessed through Privacy Enhancing Technologies (PET), including Tor.
-This technique performed poorly when applied to the Tor network, but it
-suggests that Tor traffic has particular characteristics that distinguish it
-from many existing PETs. It makes a particularly useful observation: ``The most
-frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
-−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
-
-\subsubsection{Markov Models}
-
-Hidden Markov Models (HMM) are a statistical modelling technique useful
-for classification of systems with an unobservable state
-\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
-technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
-primary identification characteristics for use with this algorithm are packet
-size and inter-packet arrival times. With refinement this algorithm is used
-with increasing accuracy in \textcite{Wright:2006p322} and
-\textcite{Dainotti:2008p1435}.
-
-In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
-discover distinguishing characteristics of traffic flows, rather than with a
-specific set of classification goals. This information is used to build HMMs
-for the purpose of traffic classification.
-
-Since HMMs model particular behaviours, they can be used to recognize
-deviations from normal behaviour as shown in
-\textcite{EstevezTapiador:2003p7201}. Motivated by
-\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
-flags and the position of individual packets in a stream to train an Observable
-Markov Model for traffic classification, achieving greater classification
-accuracy than \citeauthor{Bernaille:2005p6205}.
-
-\subsubsection{Clustering}
-
-Clustering algorithms group observations into subsets based on similar
-characteristics, they are a form of unsupervised learning technique designed to
-discover organization in unlabelled data sets. They have been the basis of a
-number of traffic classification techniques with the K-Means clustering
-technique being the most prominent.  K-Means cluster analysis appears in
-\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
-\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
-Applications with Noise (DBSCAN) algorithm appears in
-\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
-
-\subsubsection{Other Techniques}
-
-Other algorithms used for traffic classification include Nearest Neighbour and
-Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
-Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
-to identify applications and identities inside SSH tunnels was demonstrated in
-\textcite{Dusi:2008p6254}. Several algorithms are compared in
-\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
-for identifying Skype and SSH traffic.
-
-\subsubsection{Comparing Techniques}
-
-It is difficult to say what machine learning technique is the most effective as
-no consensus has been reached, the literature covers a wide variety of
-techniques each with vastly different goals and no two techniques can be
-directly compared as the data used for analysis has not been disclosed
-\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
-\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
-greatest performance and accuracy when compared to a number of Bayesian
-algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
-algorithms  to find random tree, IBI, IBK and random forest algorithms
-obtaining the greatest classification accuracy.
-
-An excellent meta study on traffic analysis techniques is presented in
-\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
-the techniques used, criteria analysed and how effectively they meet stated
-goals.
+\input litreview.tex
 
@@
 
-\section{Variables}
+\section{Variables Impacting Research}
 
@@
 
-For testing purposes, the Tor network can be simulated on a small isolated
-network. This will eliminate a lot of the variability that comes from
-monitoring the real Tor network. Factors that affect the quality of the network
-can be controlled by limiting the number of competing network applications,
-controlling the number of running Tor instances and ensuring a consistent
-configuration across all nodes.
+For this research, a simulated Tor network was constructed inside a virtual
+machine. This allowed an identical configuration to be used across experimental
+groups. Repeating the simulations and rolling back the Tor Network Guest to a
+known snapshot ensured that each experiment group was composed of simulations
+interacting with a Tor network of similar quality.
 
@@
 
-The ability of Tor to route packets in a timely fashion is highly dependent on
-the performance of the system it is executing on. This is greatly compounded by
-the usage of strong encryption which is computationally expensive. Packet
-latency is one of the key parameters used in traffic classification techniques.
-Performance related variables include:
+The ability of a computer system to route packets in a timely fashion is highly
+dependent on the performance of the system it is executing on. This is greatly
+compounded by the usage of strong encryption which is computationally expensive.
+Since packet latency is one of the key parameters used in traffic classification
+techniques, it is important to isolate packet latency affects from confounding
+variables. Components affecting packet latency include:
 
@@
 
-To remedy this, the systems used to simulate the Tor network should be made
-uniform. This means an identical hardware and software configuration for all
-systems in the simulation network.
-
 In addition it is noted that system performance can degrade over time due to
-both memory and hard disk fragmentation. This can be avoided by running the
-simulations in a virtualisation environment that support snapshots, rolling
-back to a known configuration point after each test.
+both memory and hard disk fragmentation. The affects of these variables was
+mitigated by periodically rolling back virtual machine snapshots to return to a
+known system state and using the same network and computer hardware for all
+simulations.
 
@@
 and by necessity the public Tor network are globally distributed, which means
-that circuits traverse a large variety of unpredictable network conditions. By
-isolating the test network, these variables can be controlled ensuring low
-latency high bandwidth communications or congestion as necessary.
+that circuits traverse a large variety of unpredictable network conditions.
+
+The experiment utilized an isolated test network, with unrelated network
+processes disabled ensuring no interference or congestion.
 
@@
 \parencite{website:socks}. Each of these application protocols have their own
-distinguishing communications characteristics which will influence the matching
-algorithm. It is not yet clear how transparent the Tor network will be regarding
-these characteristics and thus, for the purposes of classification a single
-protocol should be chosen.
+distinguishing communications characteristics which may influence the matching
+algorithm.
+
+For the purpose of this experiment, the protocol chosen was the HTTPS protocol.
+The treatment group was split into two components, the first part using HTTP
+over Tor and the second using HTTPS over Tor.
 
@@
 traffic and should be considered, it is important that both regular and cached
-requests appear uniformly across all experiments. Manually flushing the cache
-or rolling back to a known virtual machine snapshot between each simulation can
-ensure this outcome.
+requests appear uniformly across all experiments.
+
+Periodically rolling back virtual machine snapshots during the experiment
+ensures that the browser cache always begins at empty for a series of
+simulations.
 
@@
 
-\chapter{Results}
-
-\section{Results}
-
-The classification results are tabulated below. The best performing algorithm
-j4.8 was able to classify HTTP over Tor with 97.8\% accuracy and a false
-positive rate of 4.3\%. HTTPS was more easily identified with a 97\% accuracy
-and low false positive rate of 0.7\%.
-
-\begin{table}
-  \begin{tabular}{lrrr}
-    \toprule
-    & True Positive Rate & False Positive Rate & ROC \\
-    \midrule
-    Random Forest\\
-    \midrule
-    HTTPS & 0.957 & 0.036\\
-    HTTP over Tor & 0.937 & 0.037\\
-    HTTPS over Tor & 0.977 & 0.003\\
-    \midrule
-    j4.8 With 10 fold cross validation\\
-    \midrule
-    HTTPS & 0.951 & 0.04\\
-    HTTP over Tor & 0.978 & 0.043\\
-    HTTPS over Tor & 0.97 & 0.007\\
-    \midrule
-    Random Tree\\
-    \midrule
-    HTTPS & 0.961 & 0.046\\
-    HTTP over Tor & 0.906 & 0.04\\
-    HTTPS over Tor & 0.955 & 0.01\\
-    \midrule
-    Adaboost\\
-    \midrule
-    HTTPS & 0.95 & 0.001\\
-    HTTP over Tor & 0.999 & 0.324\\
-    HTTPS over Tor & 0 & 0\\
-    \bottomrule
-    \label{table:results}
-  \end{tabular}
-  \caption{Results}
-\end{table}
-
-\chapter{Discussion of Results}
-
-\section{Limitations}
-
-The classifiers developed within this experiment have been trained against
-a relatively small sample set of simulated data, which may only represent
-a small fraction of the width and breadth of conditions available on a wider
-area network. The characteristics that allow for classification of Tor network
-may be masked by the natural variability introduced by a heterogeneous network.
-
-\section{Addressing Research Questions}
-
-\subsection{Can the traffic be classified using automated matching techniques?}
-
-Yes, the classification algorithms trialled were all able to identify Tor traffic
-with reasonable accuracy.
-
-\subsection{Do these networks have characteristics that make them readily
-distinguishable using heuristics based matching?}
-
-\subsection{Do they have characteristics that make them distinguishable using a
-machine learning technique?}
-
-Yes.
-
-\subsection{How long does a user have to be connected to the network before a
-confident match can be made?}
-
-\section{Possible Implications of Results}
-
-\chapter{Conclusion}
-
-While it is difficult to draw a broad conclusion with the limited nature of the
-experiment conducted, the findings suggest that the strategies used by anonymous
-networks to thwart identity revealing traffic analysis may make them easier to
-identify.
-
-Research has shown that the low latency design of Tor means it is vulnerable to
-traffic analysis attacks that correlate traffic patterns with users. This
-transparency should in fact make Tor more difficult to classify than more
-'anonymous' network designs which employ batching and traffic normalizing.
-Steganography is a difficult problem and it may be that the extra traffic
-required to maintain the Tor network means it will always be easily
-differentiated from regular encrypted traffic.
+\input results.tex
 

### 2011-03-20 thesis/thesis.tex
Start of rewriting background

@@
 
-The Internet has revolutionised the political sphere in providing a platform
-for the publication of speech to a far greater audience than was ever available
-before digital communications systems \parencite{Bonchek:1997p3455}. The
-publication of less desirable political speech, criticism or challenging ideas
-still carries with it great risk, with numerous publications leading to arrest.
-This has spawned headlines such as \textcite{website:egypt-arrests},
-\citetitle{website:china-yahoo-torture}
-\parencite{website:china-yahoo-torture},
-\citetitle{website:vietnam-bloggers-arrested}
-\parencite{website:vietnam-bloggers-arrested},
-\textcite{website:iran-bloggers-arrested} and
-\citetitle{website:blogger-arrests} \parencite{website:blogger-arrests}. The
-Internet, like conventional media, is still vulnerable to censorship by
-oppressive governments and malicious attackers
-\parencite{Crandall:2007p6165,Karlin:2009p6166}.
+The first anonymous digital network, commonly known as MixNet was proposed in
+\textcite{Chaum:1981p296}. The foundation of MixNet was the use of an
+intermediary which forwarded messages from clients without any identifying
+details. Numerous proposals and implementations followed such as Freedom
+\parencite{Goldberg:1999p2231} and aChord \parencite{Hazel:2002p6929}. The
+Second Generation Onion Router (Tor), is an anonymous network which uses a
+variant of Onion Routing, to provide low latency anonymous communications to a
+wide variety of Internet communications protocols
+\parencite{Dingledine:2004p314}. It also aims to provide resistance against
+censorship based blocking attempts \parencite{Dingledine:2008p1542}.
 
-In response to these threats, a number of systems have been proposed which use
-various techniques, primarily cryptography and covering traffic, to provide
-censorship resistance and anonymity. The Second Generation Onion Router (Tor),
-is an anonymous network which uses a variant of Onion Routing, to provide low
-latency anonymous communications to a wide variety of Internet communications
-protocols \parencite{Dingledine:2004p314}. It also aims to provide resistance
-against censorship based blocking attempts \parencite{Dingledine:2008p1542}.
+Tor was originally developed by the U.S. Naval Research Lab in 1997
+\parencite{Syverson:1997kz} for application by the U.S. Navy. It has since been
+adopted by The Tor Project, Inc. and is made publicly available, finding usage
+in journalism, law enforcement, activism and military applications
+\parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most successful and
+widely deployed anonymous networks, with an average of two hundred thousand
+active users as of March 2011 \parencite{The-Tor-Project-Inc.:2011fk}.
 
-Although Tor succeeds to a certain extent in these goals, it may be possible to
-use traffic analysis techniques to automatically identify Tor connections and
-target them for attacks. Since Tor relies on large numbers of users for the
-protections it provides, attacks that affect the reliability of the network can
-discourage participation, making it ineffective. This paper proposes a traffic
-analysis methodology for identifying Tor traffic which may be used for such
-attacks in the future.
+Although Tor succeeds to a certain extent in providing anonymity and censorship
+resistance. Under controlled conditions it is possible to distinguish Tor
+traffic from other forms of encrypted traffic using traffic analysis. This makes
+it easy for Tor users to be isolated and targeted for attacks. Since Tor relies
+on large numbers of users for the protections it provides, attacks that affect
+the reliability of the network can discourage participation, making it
+ineffective. This paper describes a simple traffic analysis technique which can
+be used to distinguish Tor traffic from another form of commonly encrypted
+traffic.
 
 \section{Significance}
+
+ While it has been the subject of much
+academic literature, the primary objective of researchers has historically been
+the attempt to reveal participant identities \parencite[3]{Murdoch:2005p325}.
 
@@
     machine learning technique?
-  \item How long does a user have to be
-    connected to the network before a confident match can be made?
+  %\item How long does a user have to be
+  %  connected to the network before a confident match can be made?
 \end{enumerate*}

### 2011-03-20 thesis/thesis.tex
Rewrote significance and removed pointless paragraph from research questions

@@
 % Bibliography
-\bibliography{fullrefs,websites,patents,papers}
+\bibliography{fullrefs,websites,patents}
 
@@
 traffic from other forms of encrypted traffic using traffic analysis. This makes
-it easy for Tor users to be isolated and targeted for attacks. Since Tor relies
+it easy for Tor users to be isolated and targeted for attack. Since Tor relies
 on large numbers of users for the protections it provides, attacks that affect
@@
 
- While it has been the subject of much
-academic literature, the primary objective of researchers has historically been
-the attempt to reveal participant identities \parencite[3]{Murdoch:2005p325}.
+The Internet's expanding growth \parencite{Miniwatts-Marketing-Group:2010uq} and
+role in political discourse \parencite{Bonchek:1997p3455} have allowed for
+increased mobility and organization of activist groups
+\parencite{Alexander:2011kx,Anderson:2011vn}. The increasingly sophisticated use
+of censorship \parencite{Crandall:2007p6165,Karlin:2009p6166} and swift
+retribution for dissenting opinion
+\parencite{website:china-yahoo-torture,website:vietnam-bloggers-arrested,website:egypt-arrests,website:blogger-arrests}
+may have chilling effects, effectively neutralizing these benefits. In light of
+these threats the value of anonymous networks and anti-censorship technology can
+be recognized. It is quite telling that new and sometimes unorthodox methods of
+circumventing censorship are being deployed every day
+\parencite{The-Economist:2011fk,Brading:2011ys}.
 
-Tor is one of the most successful and widely deployed anonymous networks, with
-around one thousand, eight hundred users at the time of writing
-\parencite{website:tor-anonymity-online}. While it has been the subject of many
-traffic analysis attacks, the primary objective has historically been the
-attempt to reveal participant identities: ``The principal objective of an
-adversary attacking an anonymous communication system is to link the initiators
-of connections with their respective communication partners and vice versa''
-\parencite[3]{Murdoch:2005p325}.
-
-The traffic analysis techniques proposed will attempt to classify network
-streams belonging to Tor users to distinguish them from regular encrypted
-communications. This research may provide a greater understanding of just
-how much anonymity a user of the Tor network is provided and inspire
-the development of countermeasures against analysis.
+While Tor has been the subject of much academic literature, the primary
+objective of researchers has historically been the attempt to reveal participant
+identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
+have been somewhat academic in nature and not necessarily feasible in practice.
+Sometimes they require compromise of large parts of the Tor network, supplying
+hostile data to Tor users or complicated knowledge of usage patterns and an
+excess of patience. The technique demonstrated in this paper is a low cost
+technique, which does not require very sophisticated equipment and can be
+completed by a passive observer.
 
@@
 
-Given a motivated and universal attacker, it is inexpensive and straightforward
-to disconnect a user from these networks by blocking access to well known and
-published resources. Once these avenues of attack have been exhausted it is
-still possible to connect to the network by connecting to lesser known access
-points. Since these networks are capable of communicating using many of the
-same methods as most conventional Internet applications, a blanket ban on this
-kind of communication would be too broad and extensive.
-
 Tor employs strong encryption, the goal of which is to ensure that the data
-transmitted is indistinguishable from random noise. To an observer, data
-transmitted using encryption looks the same. Thus the traditional means of
-identifying these protocols are ineffective.
+transmitted is indistinguishable from random noise. To an observer, two
+different streams of encrypted data look almost the same. Thus the traditional
+means of identifying these protocols are ineffective.
 
@@
     distinguishable using heuristics based matching?
-  \item Do they have characteristics that make them distinguishable using a
-    machine learning technique?
+  \item Do they have characteristics that make them distinguishable using
+    machine learning techniques?
   %\item How long does a user have to be

### 2011-03-27 bibliography/fix-papers.rb
Handle new format produced by papers

@@ -9,11 +9,17 @@
 # Bibtex uses months in abbrev {Jan} -> {Dec}
 #
 MONTHS = %w[Jan Feb Mar Apr May June July Aug Sept Oct Nov Dec]
+
+def find_month(text)
+  MONTHS.each_with_index do |month, index|
+    return (index + 1) if month =~ /\A#{month}/i
+  end
+end
+
 File.open(ARGV[0]) do |file|
   file.each do |line|
-    matches = line.match(/month\s*=\s*\{([A-Za-z]+)\}/)
-    if matches #and MONTHS.include?(matches[1])
-      index = MONTHS.index(matches[1]) + 1
+    matches = line.match(/month\s*=\s*\{([A-Za-z]+)\}/i)
+    if matches && (index = find_month(matches[1]))
       puts "#{line[0..(matches.offset(1)[0] - 1)]}#{index}#{line[(matches.offset(1)[1])..-1]}"
     else
       puts line

### 2011-03-27 thesis/thesis.tex
Quick reference to the 23rd racoon
Start of integrating lit review into introduction

@@
 
-The first anonymous digital network, commonly known as MixNet was proposed in
-\textcite{Chaum:1981p296}. The foundation of MixNet was the use of an
-intermediary which forwarded messages from clients without any identifying
-details. Numerous proposals and implementations followed such as Freedom
-\parencite{Goldberg:1999p2231} and aChord \parencite{Hazel:2002p6929}. The
-Second Generation Onion Router (Tor), is an anonymous network which uses a
+The first anonymous digital network, commonly known as MixNet was proposed by
+\citeauthor{Chaum:1981p296} in \citetitle{Chaum:1981p296}
+\parencite{Chaum:1981p296}. This paper introduced a concept integral to many
+future anonymity providing designs, an intermediate system responsible for
+delivering messages without the identifying details of correspondents. The
+intermediate system, referred to as a 'mix' also employed public key
+cryptography to ensure that eavesdroppers could not obtain delivery information.
+
+This seminal paper spurred research into new techniques for providing anonymity
+and privacy for digital networks. Remailers such as Babel
+\parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
+mix to deliver anonymous email. Research produced designs that yielded
+mathematically provable anonymity
+\parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303} and networks that
+degrade gracefully when subject to attack, so called robust anonymity
+\parencite{Waidner:1989p5870,Jakobsson:1998p5137}. Designs such as MorphMix
+\parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
+\parencite{P5Sherwood:2005p5872} aimed to provide anonymity features to
+peer-to-peer (P2P) networks.
+
+The goal of anonymity sometimes aligns with that of providing resistance to
+censorship. Many censorship resistance systems are built on top of anonymity
+providing designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a
+censorship resistant system built on top of AN.ON
+\parencite{springerlink:10.1007/3-540-44702-4_7}.  Anonymous publishing systems
+such as Freedom \parencite{Goldberg:1999p2231} and Freenet
+\parencite{Clarke:2001p2435} also provide some measure of censorship resistance.
+The goal of aChord \parencite{Hazel:2002p6929} is to provide a distributed
+lookup system for peer-to-peer publishing systems, based on Chord
+\parencite{Stoica:2001:CSP:383059.383071}.
+
+Censorship resistance in aChord and gnuNet
+\parencite{Hazel:2002p6929}, Infranet \parencite{Feamster:2002p307}.
+
+Anonymous networks by acting as a relay for network traffic, provide some level
+of censorship resistance though these goals do not always align.
+
+The Second Generation Onion Router (Tor), is an anonymous network which uses a
 variant of Onion Routing, to provide low latency anonymous communications to a
@@
 
-Tor was originally developed by the U.S. Naval Research Lab in 1997
-\parencite{Syverson:1997kz} for application by the U.S. Navy. It has since been
-adopted by The Tor Project, Inc. and is made publicly available, finding usage
-in journalism, law enforcement, activism and military applications
-\parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most successful and
-widely deployed anonymous networks, with an average of two hundred thousand
-active users as of March 2011 \parencite{The-Tor-Project-Inc.:2011fk}.
+\section{The Second Generation Onion Router}
+
+Onion routing was originally developed by the U.S. Naval Research Lab in 1996
+\parencite{Goldschlag:1996wy} for application by the U.S. Navy. Like a mix,
+messages sent over an onion routing network were encrypted with their routing
+information and delivered to an intermediate server for forward delivery.
+Unlike the mix however, messages delivered using the onion routing network were
+encrypted multiple times, each 'layer' using a different key and routing
+instructions. The first node in a chain would only be able to encrypt the
+routing instructions to deliver the message to the next node. Each node in the
+sequence decrypting a layer until the complete message is decrypted and
+transmitted to the destination. This invention was granted a patent by the U.S.
+Patent Office in 2001 \parencite{Michael:2001}.
+
+This proposal was expanded on in \citetitle{Dingledine:2004p314} and addressed a
+number of weaknesses in the original onion router proposal
+\parencite{Dingledine:2004p314}. It also added some usability and anonymity
+features and deviates sufficiently from the original onion routing design in
+order to avoid patent claims. The technique employed by Tor is known as
+telescopic onion routing.
+
+In the Tor network, the intermediate nodes responsible for routing messages are
+known as relays and are typically chained together to construct a circuit.
+Clients connect to the Tor network by communicating with a special relay known
+as a bridge, which constitutes the first relay in a circuit. Traffic is
+repeatedly delivered through relays until it reaches another special relay known
+as an exit node, where it is delivered unencrypted to the final destination.
+Figure \ref{tor-network} shows this typical usage of the Tor network.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
+  \caption{The Tor Network}
+  \label{tor-network}
+\end{figure}
+
+Circuits are built incrementally, obtaining a session key from each
+successive relay in the circuit and encrypting messages so that intermediate
+relays are unable to decrypt the message. Since circuits can take some time to
+build, they are pre-emptively created at regular intervals
+\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
+traffic normalization techniques that provide strong anonymity, messages passed
+through the Tor network are packaged in cells of a fixed size of 512 bytes
+\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
+that remove identifying features from common application protocols.
+
+Tor is developed and maintained  by The Tor Project, Inc. and is made publicly
+available, finding usage in journalism, law enforcement, activism and military
+applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
+successful and widely deployed anonymous networks, with an average of two
+hundred thousand active users as of March 2011
+\parencite{The-Tor-Project-Inc.:2011fk}.
 
@@
 traffic.
+
+\section{Traffic Analysis}
+
+Research into Tor weaknesses has included the use of hostile exit nodes to
+capture private information \parencite{website:tor-password-leak}, attacks that
+take advantages of web based technologies such as Javascript and Flash to reveal
+user's identities \parencite{Abbott:2007p298} and a number of identity revealing
+traffic analysis techniques
+\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}.
+\citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
+operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.  It
+is believed that this is the first proposal of a traffic analysis technique for
+classification of Tor network streams.
+
+When considering the use of traffic analysis for classification of Internet
+communications, three techniques are used. These are: exact matching, heuristic
+matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
+techniques recognise properties of communications that mirror known protocols
+and communication patterns. This might include the port an application uses or
+the format of its payload. Since Tor employs strong encryption and communicates
+using known and commonly used protocols, exact matching techniques would prove
+ineffective for classification. Heuristic matching looks for patterns in
+conversations to determine communications patterns and infer relationships,
+while machine learning involves the use of statistics to train computer
+algorithms to classify traffic. Both heuristic and machine matching techniques
+are suitable for traffic analysis of anonymous networks because they do not
+rely on analysing the content of messages.
+
+\subsection{Heuristic Techniques}
+
+The increasing burden of peer to peer (P2P) applications on campus networks,
+and their shift to encryption motivated the development of heuristics based
+techniques for identifying P2P traffic. Early techniques include identifying
+known properties of P2P networks such as often communicating using both the UDP
+and TCP protocols simultaneously and using a solitary connection to transfer
+high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
+number of false positives by eliminating packets that matched known
+communications protocols.
+
+Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
+\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
+through early elimination of false positives and by expanding the scope of
+matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
+to identify P2P nodes before applying a secondary heuristic to identify
+‘supernodes’ which are a subset of all P2P nodes.
+
+Classifying traffic based on system roles is a key feature of the technique
+that appears in \citetitle{Karagiannis:2005p6359}
+\parencite{Karagiannis:2005p6359}. By analysing communications at the host
+level then at increasing levels of granularity, a greater level of accuracy is
+achieved.
+
+The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
+\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
+flows are represented in a TDG, mathematical properties of the flow can be
+analysed to make positive identifications.
+
+Viruses have also posed a problem for network administrators, often
+over-utilizing network resources and using the network to infect new machines.
+A technique for identifying various worms was proposed in
+\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
+from network administrators to avoid detection, presenting the same problems of
+identification as Tor network traffic.
+
+\subsection{Machine Learning Techniques}
+
+\subsubsection{Expectation-Maximisation}
+
+The first use of machine learning to categorise traffic flows appears in
+\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
+be used for machine learning and an attempt at coarse grained classification
+using an expectation-maximisation (EM) algorithm are demonstrated. The
+expectation-maximisation algorithm is a method for finding probabilistic
+estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
+same technique is also demonstrated in \textcite{Soule:2004p3817} using
+histograms for finer grained classification.  The EM algorithm is again used in
+\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
+comparing EM favourably against a Na\"{i}ve Bayes classifier.
+
+\subsubsection{Na\"{i}ve Bayes}
+
+\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
+flows that have previously been sorted into groups by analysing the flow
+content. This paper focuses on many of the most commonly used Internet
+protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
+identifying traffic belonging to the Skype application.
+
+\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
+websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+This technique performed poorly when applied to the Tor network, but it
+suggests that Tor traffic has particular characteristics that distinguish it
+from many existing PETs. It makes a particularly useful observation: ``The most
+frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
+−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
+
+\subsubsection{Markov Models}
+
+Hidden Markov Models (HMM) are a statistical modelling technique useful
+for classification of systems with an unobservable state
+\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
+technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
+primary identification characteristics for use with this algorithm are packet
+size and inter-packet arrival times. With refinement this algorithm is used
+with increasing accuracy in \textcite{Wright:2006p322} and
+\textcite{Dainotti:2008p1435}.
+
+In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
+discover distinguishing characteristics of traffic flows, rather than with a
+specific set of classification goals. This information is used to build HMMs
+for the purpose of traffic classification.
+
+Since HMMs model particular behaviours, they can be used to recognize
+deviations from normal behaviour as shown in
+\textcite{EstevezTapiador:2003p7201}. Motivated by
+\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
+flags and the position of individual packets in a stream to train an Observable
+Markov Model for traffic classification, achieving greater classification
+accuracy than \citeauthor{Bernaille:2005p6205}.
+
+\subsubsection{Clustering}
+
+Clustering algorithms group observations into subsets based on similar
+characteristics, they are a form of unsupervised learning technique designed to
+discover organization in unlabelled data sets. They have been the basis of a
+number of traffic classification techniques with the K-Means clustering
+technique being the most prominent.  K-Means cluster analysis appears in
+\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
+\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
+Applications with Noise (DBSCAN) algorithm appears in
+\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
+
+\subsubsection{Other Techniques}
+
+Other algorithms used for traffic classification include Nearest Neighbour and
+Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
+Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
+to identify applications and identities inside SSH tunnels was demonstrated in
+\textcite{Dusi:2008p6254}. Several algorithms are compared in
+\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
+for identifying Skype and SSH traffic.
+
+\subsubsection{Comparing Techniques}
+
+It is difficult to say what machine learning technique is the most effective as
+no consensus has been reached, the literature covers a wide variety of
+techniques each with vastly different goals and no two techniques can be
+directly compared as the data used for analysis has not been disclosed
+\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
+\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
+greatest performance and accuracy when compared to a number of Bayesian
+algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
+algorithms  to find random tree, IBI, IBK and random forest algorithms
+obtaining the greatest classification accuracy.
+
+An excellent meta study on traffic analysis techniques is presented in
+\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
+the techniques used, criteria analysed and how effectively they meet stated
+goals.
 
@@
 identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
-have been somewhat academic in nature and not necessarily feasible in practice.
-Sometimes they require compromise of large parts of the Tor network, supplying
-hostile data to Tor users or complicated knowledge of usage patterns and an
-excess of patience. The technique demonstrated in this paper is a low cost
-technique, which does not require very sophisticated equipment and can be
-completed by a passive observer.
+have been somewhat academic in nature and not necessarily feasible in practice
+\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
+the Tor network, supplying hostile data to Tor users or complicated knowledge of
+usage patterns and an excess of patience. The technique demonstrated in this
+paper is a low cost technique, which does not require very sophisticated
+equipment and can be completed by a passive observer.
 
@@
 \end{enumerate*}
-
-\input litreview.tex
 

### 2011-03-27 thesis/thesis.tex
Another paragraph to intro censorship

@@
 
+Providing resistance to blocking or censorship comes in many forms. The People's
+Republic of China operates a sophisticated Internet firewall capable of blocking
+requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
+This system is often referred to as the Great Firewall of China. Resisting this
+system can involve ignoring spurious reset packets injected into the stream of
+forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
+simple as accessing data through an encrypted proxy as is done in FreeGate
+\parencite{Smart:2008kx}.
+
 The goal of anonymity sometimes aligns with that of providing resistance to
@@
 censorship resistant system built on top of AN.ON
-\parencite{springerlink:10.1007/3-540-44702-4_7}.  Anonymous publishing systems
-such as Freedom \parencite{Goldberg:1999p2231} and Freenet
-\parencite{Clarke:2001p2435} also provide some measure of censorship resistance.
-The goal of aChord \parencite{Hazel:2002p6929} is to provide a distributed
-lookup system for peer-to-peer publishing systems, based on Chord
-\parencite{Stoica:2001:CSP:383059.383071}.
-
-Censorship resistance in aChord and gnuNet
-\parencite{Hazel:2002p6929}, Infranet \parencite{Feamster:2002p307}.
-
-Anonymous networks by acting as a relay for network traffic, provide some level
-of censorship resistance though these goals do not always align.
+\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
+Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
+aim to provide censorship resistance as well as anonymity. Infranet uses
+steganography to hide sensitive messages in innocuous content Infranet
+\parencite{Feamster:2002p307}.
 
@@
 
-Although Tor succeeds to a certain extent in providing anonymity and censorship
-resistance. Under controlled conditions it is possible to distinguish Tor
-traffic from other forms of encrypted traffic using traffic analysis. This makes
-it easy for Tor users to be isolated and targeted for attack. Since Tor relies
-on large numbers of users for the protections it provides, attacks that affect
-the reliability of the network can discourage participation, making it
-ineffective. This paper describes a simple traffic analysis technique which can
-be used to distinguish Tor traffic from another form of commonly encrypted
-traffic.
+%Although Tor succeeds to a certain extent in providing anonymity and censorship
+%resistance. Under controlled conditions it is possible to distinguish Tor
+%traffic from other forms of encrypted traffic using traffic analysis. This makes
+%it easy for Tor users to be isolated and targeted for attack. Since Tor relies
+%on large numbers of users for the protections it provides, attacks that affect
+%the reliability of the network can discourage participation, making it
+%ineffective. This paper describes a simple traffic analysis technique which can
+%be used to distinguish Tor traffic from another form of commonly encrypted
+%traffic.
 
-\section{Traffic Analysis}
+\section{Tor Weaknesses}
 
@@
 \citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
-operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.  It
-is believed that this is the first proposal of a traffic analysis technique for
-classification of Tor network streams.
+operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.
 

### 2011-03-27 thesis/thesis.tex
Little bit more work in vulnerabilities

--- 2011-03-20 thesis/thesis.tex
@@
 
-The first anonymous digital network, commonly known as MixNet was proposed in
-\textcite{Chaum:1981p296}. The foundation of MixNet was the use of an
-intermediary which forwarded messages from clients without any identifying
-details. Numerous proposals and implementations followed such as Freedom
-\parencite{Goldberg:1999p2231} and aChord \parencite{Hazel:2002p6929}. The
-Second Generation Onion Router (Tor), is an anonymous network which uses a
+The first anonymous digital network, commonly known as MixNet was proposed by
+\citeauthor{Chaum:1981p296} in \citetitle{Chaum:1981p296}
+\parencite{Chaum:1981p296}. This paper introduced a concept integral to many
+future anonymity providing designs, an intermediate system responsible for
+delivering messages without the identifying details of correspondents. The
+intermediate system, referred to as a 'mix' also employed public key
+cryptography to ensure that eavesdroppers could not obtain delivery information.
+
+This seminal paper spurred research into new techniques for providing anonymity
+and privacy for digital networks. Remailers such as Babel
+\parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
+mix to deliver anonymous email. Research produced designs that yielded
+mathematically provable anonymity
+\parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303} and networks that
+degrade gracefully when subject to attack, so called robust anonymity
+\parencite{Waidner:1989p5870,Jakobsson:1998p5137}. Designs such as MorphMix
+\parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
+\parencite{P5Sherwood:2005p5872} aimed to provide anonymity features to
+peer-to-peer (P2P) networks.
+
+Providing resistance to blocking or censorship comes in many forms. The People's
+Republic of China operates a sophisticated Internet firewall capable of blocking
+requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
+This system is often referred to as the Great Firewall of China. Resisting this
+system can involve ignoring spurious reset packets injected into the stream of
+forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
+simple as accessing data through an encrypted proxy as is done in FreeGate
+\parencite{Smart:2008kx}.
+
+More sophisticated circumvention tend to be based on anonymity providing
+designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
+resistant system built on top of AN.ON
+\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
+Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
+aim to provide censorship resistance as well as anonymity. Infranet uses
+steganography to hide sensitive messages in innocuous content Infranet
+\parencite{Feamster:2002p307}.
+
+The Second Generation Onion Router (Tor), is an anonymous network which uses a
 variant of Onion Routing, to provide low latency anonymous communications to a
@@
 
-Tor was originally developed by the U.S. Naval Research Lab in 1997
-\parencite{Syverson:1997kz} for application by the U.S. Navy. It has since been
-adopted by The Tor Project, Inc. and is made publicly available, finding usage
-in journalism, law enforcement, activism and military applications
-\parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most successful and
-widely deployed anonymous networks, with an average of two hundred thousand
-active users as of March 2011 \parencite{The-Tor-Project-Inc.:2011fk}.
+\section{The Second Generation Onion Router}
 
-Although Tor succeeds to a certain extent in providing anonymity and censorship
-resistance. Under controlled conditions it is possible to distinguish Tor
-traffic from other forms of encrypted traffic using traffic analysis. This makes
-it easy for Tor users to be isolated and targeted for attack. Since Tor relies
-on large numbers of users for the protections it provides, attacks that affect
-the reliability of the network can discourage participation, making it
-ineffective. This paper describes a simple traffic analysis technique which can
-be used to distinguish Tor traffic from another form of commonly encrypted
-traffic.
+Onion routing was originally developed by the U.S. Naval Research Lab in 1996
+\parencite{Goldschlag:1996wy} for application by the U.S. Navy. Like a mix,
+messages sent over an onion routing network were encrypted with their routing
+information and delivered to an intermediate server for forward delivery.
+Unlike the mix however, messages delivered using the onion routing network were
+encrypted multiple times, each 'layer' using a different key and routing
+instructions. The first node in a chain would only be able to encrypt the
+routing instructions to deliver the message to the next node. Each node in the
+sequence decrypting a layer until the complete message is decrypted and
+transmitted to the destination. This invention was granted a patent by the U.S.
+Patent Office in 2001 \parencite{Michael:2001}.
+
+This proposal was expanded on in \citetitle{Dingledine:2004p314} and addressed a
+number of weaknesses in the original onion router proposal
+\parencite{Dingledine:2004p314}. It also added some usability and anonymity
+features and deviates sufficiently from the original onion routing design in
+order to avoid patent claims. The technique employed by Tor is known as
+telescopic onion routing.
+
+In the Tor network, the intermediate nodes responsible for routing messages are
+known as relays and are typically chained together to construct a circuit.
+Traffic is repeatedly delivered through relays until it reaches another special
+relay known as an exit node, where it is delivered unencrypted to the final
+destination.  Figure \ref{tor-network} shows this typical usage of the Tor
+network.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
+  \caption{The Tor Network}
+  \label{tor-network}
+\end{figure}
+
+Circuits are built incrementally, obtaining a session key from each
+successive relay in the circuit and encrypting messages so that intermediate
+relays are unable to decrypt the message. Since circuits can take some time to
+build, they are pre-emptively created at regular intervals
+\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
+traffic normalization techniques that provide strong anonymity, messages passed
+through the Tor network are packaged in cells of a fixed size of 512 bytes
+\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
+that remove identifying features from common application protocols.
+
+Tor is developed and maintained  by The Tor Project, Inc. and is made publicly
+available, finding usage in journalism, law enforcement, activism and military
+applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
+successful and widely deployed anonymous networks, with an average of two
+hundred thousand active users as of March 2011
+\parencite{The-Tor-Project-Inc.:2011fk}.
+
+\section{Vulnerabilities and Weaknesses}
+
+The Tor system was designed with a number of compromises, sacrificing some level
+of anonymity in favour of usability and efficiency. This means that it is
+vulnerable to attacks that aim to disrupt users, steal information or identify
+users. A well known attack involves sniffing traffic that leaves exit nodes to
+capture private information \parencite{website:tor-password-leak}. Many users
+assume that Tor provides end to end encryption, and transmit private information
+over the Tor network.
+
+Technologies such as Javascript and Flash can be embedded in web pages accessed
+by Tor users, and have control over network resources. By injecting network
+traffic with certain patterns alongside regular network traffic, Tor users can
+be identified \parencite{Abbott:2007p298}.
+
+Tor bridges, intended as a way to get censored users access to Tor are easily
+identified. They are also vulnerable to clogging attacks which make bridge
+operators more easily identified \textcite{McLachlan:2009p197}.
+
+Most conventional attacks against secure networks are known as traffic analysis,
+this is the process of examining information about the communications rather
+than the information contained within them. This information may include the
+size of messages communicated, their frequency and timing. Many researchers have
+proposed traffic analysis techniques that allow attackers to reveal the
+identities of Tor users.
+
+\textcite{Murdoch:2005p325} proposes a technique to identify users by estimating
+the latency of individual Tor nodes using a hostile Tor node. The hostile Tor
+node is able to send data to users using a predictable traffic pattern and
+identify this pattern as it is repeated through the network, correlating streams
+back to individuals.
+
+This attack was shown to be impractical as the Tor network grew in size, with 
+the increased number of users adding enough congestion to mask the introduced
+identifying patterns \parencite{Evans:2009p315}. However a weakness in the Tor
+design meant that particularly configured hostile nodes could amplify the
+deliberately introduced congestion to make individuals identifiable on the
+larger network.
 
@@
 identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
-have been somewhat academic in nature and not necessarily feasible in practice.
-Sometimes they require compromise of large parts of the Tor network, supplying
-hostile data to Tor users or complicated knowledge of usage patterns and an
-excess of patience. The technique demonstrated in this paper is a low cost
-technique, which does not require very sophisticated equipment and can be
-completed by a passive observer.
+have been somewhat academic in nature and not necessarily feasible in practice
+\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
+the Tor network, supplying hostile data to Tor users or complicated knowledge of
+usage patterns and an excess of patience. The technique demonstrated in this
+paper is a low cost technique, which does not require very sophisticated
+equipment and can be completed by a passive observer.
+
+This paper describes a simple traffic analysis technique which can be used to
+distinguish Tor traffic from another form of commonly encrypted traffic.
+Utilized properly this technique could be used to automatically identify Tor
+nodes and block them, preventing Tor from being used as a censorship
+circumvention tool.  Alternatively it could be used to isolate Tor users and
+target them for attack, be it technically orientated such as a denial of service
+attack or socially; coercion or arrest. Any direct attack on Tor users can
+discourage participation, making the network less effective.
+
+%Although Tor succeeds to a certain extent in providing anonymity and censorship
+%resistance. Under controlled conditions it is possible to distinguish Tor
+%traffic from other forms of encrypted traffic using traffic analysis. This makes
+%it easy for Tor users to be isolated and targeted for attack. Since Tor relies
+%on large numbers of users for the protections it provides, attacks that affect
+%the reliability of the network can discourage participation, making it
+%ineffective. This paper describes a simple traffic analysis technique which can
+%be used to distinguish Tor traffic from another form of commonly encrypted
+%traffic.
+
+%\section{Traffic Classification}
+
+%When considering the use of traffic analysis for classification of Internet
+%communications, three techniques are used. These are: exact matching, heuristic
+%matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
+%techniques recognise properties of communications that mirror known protocols
+%and communication patterns. This might include the port an application uses or
+%the format of its payload. Since Tor employs strong encryption and communicates
+%using known and commonly used protocols, exact matching techniques would prove
+%ineffective for classification. Heuristic matching looks for patterns in
+%conversations to determine communications patterns and infer relationships,
+%while machine learning involves the use of statistics to train computer
+%algorithms to classify traffic. Both heuristic and machine matching techniques
+%are suitable for traffic analysis of anonymous networks because they do not
+%rely on analysing the content of messages.
+
+%\subsection{Heuristic Techniques}
+
+%The increasing burden of peer to peer (P2P) applications on campus networks,
+%and their shift to encryption motivated the development of heuristics based
+%techniques for identifying P2P traffic. Early techniques include identifying
+%known properties of P2P networks such as often communicating using both the UDP
+%and TCP protocols simultaneously and using a solitary connection to transfer
+%high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
+%number of false positives by eliminating packets that matched known
+%communications protocols.
+
+%Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
+%\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
+%through early elimination of false positives and by expanding the scope of
+%matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
+%to identify P2P nodes before applying a secondary heuristic to identify
+%‘supernodes’ which are a subset of all P2P nodes.
+
+%Classifying traffic based on system roles is a key feature of the technique
+%that appears in \citetitle{Karagiannis:2005p6359}
+%\parencite{Karagiannis:2005p6359}. By analysing communications at the host
+%level then at increasing levels of granularity, a greater level of accuracy is
+%achieved.
+
+%The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
+%\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
+%flows are represented in a TDG, mathematical properties of the flow can be
+%analysed to make positive identifications.
+
+%Viruses have also posed a problem for network administrators, often
+%over-utilizing network resources and using the network to infect new machines.
+%A technique for identifying various worms was proposed in
+%\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
+%from network administrators to avoid detection, presenting the same problems of
+%identification as Tor network traffic.
+
+%\subsection{Machine Learning Techniques}
+
+%\subsubsection{Expectation-Maximisation}
+
+%The first use of machine learning to categorise traffic flows appears in
+%\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
+%be used for machine learning and an attempt at coarse grained classification
+%using an expectation-maximisation (EM) algorithm are demonstrated. The
+%expectation-maximisation algorithm is a method for finding probabilistic
+%estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
+%same technique is also demonstrated in \textcite{Soule:2004p3817} using
+%histograms for finer grained classification.  The EM algorithm is again used in
+%\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
+%comparing EM favourably against a Na\"{i}ve Bayes classifier.
+
+%\subsubsection{Na\"{i}ve Bayes}
+
+%\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
+%flows that have previously been sorted into groups by analysing the flow
+%content. This paper focuses on many of the most commonly used Internet
+%protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
+%identifying traffic belonging to the Skype application.
+
+%\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
+%websites accessed through Privacy Enhancing Technologies (PET), including Tor.
+%This technique performed poorly when applied to the Tor network, but it
+%suggests that Tor traffic has particular characteristics that distinguish it
+%from many existing PETs. It makes a particularly useful observation: ``The most
+%frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
+%−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
+
+%\subsubsection{Markov Models}
+
+%Hidden Markov Models (HMM) are a statistical modelling technique useful
+%for classification of systems with an unobservable state
+%\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
+%technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
+%primary identification characteristics for use with this algorithm are packet
+%size and inter-packet arrival times. With refinement this algorithm is used
+%with increasing accuracy in \textcite{Wright:2006p322} and
+%\textcite{Dainotti:2008p1435}.
+
+%In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
+%discover distinguishing characteristics of traffic flows, rather than with a
+%specific set of classification goals. This information is used to build HMMs
+%for the purpose of traffic classification.
+
+%Since HMMs model particular behaviours, they can be used to recognize
+%deviations from normal behaviour as shown in
+%\textcite{EstevezTapiador:2003p7201}. Motivated by
+%\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
+%flags and the position of individual packets in a stream to train an Observable
+%Markov Model for traffic classification, achieving greater classification
+%accuracy than \citeauthor{Bernaille:2005p6205}.
+
+%\subsubsection{Clustering}
+
+%Clustering algorithms group observations into subsets based on similar
+%characteristics, they are a form of unsupervised learning technique designed to
+%discover organization in unlabelled data sets. They have been the basis of a
+%number of traffic classification techniques with the K-Means clustering
+%technique being the most prominent.  K-Means cluster analysis appears in
+%\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
+%\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
+%Applications with Noise (DBSCAN) algorithm appears in
+%\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
+
+%\subsubsection{Other Techniques}
+
+%Other algorithms used for traffic classification include Nearest Neighbour and
+%Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
+%Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
+%to identify applications and identities inside SSH tunnels was demonstrated in
+%\textcite{Dusi:2008p6254}. Several algorithms are compared in
+%\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
+%for identifying Skype and SSH traffic.
+
+%\subsubsection{Comparing Techniques}
+
+%It is difficult to say what machine learning technique is the most effective as
+%no consensus has been reached, the literature covers a wide variety of
+%techniques each with vastly different goals and no two techniques can be
+%directly compared as the data used for analysis has not been disclosed
+%\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
+%\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
+%greatest performance and accuracy when compared to a number of Bayesian
+%algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
+%algorithms  to find random tree, IBI, IBK and random forest algorithms
+%obtaining the greatest classification accuracy.
+
+%An excellent meta study on traffic analysis techniques is presented in
+%\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
+%the techniques used, criteria analysed and how effectively they meet stated
+%goals.
 
@@
 
-Tor employs strong encryption, the goal of which is to ensure that the data
-transmitted is indistinguishable from random noise. To an observer, two
-different streams of encrypted data look almost the same. Thus the traditional
-means of identifying these protocols are ineffective.
-
-This raises the question: is it possible to distinguish the traffic created by
-these networks, from encrypted traffic produced by conventional software? This
-question can be broken down further:
-
 \begin{enumerate*}
-  \item Can the traffic be classified using automated matching techniques?
-  \item Do these networks have characteristics that make them readily
-    distinguishable using heuristics based matching?
+  \item Can Tor traffic be identified using automated matching techniques?
+  \item Does Tor have characteristics that make it readily distinguishable using
+    heuristics based matching?
   \item Do they have characteristics that make them distinguishable using
     machine learning techniques?
-  %\item How long does a user have to be
-  %  connected to the network before a confident match can be made?
 \end{enumerate*}
-
-\input litreview.tex
 

### 2011-04-03 thesis/thesis.tex
Bit of work on tor section, more detail, more detail on vulnerabilities

--- 2011-03-27 thesis/thesis.tex
@@
 
-The goal of anonymity sometimes aligns with that of providing resistance to
-censorship. Many censorship resistance systems are built on top of anonymity
-providing designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a
-censorship resistant system built on top of AN.ON
+More sophisticated circumvention tend to be based on anonymity providing
+designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
+resistant system built on top of AN.ON
 \parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
@@
 
-In the Tor network, the intermediate nodes responsible for routing messages are
-known as relays and are typically chained together to construct a circuit.
-Clients connect to the Tor network by communicating with a special relay known
-as a bridge, which constitutes the first relay in a circuit. Traffic is
-repeatedly delivered through relays until it reaches another special relay known
-as an exit node, where it is delivered unencrypted to the final destination.
-Figure \ref{tor-network} shows this typical usage of the Tor network.
+Tor is developed and maintained  by The Tor Project, Inc. and is made publicly
+available, finding usage in journalism, law enforcement, activism and military
+applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
+successful and widely deployed anonymous networks, with an average of two
+hundred thousand active users as of March 2011
+\parencite{The-Tor-Project-Inc.:2011fk}.
+
+Traffic enters the Tor network through an onion proxy which accepts TCP streams.
+Some identifying features are scrubbed from the data using application filters
+before the data is relayed over the network through TLS \parencite{website:TLS}
+encrypted connections. The intermediate nodes responsible for routing messages
+are known as relays and are typically chained together to construct a circuit.
+When traffic leaves the Tor network it is delivered by a special kind of relay
+known as an exit node. At an exit node the data is transmitted in the original
+format it was supplied to at the onion proxy.
+
+Figure \ref{tor-network} shows the typical path a message takes through the Tor
+network.
 
@@
 
-Circuits are built incrementally, obtaining a session key from each
-successive relay in the circuit and encrypting messages so that intermediate
-relays are unable to decrypt the message. Since circuits can take some time to
-build, they are pre-emptively created at regular intervals
-\parencite[5]{Dingledine:2004p314}. Although Tor does not support many of the
-traffic normalization techniques that provide strong anonymity, messages passed
-through the Tor network are packaged in cells of a fixed size of 512 bytes
-\parencite[5]{Dingledine:2004p314}. Tor also provides application level filters
-that remove identifying features from common application protocols.
+The onion proxy builds circuits incrementally, first obtaining a session key
+from each successive relay in a circuit. Once all session keys for a circuit
+have been obtained, the message is broken into fixed sized cells of 512 bytes
+and iteratively encrypted using the session key of each node in the circuit in
+the reverse order that the data traverses the network. Cells come in two forms:
+control cells and relay cells. Control cells are used to create and maintain
+circuits, while relay cells contain commands for circuit maintenance and
+additional data for verifying message integrity and identifying streams.
 
-Tor is developed and maintained  by The Tor Project, Inc. and is made publicly
-available, finding usage in journalism, law enforcement, activism and military
-applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
-successful and widely deployed anonymous networks, with an average of two
-hundred thousand active users as of March 2011
-\parencite{The-Tor-Project-Inc.:2011fk}.
+When the first node in the circuit receives a cell, it removes a layer by
+decrypting the message using it's session key. The cell is delivered along the
+circuit and at each node a layer is removed until the cell is completely
+decrypted and can be delivered successfully. Since circuits can take some time
+to build, they are pre-emptively created at regular intervals
+\parencite[5]{Dingledine:2004p314}.
+
+\section{Vulnerabilities and Weaknesses}
+
+When designing a system such as Tor, a number of trade-offs have to be made
+between the strength of the security provided and the convenience and
+performance of the system. The Tor designers consciously prioritized low
+latency, usability and flexibility against security goals such as security
+against end to end attacks \parencite[4]{Dingledine:2004p314}. These design
+decisions mean that Tor is vulnerable to several kinds of attacks, some of them
+expected and some not.
+
+A well known attack involves sniffing traffic that leaves exit nodes to
+capture private information \parencite{website:tor-password-leak}. Many users
+assume that Tor provides end to end encryption, and transmit private information
+over the Tor network.
+
+Most conventional attacks against secure networks are known as traffic analysis,
+this is the process of examining information about the communications rather
+than the information contained within them. This information may include the
+size of messages communicated, their frequency and timing. Many researchers have
+proposed traffic analysis techniques that allow attackers to reveal the
+identities of Tor users.
+
+Technologies such as Javascript and Flash can be embedded in web pages accessed
+by Tor users, and have control over network resources. By injecting network
+traffic with certain patterns alongside regular network traffic, Tor users can
+be identified \parencite{Abbott:2007p298}.
+
+Tor bridges, intended as a way to get censored users access to Tor are easily
+identified. They are also vulnerable to clogging attacks which make bridge
+operators more easily identified \textcite{McLachlan:2009p197}.
+
+\textcite{Murdoch:2005p325} proposes a technique to identify users by estimating
+the latency of individual Tor nodes using a hostile Tor node. The hostile Tor
+node is able to send data to users using a predictable traffic pattern and
+identify this pattern as it is repeated through the network, correlating streams
+back to individuals.
+
+This attack was shown to be impractical as the Tor network grew in size, with 
+the increased number of users adding enough congestion to mask the introduced
+identifying patterns \parencite{Evans:2009p315}. However a weakness in the Tor
+design meant that particularly configured hostile nodes could amplify the
+deliberately introduced congestion to make individuals identifiable on the
+larger network.
+
+\section{Significance}
+
+The Internet's expanding growth \parencite{Miniwatts-Marketing-Group:2010uq} and
+role in political discourse \parencite{Bonchek:1997p3455} have allowed for
+increased mobility and organization of activist groups
+\parencite{Alexander:2011kx,Anderson:2011vn}. The increasingly sophisticated use
+of censorship \parencite{Crandall:2007p6165,Karlin:2009p6166} and swift
+retribution for dissenting opinion
+\parencite{website:china-yahoo-torture,website:vietnam-bloggers-arrested,website:egypt-arrests,website:blogger-arrests}
+may have chilling effects, effectively neutralizing these benefits. In light of
+these threats the value of anonymous networks and anti-censorship technology can
+be recognized. It is quite telling that new and sometimes unorthodox methods of
+circumventing censorship are being deployed every day
+\parencite{The-Economist:2011fk,Brading:2011ys}.
+
+While Tor has been the subject of much academic literature, the primary
+objective of researchers has historically been the attempt to reveal participant
+identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
+have been somewhat academic in nature and not necessarily feasible in practice
+\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
+the Tor network, supplying hostile data to Tor users or complicated knowledge of
+usage patterns and an excess of patience. The technique demonstrated in this
+paper is a low cost technique, which does not require very sophisticated
+equipment and can be completed by a passive observer.
+
+This paper describes a simple traffic analysis technique which can be used to
+distinguish Tor traffic from another form of commonly encrypted traffic.
+Utilized properly this technique could be used to automatically identify Tor
+nodes and block them, preventing Tor from being used as a censorship
+circumvention tool.  Alternatively it could be used to isolate Tor users and
+target them for attack, be it technically orientated such as a denial of service
+attack or socially; coercion or arrest. Any direct attack on Tor users can
+discourage participation, making the network less effective.
 
@@
 
-\section{Tor Weaknesses}
-
-Research into Tor weaknesses has included the use of hostile exit nodes to
-capture private information \parencite{website:tor-password-leak}, attacks that
-take advantages of web based technologies such as Javascript and Flash to reveal
-user's identities \parencite{Abbott:2007p298} and a number of identity revealing
-traffic analysis techniques
-\parencite{Murdoch:2005p325,Abbott:2007p298,Evans:2009p315}.
-\citeauthor{McLachlan:2009p197} reveals a method for identifying bridge
-operators in \textcite{McLachlan:2009p197} using the Tor protocol directly.
+\section{Traffic Analysis as Classification}
 
@@
 
-\section{Significance}
-
-The Internet's expanding growth \parencite{Miniwatts-Marketing-Group:2010uq} and
-role in political discourse \parencite{Bonchek:1997p3455} have allowed for
-increased mobility and organization of activist groups
-\parencite{Alexander:2011kx,Anderson:2011vn}. The increasingly sophisticated use
-of censorship \parencite{Crandall:2007p6165,Karlin:2009p6166} and swift
-retribution for dissenting opinion
-\parencite{website:china-yahoo-torture,website:vietnam-bloggers-arrested,website:egypt-arrests,website:blogger-arrests}
-may have chilling effects, effectively neutralizing these benefits. In light of
-these threats the value of anonymous networks and anti-censorship technology can
-be recognized. It is quite telling that new and sometimes unorthodox methods of
-circumventing censorship are being deployed every day
-\parencite{The-Economist:2011fk,Brading:2011ys}.
-
-While Tor has been the subject of much academic literature, the primary
-objective of researchers has historically been the attempt to reveal participant
-identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
-have been somewhat academic in nature and not necessarily feasible in practice
-\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
-the Tor network, supplying hostile data to Tor users or complicated knowledge of
-usage patterns and an excess of patience. The technique demonstrated in this
-paper is a low cost technique, which does not require very sophisticated
-equipment and can be completed by a passive observer.
-
 \section{Research Questions}
 
-Tor employs strong encryption, the goal of which is to ensure that the data
-transmitted is indistinguishable from random noise. To an observer, two
-different streams of encrypted data look almost the same. Thus the traditional
-means of identifying these protocols are ineffective.
-
-This raises the question: is it possible to distinguish the traffic created by
-these networks, from encrypted traffic produced by conventional software? This
-question can be broken down further:
-
 \begin{enumerate*}
-  \item Can the traffic be classified using automated matching techniques?
-  \item Do these networks have characteristics that make them readily
-    distinguishable using heuristics based matching?
+  \item Can Tor traffic be identified using automated matching techniques?
+  \item Does Tor have characteristics that make it readily distinguishable using
+    heuristics based matching?
   \item Do they have characteristics that make them distinguishable using
     machine learning techniques?
-  %\item How long does a user have to be
-  %  connected to the network before a confident match can be made?
 \end{enumerate*}

### 2011-04-17 thesis/thesis.tex
Refer to document as 'this thesis' not 'this paper'

@@
 anonymous network which uses a form of Onion Routing to provide low latency
-anonymous communications. This paper demonstrates that traffic from a simulated
+anonymous communications. This thesis demonstrates that traffic from a simulated
 Tor network can be distinguished from regular encrypted traffic, suggesting that
@@
 usage patterns and an excess of patience. The technique demonstrated in this
-paper is a low cost technique, which does not require very sophisticated
+thesis is a low cost technique, which does not require very sophisticated
 equipment and can be completed by a passive observer.
 
-This paper describes a simple traffic analysis technique which can be used to
+This thesis describes a simple traffic analysis technique which can be used to
 distinguish Tor traffic from another form of commonly encrypted traffic.
@@
 %the reliability of the network can discourage participation, making it
-%ineffective. This paper describes a simple traffic analysis technique which can
+%ineffective. This thesis describes a simple traffic analysis technique which can
 %be used to distinguish Tor traffic from another form of commonly encrypted
@@
 
-The experiment conducted in this paper utilize a non-equivalent group design.
+The experiment conducted in this thesis utilize a non-equivalent group design.
 The experimental groups are generated using simulations which allow for a great

### 2011-04-17 thesis/experiment.tex
Added software versions.

@@
   delivered to the addressed host. This makes eavesdropping difficult. For
-  the purpose of this experiment a simple hub or repeater is required. A hub
+  the purpose of this experiment a Netgear DS106 dual speed hub was used. A hub
   does not examine packet delivery information, it simple broadcasts all packets
@@
   by tcpdump is well documented \parencite{:nx} which makes it ideal for
-  transformation and processing by third party tools.
+  transformation and processing by third party tools. Tcpdump version 4.0.0
+  combined with libpcap 1.0.0 was used for this experiment.
 
@@
   which make it useful for running a controlled experiment \parencite{Oracle:2011kx}.
+  VirtualBox version 3.2.6 r63112 was used in this experiment.
 
@@
   Gems include support for the Selenium browser testing framework, process
-  monitoring, dynamic web content generation and automated testing.
+  monitoring, dynamic web content generation and automated testing. The Ruby
+  1.8.7 (2010-01-10 patchlevel 249) Ubuntu package was installed where Ruby was
+  required. The exact version of all gems used in the experiment are shown in
+  table \ref{table:gems}.
+
+  \begin{center}
+    \begin{minipage}[t]{\linewidth}
+      \begin{table}[H]
+        \begin{tabular}{llr}
+          \toprule
+          Gem name & Purpose & Version \\
+          \midrule
+          bundler & Application gem manager & 1.0.2 \\
+          daemon\_controller & Monitor and control daemon processes & 0.2.6 \\
+          rspec & Testing and control of selenium & 1.3.0 \\
+          selenium-client & Control browser using selenium and ruby & 1.2.18 \\
+          haml & A simple HTML like markup language & 3.0.21 \\
+          rack & Rack web serving framework & 1.2.1 \\
+          sinatra & Ruby web framework & 1.0 \\
+          \bottomrule
+        \end{tabular}
+        \caption{Ruby Gems}
+        \label{table:gems}
+      \end{table}
+    \end{minipage}
+  \end{center}
 
@@
   consistent way with typical set of POSIX tools and the 'apt-get' package
-  manager \parencite{Pereira:2011uq}.
+  manager \parencite{Pereira:2011uq}. Both the desktop and server editions were
+  used for this experiment, version 10.04 commonly referred to as lucid lynx.
 
@@
   Ruby. Using Selenium the typical interactions a user makes when viewing a
-  website can be simulated.
+  website can be simulated. Selenium version 1.0.6 was used for this experiment.
 
@@
   \parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
-  candidate for this experiment.
+  candidate for this experiment. The Ubuntu Firefox package was used in this
+  expriment, version 3.6.8.
 
@@
   default on the Ubuntu operating system and the server component is easily
-  installed using the apt-get package management system.
+  installed using the apt-get package management system. The version used for
+  this experiment was OpenSSH\_5.3p1 Debian-3ubuntu4, OpenSSL 0.9.8k 25 Mar 2009.
 
@@
   both the HTTP and HTTPS protocols \parencite{Foundation:2011uq}. Combined with
-  software such as Sinatra it can serve dynamic web content.
+  software such as Sinatra it can serve dynamic web content. Apache version
+  2.2.14/Ubuntu was used to serve web sites in this experiment.
 
@@
   configuration and development time to develop dynamic web applications.
+  Sinatra version 1.0 was used in this experiment.
 
@@
   \parencite{Chelimsky:2010vn}. It is well integrated with Selenium which makes
-  it ideal for running large suites of Selenium tests.
+  it ideal for running large suites of Selenium tests. RSpec version 1.3.0 was
+  used in this experiment.
 

### 2011-04-17 thesis/results.tex
Put conclusion and results back into their own chapter.
Add description of ROC area statistic in results table

@@
-\chapter{Discussion of Results}
+\chapter{Results}
 
@@
 
+The table includes the true positive and false positive rate rate of each algorithm and
+include the area under the receiver operating characteristic (ROC) curve. The
+ROC is a tool used for evaluating the usefulness and comparing different
+matching algorithms and is often used to compare Internet traffic
+classification techniques \parencite{citeulike:167557,Nguyen:2008p3837}.
+
 \begin{table}[H]
@@
     \toprule
-    & True Positive Rate & False Positive Rate & ROC \\
+    & True Positive Rate & False Positive Rate & ROC Area \\
     \midrule
@@
 \end{table}
+
+\chapter{Discussion of Results}
 
@@
 
+\chapter{Conclusion}
+
 \section{Conclusion}

### 2011-04-17 thesis/results.tex
Revised questions a little, added paragraph to limitations

@@
     \toprule
-    & True Positive Rate & False Positive Rate & ROC Area \\
+    Algorithm & True Positive Rate & False Positive Rate & ROC Area \\
     \midrule
@@
 
+The real Tor network consists of over two hundred thousand computer systems,
+with over two thousand routers \parencite{TorStatus:2011fk}, all with different
+operating systems, different hardware, different configurations and available
+bandwidth. All the variables that were controlled for during this experiment
+are present in the real network, and may be amplified by it's greater size.
+Without further research it is difficult to say if the technique demonstrated
+here will apply in the wild.
+
 \section{Addressing Research Questions}
@@
 \begin{enumerate*}
-  \item{Can the traffic be classified using automated matching techniques?}
+  \item{Can Tor traffic be distinguished from other network traffic that uses
+    similar or the same encryption and protocols?}
 
@@
 
-  \item{Do these networks have characteristics that make them readily
-  distinguishable using heuristics based matching?}
+  \item{Can Tor traffic be identified using automated matching techniques?}
+
+  All the classification algorithms trialled were able to successfully classify
+  web browser traffic routed over the simulated Tor network, with the best
+  performing algorithm able to correctly classify 95\%.
+
+  The value of this level of accuracy depends on the application. Identifying
+  multiple regular connections to the Tor network may provide sufficient
+  confidence to classify a system as a Tor node. This could be combined with
+  other known properties of the Tor network to increase confidence.
+
+  \item{Does Tor traffic have characteristics that make it readily distinguishable using
+    heuristics based matching?}
 
@@
 
-  \item{Do they have characteristics that make them distinguishable using a
-  machine learning technique?}
-
-  Insert answer here.
-
-  \item{How long does a user have to be connected to the network before a
-  confident match can be made?}
+  \item{Does Tor traffic have characteristics that make it distinguishable using
+    machine learning techniques?}
 

### 2011-04-17 thesis/thesis.tex
Revised questions a little, added paragraph to limitations

@@
 \begin{enumerate*}
+  \item Can Tor traffic be distinguished from other network traffic that uses
+    similar or the same encryption and protocols?
   \item Can Tor traffic be identified using automated matching techniques?
-  \item Does Tor have characteristics that make it readily distinguishable using
+  \item Does Tor traffic have characteristics that make it readily distinguishable using
     heuristics based matching?
-  \item Do they have characteristics that make them distinguishable using
+  \item Does Tor traffic have characteristics that make it distinguishable using
     machine learning techniques?

### 2011-04-26 thesis/thesis.tex
Underscores in notes and in refkeys changed

@@
 system can involve ignoring spurious reset packets injected into the stream of
-forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
+forbidden communications \parencite{springerlink:10.1007/11957454-2}, or be as
 simple as accessing data through an encrypted proxy as is done in FreeGate
@@
 resistant system built on top of AN.ON
-\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
+\parencite{springerlink:10.1007/3-540-44702-4-7}. Publishing systems such as
 Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}

### 2011-05-01 thesis/results.tex
Adding some more content to the results section, adding a bit more of a description to the results. Remove redundant question.

@@
 
-The classification results are tabulated below. The best performing algorithm
-random forest was able to classify HTTP over Tor with 93.7\% accuracy and a
-false positive rate of 3.7\%. HTTPS over Tor was more easily identified with a
-97.7\% accuracy and low false positive rate of 0.3\%.
+Traffic classification algorithms are evaluated using a number of metrics, the
+primary of these being the true positive rate sometimes known as the detection
+rate (DR) and the false positive rate. A strong traffic classifier typically
+has a high true positive rate and a low false positive rate. In table
+\ref{table:results} the true positive rate indicates the percentage of
+individual sessions correctly classified as the listed protocol. The false
+positive rate indicates the percentage of sessions incorrectly labelled as the
+listed protocol. Included with these is the area under the receiver operating
+characteristic (ROC) curve. The ROC is a tool used for evaluating the
+usefulness and comparing different matching algorithms and is often used to
+compare Internet traffic classification techniques
+\parencite{citeulike:167557,Nguyen:2008p3837}.
 
-The table includes the true positive and false positive rate rate of each algorithm and
-include the area under the receiver operating characteristic (ROC) curve. The
-ROC is a tool used for evaluating the usefulness and comparing different
-matching algorithms and is often used to compare Internet traffic
-classification techniques \parencite{citeulike:167557,Nguyen:2008p3837}.
+All of the algorithms chosen were able to successfully classify HTTPS and HTTP
+over Tor traffic with accuracy in excess of 90\%, with the Adaboost algorithm
+unable to classify HTTPS over Tor. The best performing algorithm random forest
+was able to classify HTTP over Tor with 93.7\% accuracy and a false positive
+rate of 3.7\%. HTTPS over Tor was more easily identified with a 97.7\% accuracy
+and low false positive rate of 0.3\%.
 
@@
     \toprule
-    Algorithm & True Positive Rate & False Positive Rate & ROC Area \\
+    & True Positive Rate & False Positive Rate & ROC Area \\
     \midrule
@@
 
-  Yes, the classification algorithms trialled were all able to identify Tor traffic
-  with reasonable accuracy.
+    Under the controlled conditions of the experiment demonstrated within this
+    thesis, comparing a sample of simulated encrypted network traffic produced
+    by a commonly used web browser versus the same traffic routed over a
+    demonstration Tor network, all the techniques used were able to classify
+    Tor traffic with a high level of accuracy.
 
@@
     heuristics based matching?}
-
-  Insert answer here.
-
-  \item{Does Tor traffic have characteristics that make it distinguishable using
-    machine learning techniques?}
-
-  Insert answer here.
 

### 2011-05-02 thesis/results.tex
Describing the algorithms used for machine learning, added refs. Started answering heuristics question.

@@
 
+\section{Algorithms Used}
+
+A brief description of the machine learning algorithms utilized as well as the
+motivation for their inclusion is described below.
+
+\subsection{Random Forest}
+
+The random forest algorithm is a classifier that builds multiple decision trees
+with random sets of features. An input is processed by each tree, and the
+classification chosen is the one which is produced by most of the trees
+\parencite{Ho:1995vm}. For this experiment, the random forest algorithm
+generated 10 trees and used 6 random features.
+
+The random forest algorithm was chosen for its unparalleled accuracy and strong
+performance \parencite{Leo-Breiman:2004fk}.
+
+\subsection{j4.8}
+
+j4.8 is a free Java version of the C4.5 algorithm, a classifier which builds a
+decision tree using the concept of information entropy
+\parencite{Quinlan:1993:CPM:152181}. This algorithm was chosen because of it's
+successful use in earlier traffic classification publications.
+
+\subsection{Random Tree}
+
+\subsection{Adaboost}
+
+AdaBoost or Adaptive Boosting
+
 \chapter{Discussion of Results}
@@
 
+    While each phase of the experiment was conducted over a similar time
+    period, the number of sessions captured differs greatly. This suggests that
+    the Tor network may introduce significant overhead to communications
+    streams. How this latency manifests itself will determine how useful it is
+    as an identifying characteristic.
+
 \end{enumerate*}

### 2011-05-15 thesis/experiment.tex
Added in Weka version
Describing the algorithms used for machine learning, added refs. Started answering heuristics question.
Refer to items in ARFF file as instances, as they're known in the literature, also reference the manual

@@
   sources using a wide variety of machine learning algorithms
-  \parencite{Hall:2009p7662}. It supports processing of an input
-  Attribute-Relation File Format (ARFF), a file which contains ASCII text
-  describing a list of items with common attributes. Items can be given an
-  attribute which provides a nominal classification for verification purposes.
+  \parencite{Hall:2009p7662,Bouckaert:2010we}. It supports processing of an
+  input Attribute-Relation File Format (ARFF), a file which contains ASCII text
+  describing a list of items with common attributes known as instances.
+  Instances can be given an attribute which provides a nominal classification
+  for verification purposes in Weka. Version 3.6.4 of Weka was used for
+  classification during this experiment.
 
@@
 
-The final stage simulation will be run in three phases:
+The simulation involves three separate phases of equal length, each simulating a
+different kind of network traffic:
 

### 2011-05-15 thesis/experiment.tex
Explain the attributes examined by netAI

@@
 with mergecap and processed by NetAI to produce ARFF format files for use by
-Weka. Each data set were given the nominal classification 'http',
-'http\_over\_tor' and 'https\_over\_tor', all other nominal attributes were
-removed.
+Weka. NetAI identifies flows inside the capture files and produces a number
+of statistics to be used as attributes for classification. The attributes
+produced by NetAI are shown in table \ref{table:netmate-attributes}.
+
+\begin{table}[H]
+  \begin{tabular}{lll}
+    \toprule
+    Attribute name & Description \\
+    \midrule
+    srcip & Source IP address \\
+    srcport & Source port \\
+    dstip & Destination IP address \\
+    dstport & Destination port \\
+    proto & Protocol (TCP, UDP) \\
+    total\_fpackets & Total forward packets \\
+    total\_fvolume & Total forward volume \\
+    total\_bpackets & Total backward packets \\
+    total\_bvolume & Total backward volume \\
+    min\_fpktl & Minimum forward packet length \\
+    mean\_fpktl & Mean forward packet length \\
+    max\_fpktl & Maximum forward packet length \\
+    std\_fpktl & Std. Deviation of forward packet length \\
+    min\_bpktl & Minmum backward packet length \\
+    mean\_bpktl & Mean backward packet length \\
+    max\_bpktl & Maximum backward packet length \\
+    std\_bpktl & Std. Deviation of backward packet length \\
+    min\_fiat & Minimum forward inter arrival time \\
+    mean\_fiat & Mean forward inter arrival time \\
+    max\_fiat & Maximum forward inter arrival time \\
+    std\_fiat & Std. Deviation of forward inter arrival time \\
+    min\_biat & Minimum backward inter arrival time \\
+    mean\_biat & Mean backward inter arrival time \\
+    max\_biat & Maximum backward inter arrival time \\
+    std\_biat & Std. Devation of backward inter arrival time \\
+    duration & Session duration \\
+    min\_active & Minimum active \\
+    mean\_active & Mean active \\
+    max\_active & Maximum active \\
+    std\_active & Std. Deviation active \\
+    min\_idle & Minimum idle \\
+    mean\_idle & Mean idle \\
+    max\_idle & Maximum idle \\
+    std\_idle & Std. Deviation of idle \\
+    sflow\_fpackets & Sub flow forward packets \\
+    sflow\_fbytes & Sub flow forward bytes \\
+    sflow\_bpackets & Sub flow backward packets \\
+    sflow\_bbytes & Sub flow backward bytes \\
+    fpsh\_cnt & Forward push counter \\
+    bpsh\_cnt & Backward push counter \\
+    furg\_cnt & Forward urgent counter \\
+    burg\_cnt & Backward urgent counter \\
+    total\_fhlen & Total forward header length \\
+    total\_bhlen & Total backward header length \\
+    \bottomrule
+    \label{table:netmate-attributes}
+  \end{tabular}
+  \caption{Captured Data}
+\end{table}
+
+Each data set was given the nominal classification 'http',
+'http\_over\_tor' and 'https\_over\_tor', this attribute was appended as the
+last attribute in the ARFF file.
+
+This file was imported into the Weka program, all nominal attributes other than
+the classification were removed and a number of classification algorithms were
+trialled. The results of classification with all forty attributes is shown in
+table \ref{table:results}.
 

### 2011-05-15 thesis/results.tex
Explain the adaboost and j4.8 algorithms

@@
 
-j4.8 is a free Java version of the C4.5 algorithm, a classifier which builds a
-decision tree using the concept of information entropy
-\parencite{Quinlan:1993:CPM:152181}. This algorithm was chosen because of it's
-successful use in earlier traffic classification publications.
+j4.8 is a Java version of the C4.5 classification algorithm, which has a
+permissive open source license and is available in the Weka software suite. It
+builds a decision tree using the concept of information entropy
+\parencite{Quinlan:1993:CPM:152181}, creating decision branches for features of
+a set of data that display the most uncertainty. This algorithm was chosen
+because of it's successful use in earlier traffic classification publications.
 
@@
 
-\subsection{Adaboost}
+\subsection{AdaBoost}
 
-AdaBoost or Adaptive Boosting
+Adaptive Boosting is a technique of combining various weak classifiers to
+create a strong classifier \parencite{Schapire:1999uq}, the AdaBoost algorithm.
+It has been used successfully in several traffic classification applications
+\parencite{Alshammari:2009p7474,Haffner:2005p3822,Mohd:2009p6484} and purports
+to not suffer from the problem of over-fitting.
 

### 2011-05-15 thesis/experiment.tex
Add in index to table, remove nominal/non statistical attributes

--- 2011-05-15 thesis/experiment.tex
@@
 with mergecap and processed by NetAI to produce ARFF format files for use by
-Weka. Each data set were given the nominal classification 'http',
-'http\_over\_tor' and 'https\_over\_tor', all other nominal attributes were
-removed.
+Weka. NetAI identifies flows inside the capture files and produces a number
+of statistics to be used as attributes for classification. The statistical
+attributes produced by NetAI are shown in table \ref{table:netmate-attributes}.
+
+\begin{table}[H]
+
+  \newcounter{netAICounter}
+  \newcommand{\netaicnt}[0]{\stepcounter{netAICounter}\arabic{netAICounter}}
+
+  \begin{tabular}{lll}
+    \toprule
+    Index & Attribute name & Description \\
+    \midrule
+    %\netaicnt & srcip & Source IP address \\
+    %\netaicnt & srcport & Source port \\
+    %\netaicnt & dstip & Destination IP address \\
+    %\netaicnt & dstport & Destination port \\
+    %\netaicnt & proto & Protocol (TCP, UDP) \\
+    \netaicnt & total\_fpackets & Total forward packets \\
+    \netaicnt & total\_fvolume & Total forward volume \\
+    \netaicnt & total\_bpackets & Total backward packets \\
+    \netaicnt & total\_bvolume & Total backward volume \\
+    \netaicnt & min\_fpktl & Minimum forward packet length \\
+    \netaicnt & mean\_fpktl & Mean forward packet length \\
+    \netaicnt & max\_fpktl & Maximum forward packet length \\
+    \netaicnt & std\_fpktl & Std. Deviation of forward packet length \\
+    \netaicnt & min\_bpktl & Minmum backward packet length \\
+    \netaicnt & mean\_bpktl & Mean backward packet length \\
+    \netaicnt & max\_bpktl & Maximum backward packet length \\
+    \netaicnt & std\_bpktl & Std. Deviation of backward packet length \\
+    \netaicnt & min\_fiat & Minimum forward inter arrival time \\
+    \netaicnt & mean\_fiat & Mean forward inter arrival time \\
+    \netaicnt & max\_fiat & Maximum forward inter arrival time \\
+    \netaicnt & std\_fiat & Std. Deviation of forward inter arrival time \\
+    \netaicnt & min\_biat & Minimum backward inter arrival time \\
+    \netaicnt & mean\_biat & Mean backward inter arrival time \\
+    \netaicnt & max\_biat & Maximum backward inter arrival time \\
+    \netaicnt & std\_biat & Std. Devation of backward inter arrival time \\
+    \netaicnt & duration & Session duration \\
+    \netaicnt & min\_active & Minimum active \\
+    \netaicnt & mean\_active & Mean active \\
+    \netaicnt & max\_active & Maximum active \\
+    \netaicnt & std\_active & Std. Deviation active \\
+    \netaicnt & min\_idle & Minimum idle \\
+    \netaicnt & mean\_idle & Mean idle \\
+    \netaicnt & max\_idle & Maximum idle \\
+    \netaicnt & std\_idle & Std. Deviation of idle \\
+    \netaicnt & sflow\_fpackets & Sub flow forward packets \\
+    \netaicnt & sflow\_fbytes & Sub flow forward bytes \\
+    \netaicnt & sflow\_bpackets & Sub flow backward packets \\
+    \netaicnt & sflow\_bbytes & Sub flow backward bytes \\
+    \netaicnt & fpsh\_cnt & Forward push counter \\
+    \netaicnt & bpsh\_cnt & Backward push counter \\
+    \netaicnt & furg\_cnt & Forward urgent counter \\
+    \netaicnt & burg\_cnt & Backward urgent counter \\
+    \netaicnt & total\_fhlen & Total forward header length \\
+    \netaicnt & total\_bhlen & Total backward header length \\
+    \bottomrule
+    \label{table:netmate-attributes}
+  \end{tabular}
+  \caption{Captured Data}
+\end{table}
+
+Each data set was given the nominal classification 'http',
+'http\_over\_tor' and 'https\_over\_tor', this attribute was appended as the
+last attribute in the ARFF file.
+
+This file was imported into the Weka program, all nominal attributes other than
+the classification were removed and a number of classification algorithms were
+trialled. The results of classification with all forty attributes is shown in
+table \ref{table:results}.
 

### 2011-05-15 thesis/experiment.tex
Detailed netAI software

@@
   classification during this experiment.
+
+  \item netAI Software
+
+  netAI is capable of processing packet traces such as the one produced by
+  tcpdump, analysing flows and producing ARFF files containing every flow
+  identified as an individual instance \parencite{swinbut:2006fk}. Each instance
+  includes many attributes produced from statistical analysis of these flows
+  which are useful for traffic classification. An explanation of the statistics
+  gathered by netAI is included in table \ref{table:netmate-attributes}.
 

### 2011-05-15 thesis/results.tex
Remove section on random tree, can't find much info about this algorithm, suspect it's just another version of random forest
More detail in conclusion

@@
     \midrule
-    Random Tree\\
-    \midrule
-    HTTPS & 0.961 & 0.046 & 0.963\\
-    HTTP over Tor & 0.906 & 0.04 & 0.94\\
-    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
-    Weighted Avg. & 0.941 & 0.037 & 0.957\\
-    \midrule
     Adaboost\\
@@
 
-\subsection{Random Tree}
-
 \subsection{AdaBoost}
@@
 are present in the real network, and may be amplified by it's greater size.
+
+Real world traffic may produce completely different statistical properties.
+This could simply mean that new features should be selected to create a real
+world Tor classifier, or it could mean that there is too much variability
+present for modern classification algorithms. The AdaBoost algorithm for
+instance, has shown to be defeated by the presence of random noise which would
+be more likely in an real environment \parencite{Long:2008ha}.
+
 Without further research it is difficult to say if the technique demonstrated
@@
 
-\begin{enumerate*}
-  \item{Can Tor traffic be distinguished from other network traffic that uses
-    similar or the same encryption and protocols?}
+\subsection{Can Tor traffic be distinguished from other network traffic that
+uses similar or the same encryption and protocols?}
 
@@
 
-  \item{Can Tor traffic be identified using automated matching techniques?}
+\subsection{Can Tor traffic be identified using automated matching techniques?}
 
@@
 
-    The value of this level of accuracy depends on the application. Identifying
-    multiple regular connections to the Tor network may provide sufficient
-    confidence to classify a system as a Tor node. This could be combined with
-    other known properties of the Tor network to increase confidence.
+The value of this level of accuracy depends on the application. A
+commercial Internet Service Provider (ISP) or University network may risk
+upsetting its users if it were to accidentally block 5\% of regular
+encrypted traffic by implementing a firewall that blocked based on this
+classifier. Alternatively it could prove useful for identifying systems
+running the Tor software. Tor nodes make multiple connections to the
+network, both in parallel and over time. Recognizing several Tor streams to
+an individual system would provide sufficient confidence to classify it as
+a Tor node.
 
-  \item{Does Tor traffic have characteristics that make it readily distinguishable using
-    heuristics based matching?}
+\subsection{Does Tor traffic have characteristics that make it readily
+distinguishable using heuristics based matching?}
 
@@
 as an identifying characteristic.
-
-\end{enumerate*}
 
@@
 
-Using Tor as a communications proxy incurs some overhead, sufficient enough that
-when using a Tor proxy in controlled conditions, Tor traffic can be
+Using Tor as a communications proxy incurs some overhead, sufficient enough
+that when using a Tor proxy in controlled conditions, its traffic can be
 distinguished from regularly encrypted traffic. This overhead may be sufficient
-enough that Tor nodes in a real world network can be identified by using readily
-available eavesdropping techniques.
+enough that Tor nodes in a real world network can be identified by using
+readily available eavesdropping techniques.
 
 However, this experiment was based on a small set of simulated data, with which
-it would be impossible to cover all the possible real world conditions. The
-variability present in the real Tor network may make this classification
-technique impossible. Further research needs to be conducted with live packet
-traces from real participants in the Tor network.
+it would be impossible to cover all possible real world conditions. The
+variability and noise present in the real Tor network may make this
+classification technique impossible.
+
+Further research needs to be conducted with live packet traces from real
+participants in the Tor network. Most existing traffic classification research
+operates this way, using exact matching techniques to separate traces collected
+into treatment and control groups. Real Tor traffic might be captured from
+publicly available and co-operating Tor nodes and compared to real encrypted
+sessions between well known public HTTPS servers.

### 2011-05-29 thesis/results.tex
Add in summary statistics and histograms

@@
 
+Examining all of the data sets, we find the following statistics of packet
+sizes:
+
+\begin{table}[H]
+  \begin{tabular}{lrrrrrr}
+    \toprule
+    Phase & Minimum & 1st Quartile & Median & Mean & 3rd Quartile & Max \\
+    \midrule
+    1 & 66 & 66 & 699 & 860.4 & 1514 & 1514\\
+    2 & 66 & 66 & 652 & 760.3 & 1514 & 1514\\
+    3 & 66 & 66 & 652 & 733.7 & 1514 & 1514\\
+    \bottomrule
+  \end{tabular}
+  \caption{Summary of packet sizes}
+  \label{table:packet_size_summary}
+\end{table}
+
+These statistics don't suggest much, the minimum size and 1st quartile
+represent the presence of empty packets typically sent to create and destroy
+connections as well as acknowledge received data. The 3rd quartile and maximum
+sizes represent the maximum transmission unit for the Ethernet specification
+(TODO: ref). Only the median and mean statistics suggest any difference, with
+Tor traffic showing a possible preference for slightly smaller packets.
+Representing each phase as a histogram however, shows a very clear distinction
+between regular and Tor traffic.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{https_hist}
+  \caption{Histogram of packet size for HTTPS traffic}
+  \label{https_hist}
+\end{figure}
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{http_tor_hist}
+  \caption{Histogram of packet size for HTTP traffic over Tor}
+  \label{http_tor_hist}
+\end{figure}
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{https_tor_hist}
+  \caption{Histogram of packet size for HTTPS traffic over Tor}
+  \label{https_tor_hist}
+\end{figure}
+
+In fact, the peaks seen in each graph represent individual packet sizes, the
+count for each phase is shown in table \ref{table:packet_size_summary}.
+
+\begin{table}[H]
+  \begin{tabular}{lrrrrrr}
+    \toprule
+    Size & HTTPS & HTTP over Tor & HTTPS over Tor \\
+    \midrule
+    1514 & 5,158,795 & 4,753,794 & 2,245,490\\
+    652 & 347,365 & 4,452,695 & 3,082,768\\
+    66 & 2,954,910 & 4,536,500 & 2,295,206\\
+    \bottomrule
+  \end{tabular}
+  \caption{Summary of packet sizes}
+  \label{table:packet_size_summary}
+\end{table}
+
 \section{Possible Implications of Results}

### 2011-05-29 thesis/experiment.tex
Add number of packets and fix size in bytes

@@
 \begin{table}[H]
-  \begin{tabular}{lrr}
+  \begin{tabular}{lrrr}
     \toprule
-    Phase & Size in bytes & Number of sessions\\
+    Phase & Size in bytes & Number of packets & Number of sessions\\
     \midrule
-    HTTPS & 2326328 & 236659\\
-    HTTP over Tor & 2869624 & 168876\\
-    HTTPS over Tor & 1591112 & 95203\\
+    HTTPS & 10,225,257,319 & 11,883,703 & 236,659\\
+    HTTP over Tor & 11,270,515,232 & 14,823,849 & 168,876\\
+    HTTPS over Tor & 5,988,282,097 & 8,161,620 & 95,203\\
     \bottomrule

### 2011-05-29 thesis/results.tex
Add analysis of stream and pseudo code algorithm

@@
 sizes represent the maximum transmission unit for the Ethernet specification
-(TODO: ref). Only the median and mean statistics suggest any difference, with
-Tor traffic showing a possible preference for slightly smaller packets.
-Representing each phase as a histogram however, shows a very clear distinction
-between regular and Tor traffic.
+\parencite{Postel:1988fk}. Only the median and mean statistics suggest any
+difference, with Tor traffic showing a possible preference for slightly smaller
+packets.  Representing each phase as a histogram however, shows a very clear
+distinction between regular and Tor traffic.
 
@@
   \label{table:packet_size_summary}
+\end{table}
+
+Investigating more closely, by examining individual packet traces some
+significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
+packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
+phase of data captured. The first few packets contain 0 bytes of data, these
+are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
+a TCP/IP connection. Following that only two packet sizes are seen for HTTP
+connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
+152. This knowledge can be used to build a very rudimentary classification
+algorithm to identify Tor traffic, as seen in the pseudo-code below:
+
+\begin{lstlisting}[language=ruby]
+if packet[3] > 130 && packet[3] <  153 && packet[5] > 913 && packet[5] < 937
+  is_tor = true
+else
+  is_tor = false
+end
+\end{lstlisting}
+
+Applying this algorithm to a 10\% sample of each of the packet traces yields
+the results as seen in table \ref{table:heuristic-results}.
+
+\begin{table}[H]
+  \begin{tabular}{lr}
+    \toprule
+    Protocol & Identified as Tor\\
+    \midrule
+    HTTPS & 0.0000\% \\
+    HTTP over Tor & 0.9903\% \\
+    HTTPS over Tor & 0.9826\% \\
+    \bottomrule
+  \end{tabular}
+  \caption{Results}
+  \label{table:heuristic-results}
+\end{table}
+
+\begin{table}[H]
+  \begin{tabular}{lp{14cm}}
+    \toprule
+    Index in Stream & Observed Packet Sizes\\
+    \midrule
+    HTTPS\\
+    \midrule
+    0 & 0\\
+    1 & 0\\
+    2 & 0\\
+    3 & 100, 110\\
+    4 & 0\\
+    5 & 122, 516\\
+    6 & 0\\
+    7 & 6, 139\\
+    8 & 0, 6, 37\\
+    9 & 0, 37, 459, 465, 471, 514, 515\\
+    10 & 0, 37, 417, 418, 419, 429, 436, 438, 439, 447, 448, 449, 454, 459, 463, 464, 465, 466, 470, 471, 486, 497, 499, 512, 513, 514, 523\\
+    \midrule
+    HTTP Over Tor\\
+    \midrule
+    0 & 0\\
+    1 & 0\\
+    2 & 0\\
+    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
+    4 & 0\\
+    5 & 915, 916, 917, 918, 919, 920, 921, 922, 923, 924, 925, 926, 927, 928, 929, 930, 931, 932, 933, 934\\
+    6 & 0\\
+    7 & 198\\
+    8 & 0, 250, 266\\
+    9 & 0, 250, 266, 293, 309, 325\\
+    10 & 0, 293, 309, 325, 1448\\
+    \midrule
+    HTTPS Over Tor\\
+    \midrule
+    0 & 0\\
+    1 & 0\\
+    2 & 0\\
+    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
+    4 & 0\\
+    5 & 914, 915, 916, 918, 919, 920, 921, 922, 923, 925, 926, 927, 928, 929, 930, 932, 934, 935, 936\\
+    6 & 0\\
+    7 & 197, 198\\
+    8 & 0, 250, 266\\
+    9 & 0, 250, 266, 293, 309, 325\\
+    10 & 0, 293, 309, 325, 1448\\
+    \bottomrule
+  \end{tabular}
+  \caption{Packet sizes}
+  \label{table:packet_sizes}
 \end{table}

### 2011-06-11 ieee-conference-paper/paper.tex
Add IEEE conference paper files

--- 2011-04-17 thesis/thesis.tex
@@
-\documentclass{ecuthesis}
+% IEEE Conference paper document class
+\documentclass[conference]{IEEEtran}
 
-% For graphics
-\usepackage{graphicx}
+% Use hyperlinks for convenience, but let's not make them coloured
+\RequirePackage[bookmarks,colorlinks,breaklinks]{hyperref}
+\hypersetup{
+  colorlinks,
+  citecolor=black,
+  filecolor=black,
+  linkcolor=black,
+  urlcolor=black
+}
+
+% Use biblatex with IEEE style
+\RequirePackage[american]{babel}
+\RequirePackage{csquotes}
+
+% Use the excellent biblatex package with apa style
+% minnames=1,maxnames=2 - abbreviates all author names in citations
+% hyperref - links in pdf
+\RequirePackage[
+  backend=biber,
+  url = false,
+  hyperref = true,
+  style = ieee,
+  minnames = 1,
+  maxnames = 2,
+  bibencoding = utf8]{biblatex}
+\DeclareLanguageMapping{american}{american-apa}
+\DefineBibliographyStrings{american}{% adapt language
+  page = {{}p\adddot},
+  pages = {{}pp\adddot},
+}
 
 % Bibliography
-\bibliography{fullrefs,websites,patents}
+\bibliography{fullrefs}
 
-% Setup the variables for the title page
+\begin{document}
+
 \title{Using traffic analysis to identify The Second Generation Onion Router}
-\author{John Barker}
-\department{School of Computer and Security Science}
-\school{Edith Cowan University}
-\degree{Computer Science (Honours)}
-\email{jebarker@our.ecu.edu.au}
-\studentid{0991300}
-\supervisor{Dr Andrew Woodward}
-\supervisor{Mr Peter Hannay}
-\supervisor{Mr Patryk Szewczyk}
 
-% Begin document
-\begin{document}
+\author{
+  \IEEEauthorblockN{John Barker}
+  \IEEEauthorblockA{
+  School of Computer and\\Security Science\\
+  Edith Cowan University\\
+  Mt Lawley, Western Australia\\
+  Email: john.barker@our.ecu.edu.au}
+  \and
+  \IEEEauthorblockN{Peter Hannay}
+  \IEEEauthorblockA{
+  School of Computer and\\Security Science\\
+  Edith Cowan University\\
+  Mt Lawley, Western Australia\\
+  Email: p.hannay@ecu.edu.au\\
+  Telephone: (08) 9370 6374}
+  \and
+  \IEEEauthorblockN{Patryk Szewczyk}
+  \IEEEauthorblockA{
+  School of Computer and\\Security Science\\
+  Edith Cowan University\\
+  Mt Lawley, Western Australia\\
+  Email: p.szewczyk@ecu.edu.au\\
+  Telephone: (08) 9370 6979\\
+  Fax: (08) 9370 6100}
+}
+
 \maketitle
 
-\tableofcontents
-\listoftables
-\listoffigures
-
 \begin{abstract}
-\thispagestyle{empty}
-
 Anonymous networks provide security for users by obfuscating messages with
@@
 real world Tor users may be vulnerable to the same analysis.
-
 \end{abstract}
 
-\chapter{Introduction}
-
-\section{Background}
+\section{Introduction}
 
@@
 This seminal paper spurred research into new techniques for providing anonymity
-and privacy for digital networks. Remailers such as Babel
-\parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
-mix to deliver anonymous email. Research produced designs that yielded
-mathematically provable anonymity
-\parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303} and networks that
-degrade gracefully when subject to attack, so called robust anonymity
-\parencite{Waidner:1989p5870,Jakobsson:1998p5137}. Designs such as MorphMix
-\parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
-\parencite{P5Sherwood:2005p5872} aimed to provide anonymity features to
-peer-to-peer (P2P) networks.
+and privacy for digital networks. One of these, The Second Generation Onion
+Router (Tor) is based on technology originally designed by the U.S. Naval
+Research Lab in 1996 \parencite{Goldschlag:1996wy} and enjoys some measure of
+popularity, with an average of two hundred thousand active users as of March
+2011 \parencite{The-Tor-Project-Inc.:2011fk}.
 
-Providing resistance to blocking or censorship comes in many forms. The People's
-Republic of China operates a sophisticated Internet firewall capable of blocking
-requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
-This system is often referred to as the Great Firewall of China. Resisting this
-system can involve ignoring spurious reset packets injected into the stream of
-forbidden communications \parencite{springerlink:10.1007/11957454_2}, or be as
-simple as accessing data through an encrypted proxy as is done in FreeGate
-\parencite{Smart:2008kx}.
+\section{The Second Generation Onion Router (Tor)}
 
-More sophisticated circumvention tend to be based on anonymity providing
-designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
-resistant system built on top of AN.ON
-\parencite{springerlink:10.1007/3-540-44702-4_7}. Publishing systems such as
-Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
-aim to provide censorship resistance as well as anonymity. Infranet uses
-steganography to hide sensitive messages in innocuous content Infranet
-\parencite{Feamster:2002p307}.
-
-The Second Generation Onion Router (Tor), is an anonymous network which uses a
-variant of Onion Routing, to provide low latency anonymous communications to a
-wide variety of Internet communications protocols
-\parencite{Dingledine:2004p314}. It also aims to provide resistance against
-censorship based blocking attempts \parencite{Dingledine:2008p1542}.
-
-\section{The Second Generation Onion Router}
-
-Onion routing was originally developed by the U.S. Naval Research Lab in 1996
-\parencite{Goldschlag:1996wy} for application by the U.S. Navy. Like a mix,
-messages sent over an onion routing network were encrypted with their routing
-information and delivered to an intermediate server for forward delivery.
-Unlike the mix however, messages delivered using the onion routing network were
-encrypted multiple times, each 'layer' using a different key and routing
-instructions. The first node in a chain would only be able to encrypt the
-routing instructions to deliver the message to the next node. Each node in the
-sequence decrypting a layer until the complete message is decrypted and
-transmitted to the destination. This invention was granted a patent by the U.S.
-Patent Office in 2001 \parencite{Michael:2001}.
-
-This proposal was expanded on in \citetitle{Dingledine:2004p314} and addressed a
-number of weaknesses in the original onion router proposal
-\parencite{Dingledine:2004p314}. It also added some usability and anonymity
-features and deviates sufficiently from the original onion routing design in
-order to avoid patent claims. The technique employed by Tor is known as
-telescopic onion routing.
-
-Tor is developed and maintained  by The Tor Project, Inc. and is made publicly
-available, finding usage in journalism, law enforcement, activism and military
-applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
-successful and widely deployed anonymous networks, with an average of two
-hundred thousand active users as of March 2011
-\parencite{The-Tor-Project-Inc.:2011fk}.
+Like a mix, messages sent over an onion routing network were encrypted with
+their routing information and delivered to an intermediate server for forward
+delivery.  Unlike the mix however, messages delivered using the onion routing
+network were encrypted multiple times, each 'layer' using a different key and
+routing instructions. The first node in a chain would only be able to encrypt
+the routing instructions to deliver the message to the next node. Each node in
+the sequence decrypting a layer until the complete message is decrypted and
+transmitted to the destination.
 
@@
 format it was supplied to at the onion proxy.
-
-Figure \ref{tor-network} shows the typical path a message takes through the Tor
-network.
-
-\begin{figure}[H]
-  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
-  \caption{The Tor Network}
-  \label{tor-network}
-\end{figure}
 
@@
 to build, they are pre-emptively created at regular intervals
-\parencite[5]{Dingledine:2004p314}.
 
-\section{Vulnerabilities and Weaknesses}
+\section{Weaknesses and Attacks}
 
@@
 
-The Internet's expanding growth \parencite{Miniwatts-Marketing-Group:2010uq} and
-role in political discourse \parencite{Bonchek:1997p3455} have allowed for
-increased mobility and organization of activist groups
-\parencite{Alexander:2011kx,Anderson:2011vn}. The increasingly sophisticated use
-of censorship \parencite{Crandall:2007p6165,Karlin:2009p6166} and swift
-retribution for dissenting opinion
-\parencite{website:china-yahoo-torture,website:vietnam-bloggers-arrested,website:egypt-arrests,website:blogger-arrests}
-may have chilling effects, effectively neutralizing these benefits. In light of
-these threats the value of anonymous networks and anti-censorship technology can
-be recognized. It is quite telling that new and sometimes unorthodox methods of
-circumventing censorship are being deployed every day
-\parencite{The-Economist:2011fk,Brading:2011ys}.
-
 While Tor has been the subject of much academic literature, the primary
@@
 
-This thesis describes a simple traffic analysis technique which can be used to
-distinguish Tor traffic from another form of commonly encrypted traffic.
-Utilized properly this technique could be used to automatically identify Tor
-nodes and block them, preventing Tor from being used as a censorship
-circumvention tool.  Alternatively it could be used to isolate Tor users and
-target them for attack, be it technically orientated such as a denial of service
-attack or socially; coercion or arrest. Any direct attack on Tor users can
-discourage participation, making the network less effective.
+\parencite[5]{Dingledine:2004p314}.
 
-%Although Tor succeeds to a certain extent in providing anonymity and censorship
-%resistance. Under controlled conditions it is possible to distinguish Tor
-%traffic from other forms of encrypted traffic using traffic analysis. This makes
-%it easy for Tor users to be isolated and targeted for attack. Since Tor relies
-%on large numbers of users for the protections it provides, attacks that affect
-%the reliability of the network can discourage participation, making it
-%ineffective. This thesis describes a simple traffic analysis technique which can
-%be used to distinguish Tor traffic from another form of commonly encrypted
-%traffic.
-
-\section{Traffic Analysis as Classification}
-
-When considering the use of traffic analysis for classification of Internet
-communications, three techniques are used. These are: exact matching, heuristic
-matching and machine learning \parencite{Zhang:2009p1188}. Exact matching
-techniques recognise properties of communications that mirror known protocols
-and communication patterns. This might include the port an application uses or
-the format of its payload. Since Tor employs strong encryption and communicates
-using known and commonly used protocols, exact matching techniques would prove
-ineffective for classification. Heuristic matching looks for patterns in
-conversations to determine communications patterns and infer relationships,
-while machine learning involves the use of statistics to train computer
-algorithms to classify traffic. Both heuristic and machine matching techniques
-are suitable for traffic analysis of anonymous networks because they do not
-rely on analysing the content of messages.
-
-\subsection{Heuristic Techniques}
-
-The increasing burden of peer to peer (P2P) applications on campus networks,
-and their shift to encryption motivated the development of heuristics based
-techniques for identifying P2P traffic. Early techniques include identifying
-known properties of P2P networks such as often communicating using both the UDP
-and TCP protocols simultaneously and using a solitary connection to transfer
-high volumes \parencite{Karagiannis:2004p6400}. This paper also reduced the
-number of false positives by eliminating packets that matched known
-communications protocols.
-
-Similar techniques have been developed in \textcite{Perenyi:2006p6325} and
-\textcite{John:2008p1376}, both of which attempt to improve matching accuracy
-through early elimination of false positives and by expanding the scope of
-matching parameters. In \textcite{Oneil:2004p6451} the same heuristics are used
-to identify P2P nodes before applying a secondary heuristic to identify
-‘supernodes’ which are a subset of all P2P nodes.
-
-Classifying traffic based on system roles is a key feature of the technique
-that appears in \citetitle{Karagiannis:2005p6359}
-\parencite{Karagiannis:2005p6359}. By analysing communications at the host
-level then at increasing levels of granularity, a greater level of accuracy is
-achieved.
-
-The use of Traffic Dispersion Graphs or TDGs to identify P2P traffic appears in
-\textcite{Iliofotou:2008p6373} and \textcite{Iliofotou:2009p6461}. Once traffic
-flows are represented in a TDG, mathematical properties of the flow can be
-analysed to make positive identifications.
-
-Viruses have also posed a problem for network administrators, often
-over-utilizing network resources and using the network to infect new machines.
-A technique for identifying various worms was proposed in
-\textcite{Lazarevic:2003p6450}. Worms often attempt to hide their communications
-from network administrators to avoid detection, presenting the same problems of
-identification as Tor network traffic.
-
-\subsection{Machine Learning Techniques}
-
-\subsubsection{Expectation-Maximisation}
-
-The first use of machine learning to categorise traffic flows appears in
-\textcite{McGregor:2004p3826}. A detailed analysis of the attributes that can
-be used for machine learning and an attempt at coarse grained classification
-using an expectation-maximisation (EM) algorithm are demonstrated. The
-expectation-maximisation algorithm is a method for finding probabilistic
-estimates of parameters in a statistical model \parencite{UW:2010p7083}. The
-same technique is also demonstrated in \textcite{Soule:2004p3817} using
-histograms for finer grained classification.  The EM algorithm is again used in
-\textcite{Zander:2005p6212} and \textcite{Erman:2006p3825}, with the latter
-comparing EM favourably against a Na\"{i}ve Bayes classifier.
-
-\subsubsection{Na\"{i}ve Bayes}
-
-\textcite{Moore:2005p3827} use a supervised Na\"{i}ve Bayes to classify traffic
-flows that have previously been sorted into groups by analysing the flow
-content. This paper focuses on many of the most commonly used Internet
-protocols while \textcite{Bonfiglio:2007p6453} uses the technique for
-identifying traffic belonging to the Skype application.
-
-\textcite{Herrmann:2009p1189} uses Bayesian networks to fingerprint visited
-websites accessed through Privacy Enhancing Technologies (PET), including Tor.
-This technique performed poorly when applied to the Tor network, but it
-suggests that Tor traffic has particular characteristics that distinguish it
-from many existing PETs. It makes a particularly useful observation: ``The most
-frequent packet sizes in the Tor traffic dumps are, in descending order, 1500,
-−52, −638, 52, 638 and 1150 bytes, accounting for 87.6 \% of all Tor packets.''
-
-\subsubsection{Markov Models}
-
-Hidden Markov Models (HMM) are a statistical modelling technique useful
-for classification of systems with an unobservable state
-\parencite{Rabiner:1990p1153}. HMMs are first used as a traffic analysis
-technique in \citetitle{Wright:2004p3860} \parencite{Wright:2004p3860}. The
-primary identification characteristics for use with this algorithm are packet
-size and inter-packet arrival times. With refinement this algorithm is used
-with increasing accuracy in \textcite{Wright:2006p322} and
-\textcite{Dainotti:2008p1435}.
-
-In \textcite{Bernaille:2005p6205} a spectral clustering algorithm is used to
-discover distinguishing characteristics of traffic flows, rather than with a
-specific set of classification goals. This information is used to build HMMs
-for the purpose of traffic classification.
-
-Since HMMs model particular behaviours, they can be used to recognize
-deviations from normal behaviour as shown in
-\textcite{EstevezTapiador:2003p7201}. Motivated by
-\citeauthor{EstevezTapiador:2003p7201}, \textcite{Munz:2010p7085} uses TCP
-flags and the position of individual packets in a stream to train an Observable
-Markov Model for traffic classification, achieving greater classification
-accuracy than \citeauthor{Bernaille:2005p6205}.
-
-\subsubsection{Clustering}
-
-Clustering algorithms group observations into subsets based on similar
-characteristics, they are a form of unsupervised learning technique designed to
-discover organization in unlabelled data sets. They have been the basis of a
-number of traffic classification techniques with the K-Means clustering
-technique being the most prominent.  K-Means cluster analysis appears in
-\textcite{Bernaille:2006p2366}, \textcite{Erman:2007p3764} and
-\textcite{Erman:2007p6206}. The use of the Density Based Spatial Clustering of
-Applications with Noise (DBSCAN) algorithm appears in
-\textcite{Erman:2006p3766}, alongside K-Means and Autoscan algorithms.
-
-\subsubsection{Other Techniques}
-
-Other algorithms used for traffic classification include Nearest Neighbour and
-Linear Discriminant Analysis \parencite{Roughan:2004p3823}, Normalized
-Threshold \parencite{Crotti:2007p3824}. The use of the Gaussian Mixture Model
-to identify applications and identities inside SSH tunnels was demonstrated in
-\textcite{Dusi:2008p6254}. Several algorithms are compared in
-\textcite{Alshammari:2009p7474}, finding the C4.5 algorithm the most accurate
-for identifying Skype and SSH traffic.
-
-\subsubsection{Comparing Techniques}
-
-It is difficult to say what machine learning technique is the most effective as
-no consensus has been reached, the literature covers a wide variety of
-techniques each with vastly different goals and no two techniques can be
-directly compared as the data used for analysis has not been disclosed
-\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
-\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
-greatest performance and accuracy when compared to a number of Bayesian
-algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
-algorithms  to find random tree, IBI, IBK and random forest algorithms
-obtaining the greatest classification accuracy.
-
-An excellent meta study on traffic analysis techniques is presented in
-\textcite{Nguyen:2008p3837}. This paper compares many of the published papers,
-the techniques used, criteria analysed and how effectively they meet stated
-goals.
-
-\section{Research Questions}
-
-\begin{enumerate*}
-  \item Can Tor traffic be identified using automated matching techniques?
-  \item Does Tor have characteristics that make it readily distinguishable using
-    heuristics based matching?
-  \item Do they have characteristics that make them distinguishable using
-    machine learning techniques?
-\end{enumerate*}
-
-\chapter{Theoretical Framework}
-
-\section{Research Methodology}
-
-The experiment conducted in this thesis utilize a non-equivalent group design.
-The experimental groups are generated using simulations which allow for a great
-deal of control over confounding variables, ensuring minimal difference between
-the control and treatment groups. Both experiment groups perform the exact same
-simulations. The control group performs all simulations using regular HTTPS,
-while the treatment group proxies all communications over Tor. The treatment
-group can be broken into HTTP over Tor and HTTPS over Tor based simulations.
-
-\section{Assumptions}
-
-It is assumed that the usage patterns exhibited by individual users will be
-smaller than the communications characteristics that will lead to the
-identification of anonymous and censorship resistant networks. Thus there is no
-need to obtain a large sample of regular network traffic from varying user
-profiles.
-
-As of the current implementation, Tor network traffic is readily
-distinguishable by looking at the handshake packets. It is likely that this
-weakness will be addressed in a future version of the Tor protocol as it is
-recognised as a design goal in \textcite{Dingledine:2008p1542}. For this
-reason, this proposal focuses on traffic analysis techniques that are content
-agnostic.
-
-\section{Variables Impacting Research}
-
-The data capturing stage will be affected by a number of variables that will
-influence the accuracy of the chosen matching algorithms.
-
-\subsection{Quality of the Anonymous Network}
-
-An individual connection to the Tor network traverses a number of nodes to
-create a circuit. The path a circuit uses is first defined by the exit node,
-then chosen based on a number of constraints with a preference for high
-bandwidth relays \parencite{website:tor-path-selection}. Since each connection
-uses a different circuit and bandwidth demands are constantly changing, it is
-difficult to predict the composition of a Tor circuit.
-
-This means that any individual Tor circuit could be composed of systems with
-differing capabilities, network throughput and configuration.
-
-For this research, a simulated Tor network was constructed inside a virtual
-machine. This allowed an identical configuration to be used across experimental
-groups. Repeating the simulations and rolling back the Tor Network Guest to a
-known snapshot ensured that each experiment group was composed of simulations
-interacting with a Tor network of similar quality.
-
-\subsection{System Performance}
-
-The ability of a computer system to route packets in a timely fashion is highly
-dependent on the performance of the system it is executing on. This is greatly
-compounded by the usage of strong encryption which is computationally expensive.
-Since packet latency is one of the key parameters used in traffic classification
-techniques, it is important to isolate packet latency affects from confounding
-variables. Components affecting packet latency include:
-
-\begin{itemize*}
-  \item CPU speed and number of cores
-  \item RAM speed and capacity
-  \item Performance of integrated components, system bus etc.
-  \item Hard disk size, access time and throughput
-  \item Installed and running applications
-  \item System configuration
-\end{itemize*}
-
-In addition it is noted that system performance can degrade over time due to
-both memory and hard disk fragmentation. The affects of these variables was
-mitigated by periodically rolling back virtual machine snapshots to return to a
-known system state and using the same network and computer hardware for all
-simulations.
-
-\subsection{Network Performance}
-
-Like system performance, latency is also dependent on the quality of the
-network. Network switching equipment has limited resources for routing packets
-and competing network traffic can introduce congestion which would radically
-alter the observable communications patterns \parencite{Jacobson:1995p6768}.
-Tor also supports congestion mitigation techniques which alter communication
-patterns \parencite[8]{Dingledine:2004p314}.
-
-Latency and network performance over the Internet are highly variable and
-beyond the control of any one individual. Usage patterns vary according to
-geographic region, societal conventions and the period in which they occur
-\parencite{Thompson97wide-areainternet,Ken03longitudinalstudy}. The Internet,
-and by necessity the public Tor network are globally distributed, which means
-that circuits traverse a large variety of unpredictable network conditions.
-
-The experiment utilized an isolated test network, with unrelated network
-processes disabled ensuring no interference or congestion.
-
-\subsection{Application Protocol}
-
-Tor provides communications facilities to a number of Internet enabled
-applications by providing an interface using the SOCKS protocol
-\parencite[17]{Dingledine:2004p314}. This means that the Tor network can proxy
-regular web browsing, email or any other TCP or UDP based communication protocol
-\parencite{website:socks}. Each of these application protocols have their own
-distinguishing communications characteristics which may influence the matching
-algorithm.
-
-For the purpose of this experiment, the protocol chosen was the HTTPS protocol.
-The treatment group was split into two components, the first part using HTTP
-over Tor and the second using HTTPS over Tor.
-
-\subsection{Caching}
-
-Both web browsers and web servers are designed for high performance and often
-cache requests so that they can be delivered faster in the future
-\parencite{Caceres:1998p7419}. While this is a normal part of communications
-traffic and should be considered, it is important that both regular and cached
-requests appear uniformly across all experiments.
-
-Periodically rolling back virtual machine snapshots during the experiment
-ensures that the browser cache always begins at empty for a series of
-simulations.
-
-\input experiment.tex
-
-\input results.tex
-
-\chapter{Appendix}
-
-\section{Manager Script}
-
-\label{manager-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/manager/run_simulation.rb}
-
-\section{Client Script}
-
-\label{client-script}
-\lstinputlisting[language=ruby]{../experiment/simulation/client/client.rb}
-
-\section{Generate Tor Network Script}
-
-\label{generate-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/make_private_network.sh}
-
-\section{Run Tor Network Script}
-
-\label{run-tor-network-script}
-\lstinputlisting[language=sh]{../experiment/simulation/tor/run_private_network.sh}
-
-\printbibliography[title=REFERENCES]
+\printbibliography
 
 \end{document}
-
-% vim: fdm=syntax tw=80

### 2011-06-11 ieee-conference-paper/paper.tex
Moving tables out into separate files and formatting widths a bit cleaner

@@
 \documentclass[conference]{IEEEtran}
+
+% For wrapping text in tables
+\usepackage{array}
+
+\usepackage[pdftex]{graphicx}
+% declare the path(s) where your graphic files are
+\graphicspath{{../thesis/}}
+
+% Support for floats
+\RequirePackage{float}
+
+% For more table formatting
+\RequirePackage{booktabs}
 
@@
 \RequirePackage[
-  backend=biber,
   url = false,
@@
   style = ieee,
-  minnames = 1,
-  maxnames = 2,
   bibencoding = utf8]{biblatex}
 \DeclareLanguageMapping{american}{american-apa}
-\DefineBibliographyStrings{american}{% adapt language
-  page = {{}p\adddot},
-  pages = {{}pp\adddot},
-}
 
@@
 anonymous network which uses a form of Onion Routing to provide low latency
-anonymous communications. This thesis demonstrates that traffic from a simulated
+anonymous communications. This paper demonstrates that traffic from a simulated
 Tor network can be distinguished from regular encrypted traffic, suggesting that
@@
 usage patterns and an excess of patience. The technique demonstrated in this
-thesis is a low cost technique, which does not require very sophisticated
+paper is a low cost technique, which does not require very sophisticated
 equipment and can be completed by a passive observer.
 
-\parencite[5]{Dingledine:2004p314}.
+\section{Traffic Classification}
+
+When considering the use of traffic analysis for classification of Internet
+communications, three techniques are used. These are: exact matching, heuristic
+matching and machine learning \parencite{Zhang:2009p1188}.
+
+It is difficult to say what machine learning technique is the most effective as
+no consensus has been reached, the literature covers a wide variety of
+techniques each with vastly different goals and no two techniques can be
+directly compared as the data used for analysis has not been disclosed
+\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
+\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
+greatest performance and accuracy when compared to a number of Bayesian
+algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
+algorithms to find random tree, IBI, IBK and random forest algorithms
+obtaining the greatest classification accuracy.
+
+\section{Experiment}
+
+\section{Results}
+
+The experiment was run over the course of 8 weeks yielding three sets of sample
+data.
+
+\begin{table}[H]
+  \begin{tabular*}{\linewidth}{lrrr}
+    \toprule
+    Phase & Total Size & Packets & Sessions\\
+    \midrule
+    HTTPS & 9.52GB & 11,883,703 & 236,659\\
+    HTTP over Tor & 10.50GB & 14,823,849 & 168,876\\
+    HTTPS over Tor & 5.58GB & 8,161,620 & 95,203\\
+    \bottomrule
+  \end{tabular*}
+  \caption{Captured Data} \label{table:datasets}
+\end{table}
+
+All of the algorithms chosen were able to successfully classify HTTPS and HTTP
+over Tor traffic with accuracy in excess of 90\%, with the Adaboost algorithm
+unable to classify HTTPS over Tor. The best performing algorithm random forest
+was able to classify HTTP over Tor with 93.7\% accuracy and a false positive
+rate of 3.7\%. HTTPS over Tor was more easily identified with a 97.7\% accuracy
+and low false positive rate of 0.3\%.
+
+\input{../thesis/weka-automated-results.tex}
+
+When a histogram of packet sizes for each of the packet traces is produced, a
+pattern becomes very apparent.
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{https_hist}
+  \caption{Histogram of packet size for HTTPS traffic}
+  \label{https_hist}
+\end{figure}
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{http_tor_hist}
+  \caption{Histogram of packet size for HTTP traffic over Tor}
+  \label{http_tor_hist}
+\end{figure}
+
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{https_tor_hist}
+  \caption{Histogram of packet size for HTTPS traffic over Tor}
+  \label{https_tor_hist}
+\end{figure}
+
+In fact, if i
+
+\input{../thesis/session-packet-sizes.tex}
+
+\section{Conclusion}
+
+Using Tor as a communications proxy incurs some overhead, sufficient enough
+that when using a Tor proxy in controlled conditions, its traffic can be
+distinguished from regularly encrypted traffic. This overhead may be sufficient
+enough that Tor nodes in a real world network can be identified by using
+readily available eavesdropping techniques.
+
+However, this experiment was based on a small set of simulated data, with which
+it would be impossible to cover all possible real world conditions. The
+variability and noise present in the real Tor network may make this
+classification technique impossible.
+
+Further research needs to be conducted with live packet traces from real
+participants in the Tor network. Most existing traffic classification research
+operates this way, using exact matching techniques to separate traces collected
+into treatment and control groups. Real Tor traffic might be captured from
+publicly available and co-operating Tor nodes and compared to real encrypted
+sessions between well known public HTTPS servers.
 

### 2011-06-11 thesis/results.tex
Moving tables out into separate files and formatting widths a bit cleaner

@@
 
-\begin{table}[H]
-  \begin{tabular}{lrrr}
-    \toprule
-    & True Positive Rate & False Positive Rate & ROC Area \\
-    \midrule
-    Random Forest\\
-    \midrule
-    HTTPS & 0.957 & 0.036 & 0.99\\
-    HTTP over Tor & 0.937 & 0.037 & 0.986\\
-    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
-    Weighted Avg. & 0.954 & 0.03 & 0.99\\
-    \midrule
-    j4.8 With 10 fold cross validation\\
-    \midrule
-    HTTPS & 0.951 & 0.04 & 0.989\\
-    HTTP over Tor & 0.978 & 0.043 & 0.98\\
-    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
-    Weighted Avg. & 0.964 & 0.018 & 0.986\\
-    \midrule
-    Adaboost\\
-    \midrule
-    HTTPS & 0.95 & 0.001 & 0.975\\
-    HTTP over Tor & 0.999 & 0.324 & 0.838\\
-    HTTPS over Tor & 0 & 0 & 0.777\\
-    Weighted Avg. & 0.785 & 0.109 & 0.891\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results}
-  \label{table:results}
-\end{table}
+\input weka-automated-results.tex
 
@@
 
-Examining all of the data sets, we find the following statistics of packet
-sizes:
+Examining all of the data sets, the following set of statistics are obtained:
 
@@
 
-\begin{table}[H]
-  \begin{tabular}{lp{14cm}}
-    \toprule
-    Index in Stream & Observed Packet Sizes\\
-    \midrule
-    HTTPS\\
-    \midrule
-    0 & 0\\
-    1 & 0\\
-    2 & 0\\
-    3 & 100, 110\\
-    4 & 0\\
-    5 & 122, 516\\
-    6 & 0\\
-    7 & 6, 139\\
-    8 & 0, 6, 37\\
-    9 & 0, 37, 459, 465, 471, 514, 515\\
-    10 & 0, 37, 417, 418, 419, 429, 436, 438, 439, 447, 448, 449, 454, 459, 463, 464, 465, 466, 470, 471, 486, 497, 499, 512, 513, 514, 523\\
-    \midrule
-    HTTP Over Tor\\
-    \midrule
-    0 & 0\\
-    1 & 0\\
-    2 & 0\\
-    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
-    4 & 0\\
-    5 & 915, 916, 917, 918, 919, 920, 921, 922, 923, 924, 925, 926, 927, 928, 929, 930, 931, 932, 933, 934\\
-    6 & 0\\
-    7 & 198\\
-    8 & 0, 250, 266\\
-    9 & 0, 250, 266, 293, 309, 325\\
-    10 & 0, 293, 309, 325, 1448\\
-    \midrule
-    HTTPS Over Tor\\
-    \midrule
-    0 & 0\\
-    1 & 0\\
-    2 & 0\\
-    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
-    4 & 0\\
-    5 & 914, 915, 916, 918, 919, 920, 921, 922, 923, 925, 926, 927, 928, 929, 930, 932, 934, 935, 936\\
-    6 & 0\\
-    7 & 197, 198\\
-    8 & 0, 250, 266\\
-    9 & 0, 250, 266, 293, 309, 325\\
-    10 & 0, 293, 309, 325, 1448\\
-    \bottomrule
-  \end{tabular}
-  \caption{Packet sizes}
-  \label{table:packet_sizes}
-\end{table}
+\input{session-packet-sizes.tex}
 

### 2011-06-12 ieee-conference-paper/paper.tex
Start work on results section

@@
 \documentclass[conference]{IEEEtran}
+
+% code listings
+\RequirePackage{listings}
+\lstset{
+  basicstyle=\ttfamily,
+  xleftmargin=36pt,
+  xrightmargin=12pt,
+  numberstyle=\tiny,              % the size of the fonts that are used for the line-numbers
+  numbers=left,                   % where to put the line-numbers
+  stepnumber=1,                   % the step between two line-numbers. If it's 1 each line
+  tabsize=2,                      % sets default tabsize to 2 spaces
+  breaklines=true,                % sets automatic line breaking
+  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
+  escapeinside={\%*}{*)},         % if you want to add a comment within your code
+  showstringspaces=false,         % don't show spaces in strings as little _ style characters
+}
 
@@
 
-\section{Results}
+To determine if Tor traffic can be distinguished from regular encrypted
+traffic, an experiment was conducted to generate a series of traces for
+comparison. HTTPS traffic was generated using the commonly available Firefox
+browser, with a series of typical user interactions simulated with the Selenium
+browser testing framework. The same simulations were run through a simulated
+Tor network using both the HTTP and HTTPS protocol.
 
@@
 \end{table}
+
+\section{Results}
 
@@
 
-In fact, if i
+Investigating more closely, by examining individual packet traces some
+significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
+packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
+phase of data captured. The first few packets contain 0 bytes of data, these
+are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
+a TCP/IP connection. Following that only two packet sizes are seen for HTTP
+connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
+152. This knowledge can be used to build a very rudimentary classification
+algorithm to identify Tor traffic, as seen in the pseudo-code below:
 
 \input{../thesis/session-packet-sizes.tex}
+
+\begin{lstlisting}[language=ruby]
+if packet[3] > 130 && packet[3] <  153 && packet[5] > 913 && packet[5] < 937
+  is_tor = true
+else
+  is_tor = false
+end
+\end{lstlisting}
+
+Applying this algorithm to a 10\% sample of each of the packet traces yields
+the results as seen in table \ref{table:heuristic-results}.
+
+\begin{table}[H]
+  \begin{tabular*}{\linewidth}{lr}
+    \toprule
+    Protocol & Identified as Tor\\
+    \midrule
+    HTTPS & 0.0000\% \\
+    HTTP over Tor & 0.9903\% \\
+    HTTPS over Tor & 0.9826\% \\
+    \bottomrule
+  \end{tabular*}
+  \caption{Results}
+  \label{table:heuristic-results}
+\end{table}
 

### 2011-06-13 thesis/experiment.tex
Refer to netAI in it's properly formatted name.

@@
 The data captured was in the form of 1MB capture files which were recombined
-with mergecap and processed by NetAI to produce ARFF format files for use by
-Weka. NetAI identifies flows inside the capture files and produces a number
+with mergecap and processed by netAI to produce ARFF format files for use by
+Weka. netAI identifies flows inside the capture files and produces a number
 of statistics to be used as attributes for classification. The statistical
-attributes produced by NetAI are shown in table \ref{table:netmate-attributes}.
+attributes produced by netAI are shown in table \ref{table:netmate-attributes}.
 

### 2011-06-13 ieee-conference-paper/paper.tex
Don't use any sorting, this means the bibliography gets ordered by appearance!
Some wording improvements, eliminated an unneeded paragraph, details about the processing of files. Added details of building matcher.

@@
 \RequirePackage[
+  sorting = none,
   url = false,
@@
 delivery.  Unlike the mix however, messages delivered using the onion routing
-network were encrypted multiple times, each 'layer' using a different key and
-routing instructions. The first node in a chain would only be able to encrypt
-the routing instructions to deliver the message to the next node. Each node in
-the sequence decrypting a layer until the complete message is decrypted and
-transmitted to the destination.
+network were encrypted multiple times, each 'layer' using a different
+encryption key and routing instructions. The first node in a chain would only
+be able to encrypt the routing instructions to deliver the message to the next
+node. Each node in the sequence decrypting a layer until the complete message
+is decrypted and transmitted to the destination.
 
@@
 additional data for verifying message integrity and identifying streams.
-
-When the first node in the circuit receives a cell, it removes a layer by
-decrypting the message using it's session key. The cell is delivered along the
-circuit and at each node a layer is removed until the cell is completely
-decrypted and can be delivered successfully. Since circuits can take some time
-to build, they are pre-emptively created at regular intervals
 
@@
 The experiment was run over the course of 8 weeks yielding three sets of sample
-data.
+data:
 
@@
 
+The data captured was in the form of 1MB capture files which were recombined
+with mergecap and processed by NetAI \parencite{swinbut:2006fk} to produce ARFF
+format files for use by Weka \parencite{Hall:2009p7662,Bouckaert:2010we}. NetAI
+identifies flows inside the capture files and produces a number of statistics
+to be used as attributes for classification.
+
 All of the algorithms chosen were able to successfully classify HTTPS and HTTP
@@
 
-When a histogram of packet sizes for each of the packet traces is produced, a
-pattern becomes very apparent.
+With some relative success classifying Tor traffic using unsupervised machine
+learning techniques, the captures were examined for a heuristics based
+classification approach. When a histogram of packet sizes for each of the
+packet traces is produced, a clear distinction can between seen between the
+sample sets:
 
@@
 are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
-a TCP/IP connection. Following that only two packet sizes are seen for HTTP
-connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
-152. This knowledge can be used to build a very rudimentary classification
-algorithm to identify Tor traffic, as seen in the pseudo-code below:
-
-\input{../thesis/session-packet-sizes.tex}
+a TCP/IP connection. Following that only two packet sizes are seen for HTTPS
+connections. For Tor sessions a range of packet sizes from 131 to 152. This
+knowledge can be used to build a very rudimentary classification algorithm to
+identify Tor traffic, as seen in the pseudo-code below:
 
@@
 
+When examining the cases where the algorithm failed to identify Tor streams, in
+all cases the session had failed to successfully initiate the handshake
+required for a TCP session. Which meant that no meaningful data could have been
+transmitted.
+
+\input{../thesis/session-packet-sizes.tex}
+
 \section{Conclusion}

### 2011-06-13 ieee-conference-paper/paper.tex
Fix wording of last sentence in Tor vulnerabilities paragraph

@@
 between the strength of the security provided and the convenience and
-performance of the system. The Tor designers consciously prioritized low
-latency, usability and flexibility against security goals such as security
-against end to end attacks \parencite[4]{Dingledine:2004p314}. These design
-decisions mean that Tor is vulnerable to several kinds of attacks, some of them
-expected and some not.
+performance of the system. Tor designers consciously prioritized low latency,
+usability and flexibility against security goals such as security against end
+to end attacks \parencite[4]{Dingledine:2004p314}. This means that by design,
+Tor is vulnerable to a global passive adversary, however there are some attacks
+that were not expected by the designers.
 

### 2011-06-13 ieee-conference-paper/paper.tex
Remove paragraph about traffic analysis here, seems a bit out of place

@@
 over the Tor network.
-
-Most conventional attacks against secure networks are known as traffic analysis,
-this is the process of examining information about the communications rather
-than the information contained within them. This information may include the
-size of messages communicated, their frequency and timing. Many researchers have
-proposed traffic analysis techniques that allow attackers to reveal the
-identities of Tor users.
 

### 2011-06-13 ieee-conference-paper/paper.tex
Should be parencite, not in text.
"In certain circumstances" instead of "sometimes"

@@
 identified. They are also vulnerable to clogging attacks which make bridge
-operators more easily identified \textcite{McLachlan:2009p197}.
+operators more easily identified \parencite{McLachlan:2009p197}.
 
@@
 have been somewhat academic in nature and not necessarily feasible in practice
-\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
-the Tor network, supplying hostile data to Tor users or complicated knowledge of
-usage patterns and an excess of patience. The technique demonstrated in this
-paper is a low cost technique, which does not require very sophisticated
-equipment and can be completed by a passive observer.
+\parencite{Raccoon:2008fk}. In certain circumstances they require compromise of
+large parts of the Tor network, supplying hostile data to Tor users or
+complicated knowledge of usage patterns and an excess of patience. The
+technique demonstrated in this paper is a low cost technique, which does not
+require sophisticated equipment and can be completed by a passive observer.
 

### 2011-06-13 ieee-conference-paper/paper.tex
Paragraph about traffic analysis in significance section

@@
 
+Most conventional attacks against secure networks are known as traffic analysis,
+this is the process of examining information about the communications rather
+than the information contained within them. This information may include the
+size of messages communicated, their frequency and timing. Many researchers have
+proposed traffic analysis techniques that allow attackers to reveal the
+identities of Tor users.
+
 While Tor has been the subject of much academic literature, the primary

### 2011-06-13 thesis/thesis.tex
Adding some more content to the results section, adding a bit more of a description to the results. Remove redundant question.
Moving tables out into separate files and formatting widths a bit cleaner
Spacing

@@
 Unlike the mix however, messages delivered using the onion routing network were
-encrypted multiple times, each 'layer' using a different key and routing
-instructions. The first node in a chain would only be able to encrypt the
-routing instructions to deliver the message to the next node. Each node in the
-sequence decrypting a layer until the complete message is decrypted and
+encrypted multiple times, each 'layer' using a different encryption key and
+routing instructions. The first node in a chain would only be able to encrypt
+the routing instructions to deliver the message to the next node. Each node in
+the sequence decrypting a layer until the complete message is decrypted and
 transmitted to the destination. This invention was granted a patent by the U.S.
@@
     heuristics based matching?
-  \item Does Tor traffic have characteristics that make it distinguishable using
-    machine learning techniques?
 \end{enumerate*}

### 2011-06-13 ieee-conference-paper/paper.tex
Remove phone numbers

@@
   Mt Lawley, Western Australia\\
-  Email: p.hannay@ecu.edu.au\\
-  Telephone: (08) 9370 6374}
+  Email: p.hannay@ecu.edu.au}
   \and
@@
   Mt Lawley, Western Australia\\
-  Email: p.szewczyk@ecu.edu.au\\
-  Telephone: (08) 9370 6979\\
-  Fax: (08) 9370 6100}
+  Email: p.szewczyk@ecu.edu.au}
 }

### 2011-06-13 ieee-conference-paper/paper.tex
Added three references I hadn't already used to emphasise wealth of the literature

@@
 
-While Tor has been the subject of much academic literature, the primary
-objective of researchers has historically been the attempt to reveal participant
-identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
-have been somewhat academic in nature and not necessarily feasible in practice
-\parencite{Raccoon:2008fk}. In certain circumstances they require compromise of
-large parts of the Tor network, supplying hostile data to Tor users or
-complicated knowledge of usage patterns and an excess of patience. The
+While Tor has been the subject of much academic literature
+\parencite{Hopper:2007p347,Murdoch:2007p320,Herrmann:2009p1189}, the primary
+objective of researchers has historically been the attempt to reveal
+participant identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques
+proposed have been somewhat academic in nature and not necessarily feasible in
+practice \parencite{Raccoon:2008fk}. In certain circumstances they require
+compromise of large parts of the Tor network, supplying hostile data to Tor
+users or complicated knowledge of usage patterns and an excess of patience. The
 technique demonstrated in this paper is a low cost technique, which does not

### 2011-06-13 ieee-conference-paper/paper.tex
don't say 3: including (exact list of items), just say three techniques: these are.

@@
 When considering the use of traffic analysis for classification of Internet
-communications, three techniques are used. These are: exact matching, heuristic
-matching and machine learning \parencite{Zhang:2009p1188}.
+communications, three techniques are used: exact matching, heuristic matching
+and machine learning \parencite{Zhang:2009p1188}.
 

### 2011-06-13 ieee-conference-paper/paper.tex
IEEE biblatex, describe why not using any sorting
More details in experiment section, versions of software, dates of phases

@@
 
-% Use biblatex with IEEE style
+% Use the excellent biblatex package with IEEE style, sorted = none makes the numbering appear in order
 \RequirePackage[american]{babel}
 \RequirePackage{csquotes}
-
-% Use the excellent biblatex package with apa style
-% minnames=1,maxnames=2 - abbreviates all author names in citations
-% hyperref - links in pdf
 \RequirePackage[
@@
 traffic, an experiment was conducted to generate a series of traces for
-comparison. HTTPS traffic was generated using the commonly available Firefox
-browser, with a series of typical user interactions simulated with the Selenium
-browser testing framework. The same simulations were run through a simulated
-Tor network using both the HTTP and HTTPS protocol.
+comparison. Network traffic was generated using the commonly available Firefox
+browser, version 3.6.8 installed on an Ubuntu 10.04 desktop operating system.
+One hundred and seventy simulations were run of varied user interactions
+against a sample of thirty websites, using version 1.0.6 of the Selenium
+Browser testing framework. A private Tor network was configured running three
+directory servers and fifteen relays, with version 0.2.1.26.
 
-The experiment was run over the course of 8 weeks yielding three sets of sample
-data:
+The experiment consisted of three phases, the first was the capture of regular
+HTTPS traffic which began Sunday the 3rd of October 2010 and finished Sunday
+the 17th that same month. Phase two began immediately after and continued two
+weeks till the 31st of October. This phase involved capturing regular HTTP
+traffic routed through a private Tor network. The final phase began on the 7th
+of November and concluded on the 21st, this phase was the capture of HTTPS
+traffic through a private Tor network.
+
+To reduce the affect of confounding variables, all phases conducted the same
+simulations, on an isolated test network and were conducted within a virtual
+machine snapshot which was periodically rolled back to a clean, known state.
+The experiment yielded three sets of sample data:
 

### 2011-06-13 ieee-conference-paper/paper.tex
Pad out discussion/future work and conclusion

@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering\includegraphics[width=\linewidth]{https_hist}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering\includegraphics[width=\linewidth]{http_tor_hist}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering\includegraphics[width=\linewidth]{https_tor_hist}
@@
 
-\begin{table}[H]
+\begin{table}[h]
   \begin{tabular*}{\linewidth}{lr}
@@
 
-\section{Conclusion}
+\section{Discussion}
 
@@
 
+The encryption layers that wrap Tor level communications, do not
+appear to obfuscate the size of communications sent between Tor nodes. This is
+most apparent in the composition of packet sizes that make up an individual
+session, with Tor sessions showing a large percentage of packets just large
+enough to fit the 512 byte cells that make up the Tor protocol.
+
 However, this experiment was based on a small set of simulated data, with which
@@
 classification technique impossible.
+
+\section{Future Research}
 
@@
 
+Training a classifier against real world traffic will account for the different
+and varied nature of packet switching hardware, with different maximum
+transmission units, performance capabilities and geographic location.
+
+The heuristic based classifier used in this paper used a single attribute: the
+size of individual packets in a stream, to classify with great accuracy. But
+other attributes may be considered, the most typical of these being inter
+packet arrival time - though this is likely to be more affected by natural
+variability.
+
+The encrypted traffic generated in the first phase of the experiment, only
+covered a single application and version. It may be possible that other
+applications use the same protocol with encryption and have characteristics
+similar to that produced by Tor. This would lead to any proposed classifier
+generating false positives. Further research should also consider the nature
+and characteristics of a wider set of encrypted communications.
+
+\section{Conclusion}
+
+This research demonstrates that Tor does have characteristics that make it
+distinguishable from regular encrypted traffic. The encryption used by Tor does
+not appear to blur the size of communication cells sufficiently to prevent
+automated identification of Tor traffic, even with only a few observed packets.
+While the scope of this research is limited, it suggests that it may be
+possible to build simple software to automatically identify Tor users and block
+them from the network.
+
 \printbibliography

### 2011-06-18 ieee-conference-paper/paper.tex
Fix email address, IB1 algorithm not IBI, move future research details into conclusion.

@@
   Mt Lawley, Western Australia\\
-  Email: john.barker@our.ecu.edu.au}
+  Email: jebarker@our.ecu.edu.au}
   \and
@@
 algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
-algorithms to find random tree, IBI, IBK and random forest algorithms
+algorithms to find random tree, IB1, IBK and random forest algorithms
 obtaining the greatest classification accuracy.
@@
 
-\section{Future Research}
+\section{Conclusion}
+
+This research demonstrates that Tor does have characteristics that make it
+distinguishable from regular encrypted traffic. The encryption used by Tor does
+not appear to blur the size of communication cells sufficiently to prevent
+automated identification of Tor traffic, even with only a few observed packets.
+While the scope of this research is limited, it suggests that it may be
+possible to build simple software to automatically identify Tor users and block
+them from the network.
 
@@
 
-\section{Conclusion}
-
-This research demonstrates that Tor does have characteristics that make it
-distinguishable from regular encrypted traffic. The encryption used by Tor does
-not appear to blur the size of communication cells sufficiently to prevent
-automated identification of Tor traffic, even with only a few observed packets.
-While the scope of this research is limited, it suggests that it may be
-possible to build simple software to automatically identify Tor users and block
-them from the network.
-
 \printbibliography

### 2011-06-26 thesis/results.tex
Unique name for stats table
Fixes from IEEE conference paper

@@
   \caption{Summary of packet sizes}
-  \label{table:packet_size_summary}
+  \label{table:packet_size_statistics}
 \end{table}
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Research}
 
-Using Tor as a communications proxy incurs some overhead, sufficient enough
-that when using a Tor proxy in controlled conditions, its traffic can be
-distinguished from regularly encrypted traffic. This overhead may be sufficient
-enough that Tor nodes in a real world network can be identified by using
-readily available eavesdropping techniques.
-
-However, this experiment was based on a small set of simulated data, with which
-it would be impossible to cover all possible real world conditions. The
-variability and noise present in the real Tor network may make this
-classification technique impossible.
+This research demonstrates that Tor does have characteristics that make it
+distinguishable from regular encrypted traffic. The encryption used by Tor does
+not appear to blur the size of communication cells sufficiently to prevent
+automated identification of Tor traffic, even with only a few observed packets.
+While the scope of this research is limited, it suggests that it may be
+possible to build simple software to automatically identify Tor users and block
+them from the network.
 
@@
 sessions between well known public HTTPS servers.
+
+Training a classifier against real world traffic will account for the different
+and varied nature of packet switching hardware, with different maximum
+transmission units, performance capabilities and geographic location.
+
+The heuristic based classifier used in this paper used a single attribute: the
+size of individual packets in a stream, to classify with great accuracy. But
+other attributes may be considered, the most typical of these being inter
+packet arrival time - though this is likely to be more affected by natural
+variability.
+
+The encrypted traffic generated in the first phase of the experiment, only
+covered a single application and version. It may be possible that other
+applications use the same protocol with encryption and have characteristics
+similar to that produced by Tor. This would lead to any proposed classifier
+generating false positives. Further research should also consider the nature
+and characteristics of a wider set of encrypted communications.

### 2011-06-26 thesis/thesis.tex
Fixes from IEEE conference paper

@@
 
-While Tor has been the subject of much academic literature, the primary
-objective of researchers has historically been the attempt to reveal participant
-identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
-have been somewhat academic in nature and not necessarily feasible in practice
-\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
-the Tor network, supplying hostile data to Tor users or complicated knowledge of
-usage patterns and an excess of patience. The technique demonstrated in this
-thesis is a low cost technique, which does not require very sophisticated
-equipment and can be completed by a passive observer.
+While Tor has been the subject of much academic literature
+\parencite{Hopper:2007p347,Murdoch:2007p320,Herrmann:2009p1189}, the primary
+objective of researchers has historically been the attempt to reveal
+participant identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques
+proposed have been somewhat academic in nature and not necessarily feasible in
+practice \parencite{Raccoon:2008fk}. In certain circumstances they require
+compromise of large parts of the Tor network, supplying hostile data to Tor
+users or complicated knowledge of usage patterns and an excess of patience. The
+technique demonstrated in this paper is a low cost technique, which does not
+require sophisticated equipment and can be completed by a passive observer.
 

### 2011-06-26 thesis/results.tex
Add back in the fourth question from the proposal

@@
 
+\subsection{How long does a user have to be connected to the network before a
+confident match can be made?}
+
+The basic algorithm designed using a simple heuristic approach matches on the
+4th and 5th packets of an individual TCP session. Given that the first three
+packets of any TCP session are the session negotiation packets, the
+demonstrated algorithm only requires two packets before being confident of a
+positive match. It is likely that this is far earlier than any user data has
+had a chance to traverse the Tor network.
+
 \chapter{Conclusion}

### 2011-06-26 thesis/thesis.tex
Clean up title page a bit, remove page number
Add back in the fourth question from the proposal
Wording improvements to the introduction

@@
 % Setup the variables for the title page
-\title{Using traffic analysis to identify The Second Generation Onion Router}
+\title{Using Traffic Analysis to Identify the Second Generation Onion Router}
 \author{John Barker}
@@
 \begin{document}
+\doublespacing
 \maketitle
@@
 This seminal paper spurred research into new techniques for providing anonymity
-and privacy for digital networks. Remailers such as Babel
+and privacy to digital networks. Remailers such as Babel
 \parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
@@
 system can involve ignoring spurious reset packets injected into the stream of
-forbidden communications \parencite{springerlink:10.1007/11957454-2}, or be as
-simple as accessing data through an encrypted proxy as is done in FreeGate
+forbidden communications \parencite{springerlink:10.1007/11957454-2}, or
+accessing censored sites through an encrypted proxy such as FreeGate
 \parencite{Smart:2008kx}.
 
-More sophisticated circumvention tend to be based on anonymity providing
-designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
-resistant system built on top of AN.ON
-\parencite{springerlink:10.1007/3-540-44702-4-7}. Publishing systems such as
+More sophisticated censorship circumvention involves anonymous digital networks.
+\textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship resistant
+system built on top of AN.ON \parencite{springerlink:10.1007/3-540-44702-4-7}.
 Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
-aim to provide censorship resistance as well as anonymity. Infranet uses
-steganography to hide sensitive messages in innocuous content Infranet
-\parencite{Feamster:2002p307}.
+provide a document publication network that aims to provide censorship
+resistance as well as anonymity. Infranet uses steganography to hide sensitive
+messages in images transferred as part of anodyne HTTP sessions
+\parencite{Feamster:2002p307}. However many of these systems have not attained
+significant public exposure.
+
+\section{The Second Generation Onion Router}
 
@@
 censorship based blocking attempts \parencite{Dingledine:2008p1542}.
-
-\section{The Second Generation Onion Router}
 
@@
     heuristics based matching?
+  \item How long does a user have to be connected to the network before a
+    confident match can be made?
 \end{enumerate*}

### 2011-06-26 thesis/thesis.tex
Updated tor usage stats

@@
 
-The Second Generation Onion Router (Tor), is an anonymous network which uses a
+The Second Generation Onion Router (Tor) is an anonymous network which uses a
 variant of Onion Routing, to provide low latency anonymous communications to a
@@
 available, finding usage in journalism, law enforcement, activism and military
-applications \parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most
-successful and widely deployed anonymous networks, with an average of two
-hundred thousand active users as of March 2011
-\parencite{The-Tor-Project-Inc.:2011fk}.
+applications \parencite{The-Tor-Project-Inc.:2011uq}. It is one of the most
+successful and widely deployed anonymous networks, with over three hundred
+thousand active users as of June 2011 \parencite{The-Tor-Project-Inc.:2011fk}.
 

### 2011-08-11 ieee-conference-paper/paper.tex
Some tweaking with figure positions and tables, 6 pages, slightly larger histograms

@@
 
+\begin{figure}[H]
+  \centering\includegraphics[width=\linewidth]{tor-network-diagram}
+  \caption{The Tor Network}
+  \label{tor-network}
+\end{figure}
+
 Traffic enters the Tor network through an onion proxy which accepts TCP streams.
@@
 machine snapshot which was periodically rolled back to a clean, known state.
-The experiment yielded three sets of sample data:
+The experiment yielded three sets of, a summary is included in table
+\ref{table:datasets}.
 
@@
 The data captured was in the form of 1MB capture files which were recombined
-with mergecap and processed by NetAI \parencite{swinbut:2006fk} to produce ARFF
-format files for use by Weka \parencite{Hall:2009p7662,Bouckaert:2010we}. NetAI
-identifies flows inside the capture files and produces a number of statistics
-to be used as attributes for classification.
+with mergecap \parencite{Renfro:fk} and processed by NetAI
+\parencite{swinbut:2006fk} to produce ARFF format files for use by Weka
+\parencite{Hall:2009p7662,Bouckaert:2010we}. NetAI identifies flows inside the
+capture files and produces a number of statistics to be used as attributes for
+classification.
 
@@
 rate of 3.7\%. HTTPS over Tor was more easily identified with a 97.7\% accuracy
-and low false positive rate of 0.3\%.
+and low false positive rate of 0.3\%. A summary of the results obtained by
+these machine learning classifiers is available in Table \ref{table:results}.
 
@@
 packet traces is produced, a clear distinction can between seen between the
-sample sets:
+sample sets as seen in Figures \ref{https_hist}, \ref{http_tor_hist} and
+\ref{https_tor_hist}.
 
-\begin{figure}[h]
-  \centering\includegraphics[width=\linewidth]{https_hist}
+\begin{figure*}
+  \centering\includegraphics[width=0.6\linewidth]{https_hist}
   \caption{Histogram of packet size for HTTPS traffic}
   \label{https_hist}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h]
-  \centering\includegraphics[width=\linewidth]{http_tor_hist}
+\begin{figure*}
+  \centering\includegraphics[width=0.6\linewidth]{http_tor_hist}
   \caption{Histogram of packet size for HTTP traffic over Tor}
   \label{http_tor_hist}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h]
-  \centering\includegraphics[width=\linewidth]{https_tor_hist}
+\begin{figure*}
+  \centering\includegraphics[width=0.6\linewidth]{https_tor_hist}
   \caption{Histogram of packet size for HTTPS traffic over Tor}
   \label{https_tor_hist}
-\end{figure}
+\end{figure*}
 
@@
 significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
-packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
+packet sizes seen for the first 6 packets of a 1\% sample of sessions in each
 phase of data captured. The first few packets contain 0 bytes of data, these
@@
 a TCP/IP connection. Following that only two packet sizes are seen for HTTPS
-connections. For Tor sessions a range of packet sizes from 131 to 152. This
-knowledge can be used to build a very rudimentary classification algorithm to
-identify Tor traffic, as seen in the pseudo-code below:
+connections. For Tor sessions a range of packet sizes from 131 to 152.
 
-\begin{lstlisting}[language=ruby]
-if packet[3] > 130 && packet[3] <  153 && packet[5] > 913 && packet[5] < 937
-  is_tor = true
-else
-  is_tor = false
-end
-\end{lstlisting}
+\input{../thesis/session-packet-sizes.tex}
 
-Applying this algorithm to a 10\% sample of each of the packet traces yields
-the results as seen in table \ref{table:heuristic-results}.
+This knowledge can be used to build a rudimentary classification algorithm to
+identify Tor traffic, the pseudo code for an example algorithm is included in
+Figure \ref{psuedo_matcher}. Applying this algorithm to the complete traces
+yields the results as seen in Table \ref{table:heuristic-results}.
 
-\begin{table}[h]
+\begin{table}[H]
   \begin{tabular*}{\linewidth}{lr}
@@
     \midrule
-    HTTPS & 0.0000\% \\
-    HTTP over Tor & 0.9903\% \\
-    HTTPS over Tor & 0.9826\% \\
+    HTTPS & 1.06\%\\
+    HTTP over Tor & 98.13\%\\
+    HTTPS over Tor & 97.54\%\\
     \bottomrule
   \end{tabular*}
-  \caption{Results}
+  \caption{Results from Heuristic Classifier}
   \label{table:heuristic-results}
@@
 transmitted.
-
-\input{../thesis/session-packet-sizes.tex}
 
@@
 
+\begin{figure}
+  \begin{lstlisting}[language=ruby]
+    if  packet[3] > 130 and
+        packet[3] <  153 and
+        packet[5] > 913 and
+        packet[5] < 937 then
+      is_tor = true
+    else
+      is_tor = false
+    end
+  \end{lstlisting}
+  \caption{Pseudo Code for Matching a Tor Session}
+  \label{psuedo_matcher}
+\end{figure}
+
 \printbibliography

### 2011-08-11 ieee-conference-paper/paper.tex
Even larger histograms, spread out a bit throughout the paper
Add a little bit more prior research

@@
 communications, three techniques are used: exact matching, heuristic matching
-and machine learning \parencite{Zhang:2009p1188}.
+and machine learning \parencite{Zhang:2009p1188}. Since Tor employs strong
+encryption and can communicate on any port, it can easily an exact matching
+technique through simple configuration options.
+
+Heuristic based techniques have been designed to classify encrypted
+communications, including the identification of P2P traffic
+\parencite{Karagiannis:2004p6400,Perenyi:2006p6325,John:2008p1376} and viruses
+\parencite{Lazarevic:2003p6450}.
+
+Machine learning algorithms have also been used successfully to classify
+encrypted traffic including Skype \parencite{Alshammari:2009p7474} and to
+identify application protocols tunnelled over SSH \parencite{Dusi:2008p6254}.
+An previous attempt to classify Tor using Bayesian networks was attempted in
+\textcite{Herrmann:2009p1189} without great success.
 
@@
 \begin{figure*}
-  \centering\includegraphics[width=0.6\linewidth]{https_hist}
+  \centering\includegraphics[width=0.9\linewidth]{https_hist}
   \caption{Histogram of packet size for HTTPS traffic}
@@
 \begin{figure*}
-  \centering\includegraphics[width=0.6\linewidth]{http_tor_hist}
+  \centering\includegraphics[width=0.9\linewidth]{http_tor_hist}
   \caption{Histogram of packet size for HTTP traffic over Tor}
@@
 \begin{figure*}
-  \centering\includegraphics[width=0.6\linewidth]{https_tor_hist}
+  \centering\includegraphics[width=0.9\linewidth]{https_tor_hist}
   \caption{Histogram of packet size for HTTPS traffic over Tor}
@@
 identify Tor traffic, the pseudo code for an example algorithm is included in
-Figure \ref{psuedo_matcher}. Applying this algorithm to the complete traces
+Figure \ref{psuedo_matcher}.
+
+\begin{figure}[H]
+  \begin{lstlisting}[language=ruby]
+    if  packet[3] > 130 and
+        packet[3] < 153 and
+        packet[5] > 913 and
+        packet[5] < 937 then
+      is_tor = true
+    else
+      is_tor = false
+    end
+  \end{lstlisting}
+  \caption{Pseudo Code for Matching a Tor Session}
+  \label{psuedo_matcher}
+\end{figure}
+
+Applying this algorithm to the complete traces
 yields the results as seen in Table \ref{table:heuristic-results}.
@@
 
-\begin{figure}
-  \begin{lstlisting}[language=ruby]
-    if  packet[3] > 130 and
-        packet[3] <  153 and
-        packet[5] > 913 and
-        packet[5] < 937 then
-      is_tor = true
-    else
-      is_tor = false
-    end
-  \end{lstlisting}
-  \caption{Pseudo Code for Matching a Tor Session}
-  \label{psuedo_matcher}
-\end{figure}
-
 \printbibliography
